### 2016-10-10 writeup/manuscript.tex
Back up original experiments.

\documentclass[a4paper, oneside, 11pt, onecolumn]{article}
\usepackage[T1]{fontenc}
\usepackage{newtxtext,newtxmath}
\usepackage{graphicx}
\usepackage{subfig}
\usepackage[round, comma, sort&compress, longnamesfirst]{natbib} 
% \usepackage[left=2cm,top=3cm,right=1.5cm,bottom=2cm,bindingoffset=0.5cm]{geometry}
\usepackage{enumerate}
\usepackage{fancyhdr}
\usepackage[title,titletoc,toc]{appendix}
\pagestyle{fancy}
\fancyhead{}
\fancyfoot{}
\fancyfoot[L]{\textit{running footer}}
 \fancyhead[L]{\textit{running title}}
\renewcommand{\headrulewidth}{0.8pt}
\renewcommand{\footrulewidth}{0.8pt}
\setlength\headheight{14pt}
\fancyfoot[RO] {\thepage}
\usepackage{authblk}
%%%%%%%%%%%%

\begin{document}

\title{Individual Differences Across Visual Search Tasks}

\author{A. D. F. Clarke, J. L. Irons, A. B. Leber and A. R. Hunt}
\affil{Aberdeen, Essex and Ohio}

\maketitle

\begin{abstract}
Some abstract goes here
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Methods}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Participants}
How many? Will all testing be done at the University of Aberdeen? How do we justify our sample size (a question commonly asked by journals now!)?

\subsection{Materials and Procedures}

The study consists of three different paradigms from the visual search literature in which strong individual differences were found \citep{nowakowsak2017, irons-leber2016, kristjansson2014}.

\subsubsection{A: Split-half array search}

\subsubsection{B: Attentional Control}

\subsubsection{C: Conjunction Foraging}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{appendices}
\section{Hetero-Homo-geneous Array Search}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Attentional Control Settings}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conjunction Foraging}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{appendices}

\bibliographystyle{plainnat}
\bibliography{literature}

\end{document}

### 2016-10-10 Experiments/Individual Search Differences/AdaptChoice_ForDist/AdaptChoice.m

@@ -1,0 +1,833 @@
+ 
+function AdaptChoice
+%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% Adaptive Choice visual search task
+%
+% Search array of colored squares containing digits. Two targets on every
+% trials (red square with digit between 2 and 5 inclusive, and blue square with digit
+% between 2 and 5). Participants can choose to search for either one on
+% each trial. Distractors are colored red, blue, green or "variable".
+% Variable distractors change color from red through magenta to blue and
+% back again over cycles of 24 trials. 
+
+% See Irons & Leber (2016) AP&P
+% programmed by J Irons
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% SETUP %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%% THINGS THAT MIGHT NEED TO BE ADJUSTED 
+skipsync = 1;                       % skip sync tests. 1 = yes, 0 = no
+innerradius = 240;                  % Radius of the inner ring in pixels. Might need to adjust to fit display. Default is 240 (had been used successfully with monitor resolutions of 1920x1080 and 1280x1024).
+                                    % innerrad also determines radius of middle ring (innerrad*1.5) and outer ring (innerrad*2)
+squaresize = 40;                    % Width/height of each square in search display in pixels. Might need to adjust. Default is 40
+Digitsize = 24;                     % Font size for digits
+Digitfont = 'Arial';                % Font for digits
+digadjx = 12;                        % x-pos. Small adjustment to position of the digit to centre on the square. Might need to adjust
+digadjy = 7;                       % y-pos. Small adjustment to position of the digit to centre on the square. Might need to adjust
+
+% For EyeTracking
+autocalibrate = 0;                  % If set to 1, will automatically calibrate at the start of each block, without experimenter having to be in the room. Needs additional eyelink code EyelinkDoCalibration
+recalibrate = 1;                    % If set to 1, will recalibrate automatically during the block if centre is not fixated during ITI for a specified number of trials
+fixerror = 100;                     % Radius of fixation circle for the fixation control
[…]

### 2016-10-10 Experiments/Individual Search Differences/AdaptChoice_ForDist/EyelinkDoCalibration.m

@@ -1,0 +1,123 @@
+function result=EyelinkDoCalibration(el, sendkey)
+
+% EDITED VERSION OF EyelinkDoTrackerSetup
+% AUTOMATICALLY SKIPS STRAIGHT TO CALIBRATING WITHOUT GOING TO SETUP SCREEN
+% USES EDITED FILE EyelinkTargetModeDisplay2 (INSTEAD OF EyelinkTargetModeDisplay)
+% MADE BY JESS IRONS MARCH 2015
+
+USAGE: result=EyelinkDoTrackerSetup(el [, sendkey])
+
+%		el: Eyelink default values
+%		sendkey: set to go directly into a particular mode
+% 				'v', start validation
+% 				'c', start calibration
+% 				'd', start driftcorrection
+% 				13, or el.ENTER_KEY, show 'eye' setup image
+
+%
+% 02-06-01	fwc removed use of global el, as suggest by John Palmer.
+%				el is now passed as a variable, we also initialize Tracker state bit
+%				and Eyelink key values in 'initeyelinkdefaults.m'
+% 15-10-02	fwc	added sendkey variable that allows to go directly into a particular mode
+% 22-06-06	fwc OSX-ed
+% 15-06-10	fwc added code for new callback version
+
+result=-1;
+if nargin < 1
+	error( 'USAGE: result=EyelinkDoTrackerSetup(el [,sendkey])' );
+end
+% if we have the new callback code, we call it.
+% if ~isempty(el.callback)
+%     if Eyelink('IsConnected') ~= el.notconnected
+%         if ~isempty(el.window)            
+%             rect=Screen(el.window,'Rect');
+%             % make sure we use the correct screen coordinates
+%             Eyelink('Command', 'screen_pixel_coords = %d %d %d %d',rect(1),rect(2),rect(3)-1,rect(4)-1);
+%         end
+%     else
+%         return
+%     end
+%     result = Eyelink('StartSetup', 1);
+%     return;
+% end
+% else we continue with the old version
+
+% Eyelink('Command', 'heuristic_filter = ON');
+Eyelink( 'StartSetup' );		% start setup mode
+Eyelink( 'WaitForModeReady', el.waitformodereadytime );  % time for mode change
+
[…]

### 2016-10-10 Experiments/Individual Search Differences/HalfPopOutUntimed/Data_analysis_FixOnTarg2files2.m

@@ -1,0 +1,1 @@
+% ARH/AL March 2014. Code to process data from Anna's project looking at the effect of
% gaze-contingent filtering on search strategies.
% Data recorded from EyeLink 1000.
% open the .asc file, get fixation and trial data, output to two separate
% files for Alasdair.

clear all;
numSub = 14;
filetomake = input('name the fixation results file: ', 's');
F2ID = fopen(filetomake, 'a');
fprintf(F2ID, 'subNum\t trialNo\t fixNo\t xFix\t yFix\t fixStartTime\t fixEndTime\t targPresent\t targSide\t easySide\t var\t con\n');


for subNo=1:numSub
        
    condition = 'Ul';
      

        filetoread = strcat(condition, num2str(subNo),'.asc'); % name of search data file to read
        if (fopen(filetoread, 'r')~=-1)
            FID=fopen(filetoread, 'r');
            trialRunning = 0;
            endtrialRun = 0;
            trialCount = 0;
            sacOnTime = 0;
            fileRun = 1;
            
            while fileRun
                line=fgetl(FID); %get the next line of data
                
                if line == -1  % if the end of the file has been reached
                    fclose(FID);

                    fileRun = 0; %leave the main loop
                    break;
                    %     elseif findstr(line, 'TRIALNO_80')
                    %         fclose(F2ID);
                    %         fclose(FID);
                    %         fileRun = 0; %leave the main loop
                    %         break;
                end
                
                if findstr(line, 'DISPLAY_ON')
                    faceOn = 0;
                    numFix = 0;
                    targetsOn=0;
                    trialCount = trialCount+1;
                    failSacc=0;
                    s=1;
                    xPos=zeros(1,70);
                    yPos=zeros(1,70);
                    targPres='x';
                    targSide='x';
                    TargX1='-1';
                    mes='GoodTrial';
                    easySide='x';
                    cond='x'; 
                    var='x';
                    
                    numDistLY2=0;
                    FaceOnTarget=0;
                    FaceOnDistrL4=0;
                    FaceOnRightDistr=0;
                    FaceOnLeftDistr=0;
                    trialRunning =1; %start loop to get timing / saccade info from trial

                    %         maxXvalue=0;
                    while trialRunning
                        line = fgetl(FID); %get data
                        if findstr(line, 'FACES_DRAWN')
                            index=findstr(line,'F');
                            
                            faceOnTime=str2num(line(4:index-1));
                            faceOn = 1;
                        end
                        while faceOn
[…]

### 2016-10-10 Experiments/Individual Search Differences/HalfPopOutUntimed/RunExperiment.m

@@ -1,0 +1,131 @@
+function RunExperiment(subNo, block)
+%RunExperiment(subNo, block)
+%Simulated hemianopia search experiment. 
+%Based on Anna's experiment dated Jan 9th 2014.
+%blocks should use one of these two-char codes:
+% Blocks = {...
+%     'Ul','Ur',...
+%     'Bl','Br',...
+%     'Fl','Fr',...
+%     'Dl','Dr',...
+%     };
+
+
+%% check block is valid!
+if isempty(regexp(block, '[U][l]'))
+    disp('invalid block. please try again. see help for options. Thank you.')
+    return
+end
+
+addpath('Scripts/');
+
+%%%%%%%%%%%%%%%%%%%%%%%%%
+% preliminary stuff
+%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%setup our full screen window and other initialization
+display.w = InitializeWindow(  );
+
+[fixation, ~, alphafix]= imread('letter_x.png');% read the fixation image from the file
+fixation(:,:,4)=alphafix; %add alpha channel to our fixation point
+fixationTex = Screen('MakeTexture', display.w, fixation);
+
+
+iLink.doILink = 1;
+%output.empy=0;
+%%%%%%%%%%%%%%%%%%%%%%
+% experiment
+%%%%%%%%%%%%%%%%%%%%%%
+
+
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Set experiment variables
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%this is the primary function to change all experiment parameters
+[display] = SetUpTrials(display.w);
+output.folder=strcat('Data/', num2str(subNo), '/' ,block,'/');
+output.filename = strcat(output.folder,block,num2str(subNo),'.dat'); % name of data file to write to
+iLink.edfdatafilename = strcat(block,num2str(subNo),'.edf');
+% check for existing result file to prevent accidentally overwriting
+% files from a previous subject/session (except for subject numbers > 99):
+if subNo>99
+    fopen(output.filename, 'rt');  % its a test trial
+else
+    while (fopen(output.filename, 'rt')~=-1)
+        
+        output.filename = strcat(output.folder,block,num2str(subNo),'_A.dat'); % name of search data file to write to
+        %iLink.edfdatafilename = strcat(output.folder,num2str(subNo),'.edf');
[…]

### 2016-10-10 Experiments/Individual Search Differences/HalfPopOutUntimed/RunExperimentPractice.m

@@ -1,0 +1,135 @@
+function RunExperimentPractice(subNo, block)
+%RunExperiment(subNo, block)
+%Simulated hemianopia search experiment. 
+%Based on Anna's experiment dated Jan 9th 2014.
+%blocks should use one of these two-char codes:
+% Blocks = {...
+%     'Ul','Ur',...
+%     'Bl','Br',...
+%     'Fl','Fr',...
+%     'Dl','Dr',...
+%     };
+
+
+%% check block is valid!
+if isempty(regexp(block, '[UB][lr]'))
+    disp('invalid block. please try again. see help for options. Thank you.')
+    return
+end
+
+addpath('Scripts/');
+
+%%%%%%%%%%%%%%%%%%%%%%%%%
+% preliminary stuff
+%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%setup our full screen window and other initialization
+display.w = InitializeWindow(  );
+
+
+[fixation, ~, alphafix]= imread('letter_x.png');% read the fixation image from the file
+fixation(:,:,4)=alphafix; %add alpha channel to our fixation point
+fixationTex = Screen('MakeTexture', display.w, fixation);
+
+
+
+iLink.doILink = 1;
+%output.empy=0;
+%%%%%%%%%%%%%%%%%%%%%%
+% experiment
+%%%%%%%%%%%%%%%%%%%%%%
+
+
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Set experiment variables
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%this is the primary function to change all experiment parameters
+[display] = SetUpTrials(display.w);
+output.folder=strcat('Data/', num2str(subNo), '/' ,block,'/');
+output.filename = strcat(output.folder,block,num2str(subNo),'.dat'); % name of data file to write to
+iLink.edfdatafilename = strcat(block,num2str(subNo),'.edf');
+% check for existing result file to prevent accidentally overwriting
+% files from a previous subject/session (except for subject numbers > 99):
+if subNo>99
+    fopen(output.filename, 'rt');  % its a test trial
+else
+    while (fopen(output.filename, 'rt')~=-1)
+        
+        output.filename = strcat(output.folder,block,num2str(subNo),'_A.dat'); % name of search data file to write to
+        %iLink.edfdatafilename = strcat(output.folder,num2str(subNo),'.edf');
[…]

### 2016-10-10 Experiments/Individual Search Differences/HalfPopOutUntimed/Scripts/CheckItemGrid.m

@@ -1,0 +1,20 @@
+%% check item grid!
+%% make a plot with a cross at the centre of each potential face postion
+clear all
+close all
+[destrect display] = SetUpStimGrid();
+nL = length(destrect.L);
+for i = 1:length(destrect.L)
+    x(i) = destrect.L(i).imrect(1) + (destrect.L(i).imrect(3)- destrect.L(i).imrect(1))/2;
+    y(i) = destrect.L(i).imrect(2) + (destrect.L(i).imrect(4)- destrect.L(i).imrect(2))/2;    
+end
+for i = 1:length(destrect.R)
+    x(i+nL) = destrect.R(i).imrect(1) + (destrect.R(i).imrect(3)- destrect.R(i).imrect(1))/2;
+    y(i+nL) = destrect.R(i).imrect(2) + (destrect.R(i).imrect(4)- destrect.R(i).imrect(2))/2;    
+end
+
+subplot(1,2,1);
+plot(x,y, 'x');
+
+ xlim([1,display.width]); ylim([1,display.height]) 
+    

### 2016-10-10 Experiments/Individual Search Differences/HalfPopOutUntimed/Scripts/GetSubsetOfLocations.m

@@ -1,0 +1,25 @@
+%%function to select a subset of possible search item locations
+
+function [loc] = GetSubsetOfLocations(destrect, nLoc)
+
+if nargin < 2
+    nLoc = 8;
+end
+
+if length(nLoc) == 1
+    locSplit = [floor(nLoc/2), floor(nLoc/2)];
+else
+    locSplit = nLoc;
+end
+
+
+randR = randperm(length(destrect.R));
+randL = randperm(length(destrect.L));
+destrect.R = destrect.R(randR);
+destrect.L = destrect.L(randL);
+
+loc.L = destrect.L(1:locSplit(1));
+loc.R = destrect.R(1:locSplit(2));
+
+
+end

### 2016-10-10 Experiments/Individual Search Differences/HalfPopOutUntimed/Scripts/InitEyeLink.m

@@ -1,0 +1,61 @@
+function [eyeLink] = InitEyeLink( eyeLink , w)
+%UNTITLED Summary of this function goes here
+%   Detailed explanation goes here
+
+     %initialize eyelink
+    if EyelinkInit()~= 1; %
+    	return;
+    end;
+    % 
+
+        %lets get it working without eylink for now
+        % do eyelink stuff
+    eyeLink.el=EyelinkInitDefaults(w);
+    iLink.window = w;
+    
+     eyeLink.el.backgroundcolour = (BlackIndex(w)+WhiteIndex(w))/2;
+     eyeLink.el.foregroundcolour = BlackIndex(w);
+     eyeLink.el.targetbeep =0;
+     %eyeLink.el.drift_correction_success_beep=[800 0.0 0.25];%volume to 0.0
+    eyeLink.el.eye_used = eyeLink.el.RIGHT_EYE; % use right eye  +1 for matlab array offset!!!!
+
+    if ~isempty(eyeLink.el.window) & ~isempty(eyeLink.el.callback) %#ok<AND2>
+         PsychEyelinkDispatchCallback(eyeLink.el);     %then pass it to the callback
+     end
+    
+   
+    %   SET UP TRACKER CONFIGURATION
+    Eyelink('command', 'calibration_type = HV5'); 
+    %	set parser (conservative saccade thresholds)
+    Eyelink('command', 'saccade_velocity_threshold = 35');
+    Eyelink('command', 'saccade_acceleration_threshold = 9500');
+    %	set EDF file contents
+    Eyelink('command', 'file_event_filter = LEFT,RIGHT,FIXATION,SACCADE,BLINK,MESSAGE,BUTTON');
+    %	set link data (used for gaze cursor)
+    Eyelink('command', 'link_event_filter = LEFT,RIGHT,FIXATION,BUTTON, SACCADE');
+    Eyelink('command', 'link_sample_data  = LEFT,RIGHT,GAZE,AREA,SACCADE,BLINK');
+
+
+
+    % open file to record data to
+    Eyelink('openfile', eyeLink.edfdatafilename);%string defined earlier
+ 
+    % STEP 4
+    % Calibrate the eye tracker
+    EyelinkDoTrackerSetup(eyeLink.el);
+
+    % do a final check of calibration using driftcorrection
+    %EyelinkDoDriftCorrection(eyeLink.el);
+
+    WaitSecs(0.1);
[…]

### 2016-10-10 Experiments/Individual Search Differences/HalfPopOutUntimed/Scripts/InitializeWindow.m

@@ -1,0 +1,53 @@
+function [ w ] = InitializeWindow(  )
+    % Check if all needed parameters given:
+    if nargin < 1
+        subNo = 1;
+        strcat('no subject number assigned, assigning automatically')
+        %error('Must provide required input parameter "subNo"!');
+    end
+% Clear Matlab/Octave window:
+    clc;
+    % check for Opengl compatibility, abort otherwise:
+    AssertOpenGL;
+    % Reseed the random-number generator for each expt.
+    rand('state',sum(100*clock));
+
+    % Make sure keyboard mapping is the same on all supported operating systems
+    % Apple MacOS/X, MS-Windows and GNU/Linux:
+    KbName('UnifyKeyNames');
+    % Do dummy calls to GetSecs, WaitSecs, KbCheck to make sure
+    % they are loaded and ready when we need them - without delays
+    % in the wrong moment:
+    KbCheck;
+    WaitSecs(0.1);
+    GetSecs;
+    %%%%%%%%%%%%%%%%%%%%%%
+    % open window
+    %%%%%%%%%%%%%%%%%%%%%%
+    % Get screenNumber of stimulation display. We choose the display with
+    % the maximum index, which is usually the right one, e.g., the external
+    % display on a Laptop:
+    screens=Screen('Screens');
+    %screenNumber=max(screens);
+    screenNumber=min(screens);
+    
+    % Hide the mouse cursor:
+    HideCursor();
+    % Open a double buffered fullscreen window on the stimulation screen
+    % 'screenNumber' and choose/draw a gray background. 'w' is the handle
+    % used to direct all drawing commands to that window - the "Name" of
+    % the window. 'wRect' is a rectangle defining the size of the window.
+    % See "help PsychRects" for help on such rectangles and useful helper
+    % functions:
+  [w, wRect] = Screen('OpenWindow',screenNumber,128,[],32,2);
+  %[w, wRect]=Screen('OpenWindow',screenNumber, 128, [0 0 512 512],32,2);  %try a partial window
+    % Set text size (Most Screen functions must be called after
+    % opening an onscreen window, as they only take window handles 'w' as
+    % input:
+    Screen('TextSize', w, 32);
+    %this is needed to display gif images with tranparancy 
+    Screen('Blendfunction', w,GL_SRC_ALPHA, GL_ONE_MINUS_SRC_ALPHA);
+
+
+end
+

### 2016-10-10 Experiments/Individual Search Differences/HalfPopOutUntimed/Scripts/LoadInFace.m

@@ -1,0 +1,16 @@
+function out = LoadInFace(fname)
+
+xCut = 35;
+yCut = 25;
+
+
+[pic, ~, alpha] = imread(fname);
+pic(:,:,4) = alpha;
+
+x1 = xCut+1;
+x2 = size(pic,1)-xCut;
+
+y1 = yCut+1;
+y2 = size(pic,2)-yCut;
+
+out = pic(x1:x2, y1:y2, :);

### 2016-10-10 Experiments/Individual Search Differences/HalfPopOutUntimed/Scripts/LoadInLineStimuli.m

@@ -1,0 +1,42 @@
+mainFolder = 'LineStimuli/';
+
+
+folder = 'LineStimuli/';% folder containing face stimuli
+filelist = dir([folder '*.jpg']);
+display.numImages = length(filelist);
+for f = 1:length(filelist)
+    [pict, map] = imread([folder filelist(f).name]);%repeat this one every image
+    line=[folder filelist(f).name];
+    indexN=findstr([folder filelist(f).name], 'o');
+    indexR=findstr([folder filelist(f).name], 'r');
+    indexC=findstr([folder filelist(f).name], 'c');
+    indexV=findstr([folder filelist(f).name], 'v');
+  
+    stimNo=str2num(line(indexN+1:indexR-1));
+    row=str2num(line(indexR+1:indexC-1));
+    column=str2num(line(indexC+1:indexV-1));
+    
+    display.lineSegm(f).im = pict;
+    
+    display.lineSegm(f).number=indexN;
+    display.lineSegm(f).name=[folder filelist(f).name];
+    display.lineSegm(f).row = row;
+    display.lineSegm(f).column  = column;
+    if display.lineSegm(f).row == 0
+        
+        display.lineSegm(f).targPres  =0;
+    else
+        display.lineSegm(f).targPres  =1;
+    end
+    
+    if display.lineSegm(f).column >0 & display.lineSegm(f).column<11
+        
+        display.lineSegm(f).targSide  ='left';
+    elseif display.lineSegm(f).column>12
+        display.lineSegm(f).targSide  ='right';
+    else
+        display.lineSegm(f).targSide  ='x';
+    end
+    
+    
+end

### 2016-10-10 Experiments/Individual Search Differences/HalfPopOutUntimed/Scripts/LoadInLineStimuli2.m

@@ -1,0 +1,42 @@
+mainFolder = 'LineStimuli/';
+
+
+folder = 'LineStimuli/';% folder containing face stimuli
+filelist = dir([folder '*.jpg']);
+display.numImages = length(filelist);
+for f = 1:length(filelist)
+    [pict, map] = imread([folder filelist(f).name]);%repeat this one every image
+    line=[folder filelist(f).name];
+    indexN=findstr([folder filelist(f).name], 'o');
+    indexR=findstr([folder filelist(f).name], 'r');
+    indexC=findstr([folder filelist(f).name], 'c');
+    indexV=findstr([folder filelist(f).name], 'v');
+    stimNo=str2num(line(indexN+1:indexR-1));
+    row=str2num(line(indexR+1:indexC-1));
+    column=str2num(line(indexC+1:indexV-1));
+   
+    
+    display.lineSegm(f).im = pict;
+    
+    display.lineSegm(f).number=indexN;
+    display.lineSegm(f).name=[folder filelist(f).name];
+    display.lineSegm(f).row = row;
+    display.lineSegm(f).column  = column;
+    if display.lineSegm(f).row == 0
+        
+        display.lineSegm(f).targPres  =0;
+    else
+        display.lineSegm(f).targPres  =1;
+    end
+    
+    if display.lineSegm(f).column >0 & display.lineSegm(f).column<11
+        
+        display.lineSegm(f).targSide  ='left';
+    elseif display.lineSegm(f).column>12
+        display.lineSegm(f).targSide  ='right';
+    else
+        display.lineSegm(f).targSide  ='x';
+    end
+    
+    
+end

### 2016-10-10 Experiments/Individual Search Differences/HalfPopOutUntimed/Scripts/MakeTrialImage.m

@@ -1,0 +1,37 @@
+Screen('FillRect', osw.Orig ,display.grey);
+Screen('FillRect', osw.Filt ,display.grey);
+
+%create Original offscreen faces
+%Screen('FillRect',osw.Orig ,display.grey);
+
+
+    % load in original
+    pic = display.lineSegm(trials(t)).im;
+    targTexOrig = Screen('MakeTexture', display.w, pic);
+    Screen('DrawTexture', osw.Orig, targTexOrig , []);%add location here ,display.winrect
+    % load in filtered
+    switch (block(1))
+        case 'U'
+            % unchanged - control condition
+            pic = display.lineSegm(trials(t)).im;
+            targTexFilt = Screen('MakeTexture', display.w, pic);
+            Screen('DrawTexture', osw.Filt, targTexFilt , []); %,display.winrect
+        case 'B'
+            % blank - grey level background
+       
+    end
+    
+    
+
+
+
+
+
+
+%to make an image of each trial search display
+ im = Screen('GetImage', osw.Orig);
+ imwrite(im, 'orig.png');
+%  im = Screen('GetImage', osw.Filt);
+%  imwrite(im, 'filt.png');
+
+clear pic numDistTex

### 2016-10-10 Experiments/Individual Search Differences/HalfPopOutUntimed/Scripts/RunTrial.m

@@ -1,0 +1,216 @@
+
+function RunTrial(trials,t, iLink, output, display, osw, fixationTex, block);
+
+trial_type=block(1);
+hemianopia=block(2);
+
+%initialize output
+output.message = 'GoodTrial'; %assume a good trial till proven otherwise
+output.RT = 0;
+output.keypressed = 'x';
+space=KbName('space');
+leftArrowKey=KbName('leftArrow');
+rightArrowKey= KbName('rightArrow');
+arrayOnset = 0;
+
+
+%display fixation and start trial timer
+%DrawFormattedText(display.w, 'test', 'center', 'center', WhiteIndex(display.w));
+if iLink.doILink
+    Screen('DrawTexture', display.w, fixationTex , [],display.fixRect );
+    Screen('Flip', display.w );%to clear buffer
+    EyelinkDoDriftCorrection(iLink.el, display.fixXLoc, display.fixYLoc, 0, 1);
+    % Start data recording to EDF file, BEFORE DISPLAY. */
+    status=Eyelink('startrecording');
+    % record a few samples before we actually start displaying
+    WaitSecs(0.1);
+end
+%make sure space is released
+[KeyIsDown,endrt, KeyCode]=KbCheck();
+while (KeyIsDown==1)
+    [KeyIsDown,endrt, KeyCode]=KbCheck();
+end
+
+%  while (KeyIsDown==1)
+%      [KeyIsDown, endrt, KeyCode]=KbCheck();
+%  end;
+
+trialStart = GetSecs();%to clear buffer
+
+%event flags.  set these when the events happen in the timing loop
+stimPresentedFlag =0;
+
+if iLink.doILink
+    Eyelink('message', 'DISPLAY_ON');	 % message for RT recording in analysis
+    Eyelink('message','SYNCTIME');
+end
+
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%primary timing loop.
+%each if statement in here checks for one of our events like cue onset, or
+%button response
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+xCurr = display.fixXLoc;
+yCurr = display.fixYLoc;
+
+while (trialStart + display.maxResponseTime > GetSecs() && output.RT ==0)
+    
+    %%%%%%%%%%%%%%%%%%%%%%%%
+    % 0) grab current eye position
+    if iLink.doILink
[…]

### 2016-10-10 Experiments/Individual Search Differences/HalfPopOutUntimed/Scripts/SetUpTrials.m

@@ -1,0 +1,66 @@
+function [display] = SetUpTrials(w)
+%set all variables for running the blocks.
+%these values canbe hard coded in this file, or they can be read in from a
+%text file (not yet implemented)
+%for this experiment....
+
+% Block 0:  Training
+% Block 1:  all conditions are now randomized within this block
+% including
+
+%%%%%%%%%%%%%%%%%%%%%%
+% file handling
+%%%%%%%%%%%%%%%%%%%%%%
+if nargin<1
+    display.w = [];
+    display.white=255;
+    display.black=0;
+    display.grey = 127;
+    display.width = 1024;
+    display.height = 768;
+else
+    display.w = w;
+    display.white=WhiteIndex(w);
+    display.black=BlackIndex(w);
+    display.grey = ((WhiteIndex(w)+BlackIndex(w))/2) +6;
+    [display.width, display.height]=Screen('WindowSize', w);%screen returns the size of the window
+    
+end
+
+
+
+% Define filenames of input files and result file:
+
+
+display.winrect= [0 0 display.width display.height];
+
+%these variables are common to all experiment blocks
+display.centerX                   = display.width/2;% divides the width of the screen into two
+display.centerY                   = display.height/2; %divides the height of the screen into two
+
+centW = 40.0; %screen width, cm
+centD = 45.0; %dist to screen, cm
+
+rad = 2.0*atan(centW/(centD*2));%radians of entire monitor
+deg = rad*(180/pi);%Degrees of entire monitor
+display.pixelsperdegree  = floor(display.width/deg);  %pixels per degree
+
+% fixation needed here
+display.fixXLoc                   = display.centerX;
+display.fixYLoc                   = display.centerY;
+display.fixHalfBox                = floor(0.5*display.pixelsperdegree);      %max distance we allow to still be on target for fix and saccade land
+display.fixRect                   = [display.fixXLoc-display.fixHalfBox display.fixYLoc-display.fixHalfBox display.fixXLoc+display.fixHalfBox display.fixYLoc+display.fixHalfBox];
+
+%Now details of faces
+
+%file = strcat(folder,'F02HA.png'); %if we just wanted one file we select it
+%from our folder
+%display.numFaces = length(filelist);
+display.maxResponseTime = 60.0;
+display.stimOnset       = 1.0;
+
+LoadInLineStimuli;
+
+
+end
+

### 2016-10-10 Experiments/Individual Search Differences/HalfPopOutUntimed/trialRTandAcc2.m

@@ -1,0 +1,1 @@
+% ARH/AL March 2014. Code to process data from Anna's project looking at the effect of
% gaze-contingent filtering on search strategies.
% Data recorded from EyeLink 1000.
% open the .asc file, get fixation and trial data, output trial results

clear all;
numSub = 14;
fileRun = 0;

%subNo = input('Enter the subject number: ');
filetomake = input('name the RT and accuracy file: ', 's');
F2ID = fopen(filetomake, 'a');
fprintf(F2ID, 'subNum\t trialNo\t easySide\t targPresent\t targSide\t RT\t accuracy\t var\t con\n');

for subNo=1:numSub
        condition = 'Ul';
    
    
    filetoread = strcat(condition, num2str(subNo),'.asc'); % name of search data file to read
    if (fopen(filetoread, 'r')~=-1)
        FID=fopen(filetoread, 'r');
        trialRunning = 0;
        endtrialRun = 0;
        trialCount = 0;
        sacOnTime = 0;
        fileRun = 1;
    end
        
        while fileRun
            line=fgetl(FID); %get the next line of data
            
            if line == -1  % if the end of the file has been reached
                fclose(FID);
                
                fileRun = 0; %leave the main loop
                break;
                %     elseif findstr(line, 'TRIALNO_80')
                %         fclose(F2ID);
                %         fclose(FID);
                %         fileRun = 0; %leave the main loop
                %         break;
            end
            
            if findstr(line, 'FACES_DRAWN')
                trialCount = trialCount+1;
                targPres='x';
                targSide='x';
                TargX1='-1';
                mes='GoodTrial';
                easySide='x';
                cond='x';
                trialRunning =1; %start loop to get timing / saccade info from trial
            else findstr(line, 'EARLY_RESPONSE')
                trialCount = trialCount+1;
                targPres='x';
                targSide='x';
                TargX1='-1';
                mes='GoodTrial';
                easySide='x';
                cond='x';
                trialRunning =1; %start loop to get timing / saccade info from trial
                
                
                %         maxXvalue=0;
                while trialRunning
                    line = fgetl(FID);
                    if strfind(line, 'RESPONSE_') %
                        index = strfind(line, 'SE_')+3;
                        response =line(index:length(line));
                    end
                    if strfind(line, 'TargPres_') %
                        index = strfind(line, 'TargPres')+9;
                        targPres =str2num(line(index:length(line)));
                    end
                    if strfind(line, 'TargSide_') %
[…]

### 2016-10-10 Experiments/Individual Search Differences/MultiTargForag_1/MultiTargForag_1.m

@@ -1,0 +1,562 @@
+function MultiTargForag_1
+%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% Based on Kristjansson et al (2014)
+% Forage for two types of targets among two types of distractors
+% Select targets using mouse click
+
+% Feature search (all shapes circles):
+%   Counterbalance 1: Targets = red + green, Distractors = blue + yellow
+%   Counterbalance 2: Targets = blue + yellow, Distractors = red + green
+% Conjunction search:
+%   Counterbalance 1: Targets = red circle + green square, Distractors = red square + green circle
+%   Counterbalance 2: Targets = blue circle + yellow square, Distractors = blue square + yellow circle
+%   Counterbalance 3: Targets = red square + green circle, Distractors = red circle + green square
+%   Counterbalance 4: Targets = blue square + yellow circle, Distractors = blue circle + yellow square
+
+% To quite during trial, hold down esc key and click mouse
+
+% programmed by J Irons August 2016
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% SETUP %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+    
+skipsync = 1;               % skip sync tests. 1 = yes, 0 = no
+
+%%% Trial info
+nblocks = 1;                % num blocks (with breaks in between)   
+nblocktrials = 20;          % num trials/block
+nprac = 5;                  % num prac trials
+ITItime = 2;                % Duration of intertrial interval
+
+%%% Stumulus color
+Red = [180 0 0];            % Target colors (RGB 1-255)
+Green = [20 100 40];
+Blue = [0 0 220];
+Yellow = [200 150 0];
+backgroundcol = [0 0 0];    % Display background col 
+textcol = [255 255 255];    % Text & fixation point col
+
+%%% Stimulus size/shape
+nsetitems = 20;             % Number of items per distractor set
+ngridX = 10;                % num items across array
+ngridY = 8;                 % num items down array
+isq = 20;                   % width for square shape
+icir = 22;                  % width for circle shape
+ibuffer = 15;               % Max possible buffer between two items
+clickrange = 25;            % Must click within this radius from centre of item to count as selected
[…]

### 2017-01-20 writeup/manuscript.tex
pilot data and feature notes

@@
 The study consists of three different paradigms from the visual search literature in which strong individual differences were found \citep{nowakowsak2017, irons-leber2016, kristjansson2014}.
+{}
+\subsubsection{A: Split-half array search}
+
+\subsubsection{B: Attentional Control}
+
+\subsubsection{C: Conjunction Foraging}
+
+\subsection{Planned Analysis}
 
 \subsubsection{A: Split-half array search}
+
+In order to characterise an individual's behaviour in this task, we will compute the proportion of the first $n$ fixations that were on heterogeneous (difficult) side of the stimuli, over all target absent trials\footnote{Only take correct trials?}.
+\cite{nowakowsak2017} demonstrated a strong correlation between an this metric (for $n=5$) and reaction times ($r=$).
+However, a re-analysis of their data shows that an even stronger correlation is obtained with $n=3$ (see Figure \ref{fig:nowakowskaBestN})
 

### 2017-01-20 NowakowskaClarkeHunt2017/scripts/lookAtSaccDirConfInterw2graphs5.R

@@ -19,7 +19,7 @@ levels(fixdat$subj) = 1:12
 cbPalette <- c("#56B4E9", "#E69F00")
 
 rtdat = readRDS(file="../data/processedRTandAccData.Rda")
-medianRT = aggregate(RT~subj, rtdat, "median2")
+medianRT = aggregate(RT~subj, rtdat, "median")
 
 # classify every fixation as homo (left), central, or hetro (right)
 centralWidth = 64 #change to 1 visual degree
@@ -53,9 +53,9 @@ for (nf in 2:12)
   metricVal = rbind(metricVal, data.frame(nfix=nf, r=r))
 }
 
-plt = ggplot(metricVal, aes(x=nfix, y=r)) + geom_point()
-plt = plt + scale_x_continuous(name = "including first x fixations")
-plt = plt + scale_y_continuous(name = "Pearson's r")
+plt = ggplot(metricVal, aes(x=nfix, y=r^2)) + geom_point()
+plt = plt + scale_x_continuous(name = "including first x fixations", breaks=c(2,4,6,8,10))
+plt = plt + scale_y_continuous(name = expression(R^2))
 plt = plt + theme_bw()
 ggsave("r_by_nfix.pdf", width=4, height=4)
 
@@ -64,7 +64,7 @@ d = aggregate(propHetro ~ subj, data=filter(aggData, fixNum<=nf), "mean")
 cordf = merge(d, medianRT)
  plt = ggplot(cordf, aes(x=propHetro, y=RT)) + geom_point()
  plt = plt + geom_smooth(method=lm)
- plt = plt + scale_x_continuous("mean(prop. of first 3 fixations on hetro. side", limits=c(0,1))
+ plt = plt + scale_x_continuous("mean prop. of first 3 fixations on hetro. side", limits=c(0,1))
  plt = plt + scale_y_continuous("median reaction time (secs")
  plt = plt + theme_bw()
 ggsave("best_r_scatter.pdf", width=4, height=4)

### 2017-01-20 writeup/manuscript.tex
added figures for feature design
starting to look at pilot data
but missing fix asc processing file

@@
 \usepackage{graphicx}
-\usepackage{subfig}
+\usepackage{subfigure}
 \usepackage[round, comma, sort&compress, longnamesfirst]{natbib} 
@@
 
+\begin{figure}
+\centering
+\subfigure[][]{\includegraphics[width=6cm]{../NowakowskaClarkeHunt2017/scripts/r_by_nfix.pdf}}
+\subfigure[][]{\includegraphics[width=6cm]{../NowakowskaClarkeHunt2017/scripts/best_r_scatter.pdf}}
+\caption{Selecting the best $n$.}
+\label{fig:nowakowskaBestN}
+\end{figure}
+
 \subsubsection{B: Attentional Control}
@@
 \subsubsection{C: Conjunction Foraging}
+
+\subsubsection{}
+
+\subsection{Exploratory Analysis}
+
+We will carry out additional analysis, above and beyond what has been documented above, but the exact nature of this will be contingent on the nature of the results.
+Something like PCA may be interesting.
 

### 2017-01-20 Data/pilot data/scripts/InitialAnalysisAC_AN6.R

@@ -1,0 +1,250 @@
+
+library(dplyr)
+# TODO: check subjects to replace!
+ # setwd("C:/Users/r02al13/Documents/GitHub/HalfScreenPopOut")
+
+saccInfo <- function(trialDat)
+{
+	# this is a funtion that calculates saccade amplitude and angle for a sequenece of fixations in a  trial
+	nFix = max(trialDat$fixNum)
+	saccInfo  = trialDat
+	saccAmp2 = vector()
+	theta = vector()
+	for (f in 1:(nFix-1))
+	{
+		dx = trialDat$fixX[f] - trialDat$fixX[f+1]
+		dy = trialDat$fixY[f] - trialDat$fixY[f+1]
+		saccAmp2[f] 	= dx^2 + dy^2
+		theta[f] 		= atan2(dx, dy)
+	}
+	saccAmp2[nFix] = NaN
+	theta[nFix]    = NaN
+	saccInfo$amp   = sqrt(saccAmp2)
+	saccInfo$ang   = theta
+	return(saccInfo)
+}
+
+
+# subjectsToRemove = c(2)#one experimenter nr.2, only completed a few trials, and two at chance in parallel, 4 and 15 at chance
+# max fixation duration - remove trial if it is exceeded 
+maxFixDur = 2000
+
+# read in reaction time and acc data:
+# this will allow us to remove fixation data for incorrect trials
+print("Processing RT and Acc data")
+dat1 <- read.csv("../data/Ul/Ul77.dat", sep="\t")
+dat1$session = 1
+dat2 <- read.csv("../data/Ul/Ul772.dat", sep="\t")
+dat2$session = 2
+dat = cbind(dat1, dat2)
+rm(dat1, dat2)
+
+names(dat) = c("subj", "trialNum", "hemiType", "hemiSide","easySide", "targPresent", "targSide", "RT", "X", "acc")
+dat = select(dat, subj, trialNum, easySide, targPresent, targSide, RT, acc)
+
+# Turn categorical data into factor
+dat$targPresent = as.factor(dat$targPresent)
+levels(dat$targPresent) = c("absent", "present")
+levels(dat$targSide) = c('left', 'right', 'absent')
+dat$easySide = as.factor(dat$easySide)
+levels(dat$easySide) = c("left", "right")
+
+# remove some subjects
+
+dat$subj = as.factor(dat$subj)
[…]

### 2017-01-30 writeup/manuscript.tex
updating pre-reg details

@@
 
+Following \cite{irons-leber2016}, individual differences will be characterised using two measures: 
+\begin{itemize}
+\item Proportion of optimal choices on plateaus (i.e., where the distractor colour is .
+An optimal choice is defined as responding to whichever of the two target colours has the fewest items in the display.
+This will be based on correct plateau trials only.
+\\
+\item Switching frequency.
+Switching is defined as responding to a different target color on trial $N+1$ than on trial $N$, and is presented as a proportion of the total number of trials (excluded incorrect trials, the trial after an incorrect trial, and the first trial of each block).\\
+\end{itemize}
+
+Both measures have been shown to correlate with overall RT in previous experiments (Proportion Optimal $r =-.56$, $p < .001$; Switch Frequency $r = .45$, $p = .001$; based on $N = 50$ and using the same number of trials as in the current experiment).
+As additional validation, correctional analyses between both measures and RT will also be conducted in the current experiment.
+
 \subsubsection{C: Conjunction Foraging}
 
-\subsubsection{}
+Data analysis will follow \cite{kristjansson2014,johannesson2016}.
+The main measure of interest will be the average run length per trial.
+A run is defined as a succession of one or more of the same target type which is followed and preceded by the other target type or no target.
+The average length is the average number of consecutive target selections per run.
+As with the other experiments, we will also measure the average response (time to select the final target on correct trials).
+
+\subsubsection{Correlations}
+
+We will present similarity matrices for how well the reaction times of one study correlate with the others.
+We will then go on to explore the correlations between the various strategy features outlined above.
+
+We will use Bayesian analysis to estimate all effect sizes.
+This avoids the need to correct $p$-values for multiple comparisons as is required under null hypothesis significance testing.
+Analysis will be carried out with several different choices of prior to investigate robustness (ie, uninformative/uniform [-1,1] prior and a Normal(0,1) prior).
+If a variable is highly skewed, it will be log-transformed.
+All variables will be $z$-scaled.
 
@@
 Something like PCA may be interesting.
+
+We will also explore modeling the non-linear relationships between the variables if appropriate, as there is no reason to assume that the relationships must be linear.
 

### 2017-02-03 writeup/manuscript.tex
write up correction and note on sample size.

--- 2017-01-20 writeup/manuscript.tex
@@
 \subsection{Participants}
-How many? Will all testing be done at the University of Aberdeen? How do we justify our sample size (a question commonly asked by journals now!)?
+We aim to find 64 participants to volunteer to take part in this experiment.
+Participants will be students from the University of Aberdeen, and will be compenstate £x.xx for their time.
+Sample size was determined in part due to constraints with counter-balancing <expand>.
 
@@
 
+Following \cite{irons-leber2016}, individual differences will be characterized using two measures:\\
+1) Proportion of optimal choices on plateaus.
+An optimal choice is defined as responding to whichever of the two target colours has the fewest items in the display.
+This will be based on correct plateau trials only.
+\\
+2) Switching frequency.
+Switching is defined as responding to a different target color on trial $N$+1 than on trial $N$, and is presented as a proportion of the total number of trials (excluded incorrect trials, the trial after an incorrect trial, and the first trial of each block).\\
+Both measures have been shown to correlate with overall RT in previous experiments (Proportion Optimal $r$=-.56, $p$<.001; Switch Frequency $r$=.45, $p$=.001; based on $N$=50 and using the same number of trials as in the current experiment).
+As additional validation, correlational analyses between both measures and RT will also be conducted in the current experiment.
+
 \subsubsection{C: Conjunction Foraging}
+
+Data analysis will follow \cite{kristjansson2014} and Johannesson et al.
+(2016).
+The main measure of interest will be the average run length per trial.
+A run is defined as a succession of one or more of the same target type which is followed and preceded by the other target type or no target.
+The average length is the average number of consecutive target selections per run.
+As with the other experiments, we will also measure the average response (time to select the final target on correct trials).
 

### 2017-02-07 writeup/manuscript.tex
note on half/half test-retest
note on planned sample size

@@
 We aim to find 64 participants to volunteer to take part in this experiment.
-Participants will be students from the University of Aberdeen, and will be compenstate £x.xx for their time.
-Sample size was determined in part due to constraints with counter-balancing <expand>.
+Participants will be students from the University of Aberdeen.
+Some will be compensated with course credit and some will be paid £10 for their time*.
+Sample size was determined in part due to constraints with counter-balancing; there are 16 different possible orders of tasks/conditions; we will run four participants in each order for a total of 64.
+All participants will sign a form giving informed consent.
+The study has already been approved by the University of Aberdeen Psychology Ethics Committee
 
@@
 The study consists of three different paradigms from the visual search literature in which strong individual differences were found \citep{nowakowsak2017, irons-leber2016, kristjansson2014}.
-{}
+The \cite{nowakowsak2017} experiment will be carried out twice to give us an estiamte of how consistent participants are in their search strategy.
+Both sessions were indentical.
+
 \subsubsection{A: Split-half array search}

### 2017-03-01 Scripts/lineseg/3_saccadeStrategy.R
Adding most data from 1-32
Still some asc files missing though

@@ -34,29 +34,5 @@ plt = plt + scale_x_continuous(name="fixation number", breaks=c(2,4,6,8,10))
 plt = plt + scale_y_continuous(name="proportion of fixations to heterogeneous side", limits=c(0,1))
 ggsave("scratch/strategyBySessionAndPerson.pdf")
 
-metricVal = data.frame(nfix=as.numeric(), r=as.numeric())
-for (nf in 2:12)
-{
-  d = aggregate(propHetro ~ subj, data=filter(aggData, n<=nf), "mean")
-  cordf = merge(d, medianRT)
-  r = cor(cordf$propHetro, cordf$RT)
-  metricVal = rbind(metricVal, data.frame(nfix=nf, r=r))
-}
-
-plt = ggplot(metricVal, aes(x=nfix, y=r^2)) + geom_point()
-plt = plt + scale_x_continuous(name = "including first x fixations", breaks=c(2,4,6,8,10))
-plt = plt + scale_y_continuous(name = expression(R^2))
-plt = plt + theme_bw()
-ggsave("r_by_nfix.pdf", width=4, height=4)
-
-nf = 3
-d = aggregate(propHetro ~ subj, data=filter(aggData, fixNum<=nf), "mean")
-cordf = merge(d, medianRT)
- plt = ggplot(cordf, aes(x=propHetro, y=RT)) + geom_point()
- plt = plt + geom_smooth(method=lm)
- plt = plt + scale_x_continuous("mean prop. of first 3 fixations on hetro. side", limits=c(0,1))
- plt = plt + scale_y_continuous("median reaction time (secs")
- plt = plt + theme_bw()
-ggsave("best_r_scatter.pdf", width=4, height=4)
 
 

### 2017-03-01 Scripts/lineseg/1_InitProcessing.R
init line see results

@@ -96,7 +96,8 @@ ProcessASC <- function(asc, ss)
 	return(list(fixDat, detDat))
 }
 
-participants = c(1,2,3,4,7)
+participants = 1:32
+participants = participants[-18]
 datFolder = '../../Data/'
 
 fixDat = data.frame(observer=numeric(), trial=numeric(), n=numeric(), x=numeric(), y=numeric(), dur=numeric())
@@ -105,8 +106,10 @@ trlDat = data.frame(observer=numeric(), trial=numeric(), targPres=character(), t
 resDat = data.frame(observer=numeric(), session=numeric(), xRes=numeric(), yRes=numeric())	
 for (pp in participants)
 {
-	for (ss in 1:2)
+	print(pp)
+	for (ss in c('a', 'b'))
 	{
+		print(ss)
 		filename = paste(datFolder, pp, '/lineseg/Ul', pp, ss, '.asc', sep="")
 		asc = strsplit(readLines(filename), "\t")
 		dat = ProcessASC(asc, ss)
@@ -121,7 +124,7 @@ for (pp in participants)
 	}
 }
 rm(ss, pp, filename, dat)
-
+ 
 ##### Tidy up trlDat
 
 # recode factors
@@ -169,7 +172,7 @@ fixDat$session = as.factor(fixDat$session)
 # centre x and y 
 for (pp in participants)
 {
-	for (ss in 1:2)
+	for (ss in c('a', 'b'))
 	{
 		resX = filter(resDat, observer==pp, session==ss)$xRes
 		resY = filter(resDat, observer==pp, session==ss)$yRes

### 2017-03-02 Scripts/adaptchoice/AC_data_analysis.m
Updated code and data

@@ -6,10 +6,10 @@
 % 
 % Instructions:
 % 
-% 1) Ensure all data files are in the same folder as this file
+% 1) Ensure this file is in the same folder as the individual data folders
 % 
 % 2) Update the list of subject numbers:
- sublist = [1,2,3,4,7]; 
+ sublist = [1:17,19:31]; % Missing: 18, 32
 % 
 % 3) Hit run
 % 
@@ -48,7 +48,7 @@ for s = 1:length(sublist)
     
     subNo = sublist(s)
     
-     datafilename = strcat('Data_',expname,'_',num2str(subNo),'_sess',num2str(session),'.txt');
+     datafilename = strcat(num2str(subNo),'/adaptchoice/Data_',expname,'_',num2str(subNo),'_sess',num2str(session),'.txt');
      datafile = dlmread(datafilename,'',4,0);
      
      colnums = size(datafile,2);

### 2017-03-02 Scripts/foraging/MultiTargForag_analysis.m
Updated files and data

@@ -9,10 +9,10 @@
 % 
 % Instructions:
 % 
-% 1) Ensure all data files are in the same folder as this file
+% 1) Ensure this file is in the same folder as the individual data folders
 % 
 % 2) Update the list of subject numbers:
- sublist = [1,2,3,4,7]; 
+ sublist = [1:17,19:30,32]; % Missing: 18, 31 first session
 % 
 % 3) Hit run
 % 
@@ -47,17 +47,17 @@ for s = 1:length(sublist)
     data2 = [];
     
      subNo = sublist(s)
-     if subNo < 7
+     if subNo < 5
         version = 1;    % old version of exp 
      else
         version = 2;
      end
         
      % Get Data from both sessions
-     datafilename1 = strcat('Data_',expname,'_',num2str(version),'_',num2str(subNo),'.txt');
+     datafilename1 = strcat(num2str(subNo),'/foraging/Data_',expname,'_',num2str(version),'_',num2str(subNo),'.txt');
      data1 = dlmread(datafilename1,'',3,0);
      
-     datafilename2 = strcat('Data_',expname,'_',num2str(version),'_',num2str(subNo),'a.txt');
+     datafilename2 = strcat(num2str(subNo),'/foraging/Data_',expname,'_',num2str(version),'_',num2str(subNo),'a.txt');
      data2 = dlmread(datafilename2,'',3,0);
      
      % Open one file to get the header info
@@ -73,41 +73,46 @@ for s = 1:length(sublist)
      
      if cond == 1
          condorder = [1,2]; % Feature first, then Conj
+         featuredata = data1;
+         conjdata = data2;
      else
          condorder = [2,1]; % Conj first, then feature
+         featuredata = data2;
+         conjdata = data1;
      end
+     
+     
      
      fclose(fid);
      
      % Add new column with new trial number to separate prac trials from
      % exp trials
-     newtrial = size(data1,2)+1;
+     newtrial = size(featuredata,2)+1;
      newtrialcount = 1;
-     data1(1,newtrial) = newtrialcount;
-     for c = 2:size(data1,1)
-         if data1(c,click) <= data1(c-1,click)  %If click number doesn't increase, then it's a new trial
+     featuredata(1,newtrial) = newtrialcount;
+     for c = 2:size(featuredata,1)
[…]

### 2017-03-03 Scripts/lineseg/1_InitProcessing.R
more analysis for lineseg

@@ -24,7 +24,7 @@ ProcessASC <- function(asc, ss)
 	trialDone   = grep("Done", asc)
 	nTrials = length(trialStarts)
 
-	if (length(trialEnds)!=nTrials)
+	while (length(trialEnds)!=nTrials)
 	{
 		# we probably have an early response or something
 		trialEnds=trialEnds[-min(which(trialEnds[1:nTrials]<trialStarts))]
@@ -96,7 +96,7 @@ ProcessASC <- function(asc, ss)
 	return(list(fixDat, detDat))
 }
 
-participants = 1:32
+participants = 1:31
 participants = participants[-18]
 datFolder = '../../Data/'
 

### 2017-03-03 Scripts/lineseg/2_rtAnalysis.R

@@ -8,6 +8,9 @@ library(tidyr)
 # read in processed data
 trlDat = readRDS(file="scratch/processedRTandAccData.Rda")
 
+# only take correct trials
+trlDat = filter(trlDat, acc==1)
+
 #  set colour palette
 cbPalette <- c("#E69F00", "#56B4E9","#B5CB8B")
 

### 2017-03-03 Scripts/lineseg/3_saccadeStrategy.R

@@ -10,7 +10,6 @@ fixDat = readRDS(file="scratch/processedFixationData.Rda")
 trlDat = readRDS(file="scratch/processedRTandAccData.Rda")
 
 
-# medianRT = aggregate(RT~subj, rtdat, "median")
 
 # classify every fixation as homo (left), central, or hetro (right)
 centralWidth = 0.05 # used to be 64 pixels! #change to 1 visual degree
@@ -19,20 +18,63 @@ fixDat$side[which(fixDat$x <(0-centralWidth/2))] = "homo"
 fixDat$side[which(fixDat$x >(0+centralWidth/2))] = "hetro"
 fixDat$side = as.factor(fixDat$side)
 
+
+# remove incorrect trials
+fixDat$acc = 1
+incorrectTrls = filter(trlDat, acc!=1)
+for (ii in 1:nrow(incorrectTrls))
+{
+	idx = which(fixDat$observer==incorrectTrls$observer[ii] & fixDat$session==incorrectTrls$session[ii] & fixDat$trial==incorrectTrls$trial[ii])
+	fixDat$acc[idx] = 0
+}
+
+
+trlDat = filter(trlDat, acc==1)
+fixDat = filter(fixDat, acc==1)
+
 aggData = (filter(fixDat, side!="central", n<12, n>1, targSide=="absent") 
   %>% group_by(observer, session, n) 
     %>% summarise(
+    	nTrials=length(trial),
      propHetro=mean(side=="hetro"), 
-     nTrials=length(trial),
-     lower = binom.confint(propHetro*nTrials,nTrials, method='wilson')$lower,
-     upper = binom.confint(propHetro*nTrials,nTrials, method='wilson')$upper))
+     lowerS = binom.confint(propHetro*nTrials,nTrials, method='wilson')$lower,
+     upperS = binom.confint(propHetro*nTrials,nTrials, method='wilson')$upper))
 
-plt = ggplot(aggData, aes(x=n, y=propHetro, ymin=lower, ymax=upper, colour=session))
+
+plt = ggplot(aggData, aes(x=n, y=propHetro, ymin=lowerS, ymax=upperS, colour=session))
 plt = plt + geom_point() + geom_path() + geom_errorbar()
-plt = plt + theme_bw() + facet_wrap(~observer, nrow=2)
+plt = plt + theme_bw() + facet_wrap(~observer, nrow=3)
 plt = plt + scale_x_continuous(name="fixation number", breaks=c(2,4,6,8,10))
[…]

### 2017-03-03 Scripts/collectDataFromExps.R
collecting data from different exes

@@ -1,0 +1,20 @@
+library(ggplot2)
+library(dplyr)
+
+
+lineseg = read.csv("lineseg/scratch/lineseg_output.csv")
+adapt   = read.csv("adaptchoice/Data_AdaptChoice_allsubs_Summary.txt", sep="\t")
+
+names(adapt) = c("observer", "ac_acc", "ac_rt", "ac_propOpt", "ac_switchRate")
+
+
+dat = merge(lineseg, adapt)
+
+
+
+plot(dat$lineseg_meanlogrt_hard, dat$ac_rt)
+
+cor.test(dat$lineseg_meanlogrt_hard, dat$ac_rt)
+
+
+write.csv(dat, "summaryData.csv")

### 2017-03-03 Scripts/lineseg/3_saccadeStrategy.R

@@ -50,7 +50,8 @@ ggsave("scratch/strategyBySessionAndPerson.pdf", width=12, height=5)
 
 
 
-
+###########
+# output data for cross experiment correlations!
 
 # base statistic for correlation on only first 3 fixations
 aggDataSS = (filter(fixDat, side!="central", n>1, n<=5, targSide=="absent") 
@@ -64,17 +65,21 @@ aggDataSS = (filter(fixDat, side!="central", n>1, n<=5, targSide=="absent")
 aggDataRT = (filter(trlDat, targSide=="hard") 
   %>% group_by(observer) 
     %>% summarise(
-     medianRT = median(rt)))
+     medianRT = median(rt),
+     meanLogRT = mean(log(rt))))
 
 
 
 aggData = merge(aggDataSS, aggDataRT)
 
+
 plt = ggplot(aggData, aes(x=propHetro, y=medianRT, colour=observer))
 plt = plt + geom_point() 
 ggsave("scratch/stratVrt.pdf")
 
+names(aggData) = c("observer", "ls_propHetro_absent", "ls_medianRT_hard", "ls_meanlogrt_hard")
+
+write.csv(aggData, "scratch/lineseg_output.csv")
 
 
-aggData = spread(aggData,  session, logrt)
-names(aggData)[3:4] = c("session1", "session2")
+

### 2017-03-03 Scripts/collectDataFromExps.R
initial look at core

@@ -18,3 +18,9 @@ cor.test(dat$lineseg_meanlogrt_hard, dat$ac_rt)
 
 
 write.csv(dat, "summaryData.csv")
+
+plt = ggplot(dat, aes(x=ls_meanlogrt_hard, y=ac_rt)) 
+plt = plt + geom_point()
+plt = plt + geom_smooth(method=lm)
+plt
+ggsave("ls_ac.pdf")

### 2017-03-03 Scripts/lineseg/3_saccadeStrategy.R

@@ -79,7 +79,7 @@ ggsave("scratch/stratVrt.pdf")
 
 names(aggData) = c("observer", "ls_propHetro_absent", "ls_medianRT_hard", "ls_meanlogrt_hard")
 
-write.csv(aggData, "scratch/lineseg_output.csv")
+write.csv(aggData, "scratch/lineseg_output.csv", row.names=F)
 
 
 

### 2017-03-03 Scripts/collectDataFromExps.R
pre-pub data processing

@@ -4,11 +4,21 @@ library(dplyr)
 
 lineseg = read.csv("lineseg/scratch/lineseg_output.csv")
 adapt   = read.csv("adaptchoice/Data_AdaptChoice_allsubs_Summary.txt", sep="\t")
+forage  = read.csv("foraging/Data_MultiTargForag_allsubs.txt", sep="\t")
 
-names(adapt) = c("observer", "ac_acc", "ac_rt", "ac_propOpt", "ac_switchRate")
-
+names(adapt) = c("observer", "ac_acc", "ac_rt", "ac_propOpt", "ac_switchRate", "ac_meanlogrt", "ac_medianrt")
+names(forage) = c("observer", "fg_meanrt_feature", "fg_medianrt_feature", "fg_meanlogrt_feature", "fg_runnum_feature", "fg_runlength_feature","fg_meanrt_cong", "fg_medianrt_cong", "fg_meanlogrt_cong", "fg_runnum_cong", "fg_runlength_cong")
 
 dat = merge(lineseg, adapt)
+dat = merge(dat, forage)
+
+
+rtdat = select(dat, ls_meanlogrt_hard, ac_meanlogrt, fg_meanlogrt_feature, fg_meanlogrt_cong)
+
+cor(rtdat)
+
+
+str(cor(dat[,-1]))
 
 
 

### 2018-03-23 writeup/manuscript.tex
Adding most data from 1-32
Still some asc files missing though
Started paper writing!

@@
-\documentclass[a4paper, oneside, 11pt, onecolumn]{article}
-\usepackage[T1]{fontenc}
-\usepackage{newtxtext,newtxmath}
-\usepackage{graphicx}
+\RequirePackage{fix-cm}
+\documentclass[]{rsos}%%%%where rsos is the template name
+
+%% *** Do not adjust lengths that control margins, column widths, etc. ***
 \usepackage{subfigure}
-\usepackage[round, comma, sort&compress, longnamesfirst]{natbib} 
-% \usepackage[left=2cm,top=3cm,right=1.5cm,bottom=2cm,bindingoffset=0.5cm]{geometry}
-\usepackage{enumerate}
-\usepackage{fancyhdr}
-\usepackage[title,titletoc,toc]{appendix}
-\pagestyle{fancy}
-\fancyhead{}
-\fancyfoot{}
-\fancyfoot[L]{\textit{running footer}}
- \fancyhead[L]{\textit{running title}}
-\renewcommand{\headrulewidth}{0.8pt}
-\renewcommand{\footrulewidth}{0.8pt}
-\setlength\headheight{14pt}
-\fancyfoot[RO] {\thepage}
-\usepackage{authblk}
-%%%%%%%%%%%%
-
+\usepackage{lineno}
 \begin{document}
 
-\title{Individual Differences Across Visual Search Tasks}
+\linenumbers
+%%%% Article title to be placed here
+\title{Insert the article title here}
 
-\author{A. D. F. Clarke, J. L. Irons, A. B. Leber and A. R. Hunt}
-\affil{Aberdeen, Essex and Ohio}
+\author{%%%% Author details
+Alasdair D. F. Clarke$^1$, Jess Irons$^2$, Warren James$^2$, Andrew Leber$^2$ and Amelia R Hunt$^3$}
 
-\maketitle
+%%%%%%%%% Insert author address here
+\address{
+$^{1}$Department of Psychology, University of Essex, Colchester, UK\\
+$^{2}$Department of Psychology, The Ohio State Universoty, Columbus, USA\\
+$^{3}$School of Psychology, University of Aberdeen, Aberdeen, UK
+}
+
+%%%% Subject entries to be placed here %%%%
+\subject{Behaviour, evolution}
+
+%%%% Keyword entries to be placed here %%%%
+\keywords{visual search, optimal behaviour,
+eye movements}
+
+%%%% Insert corresponding author and its email address}
+\corres{Alasdair Clarke\\
+\email{a.clarke@essex.ac.uk}}
 
@@
 
+%%%%%%%%%% Insert the texts which can accomdate on firstpage in the tag "fmtext" %%%%%
+
+\begin{fmtext}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Hello and welcome to our paper
+\end{fmtext}
+
+\maketitle
 
@@
 Participants will be students from the University of Aberdeen.
-Some will be compensated with course credit and some will be paid £10 for their time*.
+Some will be compensated with course credit and some will be paid \pounds 10 for their time.
 Sample size was determined in part due to constraints with counter-balancing; there are 16 different possible orders of tasks/conditions; we will run four participants in each order for a total of 64.
 All participants will sign a form giving informed consent.
-The study has already been approved by the University of Aberdeen Psychology Ethics Committee
+The study has already been approved by the University of Aberdeen Psychology Ethics Committee.
 
@@
 
-The study consists of three different paradigms from the visual search literature in which strong individual differences were found \citep{nowakowsak2017, irons-leber2016, kristjansson2014}.
-The \cite{nowakowsak2017} experiment will be carried out twice to give us an estiamte of how consistent participants are in their search strategy.
-Both sessions were indentical.
+The study consists of three different paradigms from the visual search literature in which large individual differences were found \cite{nowakowsak2017, irons-leber2016, kristjansson2014}.
+Example stimuli can be seen in Figure \ref{fig:exampleStimuli}.
 
-\subsubsection{A: Split-half array search}
+\begin{figure}
+\centering
+\subfigure[][]{\includegraphics[height=3cm]{figures/split-half.png}}
+\subfigure[][]{\includegraphics[height=3cm]{figures/adaptive.png}}
+\subfigure[][]{\includegraphics[height=3cm]{figures/foraging.png}}
+\caption{Example stimulus from the (a) \textit{split-half}, (b) \textit{adaptive choice} and (c) \textit{foraging} paradigms}
+\label{fig:exampleStimuli}
+\end{figure}
 
-\subsubsection{B: Attentional Control}
+The display was presented on a 17-inch CRT monitor with a resolution of $1024 \times 
+768$. Stimulus generation, presentation and data collection were controlled by MATLAB and psychophysics toolbox \cite{brainard1997} run on a Powermac.
 
-\subsubsection{C: Conjunction Foraging}
+\subsubsection{Split-half Array Search}
+
+Stimuli consisted of arrays of black oriented line segments against a grey background.
+The target was oriented $45^{\circ}$ clockwise, while the distracter items had a random orientiaton with a mean of $45^{\circ}$ anti-clockwise.
+The varience was low (xxx) on one half of the display to create a homogeneous texture, and high (xxx) on the other side to create a heterogeneous texture.
+This means that when the target is present on the homogeneous side of the stimulus, it can be easily be detected with peripheral vision, but when it is in the heterogeneous half, it is much harder to detect.
+There were a total of xxx trials and homo- and heterogeneous sides of the display were randomly vaired from trial to trial.
+
+The position of the dominant eye was recorded using a desktop-mounted EyeLink 1000 eye
+tracker (SR Research, Canada) sampling eye position at 1000 Hz.
+This paradigm was carried out twice to give us an estiamte of how consistent participants are in their search strategy over time. The two sessions were indentical.
+
+\subsubsection{Attentional Control}
+
+\subsubsection{Conjunction Foraging}
 
@@
 
-\subsubsection{A: Split-half array search}
+\subsubsection{Split-half array search}
 
@@
 \cite{nowakowsak2017} demonstrated a strong correlation between an this metric (for $n=5$) and reaction times ($r=$).
-However, a re-analysis of their data shows that an even stronger correlation is obtained with $n=3$ (see Figure \ref{fig:nowakowskaBestN})
+However, a re-analysis of their data shows that an even stronger correlation is obtained with $n=3$.
 
-\begin{figure}
-\centering
-\subfigure[][]{\includegraphics[width=6cm]{../NowakowskaClarkeHunt2017/scripts/r_by_nfix.pdf}}
-\subfigure[][]{\includegraphics[width=6cm]{../NowakowskaClarkeHunt2017/scripts/best_r_scatter.pdf}}
-\caption{Selecting the best $n$.}
-\label{fig:nowakowskaBestN}
-\end{figure}
-
-\subsubsection{B: Attentional Control}
+\subsubsection{Attentional Control}
 
@@
 
-\subsubsection{C: Conjunction Foraging}
+\subsubsection{Conjunction Foraging}
 
@@
 
+\subsection{Split-half Array Search}
+Our results are broadly in line with \cite{nowakowsak2017}.
+The correlation between accuracy and reaction times between the two sessions is shown in Figure \ref{fig:splithalf_summary}(a, b).
+We can clearly see that there are large differences from one participant to the next in terms of both the proportion of hard targets found, and reading times.
+Furthermore, test-retest reliability appears to be reasonable, with correlations of around $r = 0.78$ (the value of $r = 0.71$ or easy targets is slightly lower, likely due to the restricted range).
+
+\begin{figure}
+\centering
+\subfigure[][]{\includegraphics[width=5cm]{../Scripts/lineseg/scratch/acc_correlation.pdf}}
+\subfigure[][]{\includegraphics[width=5cm]{../Scripts/lineseg/scratch/rt_correlation.pdf}}
+\subfigure[][]{\includegraphics[width=5cm]{../Scripts/lineseg/scratch/strat_corr.pdf}}
+\subfigure[][]{\includegraphics[width=5cm]{../Scripts/lineseg/scratch/strat_compare_meanlog_rt.pdf}}
+\caption{Correlation between the two sessions of the \textit{split-half} paradigm for (a)  accuracy (TP-heterogeneous), (b) reaction times and (c) search strategy.
+(d) initial search strategy correlates with reaction times in both sessions.
+Each point represents a participant and the error-bars indicate 95\% confidence intervals.}
+\label{fig:splithalf_summary}
+\end{figure}
+
+We can also look at the initial search strategies adopted by our participants \ref{fig:splithalf_summary}(c, d).
+Again, we see large and stable individual differences across the two sessions.
+More importantly, as with \cite{nowakowsak2017}, we see that the search strategies give a good correlation with reaction times.
+
+\subsection{Adaptive Choice}
+
+\subsubsection{Conjunction Foraging}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{appendices}
-\section{Hetero-Homo-geneous Array Search}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Attentional Control Settings}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conjunction Foraging}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\end{appendices}
-
-\bibliographystyle{plainnat}
+\bibliographystyle{plain}
 \bibliography{literature}

### 2018-03-23 Scripts/bayes_correlation.R

@@ -7,14 +7,37 @@ figYn <- 4
 dat <- as.data.frame(read_csv("summaryData.csv"))
 dat <- dat[complete.cases(dat),]
 
-m <- map(
-	alist(
-		ac_meanlog2rt ~ dnorm(mu, sigma),
-		mu <- a + b * ls_mean_log_rt,
-		a ~ dnorm(0, 10),
-		b ~ dnorm(0, 10),
-		sigma ~ dcauchy(0, 1)),
-	start = list(a = mean(dat$ac_meanlog2rt), b = 0, sigma = sd(dat$ac_meanlog2rt)),
-	data = dat)
 
-post <- extract.samples(m)
+
+bayes_r <- function(x, y) {
+
+	x <- scale(x)
+	y <- scale(y)
+	df <- data.frame(x = x, y = y)
+
+	m <- map2stan(
+		alist(
+			y ~ dnorm(mu, sigma),
+			mu <- a + b*x,
+			a ~ dnorm(0, 10),
+			b ~ dnorm(0, 10),
+			sigma ~ dcauchy(0, 1)),
+		start = list(a = mean(y), b = 0, sigma = sd(y)),
+		data = df)
+
+	post <- extract.samples(m)
+
+	R2 = array(NA, 1000)
+	for (ii in 1:1000) {
+		R2[ii] <- 1 - sum((post$a[ii]+ post$b[ii] * x - y)^2) /  sum((y - mean(y))^2)
+
+	}
+
+	return(R2)
+
+}
+
+
+summary(lm(dat$ls_mean_log_rt~ dat$ac_meanlog2rt))
+
+R2 <- bayes_r(dat$ls_mean_log_rt, dat$ac_meanlog2rt)

### 2018-03-23 Scripts/compareExp.R

@@ -208,7 +208,7 @@ plt <- ggplot(dat, aes(x = ac_propOpt, y = fg_conj_run_num))
 plt <- plt + geom_point() 
 plt <- plt + geom_smooth(method = lm, colour = "black", fullrange = TRUE, linetype = 0)
 plt <- plt + theme_bw()
-plt <- plt + scale_x_continuous("split-half: prop. hetero. fixations",
+plt <- plt + scale_x_continuous("adaptive choice: prop. optimal",
     limits = c(0, 1), expand = c(0, 0), breaks = c(0,1))
 plt <- plt + scale_y_continuous("foraging (conjunction): number of runs",
     limits = c(0, 20), expand = c(0, 0))
@@ -225,7 +225,7 @@ plt <- ggplot(dat, aes(x = ac_propOpt, y = fg_conj_run_length))
 plt <- plt + geom_point() 
 plt <- plt + geom_smooth(method = lm, colour = "black", fullrange = TRUE, linetype = 0)
 plt <- plt + theme_bw()
-plt <- plt + scale_x_continuous("split-half: prop. hetero. fixations",
+plt <- plt + scale_x_continuous("adaptive choice: prop. optimal",
     limits = c(0, 1), expand = c(0, 0), breaks = c(0,1))
 plt <- plt + scale_y_continuous("foraging (conjunction): mean run length",
     limits = c(-10, 30), expand = c(0, 0))

### 2018-03-26 writeup/manuscript.tex
Minor edits to manuscript
Added in some missing details

@@
 \author{%%%% Author details
-Alasdair D. F. Clarke$^1$, Jess Irons$^2$, Warren James$^2$, Andrew Leber$^2$ and Amelia R Hunt$^3$}
+Alasdair D. F. Clarke$^1$, Jess Irons$^2$, Warren James$^3$, Andrew Leber$^2$ and Amelia R Hunt$^3$}
 
@@
 Participants will be students from the University of Aberdeen.
-Some will be compensated with course credit and some will be paid \pounds 10 for their time.
+Some will be compensated with course credit and some will be paid \pounds 15 for their time.
 Sample size was determined in part due to constraints with counter-balancing; there are 16 different possible orders of tasks/conditions; we will run four participants in each order for a total of 64.
@@
 Stimuli consisted of arrays of black oriented line segments against a grey background.
-The target was oriented $45^{\circ}$ clockwise, while the distracter items had a random orientiaton with a mean of $45^{\circ}$ anti-clockwise.
-The varience was low (xxx) on one half of the display to create a homogeneous texture, and high (xxx) on the other side to create a heterogeneous texture.
+The target was oriented $45^{\circ}$ clockwise, while the distractor items had a random orientation with a mean of $45^{\circ}$ anti-clockwise.
+The variance was low ($18^{\circ}$) on one half of the display to create a homogeneous texture, and high ($95^{\circ}$) on the other side to create a heterogeneous texture.
 This means that when the target is present on the homogeneous side of the stimulus, it can be easily be detected with peripheral vision, but when it is in the heterogeneous half, it is much harder to detect.
-There were a total of xxx trials and homo- and heterogeneous sides of the display were randomly vaired from trial to trial.
+There were a total of 160 trials and homo- and heterogeneous sides of the display were randomly varied from trial to trial.
 
@@
 tracker (SR Research, Canada) sampling eye position at 1000 Hz.
-This paradigm was carried out twice to give us an estiamte of how consistent participants are in their search strategy over time. The two sessions were indentical.
+This paradigm was carried out twice to give us an estimate of how consistent participants are in their search strategy over time. The two sessions were identical.
 
@@
 In order to characterise an individual's behaviour in this task, we will compute the proportion of the first $n$ fixations that were on heterogeneous (difficult) side of the stimuli, over all target absent trials\footnote{Only take correct trials?}.
-\cite{nowakowsak2017} demonstrated a strong correlation between an this metric (for $n=5$) and reaction times ($r=$).
+\cite{nowakowsak2017} demonstrated a strong correlation between an this metric (for $n=5$) and reaction times ($r=.53$).
 However, a re-analysis of their data shows that an even stronger correlation is obtained with $n=3$.
@@
 The correlation between accuracy and reaction times between the two sessions is shown in Figure \ref{fig:splithalf_summary}(a, b).
-We can clearly see that there are large differences from one participant to the next in terms of both the proportion of hard targets found, and reading times.
+We can clearly see that there are large differences from one participant to the next in terms of both the proportion of hard targets found, and reaction times.
 Furthermore, test-retest reliability appears to be reasonable, with correlations of around $r = 0.78$ (the value of $r = 0.71$ or easy targets is slightly lower, likely due to the restricted range).

### 2018-03-28 writeup/manuscript.tex
Update manuscript.tex

@@
 \author{%%%% Author details
-Alasdair D. F. Clarke$^1$, Jess Irons$^2$, Warren James$^3$, Andrew Leber$^2$ and Amelia R Hunt$^3$}
+Alasdair D. F. Clarke$^1$, Jessica L Irons$^2$, Warren James$^3$, Andrew B Leber$^2$ and Amelia R Hunt$^3$}
 
@@
 
-\subsubsection{Attentional Control}
+\subsubsection{Adaptive Choice Visual Search}
+
+The ACVS was based on the task described in Irons & Leber (2016), with a few changes [Or identical to the task described in Experiment 1 of Irons & Leber, in press by then hopefully].
+
+Each search display was composed of 54 small squares (size?
+What was viewing distance & screen size?) arranged in three concentric rings around fixation, with 12, 18 and 24 items in the inner, middle and outer rings respectively.
+The inner ring was XX° and the outer ring was XX° from fixation.
+Of the 54 squares, 13 were red, 13 were blue, 14 were green and 14 were “variable”.
+Variable distractors changes colors afrom trial-to-trial according to a cyclical pattern: the distractors would be red for 5 trials (called a “red plateau”), then across a period of 7 trials, they would change color from almost red to magenta (at the 4th trial in the transition) to almost blue (see Irons & Leber, 2017, for the specific color values?
+Or supplemental?).
+The variable distractor would then be blue for 5 trials (blue plateau), and then transition back from almost blue through magenta to almost red.
+This 24-trial cycle would repeat throughout the entire experiment.
+
+A white digit appeared inside each square.
+Two targets – a red square and a blue square each with a digit between 2 and 5 – were embedded in every search display.
+The two target digits were always different, to enable us to distinguish the chosen target.
+The remaining red, blue and variable squares all contained digits between 6–9.
+Green squares could contain any digit between 2-9.
+The location of the targets and distractor within the search display were randomized on each trial.
+
+Participants were informed that the search displays would contain two targets on every trial, that they need only find one target on each trial and that they were always free to search for either one.
+A trial began with a 1.5s ITI containing a central fixation cross, followed by the search display until a response was made.
+Participant responded by pressing a key that corresponded to the digit inside the target (V, B, N and M keys corresponding to 2, 3, 4 and 5 respectively).
+Participants completed 10 practice trials, followed by 3 blocks of 96 trials.
+Each block started on a red plateau.
 
 \subsubsection{Conjunction Foraging}
+
+The foraging task was based on Kristjansson, Johannesson & Thornton (2014) and Johannsesson et al (2016).
+Participants completed the feature foraging and conjunction foraging tasks on separate days, with the order counterbalanced (was it counterbalanced?).
+
+In the feature foraging task, search displays contained 80 small circles (size), 20 red (RGB: 180, 0, 0), 20 green (RGB: 20, 100, 40), 20 blue (RGB: 0, 0, 220) and 20 yellow (RGB: 200, 150, 0), presented against a black background.
+Stimuli were arranged in a 10 x 8 grid, but the position of each item within the grid space was jittered to create a more random spatial arrangement (with the restriction that two items could not be within 30 pixels of each other).
+The location of item colors to grid locations was completely randomized.
+For half of the participants, targets were red and green circles, and for the other half of participants, targets were blue and yellow circles.
+Participants were asked to collect all of the targets within a trial by using the mouse to click on each target.
+Clicking on a target caused it to disappear from the display.
+If the participant clicked erroneously on a non-target, the trial was immediately ended and a replacement trial was begun.
+Participants completed 1 practice trial and 20 full-completed experimental trials.
+
+In the conjunction foraging task, search displays were composed of both circles and squares.
+For half of the participants, the shapes were red and green (equal numbers of red circles, red squares, green circles and green squares), and for the remaining participants the shapes were blue and yellow.
+Targets were defined by conjunctions of color and shape (e.g., red squares and green circles, with red circles and green squares as distractors).
+The assignment of targets and distractors was counterbalanced across participants (was it?).
+The procedure was otherwise identical to the feature foraging task.
 
@@
 
-Following \cite{irons-leber2016}, individual differences will be characterized using two measures:\\
-1) Proportion of optimal choices on plateaus.
-An optimal choice is defined as responding to whichever of the two target colours has the fewest items in the display.
-This will be based on correct plateau trials only.
-\\
-2) Switching frequency.
-Switching is defined as responding to a different target color on trial $N$+1 than on trial $N$, and is presented as a proportion of the total number of trials (excluded incorrect trials, the trial after an incorrect trial, and the first trial of each block).\\
-Both measures have been shown to correlate with overall RT in previous experiments (Proportion Optimal $r$=-.56, $p$<.001; Switch Frequency $r$=.45, $p$=.001; based on $N$=50 and using the same number of trials as in the current experiment).
-As additional validation, correlational analyses between both measures and RT will also be conducted in the current experiment.
+Participants with accuracy more than 3 SD below the group mean were excluded from analyses.
+For RT analyses, trials with RTs less than 300ms or more than 3 SD about the participant’s mean were excluded.
+
+Two measures of individual strategy use were used: 1) Optimal choices, defined as percent of plateau trials in which the individual chose the optimal target (i.e., the target with the fewest distractors.
+When the variable distractor was red, the optimal choice was blue, and vice versa), and 2) Switch rate, the percent of trials in which the individual switched target color (i.e., the color chosen on trial N was different to the color chosen on trial N-1).
 
@@
 
-Data analysis will follow \cite{kristjansson2014} and Johannesson et al.
-(2016).
-The main measure of interest will be the average run length per trial.
-A run is defined as a succession of one or more of the same target type which is followed and preceded by the other target type or no target.
-The average length is the average number of consecutive target selections per run.
-As with the other experiments, we will also measure the average response (time to select the final target on correct trials).
+Only completed, accurate trials were analyzed.
+RTs were defined across the entire trial (i.e., from the start of the trial until the final target was collected).
+The main measure of interest was average run length per trial.
+A run was defined as a succession of one or more of the same target type, which was followed and preceded by the other target or no target.
+The average run length was the average number of target selections in a run.
 

### 2018-04-04 writeup/manuscript.tex
Compiled Jess's edits.

@@
 
-The ACVS was based on the task described in Irons & Leber (2016), with a few changes [Or identical to the task described in Experiment 1 of Irons & Leber, in press by then hopefully].
+The ACVS was based on the task described in \cite{irons-leber2016}, with a few changes [Or identical to the task described in Experiment 1 of Irons \& Leber, in press by then hopefully].
 
 Each search display was composed of 54 small squares (size?
-What was viewing distance & screen size?) arranged in three concentric rings around fixation, with 12, 18 and 24 items in the inner, middle and outer rings respectively.
-The inner ring was XX° and the outer ring was XX° from fixation.
+What was viewing distance \& screen size?) arranged in three concentric rings around fixation, with 12, 18 and 24 items in the inner, middle and outer rings respectively.
+The inner ring was $XX^{\circ}$ and the outer ring was $XX^{\circ}$ from fixation.
 Of the 54 squares, 13 were red, 13 were blue, 14 were green and 14 were “variable”.
-Variable distractors changes colors afrom trial-to-trial according to a cyclical pattern: the distractors would be red for 5 trials (called a “red plateau”), then across a period of 7 trials, they would change color from almost red to magenta (at the 4th trial in the transition) to almost blue (see Irons & Leber, 2017, for the specific color values?
+Variable distractors changes colors afrom trial-to-trial according to a cyclical pattern: the distractors would be red for 5 trials (called a “red plateau”), then across a period of 7 trials, they would change color from almost red to magenta (at the 4th trial in the transition) to almost blue (see \cite{irons-leber2017}, for the specific color values?
 Or supplemental?).
@@
 
-The foraging task was based on Kristjansson, Johannesson & Thornton (2014) and Johannsesson et al (2016).
+The foraging task was based on \cite{kristjansson2014} and \cite{johannesson2016}.
 Participants completed the feature foraging and conjunction foraging tasks on separate days, with the order counterbalanced (was it counterbalanced?).

### 2018-04-04 writeup/manuscript.tex
started on intro

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Hello and welcome to our paper
+Anybody who has ever run a visual search experiment will be aware of the large differences from one participant to the next, and noting their existence is not new \cite{mackworth1948}.
+However, these differences are largely ignored and questions about their importance and stability remain relatively under explored.
+
+This seems very relevant \cite{boot2006, boot2009}.
+
+Also \cite{proulx2011}
+
+In the related field of memory, individual differences have received more attention, for example \cite{sobel2007}.
+
+In our own work, we have previously shown that there are large differences between individuals in terms of the search strategies used to find a target among distracters.
+The Adaptive Choice Visual Search (ACVS) paradigm  \cite{irons-leber2016} \ldots.
+Even larger differences were found with the Split-Half Search Arrays \cite{nowakowsak2017} who aimed to discriminate between the optimal  \cite{najemnik-geisler2008} and stochastic \cite{clarke2016} search strategies.
+They found that while some participants initially searched the displays near optimally, others carried out strategies counter to this, failing to match the performance of the stochastic searcher.
+Examples of the stimuli are given in Figure \ref{fig:exampleStimuli}.
+
+Another example of differences in search strategy comes from the foraging literature \cite{kristjansson2014,johannesson2016}.
 \end{fmtext}
@@
 Stimuli were arranged in a 10 x 8 grid, but the position of each item within the grid space was jittered to create a more random spatial arrangement (with the restriction that two items could not be within 30 pixels of each other).
-The location of item colors to grid locations was completely randomized.
+The location of item colours to grid locations was completely randomized.
 For half of the participants, targets were red and green circles, and for the other half of participants, targets were blue and yellow circles.
@@
 Two measures of individual strategy use were used: 1) Optimal choices, defined as percent of plateau trials in which the individual chose the optimal target (i.e., the target with the fewest distractors.
-When the variable distractor was red, the optimal choice was blue, and vice versa), and 2) Switch rate, the percent of trials in which the individual switched target color (i.e., the color chosen on trial N was different to the color chosen on trial N-1).
+When the variable distractor was red, the optimal choice was blue, and vice versa), and 2) Switch rate, the percent of trials in which the individual switched target colour (i.e., the colour chosen on trial N was different to the colour chosen on trial N-1).
 
@@
 
-Only completed, accurate trials were analyzed.
+Only completed, accurate trials were analysed.
 RTs were defined across the entire trial (i.e., from the start of the trial until the final target was collected).
@@
 The average run length was the average number of target selections in a run.
-
-\subsubsection{}
 

### 2018-04-04 writeup/manuscript.tex
small edit

@@
 %%%%%%%%% Insert author address here
-\address{
-$^{1}$Department of Psychology, University of Essex, Colchester, UK\\
+\address{$^{1}$Department of Psychology, University of Essex, Colchester, UK\\
 $^{2}$Department of Psychology, The Ohio State Universoty, Columbus, USA\\
@@
 \maketitle
+
+The aim of the present study is to investigate the extent to which these differences are stable across different visual search paradigms.
+Are observers who are good at finding the target in the split-half search arrays also better in the ACVS task?
+Are the super-foragers consistently better or worse than more typical searchers in the other two paradigms?
+As a secondary question, we will measure the test-retest reliability of the differences found in the split-half array paradigm.
 

### 2018-04-05 writeup/manuscript.tex
minor edit

@@
 \address{$^{1}$Department of Psychology, University of Essex, Colchester, UK\\
-$^{2}$Department of Psychology, The Ohio State Universoty, Columbus, USA\\
+$^{2}$Department of Psychology, The Ohio State University, Columbus, USA\\
 $^{3}$School of Psychology, University of Aberdeen, Aberdeen, UK
@@
 However, these differences are largely ignored and questions about their importance and stability remain relatively under explored.
+These differences could be due to several reasons: tiredness\cite{mackworth1948}, speed-accuracy trade-off, motivation, visual impairments, and search strategies\cite{boot2006}.
 
-This seems very relevant \cite{boot2006, boot2009}.
+A striking example of the effect of strategy is given by \cite{boot2006, boot2009}.
+They found differences in visual search performance could be explained by whether observers used a scanning strategy, or simply fixated the centre of the stimulus and used peripheral vision.
 
@@
 Of the 54 squares, 13 were red, 13 were blue, 14 were green and 14 were “variable”.
-Variable distractors changes colors afrom trial-to-trial according to a cyclical pattern: the distractors would be red for 5 trials (called a “red plateau”), then across a period of 7 trials, they would change color from almost red to magenta (at the 4th trial in the transition) to almost blue (see \cite{irons-leber2017}, for the specific color values?
+Variable distractors changes colours afrom trial-to-trial according to a cyclical pattern: the distractors would be red for 5 trials (called a “red plateau”), then across a period of 7 trials, they would change colour from almost red to magenta (at the fourth trial in the transition) to almost blue (see \cite{irons-leber2017}, for the specific colour values?
 Or supplemental?).
@@
 A trial began with a 1.5s ITI containing a central fixation cross, followed by the search display until a response was made.
-Participant responded by pressing a key that corresponded to the digit inside the target (V, B, N and M keys corresponding to 2, 3, 4 and 5 respectively).
+Participant responded by pressing a key that corresponded to the digit inside the target (\texttt{V}, \texttt{B}, \texttt{N} and \texttt{M} keys corresponding to 2, 3, 4 and 5 respectively).
 Participants completed 10 practice trials, followed by 3 blocks of 96 trials.

### 2018-04-10 writeup/manuscript.tex
Small changes to manuscript
Made some more minor changes. Clarified how the shape/colour assignment was done for the foraging paper

@@
 The inner ring was $XX^{\circ}$ and the outer ring was $XX^{\circ}$ from fixation.
-Of the 54 squares, 13 were red, 13 were blue, 14 were green and 14 were “variable”.
-Variable distractors changes colours afrom trial-to-trial according to a cyclical pattern: the distractors would be red for 5 trials (called a “red plateau”), then across a period of 7 trials, they would change colour from almost red to magenta (at the fourth trial in the transition) to almost blue (see \cite{irons-leber2017}, for the specific colour values?
+Of the 54 squares, 13 were red, 13 were blue, 14 were green and 14 were "variable".
+Variable distractors changes colours from trial-to-trial according to a cyclical pattern: the distractors would be red for 5 trials (called a "red plateau"), then across a period of 7 trials, they would change colour from almost red to magenta (at the fourth trial in the transition) to almost blue (see \cite{irons-leber2017}, for the specific colour values?
 Or supplemental?).
@@
 A white digit appeared inside each square.
-Two targets – a red square and a blue square each with a digit between 2 and 5 – were embedded in every search display.
+Two targets - a red square and a blue square each with a digit between 2 and 5 - were embedded in every search display.
 The two target digits were always different, to enable us to distinguish the chosen target.
-The remaining red, blue and variable squares all contained digits between 6–9.
+The remaining red, blue and variable squares all contained digits between 6-9.
 Green squares could contain any digit between 2-9.
@@
 For half of the participants, the shapes were red and green (equal numbers of red circles, red squares, green circles and green squares), and for the remaining participants the shapes were blue and yellow.
-Targets were defined by conjunctions of color and shape (e.g., red squares and green circles, with red circles and green squares as distractors).
-The assignment of targets and distractors was counterbalanced across participants (was it?).
+Targets were defined by conjunctions of colour and shape (e.g., red squares and green circles, with red circles and green squares as distractors).
+The assignment of targets and distractors was assigned at random for each participant.
 The procedure was otherwise identical to the feature foraging task.
 
+%% For the assignment of distractors and targets, we generated a two lists of random numbers (1-2 for easy search, and 1-4 for hard search).
+Pretty sure we did that because counterbalancing became very tricky once you accounted for that as well.
 \subsection{Planned Analysis}
@@
 Participants with accuracy more than 3 SD below the group mean were excluded from analyses.
-For RT analyses, trials with RTs less than 300ms or more than 3 SD about the participant’s mean were excluded.
+For RT analyses, trials with RTs less than 300ms or more than 3 SD about the participant's mean were excluded.
 

### 2018-04-19 writeup/manuscript.tex
more results

@@
 
-Another example of differences in search strategy comes from the foraging literature \cite{kristjansson2014,johannesson2016}.
 \end{fmtext}
@@
 \maketitle
+
+Another example of differences in search strategy comes from the foraging literature \cite{kristjansson2014,johannesson2016}.
 
@@
 The study has already been approved by the University of Aberdeen Psychology Ethics Committee.
+
+A sample of 64 participants means we should be able to detect a correlations with $r > 0.342$ with $\alpha = 0.05$, $\beta = 0.80$ between the different visual search paradigms.
+Given the nature of our results, we see no need to apply a conservative correction for multiple comparisons.
 
@@
 
-\subsection{Split-half Array Search}
+\subsection{Replication of each paradigm}
+
+\subsubsection{Split-half Array Search}
 Our results are broadly in line with \cite{nowakowsak2017}.
@@
 
-\subsection{Adaptive Choice}
+\subsubsection{Adaptive Choice}
 
 \subsubsection{Conjunction Foraging}
+
+\subsection{Correlations Between Paradigms}
+
+The results above demonstrate that we have successfully replicated the previous findings around individual differences in visual search strategy.
+We now investigate whether there are correlations between paradigms: are individuals who are good at one visual search task good at another?
+We start by looking at simple reaction times (Figure \ref{fig:between_para_rt}).
+In all comparisons the correlations are weak, typically $0.27 < r <0.30$ but positive.
+None of these correlations are statistically significant ($p>0.05$).
+Even if we optimistically take all the data together as suggesting a robust correlation in reaction times from paradigm to paradigm, the upper bound of $r=0.30$ this correlation only accounts for at best $10\%$\footnote{i.e., $R^2 = 0.3^2 = 0.09$} an individual's performance.
+
+\begin{figure}
+\centering
+\subfigure[][]{\includegraphics[width=5cm]{../Scripts/scratch/ls_v_ac_mean_log2rt.pdf}}
+\subfigure[][]{\includegraphics[width=5cm]{../Scripts/scratch/ls_v_fg_conj_rt.pdf}}
+\subfigure[][]{\includegraphics[width=5cm]{../Scripts/scratch/ac_v_fg_feature_rt.pdf}}
+\subfigure[][]{\includegraphics[width=5cm]{../Scripts/scratch/ac_v_fg_conj_rt.pdf}}
+\subfigure[][]{\includegraphics[width=5cm]{../Scripts/scratch/ls_v_ac_mean_log2rt.pdf}}
+\caption{Correlation a) split-half and feature foraging; b) split-half and conjunction foraging, c) adaptive choice and feature  foraging; d) adaptive choice and conjunction foraging; e) split-half and adaptive choice.
+In all cases, these correlations are low, with $p>0.05$}
+\label{fig:between_para_rt}
+\end{figure}
+
+Given the low correlations between reaction times, it seems unlikely that we will find that individuals who search efficiently and optimally in one paradigm will search well in another (the original motivation for our study).
+The analysis supports this hypothesis.
+For example, the correlation between the proportion of fixations to the heterogeneous side of the display in the split-half paradigm, and proportion of optimal targets found in the adaptive choice task is $r=-0.03$.
+Further results are presented in supplementary materials.
 
@@
 
+The results presented above are somewhat surprising.
+
 \bibliographystyle{plain}

### 2018-04-20 writeup/manuscript.tex
A little more intro

@@
 Another example of differences in search strategy comes from the foraging literature \cite{kristjansson2014,johannesson2016}.
+Participants were asked to search through a set of items from four categories, two of which were classed as targets.
+In the conjunction condition (i.e.
+searching for red-horizontal and green-vertical line segments among red-vertical and green-horizontal distracters), most observers searched in runs of one target or another.
+This strategy has previously been observers in animal foraging literature \ldots.
+However, a sub-set of observers, termed ``super-searchers'' showed no switch cost.
 
@@
 
-The position of the dominant eye was recorded using a desktop-mounted EyeLink 1000 eye
-tracker (SR Research, Canada) sampling eye position at 1000 Hz.
+The position of the dominant eye was recorded using a desktop-mounted EyeLink 1000 eye tracker (SR Research, Canada) sampling eye position at 1000 Hz.
 This paradigm was carried out twice to give us an estimate of how consistent participants are in their search strategy over time. The two sessions were identical.

### 2018-04-24 writeup/manuscript.tex
bayes correlation

@@
 searching for red-horizontal and green-vertical line segments among red-vertical and green-horizontal distracters), most observers searched in runs of one target or another.
-This strategy has previously been observers in animal foraging literature \ldots.
+This strategy has previously been observers in animal foraging literature \cite{dawkins1971}.
 However, a sub-set of observers, termed ``super-searchers'' showed no switch cost.
@@
 
+I think he sees it as a positive thing that they tasks don't correlate, because ti suggests they capture unique variation in behaviour
+glass half full approach
+
 \bibliographystyle{plain}

### 2018-04-24 Scripts/bayes_correlation.R

@@ -1,5 +1,6 @@
 library(tidyverse)
 library(rethinking)
+library(ggridges)
 
 figXn <- 6
 figYn <- 4
@@ -8,8 +9,7 @@ dat <- as.data.frame(read_csv("summaryData.csv"))
 dat <- dat[complete.cases(dat),]
 
 
-
-bayes_r <- function(x, y) {
+bayes_R2 <- function(x, y) {
 
 	x <- scale(x)
 	y <- scale(y)
@@ -19,25 +19,47 @@ bayes_r <- function(x, y) {
 		alist(
 			y ~ dnorm(mu, sigma),
 			mu <- a + b*x,
-			a ~ dnorm(0, 10),
-			b ~ dnorm(0, 10),
+			a ~ dnorm(0, 1),
+			b ~ dnorm(0, 1),
 			sigma ~ dcauchy(0, 1)),
 		start = list(a = mean(y), b = 0, sigma = sd(y)),
 		data = df)
+
+	print(precis(m))
 
 	post <- extract.samples(m)
 
 	R2 = array(NA, 1000)
 	for (ii in 1:1000) {
 		R2[ii] <- 1 - sum((post$a[ii]+ post$b[ii] * x - y)^2) /  sum((y - mean(y))^2)
-
 	}
 
 	return(R2)
 
 }
 
+ summary(lm(scale(dat$ls_mean_log_rt) ~ scale(dat$fg_conj_log2)))
 
-summary(lm(dat$ls_mean_log_rt~ dat$ac_meanlog2rt))
+R2_ls_ac <- bayes_R2(dat$ls_mean_log_rt, dat$ac_meanlog2rt)
 
-R2 <- bayes_r(dat$ls_mean_log_rt, dat$ac_meanlog2rt)
+R2_ls_fgf <- bayes_R2(dat$ls_mean_log_rt, dat$fg_feat_log2)
+
+R2_ls_fgc <- bayes_R2(dat$ls_mean_log_rt, dat$fg_conj_log2)
+
+R2_ac_fgf <- bayes_R2(dat$ac_meanlog2rt, dat$fg_conj_log2)
+
+R2_ac_fgc <- bayes_R2(dat$ac_meanlog2rt, dat$fg_conj_log2)
+
+results <- tibble(comparison = rep(c("ls v ac", "ls v fg feat", "ls v fg conj", "ac v fg feat", "ac v fg conj"), each = 1000),
[…]

### 2018-04-30 Scripts/lineseg/2_rtAnalysis.R
graph edits etc

@@ -4,8 +4,8 @@ library(ggthemes)
 library(scales)   
 library(binom)
 
-figXn <- 6
-figYn <- 4
+figXn <- 3.5
+figYn <- 2.5
 
 # read in processed data
 trl_dat <- readRDS(file = "scratch/processedRTandAccData.Rda")
@@ -75,10 +75,10 @@ plt <- plt + geom_errorbarh(size=0.25, colour = "grey")
 plt <- plt + geom_point() 
 plt <- plt + geom_smooth(method = "lm", colour="black", fullrange = TRUE)
 plt <- plt + coord_cartesian(xlim=c(0,1), ylim=c(0,1)) 
-plt <- plt + geom_text(
-	label = paste("r = ",r), x = 0.25, y = 0.875, family="Times")
-plt <- plt + scale_x_continuous(name = "session a: accuracy (hard)", limits = c(-0.50, 1.5))
-plt <- plt + scale_y_continuous(name = "session b: accuracy (hard)", limits = c(-0.50, 1.5))
+# plt <- plt + geom_text(
+# 	label = paste("r = ",r), x = 0.25, y = 0.875, family="Times")
+plt <- plt + scale_x_continuous(name = "a: accuracy (hard)", limits = c(-0.50, 1.5))
+plt <- plt + scale_y_continuous(name = "b: accuracy (hard)", limits = c(-0.50, 1.5))
 plt <- plt + theme_bw() + scale_color_ptol(name = "target condition")
 plt <- plt + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
 ggsave("scratch/acc_correlation.pdf", width=figYn, height=figYn)
@@ -155,82 +155,89 @@ r_df = tibble(
 		paste("r = ", easy_r), paste("r = ", hard_r), paste("r = ", absent_r) ),
 	x = c(12.5, 10.55, 13.75), y = c(10.75, 12, 11.25), targSide = c("easy", "hard", "absent"))
 
-a_labels = c(1000, 2000, 4000, 8000, 16000)
-a_breaks = log(a_labels, 2)
+a_labels = c(1, 2, 4, 8, 16)
+a_breaks = log(1000*a_labels, 2)
+levels(rt_dat$targSide) = c("homo", "hetero", "absent")
+
 plt <- ggplot(rt_dat, aes(
 	x = a_log2rt,#, ,
 	y = b_log2rt,#, ,
 	colour=targSide))
[…]

### 2018-04-30 writeup/manuscript.tex

@@
 We can clearly see that there are large differences from one participant to the next in terms of both the proportion of hard targets found, and reaction times.
-Furthermore, test-retest reliability appears to be reasonable, with correlations of around $r = 0.78$ (the value of $r = 0.71$ or easy targets is slightly lower, likely due to the restricted range).
+Furthermore, test-retest reliability appears to be reasonable, with Pearson's $r \in [0.65-0.86]$ ($95\%$ confidence interval) for accuracy in finding targets on the hard heterogeneous half of the display.
+We get similar scores for the correlation between sessions \textit{a} and \textit{b} for heterogeneous targets, ($r \in [0.66-0.87]$), homogeneous targets ($r \in [0.56-0.82]$) and target absent ($r \in [0.65-0.86]$).
+The reduced correlation for the homogeneous targets is likely due to the restricted range.
 
@@
 \centering
-\subfigure[][]{\includegraphics[width=5cm]{../Scripts/lineseg/scratch/acc_correlation.pdf}}
-\subfigure[][]{\includegraphics[width=5cm]{../Scripts/lineseg/scratch/rt_correlation.pdf}}
-\subfigure[][]{\includegraphics[width=5cm]{../Scripts/lineseg/scratch/strat_corr.pdf}}
-\subfigure[][]{\includegraphics[width=5cm]{../Scripts/lineseg/scratch/strat_compare_meanlog_rt.pdf}}
+\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/lineseg/scratch/acc_correlation.pdf}}
+\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/lineseg/scratch/rt_correlation.pdf}}
+\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/lineseg/scratch/strat_corr.pdf}}
+\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/lineseg/scratch/strat_compare_meanlog_rt.pdf}}
 \caption{Correlation between the two sessions of the \textit{split-half} paradigm for (a)  accuracy (TP-heterogeneous), (b) reaction times and (c) search strategy.
@@
 We can also look at the initial search strategies adopted by our participants \ref{fig:splithalf_summary}(c, d).
-Again, we see large and stable individual differences across the two sessions.
-More importantly, as with \cite{nowakowsak2017}, we see that the search strategies give a good correlation with reaction times.
+Again, we see large and stable individual differences across the two sessions (test-retest $r \in [0.57, 0.83]$ for the proportion of the first five saccades to the heterogeneous half of the display for target absent trials).
+More importantly, as with \cite{nowakowsak2017}, we see that the search strategies give a good correlation with reaction times in both session a, $r \in [0.56, 0.84]$ and session b, $r \in [0.50, 0.81]$.
 

### 2018-05-01 Scripts/lineseg/1_init_processing.R
more graph edits

@@ -109,7 +109,7 @@ process_acs <- function(asc, ss) {
 	return(list(fixDat,trlDat))
 }
 
-participants <- 1:66
+participants <- 1:68
 participants <- participants[!(participants %in% c(18, 32, 48, 57))] 
 
 

### 2018-05-01 Scripts/lineseg/2_rtAnalysis.R

@@ -77,8 +77,8 @@ plt <- plt + geom_smooth(method = "lm", colour="black", fullrange = TRUE)
 plt <- plt + coord_cartesian(xlim=c(0,1), ylim=c(0,1)) 
 # plt <- plt + geom_text(
 # 	label = paste("r = ",r), x = 0.25, y = 0.875, family="Times")
-plt <- plt + scale_x_continuous(name = "a: accuracy (hard)", limits = c(-0.50, 1.5))
-plt <- plt + scale_y_continuous(name = "b: accuracy (hard)", limits = c(-0.50, 1.5))
+plt <- plt + scale_x_continuous(name = "a: accuracy", limits = c(-0.50, 1.5), breaks = c(0,1))
+plt <- plt + scale_y_continuous(name = "b: accuracy", limits = c(-0.50, 1.5), breaks = c(0,1))
 plt <- plt + theme_bw() + scale_color_ptol(name = "target condition")
 plt <- plt + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
 ggsave("scratch/acc_correlation.pdf", width=figYn, height=figYn)

### 2018-05-03 writeup/manuscript.tex

@@
 \subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/lineseg/scratch/strat_compare_meanlog_rt.pdf}}
-\caption{Correlation between the two sessions of the \textit{split-half} paradigm for (a)  accuracy (TP-heterogeneous), (b) reaction times and (c) search strategy.
-(d) initial search strategy correlates with reaction times in both sessions.
-Each point represents a participant and the error-bars indicate 95\% confidence intervals.}
+\caption{Each point represents a participant and the error-bars indicate 95\% confidence intervals.
+Correlation between the two sessions of the \textit{split-half} paradigm for (a)  accuracy (TP-heterogeneous trials only); (b) reaction times and (c) search strategy (TA trials only).
+(d) Initial search strategy correlates with reaction times in both sessions.
+}
 \label{fig:splithalf_summary}
@@
 \centering
-\subfigure[][]{\includegraphics[width=5cm]{../Scripts/scratch/ls_v_ac_mean_log2rt.pdf}}
-\subfigure[][]{\includegraphics[width=5cm]{../Scripts/scratch/ls_v_fg_conj_rt.pdf}}
-\subfigure[][]{\includegraphics[width=5cm]{../Scripts/scratch/ac_v_fg_feature_rt.pdf}}
-\subfigure[][]{\includegraphics[width=5cm]{../Scripts/scratch/ac_v_fg_conj_rt.pdf}}
-\subfigure[][]{\includegraphics[width=5cm]{../Scripts/scratch/ls_v_ac_mean_log2rt.pdf}}
-\caption{Correlation a) split-half and feature foraging; b) split-half and conjunction foraging, c) adaptive choice and feature  foraging; d) adaptive choice and conjunction foraging; e) split-half and adaptive choice.
-In all cases, these correlations are low, with $p>0.05$}
-\label{fig:between_para_rt}
+\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/scratch/ls_v_ac_mean_log2rt.pdf}}
+\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/scratch/ls_v_ac_opt.pdf}}
+\caption{Correlation between the split-half and adaptive choice paradigms for (a) reaction times and (b) optimal behaviour.}
 \end{figure}

### 2018-05-14 Writeup/sup_mat.tex
Participant section in sup. mat.

\documentclass[a4paper, oneside, 11pt, onecolumn]{article}

\usepackage{graphicx}
\usepackage{subfig}
\usepackage[round, comma, sort&compress, longnamesfirst]{natbib} 
\usepackage[left=2cm,top=3cm,right=1.5cm,bottom=2cm,bindingoffset=0.5cm]{geometry}
\usepackage{enumerate}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhead{}
\fancyfoot{}
\fancyfoot[L]{\textit{}}
 \fancyhead[L]{\textit{Clarke et al (20xx)}}
\renewcommand{\headrulewidth}{0.8pt}
\renewcommand{\footrulewidth}{0.8pt}
\setlength\headheight{14pt}
\fancyfoot[RO] {\thepage}
\usepackage{authblk}
%%%%%%%%%%%%

\begin{document}

\title{Supplementary Materials}

\author{A. D. F. Clarke\thanks{a.clarke@essex.ac.uk}}
 \affil{School of Psychology, University of Essex, UK}

\maketitle

\begin{abstract}

\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Participants}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Data was collected from 64 participants as originally planned. Four of these participants did not complete all parts of the experiment (either declining to participate in the second session, or could not be calibrated with the eye tracker), so four new participants were recruited to bring the total back up to 64.

\subsection{Split-Half}

Accuracy data from all participants is shown in Figure \ref{fig:splithalf_acc_all}. From this we can see that there are a number of outliers: 4, 21, 33, 56, and 58. These participants, in at least one session, either missed the majority of easy targets, or responded with false positives on the majority of target absent trials. After removing these participants, the lowest accuracy in either session was $84.6\%$ for the easy targets, and $76.9\%$ for target absent trials. This leaves us with 59 participants for the split-half paradigm.

\begin{figure}
\centering
\includegraphics[width=14cm]{../Scripts/lineseg/scratch/acc_by_session_by_person.pdf}
\caption{Accuracy data for each participant for the split-half paradigm.}
\label{fig:splithalf_acc_all}
\end{figure}

\subsection{Adaptive Choice}

\subsection{Foraging}

\subsection{Comparisons across paradigms}

Interestingly, it was not the same participants who had to be removed in each paradigm. This suggests that their poor performance in one paradigm is less likely to be due to low motivation. The number of participants available for each comparison between paradigms is given in Table \ref{tab:num_per_paradigm}.

\begin{table*}
\centering
\small
\begin{tabular}{cc|c}
 		&				& Number of participants\\
 		\hline
Split-half & Adaptive Choice & \\
Split-half & Foraging & \\
Adaptive Choice & Adaptive Choice & \\

\end{tabular}

\caption{Number of participants available for each comparison}
\label{tab:num_per_paradigm}
\end{table*}

\end{document}

### 2018-05-14 Scripts/lineseg/2_rtAnalysis.R

@@ -10,25 +10,6 @@ figYn <- 2.5
 # read in processed data
 trl_dat <- readRDS(file = "scratch/processedRTandAccData.Rda")
 
-# fix suspected coding bug
-
-# person10_a_fix <- filter(fix_dat, observer == 10, session == 'a')
-# person11_a_fix <- filter(fix_dat, observer == 11, session == 'a')
-# person10_a_fix$observer <- 11
-# person11_a_fix$observer <- 10
-# fix_dat <- filter(fix_dat, !(observer == 10 & session == 'a'))
-# fix_dat <- filter(fix_dat, !(observer == 11 & session == 'a'))
-# fix_dat <- rbind(fix_dat, person10_a_fix, person11_a_fix)
-
-# person10_a_trl <- filter(trl_dat, observer == 10, session == 'a')
-# person11_a_trl <- filter(trl_dat, observer == 11, session == 'a')
-# person10_a_trl$observer <- 11
-# person11_a_trl$observer <- 10
-# trl_dat <- filter(trl_dat, !(observer == 10 & session == 'a'))
-# trl_dat <- filter(trl_dat, !(observer == 11 & session == 'a'))
-# trl_dat <- rbind(trl_dat, person10_a_trl, person11_a_trl)
-
-
 # -----------------------------------------------------------------------------
 # look at accuracy 
 # -----------------------------------------------------------------------------
@@ -46,8 +27,10 @@ acc_dat <- select(acc_dat, -nTrials)
 plt <- ggplot(acc_dat, aes(x = targSide, y = accuracy, fill = session))
 plt <- plt + geom_bar(stat = "identity", position = position_dodge()) 
 plt <- plt + scale_x_discrete(name = "target condition")
+plt <- plt + scale_y_continuous(breaks = c(0,1))
 plt <- plt + facet_wrap( ~ observer)
 plt <- plt + theme_bw() + scale_fill_ptol()
+plt <- plt + theme(axis.text.x  = element_text(angle=90, vjust=0.5))
 ggsave("scratch/acc_by_session_by_person.pdf", width=2*figXn, height=2*figYn)
 
 # remove people with poor target easy/absent accuracy

### 2018-05-14 Writeup/sup_mat.tex
sup mat fixation processing.

@@
 
+\usepackage{multirow}
 \usepackage{graphicx}
-\usepackage{subfig}
+\usepackage{subfigure}
 \usepackage[round, comma, sort&compress, longnamesfirst]{natbib} 
@@
 Split-half 	& Foraging 			& \\
-Adaptive Choice & Adaptive Choice & \\
-
+Adaptive Choice & Foraging 		& \\
 \end{tabular}
-
 \caption{Number of participants available for each comparison}
@@
 
+\section{Data processing}
+
+\subsection{Split-Half}
+
+179 trials with invalid key responses were removed.
+After removing data from the five outlier participants (see above), all remaining incorrect trials ($n=2529$) were removed, leaving a total of 16187 trials over 59 participants.
+
+\subsubsection{Reaction Times}
+As expected, reaction times were highly skewed (Figure \ref{fig:splithalf_rt_dists_all}), so were $\log_2$ transformed (in ms units) before the participant means were calculated for each session and target condition (Figure )
+
+\begin{figure}
+\centering
+\subfigure[]{\includegraphics[width=14cm]{../Scripts/lineseg/scratch/rt_dists.pdf}}
+\subfigure[]{\includegraphics[width=14cm]{../Scripts/lineseg/scratch/rt_dists_mean.pdf}}
+\caption{Distribution of reaction times in split-half paradigm.}
+\label{fig:splithalf_rt_dists_all}
+\end{figure}
+
+\subsubsection{Eye movements}
+
+340,138 fixations were recorded.
+Of these, 7701 fell outside of the stimuli area and were removed.
+Fixations landing within a vertical strip consisting of $10\%$ of the stimuli's width were classed as \textit{central}.
+All remaining fixations were then classed as landing on the \textit{homogeneous} or \textit{heterogeneous} half of the stimulus.
+Initial fixations were not included in the analysis.
+Numbers of fixations are given in Table \ref{tab:num_fix}.
+
+\begin{table*}
+\centering
+\small
+\begin{tabular}{c|c|r|r|r}
+ 		&	& $1<n$	& $2 \leq n \leq 5$ & $2 \leq n \leq 3$\\
+\hline
+\multirow{3}{*}{easy} 
+& central		& 3931 	& 3689	& \\
+& homogeneous 	& 12452	& 8312 	&\\
+& heterogeneous & 5955	& 3241 	&\\
+\hline
+\multirow{3}{*}{hard} 
+& central		& 3804 	& 2439	& \\
+& homogeneous 	& 8781	& 3188	&	\\
+& heterogeneous & 29912	& 5294	&\\
+\hline
+\multirow{3}{*}{absent} 
+& central		& 16885 & 8303	& \\
+& homogeneous 	& 41356	& 12576	&\\
+& heterogeneous & 192348& 5763	&\\
+\hline
+\end{tabular}
+\caption{Number of fixations recorded for each condition.}
+\label{tab:num_fix}
+\end{table*}
+
+\subsection{Adaptive Choice}
+
+\subsection{Foraging}
+
 \end{document}

### 2018-05-14 Scripts/lineseg/1_init_processing.R

@@ -232,7 +232,7 @@ fixDat$y <- with(fixDat, ifelse(y > -1 & y <1, y, NaN))
 # remove trials which are invalid for one reason or another
 trlDat <- filter(trlDat, responseKey != "Key_x")
 # remove trial with incredible short rt
-trlDat <- filter(trlDat, rt > 100)
+# trlDat <- filter(trlDat, rt > 100)
 
 # now remove excluded trials from fixDat
 incTrials <- with(trlDat, paste(observer, session, trial))

### 2018-05-14 Scripts/lineseg/2_rtAnalysis.R

@@ -29,9 +29,9 @@ plt <- plt + geom_bar(stat = "identity", position = position_dodge())
 plt <- plt + scale_x_discrete(name = "target condition")
 plt <- plt + scale_y_continuous(breaks = c(0,1))
 plt <- plt + facet_wrap( ~ observer)
-plt <- plt + theme_bw() + scale_fill_ptol()
+plt <- plt + theme_bw() + scale_fill_ptol() + theme(legend.position="top")
 plt <- plt + theme(axis.text.x  = element_text(angle=90, vjust=0.5))
-ggsave("scratch/acc_by_session_by_person.pdf", width=2*figXn, height=2*figYn)
+ggsave("scratch/acc_by_session_by_person.pdf", width=2*figXn, height=2.5*figYn)
 
 # remove people with poor target easy/absent accuracy
 acc_dat <- filter(acc_dat, !(observer %in% c(4, 21, 33, 56, 58)))
@@ -94,6 +94,17 @@ trl_dat <- filter(trl_dat, accuracy == 1)
 # look at RT 
 # -----------------------------------------------------------------------------
 
+# look at distributions
+
+plt <- ggplot(trl_dat, aes(x = rt))
+plt <- plt + geom_histogram(binWidth = 1)
+plt <- plt + facet_wrap(~ targSide)
+plt <- plt + theme_bw()
+plt <- plt + scale_x_continuous(name = "reaction time (seconds)", limits = c(0, 50000))
+ggsave("scratch/rt_dists.pdf", width = 2*figXn, height = figYn)
+
+
+
 plt <- ggplot(trl_dat, aes(x = rt/1000, fill = targSide)) 
 plt <- plt + geom_density(alpha=0.7)
 plt <- plt + scale_fill_ptol(name = "target position") + theme_hc()
@@ -115,6 +126,25 @@ rt_dat <- (filter(trl_dat)
 		sderr = sd(log(rt,2)/sqrt(n)),
 		upper = logrt + 1.96*sderr,
 		lower = logrt - 1.96*sderr))
+
+
+plt <- ggplot(rt_dat, aes(x = logrt))
+plt <- plt + geom_histogram(binwidth = 0.25)
+plt <- plt + facet_wrap(~ targSide)
+plt <- plt + theme_bw()
+plt <- plt + scale_x_continuous(name = "mean log2 reaction time (ms)")
[…]

### 2018-05-14 Writeup/sup_mat.tex
shrinking methods in main text

@@
 \end{abstract}
+
+\section{Paradigm Details}
+
+\subsection{Split-half}
+
+\subsection{Adaptive Choice}
+
+The ACVS was based on the task described in \cite{irons-leber2016}, with a few changes [Or identical to the task described in Experiment 1 of Irons \& Leber, in press by then hopefully].
+
+Each search display was composed of 54 small squares (size?
+What was viewing distance \& screen size?) arranged in three concentric rings around fixation, with 12, 18 and 24 items in the inner, middle and outer rings respectively.
+The inner ring was $XX^{\circ}$ and the outer ring was $XX^{\circ}$ from fixation.
+Of the 54 squares, 13 were red, 13 were blue, 14 were green and 14 were "variable".
+Variable distractors changes colours from trial-to-trial according to a cyclical pattern: the distractors would be red for 5 trials (called a "red plateau"), then across a period of 7 trials, they would change colour from almost red to magenta (at the fourth trial in the transition) to almost blue (see \cite{irons-leber2017}, for the specific colour values?
+Or supplemental?).
+The variable distractor would then be blue for 5 trials (blue plateau), and then transition back from almost blue through magenta to almost red.
+This 24-trial cycle would repeat throughout the entire experiment.
+
+A white digit appeared inside each square.
+Two targets - a red square and a blue square each with a digit between 2 and 5 - were embedded in every search display.
+The two target digits were always different, to enable us to distinguish the chosen target.
+The remaining red, blue and variable squares all contained digits between 6-9.
+Green squares could contain any digit between 2-9.
+The location of the targets and distractor within the search display were randomized on each trial.
+
+Participants were informed that the search displays would contain two targets on every trial, that they need only find one target on each trial and that they were always free to search for either one.
+A trial began with a 1.5s ITI containing a central fixation cross, followed by the search display until a response was made.
+Participant responded by pressing a key that corresponded to the digit inside the target (\texttt{V}, \texttt{B}, \texttt{N} and \texttt{M} keys corresponding to 2, 3, 4 and 5 respectively).
+Participants completed 10 practice trials, followed by 3 blocks of 96 trials.
+Each block started on a red plateau.
+
+\subsection{Foraging}
+
+The foraging task was based on \cite{kristjansson2014} and \cite{johannesson2016}.
+Participants completed the feature foraging and conjunction foraging tasks on separate days, with the order counterbalanced (was it counterbalanced?).
+
+In the feature foraging task, search displays contained 80 small circles (size), 20 red (RGB: 180, 0, 0), 20 green (RGB: 20, 100, 40), 20 blue (RGB: 0, 0, 220) and 20 yellow (RGB: 200, 150, 0), presented against a black background.
+Stimuli were arranged in a 10 x 8 grid, but the position of each item within the grid space was jittered to create a more random spatial arrangement (with the restriction that two items could not be within 30 pixels of each other).
+The location of item colours to grid locations was completely randomized.
+For half of the participants, targets were red and green circles, and for the other half of participants, targets were blue and yellow circles.
+Participants were asked to collect all of the targets within a trial by using the mouse to click on each target.
+Clicking on a target caused it to disappear from the display.
+If the participant clicked erroneously on a non-target, the trial was immediately ended and a replacement trial was begun.
+Participants completed 1 practice trial and 20 full-completed experimental trials.
+
+In the conjunction foraging task, search displays were composed of both circles and squares.
+For half of the participants, the shapes were red and green (equal numbers of red circles, red squares, green circles and green squares), and for the remaining participants the shapes were blue and yellow.
+Targets were defined by conjunctions of colour and shape (e.g., red squares and green circles, with red circles and green squares as distractors).
+The assignment of targets and distractors was assigned at random for each participant.
+The procedure was otherwise identical to the feature foraging task.
+
+%% For the assignment of distractors and targets, we generated a two lists of random numbers (1-2 for easy search, and 1-4 for hard search).
+Pretty sure we did that because counterbalancing became very tricky once you accounted for that as well.
 
@@
 \hline
+
 \end{tabular}

### 2018-05-14 writeup/manuscript.tex
shrinking methods in main text

@@
 
+A brief overview of each paradigm is given below, with full details in \textit{supplementary materials}.
+
 \subsubsection{Split-half Array Search}
@@
 There were a total of 160 trials and homo- and heterogeneous sides of the display were randomly varied from trial to trial.
+The position of the dominant eye was recorded using a desktop-mounted EyeLink 1000 eye tracker (SR Research, Canada).
 
-The position of the dominant eye was recorded using a desktop-mounted EyeLink 1000 eye tracker (SR Research, Canada) sampling eye position at 1000 Hz.
 This paradigm was carried out twice to give us an estimate of how consistent participants are in their search strategy over time. The two sessions were identical.
@@
 
-The ACVS was based on the task described in \cite{irons-leber2016}, with a few changes [Or identical to the task described in Experiment 1 of Irons \& Leber, in press by then hopefully].
+The ACVS was based on the task described in \cite{irons-leber2016}, with a few changes.
 
@@
 What was viewing distance \& screen size?) arranged in three concentric rings around fixation, with 12, 18 and 24 items in the inner, middle and outer rings respectively.
-The inner ring was $XX^{\circ}$ and the outer ring was $XX^{\circ}$ from fixation.
 Of the 54 squares, 13 were red, 13 were blue, 14 were green and 14 were "variable".
-Variable distractors changes colours from trial-to-trial according to a cyclical pattern: the distractors would be red for 5 trials (called a "red plateau"), then across a period of 7 trials, they would change colour from almost red to magenta (at the fourth trial in the transition) to almost blue (see \cite{irons-leber2017}, for the specific colour values?
-Or supplemental?).
+Variable distractors change colours from trial-to-trial according to a 24 trial cyclical pattern: the distractors would be red for 5 trials (called a "red plateau"), then across a period of 7 trials, they would change colour from almost red to magenta (at the fourth trial in the transition) to almost blue.
 The variable distractor would then be blue for 5 trials (blue plateau), and then transition back from almost blue through magenta to almost red.
-This 24-trial cycle would repeat throughout the entire experiment.
 
@@
 Participants were informed that the search displays would contain two targets on every trial, that they need only find one target on each trial and that they were always free to search for either one.
-A trial began with a 1.5s ITI containing a central fixation cross, followed by the search display until a response was made.
-Participant responded by pressing a key that corresponded to the digit inside the target (\texttt{V}, \texttt{B}, \texttt{N} and \texttt{M} keys corresponding to 2, 3, 4 and 5 respectively).
-Participants completed 10 practice trials, followed by 3 blocks of 96 trials.
-Each block started on a red plateau.
 
@@
 
-In the feature foraging task, search displays contained 80 small circles (size), 20 red (RGB: 180, 0, 0), 20 green (RGB: 20, 100, 40), 20 blue (RGB: 0, 0, 220) and 20 yellow (RGB: 200, 150, 0), presented against a black background.
-Stimuli were arranged in a 10 x 8 grid, but the position of each item within the grid space was jittered to create a more random spatial arrangement (with the restriction that two items could not be within 30 pixels of each other).
+In the feature foraging task, search displays contained 80 small circles (size), 20 red, 20 green, 20 blue  and 20 yellow.
+Stimuli were arranged in a 10 x 8 grid, but the position of each item within the grid space was jittered to create a more random spatial arrangement.
 The location of item colours to grid locations was completely randomized.
+
 For half of the participants, targets were red and green circles, and for the other half of participants, targets were blue and yellow circles.
@@
 If the participant clicked erroneously on a non-target, the trial was immediately ended and a replacement trial was begun.
-Participants completed 1 practice trial and 20 full-completed experimental trials.
 
@@
 Pretty sure we did that because counterbalancing became very tricky once you accounted for that as well.
+
 \subsection{Planned Analysis}

### 2018-05-15 Scripts/lineseg/3_saccadeStrategy.R
latest version

@@ -11,9 +11,7 @@ figYn <- 2.5
 fix_dat <- readRDS(file="scratch/processedFixationData.Rda")
 trl_dat <- readRDS(file="scratch/processedRTandAccData.Rda")
 
-
 # only take correct trials
-
 fix_dat <- filter(left_join(fix_dat, trl_dat), accuracy == 1)
 trl_dat <- filter(trl_dat, accuracy == 1)
 
@@ -21,6 +19,9 @@ trl_dat <- filter(trl_dat, accuracy == 1)
 # remove people with poor target easy/absent accuracy
 fix_dat <- filter(fix_dat, !(observer %in% c(4, 21, 33, 56, 58)))
 trl_dat <- filter(trl_dat, !(observer %in% c(4, 21, 33, 56, 58)))
+
+# remove fixations falling outside of simulus
+fix_dat <- filter(fix_dat, is.finite(x), is.finite(y))
 
 # classify every fixation as homo (left), central, or hetro (right)
 centralWidth <- 0.1 # used to be 64 pixels! #change to 1 visual degree

### 2018-05-16 writeup/manuscript.tex
Some details added to manuscript
Details about screen resolution, distance, and stim size

@@
 
-The display was presented on a 17-inch CRT monitor with a resolution of $1024 \times 
-768$. Stimulus generation, presentation and data collection were controlled by MATLAB and psychophysics toolbox \cite{brainard1997} run on a Powermac.
+The display was presented on a 17-inch CRT monitor with a resolution of $1400 \times 
+1050$.
+However, due to a miscommunication, some participants (\textbf{get exact numbers from script}) were run at $1024 \times 768$ or $1600 \times 1200$.
+Stimulus generation, presentation and data collection were controlled by MATLAB and psychophysics toolbox \cite{brainard1997} run on a Powermac.
 
@@
 Stimuli consisted of arrays of black oriented line segments against a grey background.
+Each line segment had a length of $\approx$$1.6^{\circ}$ of visual angle irrespective of screen resolution.
 The target was oriented $45^{\circ}$ clockwise, while the distractor items had a random orientation with a mean of $45^{\circ}$ anti-clockwise.
@@
 
+% These are the sizes of the boxes for each resolution, I'm not sure how best to incorporate this into the text though... here's a table for the meantime;
+\begin{table*}
+	\centering
+	\small
+	\begin{tabular}{cc|c}
+	    Experiment	    &	Resolution	     & Size of stim \\
+		\hline
+		Adaptive Choice & $1024 \times 768$  & $\approx$$1.8^{\circ}$ \\
+		Adaptive Choice & $1400 \times 1050$ & $\approx$$1.3^{\circ}$ \\
+		Adaptive Choice & $1600 \times 1200$ & $\approx$$1.1^{\circ}$ \\
+		Foraging        & $1024 \times 768$  & $\approx$$1^{\circ}$ \\
+		Foraging        & $1400 \times 1050$ & $\approx$$0.7^{\circ}$ \\
+		Foraging        & $1600 \times 1200$ & $\approx$$0.6^{\circ}$ \\
+	\end{tabular}
+	\caption{Size of stimuli for each experiment and screen resolution}
+	\label{tab:Screen_Res}
+\end{table*}
+
 Each search display was composed of 54 small squares (size?
 What was viewing distance \& screen size?) arranged in three concentric rings around fixation, with 12, 18 and 24 items in the inner, middle and outer rings respectively.
+The same screen was used as in the Split-half Array Search, however, due to changes of screen resolution, the size of the squares changed.
+Participants, were sat $\approx$47cm from the screen.
 Of the 54 squares, 13 were red, 13 were blue, 14 were green and 14 were "variable".
@@
 \caption{Correlation between the split-half and adaptive choice paradigms for (a) reaction times and (b) optimal behaviour.}
+\label{fig:between_para_rt}
 \end{figure}

### 2018-05-16 Scripts/lineseg/1_init_processing.R

@@ -142,7 +142,12 @@ for (pp in participants) {
 }
 
 rm(ss, pp, filename)
- 
+# get number of participants that did each resolution 
+temp <- resDat %>%
+  group_by(xRes,session) %>%
+  summarise(num_participants = n())
+
+
 ##### Tidy up trlDat
 
 # convert some things to factors

### 2018-05-25 Writeup/sup_mat.tex
Update sup_mat.tex
Adding AC and FG participant exclusion info

@@
 
+Two participants whose accuracy rates were more than 3 SD below the mean were removed from analyses, leaving 60 participants remaining for ACVS analyses.
+[REMOVED FOR ACCURACY: 38, 39.
+ALSO ONE PERSON MISSING AC DATA:32; THREE PEOPLE MISSING ALL DATA: 18, 48, 57]
+
 \subsection{Foraging}
+
+[ACCURACY OK BUT MISSING DATA: ONE PERSON MISSING MISSING CONJUNCTION DATA: 1; SIX PEOPLE MISSING FEATURE DATA: 31, 35, 49, 50, 51, 52; THREE PEOPLE MISSING ALL DATA: 18, 48, 57. TOTAL N = 56]
 
@@
 
+[DON'T HAVE MUCH TO ADD HERE FOR EITHER ADAPTIVE CHOICE OR FORAGING THAT ISN'T ALREADY IN THE METHOD. BUT COULD SHIFT THAT INTO HERE IF YOU WANT]
+
 \subsection{Foraging}

### 2018-05-25 writeup/manuscript.tex
Added citation to Amor et al 2017
Update manuscript.tex
Added AC and FG results, comments to intro

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Anybody who has ever run a visual search experiment will be aware of the large differences from one participant to the next, and noting their existence is not new \cite{mackworth1948}.
-However, these differences are largely ignored and questions about their importance and stability remain relatively under explored.
-These differences could be due to several reasons: tiredness\cite{mackworth1948}, speed-accuracy trade-off, motivation, visual impairments, and search strategies\cite{boot2006}.
+%[TRIED A DIFFERENT, FEEL FREE TO CHANGE BACK
+Anybody who has ever conducted a visual search experiment will be aware of the large differences from one participant to the next.
+These differences could be emerge from several different sources of variation: tiredness\cite{mackworth1948}, information-processing ability, speed-accuracy trade-off, motivation, visual impairments, and search strategies\cite{boot2006}.
+Although their existence has previously been noted \cite{mackworth1948}, a rigorous examination of individual differences in visual search has been largely ignored and questions about their importance and stability remain relatively under explored.
+
+[MIGHT BE GOOD TO EXPLAIN HERE THAT THE EMPHASIS IS ON STRATEGY?] In the current study, we focus on one source of individual differences in visual search: strategy.
+By visual search strategies, we refer to a collection of behaviours that all observers can freely choose to engage in when they search a display, which is distinct from intrinsically unchanging characteristics such as information-processing ability [NOT REALLY SURE HOW BEST TO SAY THAT, JUST THOUGHT IT MIGHT BE GOOD TO HAVE SOME OF DEFINITION OF VS STRATS??].
+Recent studies have shown substantial variation in search strategies across individuals.
 
 A striking example of the effect of strategy is given by \cite{boot2006, boot2009}.
-They found differences in visual search performance could be explained by whether observers used a scanning strategy, or simply fixated the centre of the stimulus and used peripheral vision.
+They found differences in visual search performance could be explained by whether observers used a [active?] scanning strategy, or simply fixated the centre of the stimulus and used covert attention to search peripheral vision.
 
@@
 
+% Memory stuff might be too left field for intro?
 In the related field of memory, individual differences have received more attention, for example \cite{sobel2007}.
@@
 In our own work, we have previously shown that there are large differences between individuals in terms of the search strategies used to find a target among distracters.
-The Adaptive Choice Visual Search (ACVS) paradigm  \cite{irons-leber2016} \ldots.
-Even larger differences were found with the Split-Half Search Arrays \cite{nowakowsak2017} who aimed to discriminate between the optimal  \cite{najemnik-geisler2008} and stochastic \cite{clarke2016} search strategies.
+The Adaptive Choice Visual Search (ACVS) paradigm  \cite{irons-leber2016} examined strategies in the use of feature-based attention\cite{irons-leber2016,irons-leber2018} \ldots.
+Participants varied substantially along two key dimensions: how frequently they used the more effective target feature to search (varying from chance performance to nearly optimal), and how often they changed search features.
+Even larger differences [haha we might argue with that, depending what you mean by larger] were found with the Split-Half Search Arrays \cite{nowakowsak2017} who aimed to discriminate between the optimal  \cite{najemnik-geisler2008} and stochastic \cite{clarke2016} search strategies.
 They found that while some participants initially searched the displays near optimally, others carried out strategies counter to this, failing to match the performance of the stochastic searcher.
@@
 \maketitle
+
+Mention \cite{amor2017}
 
@@
 
+[MAYBE THERE SHOULD BE SOMETHING ELSE TO SET UP THE RESEARCH Q?] A common theme emerging from the studies in the observation that individual strategies vary in their degree of effectiveness or optimality [IF THAT IS EVEN A WORD].
+However, each task taps into a different aspect of visual search behavior (feature-based attention, [spatial/fixation patterns??]).
 The aim of the present study is to investigate the extent to which these differences are stable across different visual search paradigms.
-Are observers who are good at finding the target in the split-half search arrays also better in the ACVS task?
+Are observers who use the optimal strategy in the split-half search arrays also more optimal in the ACVS task?
 Are the super-foragers consistently better or worse than more typical searchers in the other two paradigms?
@@
 
-The ACVS was based on the task described in \cite{irons-leber2016}, with a few changes.
+The ACVS was based on the task described in \cite{irons-leber2018}, Experiment 1.
 
 % These are the sizes of the boxes for each resolution, I'm not sure how best to incorporate this into the text though... here's a table for the meantime;
+% Thanks! Stim size is not critical for our experiment, so it doesn't matter too much if it's too complicated (just habit to have it in there :)
 \begin{table*}
@@
 
-Each search display was composed of 54 small squares (size?
-What was viewing distance \& screen size?) arranged in three concentric rings around fixation, with 12, 18 and 24 items in the inner, middle and outer rings respectively.
+% Let me know if you want me to shift some of this into the Supp
+Each search display was composed of 54 small squares arranged in three concentric rings around fixation, with 12, 18 and 24 items in the inner, middle and outer rings respectively.
 The same screen was used as in the Split-half Array Search, however, due to changes of screen resolution, the size of the squares changed.
@@
 
-In the feature foraging task, search displays contained 80 small circles (size), 20 red, 20 green, 20 blue  and 20 yellow.
+In the feature foraging task, search displays contained 80 small circles, 20 red, 20 green, 20 blue  and 20 yellow.
 Stimuli were arranged in a 10 x 8 grid, but the position of each item within the grid space was jittered to create a more random spatial arrangement.
@@
 \subsection{Planned Analysis}
+
+% Structure-wise, would it be easier for the reader to have methods and planned analyses nested under each task?
 
@@
 
+The results for the ACVS were consistent with our previous findings \cite{irons-leber2016,irons-leber2018} (see Figure 3?).
+Figure 3 (?
+AC_OptCh_x_AllSw) shows that there were wide individual differences in both percent option (range $33.62\%$ – $97.50\%$, $M = 56.99$, $SD = 14.75$) and switch rate (range = $0\% - 56.68\%$, $M = 28.46$, $SD = 13.54$).
+Although we did not assess it here, good test-retest reliability has been found previously for both percent optimal ($r = .83$) and switch rate ($r = .77$) \cite{irons-leber,2018}.
+
 \subsubsection{Conjunction Foraging}
+
+The multiple-target foraging results were also in line previous findings \cite{kristjansson2014,johannesson2016}.
+As expected, run lengths were shorter for feature foraging ($M = 3.24$, $SD = 3.19$) than conjunction foraging ($M = 10.64$, $SD = 7.01$), $t(55) = 8.03$, $p < .001$ (PREFER DIFFERENT STATS HERE?
+CI [-9.25,-5.55]) suggesting more frequent foraging for multiple targets concurrently when those targets were defined by features than by conjunctions.
+However, both showed significant individual variation: Feature run length varied between 1.87 and 20, and conjunction run length varied between 1.00 and 19.67.
+Figure 4 (?) depicts run length across the trials separately for each individual.
+Twenty “super-searchers” were revealed, identified by short run lengths for both feature and conjunction targets [THAT NUMBER IS JUST BASED ON EYE-BALLING THE FIGURE, BUT WE COULD COME UP WITH SOME SORT OF PRECIOUS CUT OFF – WHAT DO YOU THINK?].
 
@@
 The results above demonstrate that we have successfully replicated the previous findings around individual differences in visual search strategy.
-We now investigate whether there are correlations between paradigms: are individuals who are good at one visual search task good at another?
-We start by looking at simple reaction times (Figure \ref{fig:between_para_rt}).
-In all comparisons the correlations are weak, typically $0.27 < r <0.30$ but positive.
+As an initial sweep, we look at overall performance in terms of RT (note that this can be influenced not only by strategy, but also by individuals’ abilities, such as their information-processing speed and their ability to ignore distractors).
+Are individuals who are fast on one visual search task fast on another?
+In all comparisons the correlations are weak, typically $0.27 < r <0.30$ but positive (Figure \ref{fig:between_para_rt}).
 None of these correlations are statistically significant ($p>0.05$).
@@
 
-Given the low correlations between reaction times, it seems unlikely that we will find that individuals who search efficiently and optimally in one paradigm will search well in another (the original motivation for our study).
+[I WONDER IF THIS SHOULD GO BEFORE THE RT CORRELATIONS?
+SINCE AS YOU SAY, THIS IS THE MAIN AIM OF THE PAPER.
+THEN RT CORRELATIONS COULD GO AS A SECONDARY AIM] Given the low correlations between reaction times, it seems unlikely that we will find that individuals who search efficiently and optimally in one paradigm will search well in another (the original motivation for our study) [I WOULD BE INCLINED NOT TO SAY THIS, BECAUSE IT SEEMS TO MINIMIZE THE PURPOSE OF LOOKING AT STRATEGY AT ALL.
+IE IT SUGGESTS THAT ALL OF THE VARIATION IN STRATEGY COULD BE ENCAPSULATED BY RT.
+BUT THERE ARE OTHER FACTORS THAT ALSO INFLUENCE RT].
 The analysis supports this hypothesis.

### 2018-06-25 writeup/manuscript.tex
A few edits

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%[TRIED A DIFFERENT, FEEL FREE TO CHANGE BACK
+
 Anybody who has ever conducted a visual search experiment will be aware of the large differences from one participant to the next.
@@
 
-[MIGHT BE GOOD TO EXPLAIN HERE THAT THE EMPHASIS IS ON STRATEGY?] In the current study, we focus on one source of individual differences in visual search: strategy.
-By visual search strategies, we refer to a collection of behaviours that all observers can freely choose to engage in when they search a display, which is distinct from intrinsically unchanging characteristics such as information-processing ability [NOT REALLY SURE HOW BEST TO SAY THAT, JUST THOUGHT IT MIGHT BE GOOD TO HAVE SOME OF DEFINITION OF VS STRATS??].
-Recent studies have shown substantial variation in search strategies across individuals.
+In the current study, we focus on one source of individual differences in visual search: strategy.
+By visual search strategies, we refer to a collection of behaviours that all observers can freely choose to engage in when they search a display, which is distinct from intrinsically unchanging characteristics such as information-processing ability and motivation.
+Perhaps surprisingly, previous literature has shown that both ideal oberver \cite{najemnik-geisler2008} and stochastic \cite{clarke2016} models can explain the number of fixations required by an average observer to locate a target in noise.
+These apparent contradictory results could potentially expained by large individual differences.
 
-A striking example of the effect of strategy is given by \cite{boot2006, boot2009}.
-They found differences in visual search performance could be explained by whether observers used a [active?] scanning strategy, or simply fixated the centre of the stimulus and used covert attention to search peripheral vision.
+A striking example of the effect of strategy is given by \cite{boot2006, boot2009}. They carried out a dynamic dot detection task 
+found differences in visual search performance could be explained by whether observers used a [active?] scanning strategy, or simply fixated the centre of the stimulus and used covert attention to search peripheral vision.
+
+\end{fmtext}
 
 Also \cite{proulx2011}
-
-% Memory stuff might be too left field for intro?
-In the related field of memory, individual differences have received more attention, for example \cite{sobel2007}.
 
@@
 Examples of the stimuli are given in Figure \ref{fig:exampleStimuli}.
-
-\end{fmtext}
 
@@
 The results for the ACVS were consistent with our previous findings \cite{irons-leber2016,irons-leber2018} (see Figure 3?).
-Figure 3 (?
+%Figure 3 (?
 AC_OptCh_x_AllSw) shows that there were wide individual differences in both percent option (range $33.62\%$ – $97.50\%$, $M = 56.99$, $SD = 14.75$) and switch rate (range = $0\% - 56.68\%$, $M = 28.46$, $SD = 13.54$).
@@
 
+% Memory stuff might be too left field for intro?
+% agree, let's try and mention it in the discussion though. 
+In the related field of memory, individual differences have received more attention, for example \cite{sobel2007}.
+
 \bibliographystyle{plain}

### 2018-06-29 writeup/manuscript.tex
Some more edits

@@
 These apparent contradictory results could potentially expained by large individual differences.
-
-A striking example of the effect of strategy is given by \cite{boot2006, boot2009}. They carried out a dynamic dot detection task 
-found differences in visual search performance could be explained by whether observers used a [active?] scanning strategy, or simply fixated the centre of the stimulus and used covert attention to search peripheral vision.
+Search strategy can also vary in how systematic is it.
+For example it is common to see top-to-bottom and left-to-right scanning behaviour in scanpaths recorded during visual search\cite{gilchrist2006}, and the degree to which this occurs is in part related to the structure of the stimuli \cite{amor2017}.
 
 \end{fmtext}
+\maketitle
 
-Also \cite{proulx2011}
+A striking example of the effect of strategy is given by \cite{boot2006}.
+They asked participants to monitor a cluttered display for an object changing colour or object onset.
+Large individual differences were found with respect to the number of saccades participants made while monitoring the stimulus, and this was negatively correlated with detection performance.
 
@@
 Participants varied substantially along two key dimensions: how frequently they used the more effective target feature to search (varying from chance performance to nearly optimal), and how often they changed search features.
-Even larger differences [haha we might argue with that, depending what you mean by larger] were found with the Split-Half Search Arrays \cite{nowakowsak2017} who aimed to discriminate between the optimal  \cite{najemnik-geisler2008} and stochastic \cite{clarke2016} search strategies.
-They found that while some participants initially searched the displays near optimally, others carried out strategies counter to this, failing to match the performance of the stochastic searcher.
+Using a different paradigm\cite{nowakowsak2017}, we aimed to discriminate between the optimal  \cite{najemnik-geisler2008} and stochastic \cite{clarke2016} search strategies.
+We found that while some participants initially searched the displays near optimally, others carried out strategies counter to this, failing to even match the performance of the stochastic searcher.
+Furthermore, the degree to which they made saccades in line with the optimal search strategy was strongly correlated with their reaction times.
 Examples of the stimuli are given in Figure \ref{fig:exampleStimuli}.
 
-\maketitle
-
-Mention \cite{amor2017}
+\begin{figure}
+\centering
+\subfigure[][]{\includegraphics[height=3cm]{figures/split-half.png}}
+\subfigure[][]{\includegraphics[height=3cm]{figures/adaptive.png}}
+\subfigure[][]{\includegraphics[height=3cm]{figures/foraging.png}}
+\caption{Example stimulus from the (a) \textit{split-half}, (b) \textit{adaptive choice} and (c) \textit{foraging} paradigms}
+\label{fig:exampleStimuli}
+\end{figure}
 
@@
 
-[MAYBE THERE SHOULD BE SOMETHING ELSE TO SET UP THE RESEARCH Q?] A common theme emerging from the studies in the observation that individual strategies vary in their degree of effectiveness or optimality [IF THAT IS EVEN A WORD].
-However, each task taps into a different aspect of visual search behavior (feature-based attention, [spatial/fixation patterns??]).
-The aim of the present study is to investigate the extent to which these differences are stable across different visual search paradigms.
+\cite{proulx2011} demonstrated that the different weighting between top-down and bottom-up factors in a conjunction search task explained \ldots Interestingly, they could that around a third of participants were unaware of the search strategy they employed.
+
+A common theme emerging from the studies in the observation that individual strategies vary in their degree of effectiveness or optimality.
+However, ``visual search'' encompasses a wide range of specific tasks, each tapping into a different aspect of behaviour (feature-based attention, [spatial/fixation patterns??]).
+The aim of the present study is to investigate the extent to which individual differences are stable across different visual search paradigms.
 Are observers who use the optimal strategy in the split-half search arrays also more optimal in the ACVS task?
+Does it make sense to talk about `super-searchers' who show above average performance in a range of search tasks?
 Are the super-foragers consistently better or worse than more typical searchers in the other two paradigms?
@@
 Example stimuli can be seen in Figure \ref{fig:exampleStimuli}.
-
-\begin{figure}
-\centering
-\subfigure[][]{\includegraphics[height=3cm]{figures/split-half.png}}
-\subfigure[][]{\includegraphics[height=3cm]{figures/adaptive.png}}
-\subfigure[][]{\includegraphics[height=3cm]{figures/foraging.png}}
-\caption{Example stimulus from the (a) \textit{split-half}, (b) \textit{adaptive choice} and (c) \textit{foraging} paradigms}
-\label{fig:exampleStimuli}
-\end{figure}
 
@@
 Figure 4 (?) depicts run length across the trials separately for each individual.
-Twenty “super-searchers” were revealed, identified by short run lengths for both feature and conjunction targets [THAT NUMBER IS JUST BASED ON EYE-BALLING THE FIGURE, BUT WE COULD COME UP WITH SOME SORT OF PRECIOUS CUT OFF – WHAT DO YOU THINK?].
+Twenty ``super-searchers'' were revealed, identified by short run lengths for both feature and conjunction targets [THAT NUMBER IS JUST BASED ON EYE-BALLING THE FIGURE, BUT WE COULD COME UP WITH SOME SORT OF PRECIOUS CUT OFF – WHAT DO YOU THINK?].
 
@@
 The results above demonstrate that we have successfully replicated the previous findings around individual differences in visual search strategy.
-As an initial sweep, we look at overall performance in terms of RT (note that this can be influenced not only by strategy, but also by individuals’ abilities, such as their information-processing speed and their ability to ignore distractors).
+As an initial sweep, we look at overall performance in terms of RT (note that this can be influenced not only by strategy, but also by individuals' abilities, such as their information-processing speed and their ability to ignore distractors).
 Are individuals who are fast on one visual search task fast on another?
@@
 
-% Memory stuff might be too left field for intro?
-% agree, let's try and mention it in the discussion though. 
-In the related field of memory, individual differences have received more attention, for example \cite{sobel2007}.
+Mention \cite{vogel2008}.
+From \cite{proulx2011} - \textit{Vogel and colleagues have found that an individual’s ability to remember a greater number of items using working memory is related to a filtering capacity in visual search that suppresses attentional capture by distracting visual information [10,11,12].
+Behavioral work in visual search has extended this research to
+demonstrate that working memory correlates only with top-down
+visual search performance where task relevance is crucial, but not
+with  bottom-up  visual  search  tasks  where  salience  in  the
+environment guides attention \cite{sobel2007}}
 

### 2018-08-08 writeup/manuscript.tex
Fixing some references.

@@
 
-I think he sees it as a positive thing that they tasks don't correlate, because ti suggests they capture unique variation in behaviour
+I think he sees it as a positive thing that they tasks don't correlate, because it suggests they capture unique variation in behaviour
 glass half full approach
@@
 
+Mention \cite{stoet2011}.
+
 \bibliographystyle{plain}

### 2018-08-08 writeup/manuscript.tex
Working on intro

@@
 
-Anybody who has ever conducted a visual search experiment will be aware of the large differences from one participant to the next.
-These differences could be emerge from several different sources of variation: tiredness\cite{mackworth1948}, information-processing ability, speed-accuracy trade-off, motivation, visual impairments, and search strategies\cite{boot2006}.
+As is common in cognitive psychology, most visual search literature has focused on how the average participant performs in the task, despite it being well known that there is a great deal of variability between one subject and the next.
+These differences can emerge from several different sources of variation: tiredness\cite{mackworth1948}, information-processing ability, speed-accuracy trade-off, motivation, visual impairments \cite{nowakowska2016}, and search strategies\cite{boot2006}.
 Although their existence has previously been noted \cite{mackworth1948}, a rigorous examination of individual differences in visual search has been largely ignored and questions about their importance and stability remain relatively under explored.
@@
 In the current study, we focus on one source of individual differences in visual search: strategy.
-By visual search strategies, we refer to a collection of behaviours that all observers can freely choose to engage in when they search a display, which is distinct from intrinsically unchanging characteristics such as information-processing ability and motivation.
-Perhaps surprisingly, previous literature has shown that both ideal oberver \cite{najemnik-geisler2008} and stochastic \cite{clarke2016} models can explain the number of fixations required by an average observer to locate a target in noise.
-These apparent contradictory results could potentially expained by large individual differences.
+By search strategies, we refer to a collection of behaviours that all observers can freely choose from when they search a display.
+Examples include choosing to adopt a systematic left-to-right and top-to-bottom strategy, or the type of guided search behaviour in which locations that are more likely to contain the target are prioritised \cite{}.
+This is distinct from intrinsically unchanging characteristics such as information-processing ability and motivation.
+Perhaps surprisingly, previous literature has shown that both ideal observer \cite{najemnik-geisler2008} and stochastic \cite{clarke2016} models can explain the number of fixations required by an average observer to locate a target in noise.
+These apparent contradictory results could potentially explained by large individual differences.
 Search strategy can also vary in how systematic is it.
-For example it is common to see top-to-bottom and left-to-right scanning behaviour in scanpaths recorded during visual search\cite{gilchrist2006}, and the degree to which this occurs is in part related to the structure of the stimuli \cite{amor2017}.
+For example it is common to see top-to-bottom and left-to-right scanning behaviour in scan-paths recorded during visual search\cite{gilchrist2006}, and the degree to which this occurs is in part related to the structure of the stimuli \cite{amor2017}.
 

### 2018-08-08 writeup/manuscript.tex
More work on the intro

@@
 By search strategies, we refer to a collection of behaviours that all observers can freely choose from when they search a display.
-Examples include choosing to adopt a systematic left-to-right and top-to-bottom strategy, or the type of guided search behaviour in which locations that are more likely to contain the target are prioritised \cite{}.
-This is distinct from intrinsically unchanging characteristics such as information-processing ability and motivation.
-Perhaps surprisingly, previous literature has shown that both ideal observer \cite{najemnik-geisler2008} and stochastic \cite{clarke2016} models can explain the number of fixations required by an average observer to locate a target in noise.
-These apparent contradictory results could potentially explained by large individual differences.
-Search strategy can also vary in how systematic is it.
-For example it is common to see top-to-bottom and left-to-right scanning behaviour in scan-paths recorded during visual search\cite{gilchrist2006}, and the degree to which this occurs is in part related to the structure of the stimuli \cite{amor2017}.
+Examples include choosing to adopt a systematic left-to-right and top-to-bottom strategy\cite{gilchrist2006}, or the type of guided search behaviour in which locations that are more likely to contain the target are prioritised \cite{wolfe2015}.
+Perhaps surprisingly, previous literature has shown that both ideal observer \cite{najemnik-geisler2008} and stochastic \cite{clarke2016} models can explain the number of fixations required to locate a target in noise.
+These apparent contradictory results could potentially explained by large individual differences \cite{nowakowska2017}.
 
@@
 
+\cite{proulx2011} demonstrated that the different weighting between top-down and bottom-up factors in a conjunction search task explained \ldots Interestingly, they could that around a third of participants were unaware of the search strategy they employed.
+
 In our own work, we have previously shown that there are large differences between individuals in terms of the search strategies used to find a target among distracters.
-The Adaptive Choice Visual Search (ACVS) paradigm  \cite{irons-leber2016} examined strategies in the use of feature-based attention\cite{irons-leber2016,irons-leber2018} \ldots.
-Participants varied substantially along two key dimensions: how frequently they used the more effective target feature to search (varying from chance performance to nearly optimal), and how often they changed search features.
-Using a different paradigm\cite{nowakowsak2017}, we aimed to discriminate between the optimal  \cite{najemnik-geisler2008} and stochastic \cite{clarke2016} search strategies.
+The Adaptive Choice Visual Search (ACVS) paradigm\cite{irons-leber2016} was used to examine strategies in the use of feature-based attention.
+[See below and supplementary materials for a description of this paradigm.] Participants varied substantially along two key dimensions: how frequently they used the more effective target feature to search (varying from chance performance to near optimal), and how often they changed search features.
+Further work has shown that these differences are stable over time (between one and ten days) with test-retest correlations of around $r = 0.8$\cite{irons-leber2018}.
+
+Using a different paradigm\cite{nowakowsak2017}, we aimed to discriminate between optimal\cite{najemnik-geisler2008} and stochastic \cite{clarke2016} search strategies in a simple visual search task involving arrays of line segments (see Figure \ref{fig:exampleStimuli}).
+The line segments were arranged such that those on one side of the display all had a very similar orientation, while those on the other side had higher variance.
+This was done so that if the target appeared on the homogeneous side, it would be highly salient.
+Trials in which the target appeared on the heterogeneous side of the display would be much harder.
+With these stimuli, the optimal eye movement strategy is to only search the heterogeneous half of the stimulus, as targets on the homogeneous side can be detected with peripheral vision.
 We found that while some participants initially searched the displays near optimally, others carried out strategies counter to this, failing to even match the performance of the stochastic searcher.
 Furthermore, the degree to which they made saccades in line with the optimal search strategy was strongly correlated with their reaction times.
-Examples of the stimuli are given in Figure \ref{fig:exampleStimuli}.
 
@@
 Another example of differences in search strategy comes from the foraging literature \cite{kristjansson2014,johannesson2016}.
+In this context, foraging is a visual search task in which there are multiple targets on each trial.
 Participants were asked to search through a set of items from four categories, two of which were classed as targets.
 In the conjunction condition (i.e.
-searching for red-horizontal and green-vertical line segments among red-vertical and green-horizontal distracters), most observers searched in runs of one target or another.
+searching for red-horizontal and green-vertical line segments among red-vertical and green-horizontal distracters), most observers searched in runs of one target category or another.
 This strategy has previously been observers in animal foraging literature \cite{dawkins1971}.
 However, a sub-set of observers, termed ``super-searchers'' showed no switch cost.
-
-\cite{proulx2011} demonstrated that the different weighting between top-down and bottom-up factors in a conjunction search task explained \ldots Interestingly, they could that around a third of participants were unaware of the search strategy they employed.
 

### 2018-08-08 writeup/manuscript.tex
more intro

@@
 $^{2}$Department of Psychology, The Ohio State University, Columbus, USA\\
-$^{3}$School of Psychology, University of Aberdeen, Aberdeen, UK
-}
+$^{3}$School of Psychology, University of Aberdeen, Aberdeen, UK}
 
@@
 
-A striking example of the effect of strategy is given by \cite{boot2006}.
+A striking example of the effect of strategy is given by Boot and colleagues\cite{boot2006}.
 They asked participants to monitor a cluttered display for an object changing colour or object onset.
@@
 
-\cite{proulx2011} demonstrated that the different weighting between top-down and bottom-up factors in a conjunction search task explained \ldots Interestingly, they could that around a third of participants were unaware of the search strategy they employed.
+Proulx\cite{proulx2011} demonstrated that the different weighting between top-down and bottom-up factors in a conjunction search task explained \ldots Interestingly, they could that around a third of participants were unaware of the search strategy they employed.
 
-In our own work, we have previously shown that there are large differences between individuals in terms of the search strategies used to find a target among distracters.
-The Adaptive Choice Visual Search (ACVS) paradigm\cite{irons-leber2016} was used to examine strategies in the use of feature-based attention.
-[See below and supplementary materials for a description of this paradigm.] Participants varied substantially along two key dimensions: how frequently they used the more effective target feature to search (varying from chance performance to near optimal), and how often they changed search features.
-Further work has shown that these differences are stable over time (between one and ten days) with test-retest correlations of around $r = 0.8$\cite{irons-leber2018}.
-
-Using a different paradigm\cite{nowakowsak2017}, we aimed to discriminate between optimal\cite{najemnik-geisler2008} and stochastic \cite{clarke2016} search strategies in a simple visual search task involving arrays of line segments (see Figure \ref{fig:exampleStimuli}).
+Eye movement strategies have also been shown to be an imporotant source or individual differences in visual search tasks.
+Nowakowska, Clarke \& Hunt\cite{nowakowska2017} designed a simple search pardigm (referred to here as the Split-Half Search Array paradigm) to discriminate between optimal\cite{najemnik-geisler2008} and stochastic \cite{clarke2016} search strategies involving arrays of line segments (see Figure \ref{fig:exampleStimuli}.
 The line segments were arranged such that those on one side of the display all had a very similar orientation, while those on the other side had higher variance.
@@
 With these stimuli, the optimal eye movement strategy is to only search the heterogeneous half of the stimulus, as targets on the homogeneous side can be detected with peripheral vision.
-We found that while some participants initially searched the displays near optimally, others carried out strategies counter to this, failing to even match the performance of the stochastic searcher.
+While some participants initially searched the displays near optimally, others carried out strategies counter to this, failing to even match the performance of the stochastic searcher.
 Furthermore, the degree to which they made saccades in line with the optimal search strategy was strongly correlated with their reaction times.
+
+A similar range of strategies, from random to near-optimal has been found by Irons \& Leber with the Adaptive Choice Visual Search (ACVS) paradigm\cite{irons-leber2016}, designed to explore how feature-based attention is used.
+This paradigm involves stimuli made up of small coloured boxes (red, blue, green and a 4th colour that varies from red, through purple, to blue and back again) with numerals written inside them (See Figure \ref{fig:exampleStimuli}).
+The target is a defined as a red or blue box with a numeral between 1 and 4, and on each trial a target of both type is present.
+The participant's task is to find one of either target as quickly as possible and report the numeral.
+One trials in which the 4th box colour is red (or close to red), participants should search through the blue boxes and report the blue target, as there will be fewer distracters.
+As the 4th colour changes to through purple to blue, participants should udpate their strategy and search for the red target.
+The results showed that participants varied substantially along two key dimensions: how frequently they used the more effective target feature to search (varying from chance performance to near optimal), and how often they changed search features.
+Further work has shown that these differences are stable over time (between one and ten days) with test-retest correlations of around $r \approx 0.8$\cite{irons-leber2018}.
 
@@
 This strategy has previously been observers in animal foraging literature \cite{dawkins1971}.
-However, a sub-set of observers, termed ``super-searchers'' showed no switch cost.
+However, a sub-set of observers, termed `super-searchers' showed no switch cost.
+
+There have been some efforts made to relate these differences to other measures such as measures of working memory or \ldots. \cite{Jóhannesson2017,}.  \ldots.
 
@@
 
-The study consists of three different paradigms from the visual search literature in which large individual differences were found \cite{nowakowsak2017, irons-leber2016, kristjansson2014}.
+The study consists of three different paradigms from the visual search literature in which large individual differences were found \cite{nowakowska2017, irons-leber2016, kristjansson2014}.
 Example stimuli can be seen in Figure \ref{fig:exampleStimuli}.
@@
 In order to characterise an individual's behaviour in this task, we will compute the proportion of the first $n$ fixations that were on heterogeneous (difficult) side of the stimuli, over all target absent trials\footnote{Only take correct trials?}.
-\cite{nowakowsak2017} demonstrated a strong correlation between an this metric (for $n=5$) and reaction times ($r=.53$).
+\cite{nowakowska2017} demonstrated a strong correlation between an this metric (for $n=5$) and reaction times ($r=.53$).
 However, a re-analysis of their data shows that an even stronger correlation is obtained with $n=3$.
@@
 \subsubsection{Split-half Array Search}
-Our results are broadly in line with \cite{nowakowsak2017}.
+Our results are broadly in line with \cite{nowakowska2017}.
 The correlation between accuracy and reaction times between the two sessions is shown in Figure \ref{fig:splithalf_summary}(a, b).
@@
 Again, we see large and stable individual differences across the two sessions (test-retest $r \in [0.57, 0.83]$ for the proportion of the first five saccades to the heterogeneous half of the display for target absent trials).
-More importantly, as with \cite{nowakowsak2017}, we see that the search strategies give a good correlation with reaction times in both session a, $r \in [0.56, 0.84]$ and session b, $r \in [0.50, 0.81]$.
+More importantly, as with \cite{nowakowska2017}, we see that the search strategies give a good correlation with reaction times in both session a, $r \in [0.56, 0.84]$ and session b, $r \in [0.50, 0.81]$.
 
@@
 
-The results presented above are somewhat surprising.
+The results presented above convincingly demonstrate that there are no strong correlations between the split-half, adaptive choice and foraging visual search paradigms.
+While we have successfully replicated the range of individual differences found in each of these studies, with a larger sample size than the original papers, the between-paradigm correlations give at most $R^2 = 0.1$, and this is a generous interpretation that would fail to pass the usual criteria for null hypothesis significance testing.
+Knowing how one person will behave in one of these paradigms apparently tells us very little about how they will perform in the others.
+This can be contrasted with the relatively high test-retest correlations of $r \in [0.65.
+0.86]$ in the split-half paradigm and $r \in [0.72, 0.9]$ for the adaptive choice paradigm\cite{irons-leber2016}.
+[AM I RIGHT IN THINKING ARNI AND CO HAVE MEASURES FOR THEIR PARADIGM???]
 
-I think he sees it as a positive thing that they tasks don't correlate, because it suggests they capture unique variation in behaviour
-glass half full approach
+I think he sees it as a positive thing that they tasks don't correlate, because it suggests they capture unique variation in behaviour glass half full approach
 

### 2018-08-09 writeup/manuscript.tex
draft of intro complete.
Still needs a new draft though!

@@
 As is common in cognitive psychology, most visual search literature has focused on how the average participant performs in the task, despite it being well known that there is a great deal of variability between one subject and the next.
-These differences can emerge from several different sources of variation: tiredness\cite{mackworth1948}, information-processing ability, speed-accuracy trade-off, motivation, visual impairments \cite{nowakowska2016}, and search strategies\cite{boot2006}.
-Although their existence has previously been noted \cite{mackworth1948}, a rigorous examination of individual differences in visual search has been largely ignored and questions about their importance and stability remain relatively under explored.
+From Treisman's work on Feature Integration Theory\cite{treisman1980} to the latest incarnation of the Guided Search Model\cite{wolfe2015}, we now have a good understanding of what makes some search targets effortless to find, while others require careful inspection.
+However, these theories and models have neglected the question of why some observers find visual search so much harder than others.
+These differences can emerge from several different sources of variation: tiredness\cite{mackworth1948}, information-processing ability, speed-accuracy trade-off, motivation, visual impairments\cite{nowakowska2016}, and search strategies\cite{boot2006}.
+Although their existence has previously been noted\cite{mackworth1948}, a rigorous examination of individual differences in visual search has been largely ignored and questions about their importance and stability remain relatively under explored.
 
@@
 By search strategies, we refer to a collection of behaviours that all observers can freely choose from when they search a display.
-Examples include choosing to adopt a systematic left-to-right and top-to-bottom strategy\cite{gilchrist2006}, or the type of guided search behaviour in which locations that are more likely to contain the target are prioritised \cite{wolfe2015}.
-Perhaps surprisingly, previous literature has shown that both ideal observer \cite{najemnik-geisler2008} and stochastic \cite{clarke2016} models can explain the number of fixations required to locate a target in noise.
-These apparent contradictory results could potentially explained by large individual differences \cite{nowakowska2017}.
-
+Examples include choosing to adopt a systematic left-to-right and top-to-bottom strategy\cite{gilchrist2006}, or the type of guided search behaviour in which locations that are more likely to contain the target are prioritised\cite{wolfe2015}.
 \end{fmtext}
@@
 Large individual differences were found with respect to the number of saccades participants made while monitoring the stimulus, and this was negatively correlated with detection performance.
+Proulx\cite{proulx2011} demonstrated that the different weighting between top-down and bottom-up factors in a conjunction search task explained \ldots Interestingly, they claim that around a third of participants were unaware of the search strategy they employed.
 
-Proulx\cite{proulx2011} demonstrated that the different weighting between top-down and bottom-up factors in a conjunction search task explained \ldots Interestingly, they could that around a third of participants were unaware of the search strategy they employed.
-
-Eye movement strategies have also been shown to be an imporotant source or individual differences in visual search tasks.
-Nowakowska, Clarke \& Hunt\cite{nowakowska2017} designed a simple search pardigm (referred to here as the Split-Half Search Array paradigm) to discriminate between optimal\cite{najemnik-geisler2008} and stochastic \cite{clarke2016} search strategies involving arrays of line segments (see Figure \ref{fig:exampleStimuli}.
+Eye movement strategies have also been shown to be an important source or individual differences in visual search tasks.
+Nowakowska, Clarke \& Hunt\cite{nowakowska2017} designed a simple search paradigm (referred to here as the Split-Half Search Array paradigm) to discriminate between optimal\cite{najemnik-geisler2008} and stochastic \cite{clarke2016} search strategies involving arrays of line segments (see Figure \ref{fig:exampleStimuli}.
 The line segments were arranged such that those on one side of the display all had a very similar orientation, while those on the other side had higher variance.
@@
 A similar range of strategies, from random to near-optimal has been found by Irons \& Leber with the Adaptive Choice Visual Search (ACVS) paradigm\cite{irons-leber2016}, designed to explore how feature-based attention is used.
-This paradigm involves stimuli made up of small coloured boxes (red, blue, green and a 4th colour that varies from red, through purple, to blue and back again) with numerals written inside them (See Figure \ref{fig:exampleStimuli}).
+This paradigm involves stimuli made up of small coloured boxes (red, blue, green and a fourth colour that varies from red, through purple, to blue and back again) with numerals written inside them (See Figure \ref{fig:exampleStimuli}).
 The target is a defined as a red or blue box with a numeral between 1 and 4, and on each trial a target of both type is present.
 The participant's task is to find one of either target as quickly as possible and report the numeral.
-One trials in which the 4th box colour is red (or close to red), participants should search through the blue boxes and report the blue target, as there will be fewer distracters.
-As the 4th colour changes to through purple to blue, participants should udpate their strategy and search for the red target.
+One trials in which the fourth box colour is red (or close to red), participants should search through the blue boxes and report the blue target, as there will be fewer distracters.
+As the fourth colour changes to through purple to blue, participants should update their strategy and search for the red target.
 The results showed that participants varied substantially along two key dimensions: how frequently they used the more effective target feature to search (varying from chance performance to near optimal), and how often they changed search features.
@@
 
-There have been some efforts made to relate these differences to other measures such as measures of working memory or \ldots. \cite{Jóhannesson2017,}.  \ldots.
+Previous research has investigated the relationship between these behaviours to psychometric measures, but to date, these differences have not shown strong correlations with other attributes.
+In the ACVS paradigm, Irons \& Leber found no evidence of a correlation between the proportion of optimal choices made by observers and measures of visual working memory or trait compulsivity\cite{irons-leber2018}.
+Similarly, the differences foraging behaviour are not accounted for by working memory or inhibitory control\cite{johannesson2017}.
 
 A common theme emerging from the studies in the observation that individual strategies vary in their degree of effectiveness or optimality.
-However, ``visual search'' encompasses a wide range of specific tasks, each tapping into a different aspect of behaviour (feature-based attention, [spatial/fixation patterns??]).
+However, ``visual search'' encompasses a wide range of specific tasks, each tapping into a different aspect of behaviour (e.g.
+feature-based attention, information sampling).
 The aim of the present study is to investigate the extent to which individual differences are stable across different visual search paradigms.
@@
 \subsection{Participants}
-We aim to find 64 participants to volunteer to take part in this experiment.
-Participants will be students from the University of Aberdeen.
-Some will be compensated with course credit and some will be paid \pounds 15 for their time.
-Sample size was determined in part due to constraints with counter-balancing; there are 16 different possible orders of tasks/conditions; we will run four participants in each order for a total of 64.
+64 students from the University of Aberdeen took part in this study.
+Participants were compensated for their time with either  course credit or \pounds 15.
 All participants will sign a form giving informed consent.
-The study has already been approved by the University of Aberdeen Psychology Ethics Committee.
+The study was approved by the University of Aberdeen Psychology Ethics Committee.
 
-A sample of 64 participants means we should be able to detect a correlations with $r > 0.342$ with $\alpha = 0.05$, $\beta = 0.80$ between the different visual search paradigms.
-Given the nature of our results, we see no need to apply a conservative correction for multiple comparisons.
+Sample size was determined in part by a power analysis, and in part due to constraints with counter-balancing; there are 16 different possible orders of tasks/conditions; we will run four participants in each order for a total of 64.
+$n = 64$ participants means we should be able to detect correlations with $r > 0.34$ with $\alpha = 0.05$, $\beta = 0.80$ between the different visual search paradigms.
+This compares to the already established value of $r \approx 0.8$ for the reliability for the ACVS paradigm.
 
@@
 
-The study consists of three different paradigms from the visual search literature in which large individual differences were found \cite{nowakowska2017, irons-leber2016, kristjansson2014}.
+The study consists of three paradigms from the visual search literature in which large individual differences have been noted found\cite{nowakowska2017, irons-leber2016, kristjansson2014}.
 Example stimuli can be seen in Figure \ref{fig:exampleStimuli}.
+A brief overview of each paradigm is given below, with full details in \textit{supplementary materials}.
 
-The display was presented on a 17-inch CRT monitor with a resolution of $1400 \times 
-1050$.
-However, due to a miscommunication, some participants (\textbf{get exact numbers from script}) were run at $1024 \times 768$ or $1600 \times 1200$.
-Stimulus generation, presentation and data collection were controlled by MATLAB and psychophysics toolbox \cite{brainard1997} run on a Powermac.
-
-A brief overview of each paradigm is given below, with full details in \textit{supplementary materials}.
+The display was presented on a 17-inch CRT monitor with a resolution of $1400 \times 1050$.
+Stimulus generation, presentation and data collection were controlled by MATLAB and the psychophysics and eyelink toolboxes \cite{brainard1997,cornelissen2002} run on a Powermac.
 

### 2018-08-09 writeup/manuscript.tex
Tidying up methods and results draft

@@
 Previous research has investigated the relationship between these behaviours to psychometric measures, but to date, these differences have not shown strong correlations with other attributes.
-In the ACVS paradigm, Irons \& Leber found no evidence of a correlation between the proportion of optimal choices made by observers and measures of visual working memory or trait compulsivity\cite{irons-leber2018}.
+In the ACVS paradigm, Irons \& Leber found no evidence of a correlation between the proportion of optimal choices made by observers and measures of visual working memory or trait compulsivity\cite{irons-leber2016}.
 Similarly, the differences foraging behaviour are not accounted for by working memory or inhibitory control\cite{johannesson2017}.
@@
 
+The methods and planned analysis for this study were registered on the Open Science Framework\footnote{insert URL} before data collection started.
+
 \subsection{Participants}
@@
 
-Sample size was determined in part by a power analysis, and in part due to constraints with counter-balancing; there are 16 different possible orders of tasks/conditions; we will run four participants in each order for a total of 64.
+Sample size was determined in part by a power analysis, and in part due to constraints with counter-balancing.
 $n = 64$ participants means we should be able to detect correlations with $r > 0.34$ with $\alpha = 0.05$, $\beta = 0.80$ between the different visual search paradigms.
@@
 A brief overview of each paradigm is given below, with full details in \textit{supplementary materials}.
+The three tasks will be completed over two sessions, approximately one week apart.
+The split-half array search will be run in both sessions allowing us to measure test-retest reliability.
+The order in which participants completed the tasks was counter-balanced.
+There are 16 different possible orders of tasks/conditions; we will run four participants in each order for a total of 64.
 
@@
 
-The ACVS was based on the task described in \cite{irons-leber2018}, Experiment 1.
+The ACVS was based on the task described in \cite{irons-leber2016}, Experiment 1.
 
@@
 
-\subsection{Planned Analysis}
+\subsection{Analysis Plan}
 
@@
 
-In order to characterise an individual's behaviour in this task, we will compute the proportion of the first $n$ fixations that were on heterogeneous (difficult) side of the stimuli, over all target absent trials\footnote{Only take correct trials?}.
-\cite{nowakowska2017} demonstrated a strong correlation between an this metric (for $n=5$) and reaction times ($r=.53$).
-However, a re-analysis of their data shows that an even stronger correlation is obtained with $n=3$.
+Only trials with a correct target absent/present response were included in the analysis.
+All reaction times were $\log_2$ transformed.
+In order to characterise an individual's behaviour in this task, we will compute the proportion of the first $n$ fixations that were on the heterogeneous (difficult) side of the stimuli, over all correct target absent trials.
+Previous work\cite{nowakowska2017} demonstrated a strong correlation between this metric (for $n=5$) and reaction times ($r=.53$).
 
@@
 Our results are broadly in line with \cite{nowakowska2017}.
+Some participants performed exceptionally poorly and were removed from further analysis (full details given in the \textit{supplementary materials}).
+
 The correlation between accuracy and reaction times between the two sessions is shown in Figure \ref{fig:splithalf_summary}(a, b).
@@
 
-The results for the ACVS were consistent with our previous findings \cite{irons-leber2016,irons-leber2018} (see Figure 3?).
-%Figure 3 (?
-AC_OptCh_x_AllSw) shows that there were wide individual differences in both percent option (range $33.62\%$ – $97.50\%$, $M = 56.99$, $SD = 14.75$) and switch rate (range = $0\% - 56.68\%$, $M = 28.46$, $SD = 13.54$).
-Although we did not assess it here, good test-retest reliability has been found previously for both percent optimal ($r = .83$) and switch rate ($r = .77$) \cite{irons-leber,2018}.
+The results for the ACVS were consistent with our previous findings \cite{irons-leber2016,irons-leber2018} (see Figure \ref{fig:acvs_summary}).
+shows that there were wide individual differences in both percent option (range $33.62\%$ – $97.50\%$, $M = 56.99$, $SD = 14.75$) and switch rate (range = $0\% - 56.68\%$, $M = 28.46$, $SD = 13.54$).
+Although we did not assess it here, good test-retest reliability has been found previously for both percent optimal ($r = .83$) and switch rate ($r = .77$) \cite{irons-leber2016}.
+
+\begin{figure}
+\centering
+\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/adaptchoice/AC_OptCh_x_SwRate.png}}
+\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/adaptchoice/AC_groupplot.pdf}}
+\caption{Needs checked and updated. replace png with pdf!}
+\label{fig:acvs_summary}
+\end{figure}
 
@@
 
+\begin{figure}
+\centering
+\includegraphics[width=\textwidth]{../Scripts/foraging/FG_IndivDiffsFig.png}
+\caption{What do we want this figure to actually be?}
+\label{fig:foraging_summary}
+\end{figure}
+
 \subsection{Correlations Between Paradigms}
 
-The results above demonstrate that we have successfully replicated the previous findings around individual differences in visual search strategy.
+The results above demonstrate that we have successfully replicated the previous findings around individual differences in visual search strategy in each of the three paradigms.
+We now turn our attention to which an individual's performance in one of the tasks tells us about how well they will do in the other two.
 As an initial sweep, we look at overall performance in terms of RT (note that this can be influenced not only by strategy, but also by individuals' abilities, such as their information-processing speed and their ability to ignore distractors).
@@
 This can be contrasted with the relatively high test-retest correlations of $r \in [0.65.
-0.86]$ in the split-half paradigm and $r \in [0.72, 0.9]$ for the adaptive choice paradigm\cite{irons-leber2016}.
+0.86]$ in the split-half paradigm and $r \in [0.72, 0.9]$ for the adaptive choice paradigm\cite{irons-leber2018}.
 [AM I RIGHT IN THINKING ARNI AND CO HAVE MEASURES FOR THEIR PARADIGM???]
@@
 From \cite{proulx2011} - \textit{Vogel and colleagues have found that an individual’s ability to remember a greater number of items using working memory is related to a filtering capacity in visual search that suppresses attentional capture by distracting visual information [10,11,12].
-Behavioral work in visual search has extended this research to
+Behavioural work in visual search has extended this research to
 demonstrate that working memory correlates only with top-down

### 2018-08-09 writeup/manuscript.tex
Fixing comment on Proulx

@@
 Large individual differences were found with respect to the number of saccades participants made while monitoring the stimulus, and this was negatively correlated with detection performance.
-Proulx\cite{proulx2011} demonstrated that the different weighting between top-down and bottom-up factors in a conjunction search task explained \ldots Interestingly, they claim that around a third of participants were unaware of the search strategy they employed.
+Proulx\cite{proulx2011} demonstrated that the different weighting between top-down and bottom-up factors in a conjunction search task explained some of the variation in how participants did in an attentional capture task.
+However, only a third of participants were unaware of the search strategy they employed.
 

### 2018-08-10 writeup/manuscript.tex
Changing figure size and reordering results section

@@
 The results above demonstrate that we have successfully replicated the previous findings around individual differences in visual search strategy in each of the three paradigms.
-We now turn our attention to which an individual's performance in one of the tasks tells us about how well they will do in the other two.
-As an initial sweep, we look at overall performance in terms of RT (note that this can be influenced not only by strategy, but also by individuals' abilities, such as their information-processing speed and their ability to ignore distractors).
-Are individuals who are fast on one visual search task fast on another?
-In all comparisons the correlations are weak, typically $0.27 < r <0.30$ but positive (Figure \ref{fig:between_para_rt}).
-None of these correlations are statistically significant ($p>0.05$).
-Even if we optimistically take all the data together as suggesting a robust correlation in reaction times from paradigm to paradigm, the upper bound of $r=0.30$ this correlation only accounts for at best $10\%$\footnote{i.e., $R^2 = 0.3^2 = 0.09$} an individual's performance.
+Furthermore, the split-half paradigm has a test-retest reliability of $r \in [0.65.
+0.86]$, similar to that of the ACVS task ($r \in [0.72, 0.9]$), suggesting that the strategies different individuals chose to use in each of these tasks are somewhat stable.
+Given this, we now investigate the extent to which an individual's performance in one of the tasks tells us about how well they will do in the other two.
+
+The results presented above convincingly demonstrate that there are no strong correlations between the split-half, adaptive choice and foraging visual search paradigms.
+While we have successfully replicated the range of individual differences found in each of these studies, with a larger sample size than the original papers, the between-paradigm correlations give at most $R^2 = 0.1$, and this is a generous interpretation that would fail to pass the usual criteria for null hypothesis significance testing.
+Knowing how one person will behave in one of these paradigms apparently tells us very little about how they will perform in the others.
+This can be contrasted with the relatively high test-retest correlations of  in the split-half paradigm and  for the adaptive choice paradigm\cite{irons-leber2018}.
+[AM I RIGHT IN THINKING ARNI AND CO HAVE MEASURES FOR THEIR PARADIGM???]
 
@@
 \end{figure}
+
+ As an initial sweep, we look at overall performance in terms of RT (note that this can be influenced not only by strategy, but also by individuals' abilities, such as their information-processing speed and their ability to ignore distractors).
+Are individuals who are fast on one visual search task fast on another?
+In all comparisons the correlations are weak, typically $0.27 < r <0.30$ but positive (Figure \ref{fig:between_para_rt}).
+None of these correlations are statistically significant ($p>0.05$).
+Even if we optimistically take all the data together as suggesting a robust correlation in reaction times from paradigm to paradigm, the upper bound of $r=0.30$ this correlation only accounts for at best $10\%$\footnote{i.e., $R^2 = 0.3^2 = 0.09$} an individual's performance.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The results presented above convincingly demonstrate that there are no strong correlations between the split-half, adaptive choice and foraging visual search paradigms.
-While we have successfully replicated the range of individual differences found in each of these studies, with a larger sample size than the original papers, the between-paradigm correlations give at most $R^2 = 0.1$, and this is a generous interpretation that would fail to pass the usual criteria for null hypothesis significance testing.
-Knowing how one person will behave in one of these paradigms apparently tells us very little about how they will perform in the others.
-This can be contrasted with the relatively high test-retest correlations of $r \in [0.65.
-0.86]$ in the split-half paradigm and $r \in [0.72, 0.9]$ for the adaptive choice paradigm\cite{irons-leber2018}.
-[AM I RIGHT IN THINKING ARNI AND CO HAVE MEASURES FOR THEIR PARADIGM???]
 

### 2018-08-10 Scripts/compareExp.R

@@ -1,7 +1,8 @@
 library(tidyverse)
 
-figXn <- 6
-figYn <- 4
+
+figXn <- 3.5
+figYn <- 2.5
 
 dat <- read_csv("summaryData.csv")
 

### 2018-08-10 Writeup/sup_mat.tex
more progres!

@@
 \section{Paradigm Details}
+
+% These are the sizes of the boxes for each resolution, I'm not sure how best to incorporate this into the text though... here's a table for the meantime;
+% Thanks! Stim size is not critical for our experiment, so it doesn't matter too much if it's too complicated (just habit to have it in there :)
+\begin{table*}
+	\centering
+	\small
+	\begin{tabular}{cc|c}
+	    Experiment	    &	Resolution	     & Size of stim \\
+		\hline
+		Adaptive Choice & $1024 \times 768$  & $\approx$$1.8^{\circ}$ \\
+		Adaptive Choice & $1400 \times 1050$ & $\approx$$1.3^{\circ}$ \\
+		Adaptive Choice & $1600 \times 1200$ & $\approx$$1.1^{\circ}$ \\
+		Foraging        & $1024 \times 768$  & $\approx$$1^{\circ}$ \\
+		Foraging        & $1400 \times 1050$ & $\approx$$0.7^{\circ}$ \\
+		Foraging        & $1600 \times 1200$ & $\approx$$0.6^{\circ}$ \\
+	\end{tabular}
+	\caption{Size of stimuli for each experiment and screen resolution}
+	\label{tab:Screen_Res}
+\end{table*}
 

### 2018-08-10 writeup/manuscript.tex
more progres!

@@
 \maketitle
-
+\twocolumn
 A striking example of the effect of strategy is given by Boot and colleagues\cite{boot2006}.
@@
 Furthermore, the degree to which they made saccades in line with the optimal search strategy was strongly correlated with their reaction times.
+A related version of this paradigm has been used in research in to (simulated) hemianopia\cite{nowakowska2016,nowakowska2018}.
+\ldots
 
@@
 
-\begin{figure}
+\begin{figure*}
 \centering
@@
 \subfigure[][]{\includegraphics[height=3cm]{figures/foraging.png}}
-\caption{Example stimulus from the (a) \textit{split-half}, (b) \textit{adaptive choice} and (c) \textit{foraging} paradigms}
+\caption{Example stimulus from the (a) \textit{split-half}, (b) \textit{adaptive choice} and (c) \textit{foraging} paradigms.}
 \label{fig:exampleStimuli}
-\end{figure}
+\end{figure*}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Methods}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 The ACVS was based on the task described in \cite{irons-leber2016}, Experiment 1.
-
-% These are the sizes of the boxes for each resolution, I'm not sure how best to incorporate this into the text though... here's a table for the meantime;
-% Thanks! Stim size is not critical for our experiment, so it doesn't matter too much if it's too complicated (just habit to have it in there :)
-\begin{table*}
-	\centering
-	\small
-	\begin{tabular}{cc|c}
-	    Experiment	    &	Resolution	     & Size of stim \\
-		\hline
-		Adaptive Choice & $1024 \times 768$  & $\approx$$1.8^{\circ}$ \\
-		Adaptive Choice & $1400 \times 1050$ & $\approx$$1.3^{\circ}$ \\
-		Adaptive Choice & $1600 \times 1200$ & $\approx$$1.1^{\circ}$ \\
-		Foraging        & $1024 \times 768$  & $\approx$$1^{\circ}$ \\
-		Foraging        & $1400 \times 1050$ & $\approx$$0.7^{\circ}$ \\
-		Foraging        & $1600 \times 1200$ & $\approx$$0.6^{\circ}$ \\
-	\end{tabular}
-	\caption{Size of stimuli for each experiment and screen resolution}
-	\label{tab:Screen_Res}
-\end{table*}
-
-% Let me know if you want me to shift some of this into the Supp
 Each search display was composed of 54 small squares arranged in three concentric rings around fixation, with 12, 18 and 24 items in the inner, middle and outer rings respectively.
@@
 
-\subsection{Analysis Plan}
-
-% Structure-wise, would it be easier for the reader to have methods and planned analyses nested under each task?
-
-\subsubsection{Split-half array search}
-
-Only trials with a correct target absent/present response were included in the analysis.
-All reaction times were $\log_2$ transformed.
-In order to characterise an individual's behaviour in this task, we will compute the proportion of the first $n$ fixations that were on the heterogeneous (difficult) side of the stimuli, over all correct target absent trials.
-Previous work\cite{nowakowska2017} demonstrated a strong correlation between this metric (for $n=5$) and reaction times ($r=.53$).
-
-\subsubsection{Attentional Control}
-
-Participants with accuracy more than 3 SD below the group mean were excluded from analyses.
-For RT analyses, trials with RTs less than 300ms or more than 3 SD about the participant's mean were excluded.
-
-Two measures of individual strategy use were used: 1) Optimal choices, defined as percent of plateau trials in which the individual chose the optimal target (i.e., the target with the fewest distractors.
-When the variable distractor was red, the optimal choice was blue, and vice versa), and 2) Switch rate, the percent of trials in which the individual switched target colour (i.e., the colour chosen on trial N was different to the colour chosen on trial N-1).
-
-\subsubsection{Conjunction Foraging}
-
-Only completed, accurate trials were analysed.
-RTs were defined across the entire trial (i.e., from the start of the trial until the final target was collected).
-The main measure of interest was average run length per trial.
-A run was defined as a succession of one or more of the same target type, which was followed and preceded by the other target or no target.
-The average run length was the average number of target selections in a run.
-
-\subsection{Exploratory Analysis}
-
-We will carry out additional analysis, above and beyond what has been documented above, but the exact nature of this will be contingent on the nature of the results.
-Something like PCA may be interesting.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Results}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \subsubsection{Split-half Array Search}
-Our results are broadly in line with \cite{nowakowska2017}.
+Our results are in line with the original split-half array study\cite{nowakowska2017}.
+Only trials with a correct target absent/present response were included in the analysis.
 Some participants performed exceptionally poorly and were removed from further analysis (full details given in the \textit{supplementary materials}).
+All reaction times were $\log_2$ transformed.
+In order to characterise an individual's behaviour in this task, we will compute the proportion of the first $n$ fixations that were on the heterogeneous (difficult) side of the stimuli, over all correct target absent trials.
+Previous work\cite{nowakowska2017} demonstrated a strong correlation between this metric (for $n=5$) and reaction times ($r=.53$).
 
@@
 
-The results for the ACVS were consistent with our previous findings \cite{irons-leber2016,irons-leber2018} (see Figure \ref{fig:acvs_summary}).
-shows that there were wide individual differences in both percent option (range $33.62\%$ – $97.50\%$, $M = 56.99$, $SD = 14.75$) and switch rate (range = $0\% - 56.68\%$, $M = 28.46$, $SD = 13.54$).
-Although we did not assess it here, good test-retest reliability has been found previously for both percent optimal ($r = .83$) and switch rate ($r = .77$) \cite{irons-leber2016}.
+Participants with accuracy more than 3 SD below the group mean were excluded from analyses.
+For RT analyses, trials with RTs less than 300ms or more than 3 SD about the participant's mean were excluded.
+
+Two measures of individual strategy use were used: 1) Optimal choices, defined as percent of plateau trials in which the individual chose the optimal target (i.e., the target with the fewest distractors.
+When the variable distractor was red, the optimal choice was blue, and vice versa), and 2) Switch rate, the percent of trials in which the individual switched target colour (i.e., the colour chosen on trial N was different to the colour chosen on trial N-1).
+
+The results for the ACVS were consistent with previous findings \cite{irons-leber2016,irons-leber2018} (see Figure \ref{fig:acvs_summary}).
+shows that there were wide individual differences in both percent option (range $33.62\%$ - $97.50\%$, $M = 56.99$, $SD = 14.75$) and switch rate (range = $0\% - 56.68\%$, $M = 28.46$, $SD = 13.54$).
 
@@
 
+Only completed, accurate trials were analysed.
+RTs were defined across the entire trial (i.e., from the start of the trial until the final target was collected).
+The main measure of interest was average run length per trial.
+A run was defined as a succession of one or more of the same target type, which was followed and preceded by the other target or no target.
+The average run length was the average number of target selections in a run.
+
 The multiple-target foraging results were also in line previous findings \cite{kristjansson2014,johannesson2016}.
@@
 However, both showed significant individual variation: Feature run length varied between 1.87 and 20, and conjunction run length varied between 1.00 and 19.67.
-Figure 4 (?) depicts run length across the trials separately for each individual.
-Twenty ``super-searchers'' were revealed, identified by short run lengths for both feature and conjunction targets [THAT NUMBER IS JUST BASED ON EYE-BALLING THE FIGURE, BUT WE COULD COME UP WITH SOME SORT OF PRECIOUS CUT OFF – WHAT DO YOU THINK?].
+Figure \ref{fig:foraging_summary} depicts run length across the trials separately for each individual.
+Twenty ``super-searchers'' were revealed, identified by short run lengths for both feature and conjunction targets.
 
-\begin{figure}
+\begin{figure*}
 \centering
@@
 \label{fig:foraging_summary}
-\end{figure}
+\end{figure*}
 
@@
 
-The results presented above convincingly demonstrate that there are no strong correlations between the split-half, adaptive choice and foraging visual search paradigms.
+The results presented in Figure \ref{fig:between_para_rt} convincingly demonstrate that there are no strong correlations between the strategies by observers in split-half, adaptive choice and foraging visual search paradigms\footnote{More comparisons are presented in the \textit{supplementary materials.}}.
+
+\begin{figure}
+\centering
+\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/scratch/ls_v_ac_opt.pdf}}
+\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/scratch/ls_v_ac_sr.pdf}}
+\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/scratch/ls_v_fg_runlength.pdf}}
+\caption{Correlation between the optimal behaviour in the split-half and (a) adaptive choice paradigms; (b) average run length in the conjunction foraging paradigm; and (b) optimal behaviour in the adaptive choice paradigm and mean run length on the conjunction experiment.}
+\label{fig:between_para_rt}
+\end{figure}
+
+While there is no indication of a relationship between strategies across the different paradigms, perhaps there is still a correlation between the reaction times due to some participants having higher levels of motivation than others, or stable speed-accuracy trade-offs between the different tasks.
+Differences relating to their information-processing speed and their ability to ignore distractors would also play in to such a correlation.However, as with search strategy, we again find all the correlations to be weak, typically $0.27 < r <0.30$ but positive (Figure \ref{fig:between_para_rt}).
+None of these correlations are statistically significant ($p>0.05$).
+Even if we optimistically take all the data together as suggesting a robust correlation in reaction times from paradigm to paradigm, the upper bound of $r=0.30$ means that this correlation only accounts for at best $10\%$\footnote{i.e., $R^2 = 0.3^2 = 0.09$} an individual's performance.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Discussion}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 While we have successfully replicated the range of individual differences found in each of these studies, with a larger sample size than the original papers, the between-paradigm correlations give at most $R^2 = 0.1$, and this is a generous interpretation that would fail to pass the usual criteria for null hypothesis significance testing.
@@
 [AM I RIGHT IN THINKING ARNI AND CO HAVE MEASURES FOR THEIR PARADIGM???]
-
-\begin{figure}
-\centering
-\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/scratch/ls_v_ac_mean_log2rt.pdf}}
-\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/scratch/ls_v_ac_opt.pdf}}
-\caption{Correlation between the split-half and adaptive choice paradigms for (a) reaction times and (b) optimal behaviour.}
-\label{fig:between_para_rt}
-\end{figure}
-
- As an initial sweep, we look at overall performance in terms of RT (note that this can be influenced not only by strategy, but also by individuals' abilities, such as their information-processing speed and their ability to ignore distractors).
-Are individuals who are fast on one visual search task fast on another?
-In all comparisons the correlations are weak, typically $0.27 < r <0.30$ but positive (Figure \ref{fig:between_para_rt}).
-None of these correlations are statistically significant ($p>0.05$).
-Even if we optimistically take all the data together as suggesting a robust correlation in reaction times from paradigm to paradigm, the upper bound of $r=0.30$ this correlation only accounts for at best $10\%$\footnote{i.e., $R^2 = 0.3^2 = 0.09$} an individual's performance.
-
-[I WONDER IF THIS SHOULD GO BEFORE THE RT CORRELATIONS?
-SINCE AS YOU SAY, THIS IS THE MAIN AIM OF THE PAPER.
-THEN RT CORRELATIONS COULD GO AS A SECONDARY AIM] Given the low correlations between reaction times, it seems unlikely that we will find that individuals who search efficiently and optimally in one paradigm will search well in another (the original motivation for our study) [I WOULD BE INCLINED NOT TO SAY THIS, BECAUSE IT SEEMS TO MINIMIZE THE PURPOSE OF LOOKING AT STRATEGY AT ALL.
-IE IT SUGGESTS THAT ALL OF THE VARIATION IN STRATEGY COULD BE ENCAPSULATED BY RT.
-BUT THERE ARE OTHER FACTORS THAT ALSO INFLUENCE RT].
-The analysis supports this hypothesis.
-For example, the correlation between the proportion of fixations to the heterogeneous side of the display in the split-half paradigm, and proportion of optimal targets found in the adaptive choice task is $r=-0.03$.
-Further results are presented in supplementary materials.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Discussion}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2018-08-10 Scripts/compareExp.R

@@ -72,9 +72,9 @@ plt <- plt + geom_smooth(method = lm, colour = "black", fullrange = TRUE, linety
 plt <- plt + theme_bw()
 plt <- plt + scale_x_continuous("split-half: mean log rt (ms)",
    limits = c(8, 14.1), breaks = x_breaks, labels = x_labels, expand = c(0, 0))
-plt <- plt + scale_y_continuous("foraging (conjunction): mean log rt (ms)",
+plt <- plt + scale_y_continuous("foraging (conj.): mean log rt (ms)",
     limits = c(y_breaks[1], y_breaks[3]), breaks = y_breaks, labels = y_labels,expand = c(0, 0))
-plt <- plt + geom_text(label=paste("r =", r_conj), x= 12, y=14.5)
+# plt <- plt + geom_text(label=paste("r =", r_conj), x= 12, y=14.5)
 plt <- plt + coord_cartesian(xlim=c(min(x_breaks),max(x_breaks)+0.2), ylim=c(y_breaks[1],max(y_breaks)))
 plt <- plt + theme(
   panel.grid.major = element_blank(), 
@@ -100,7 +100,7 @@ plt <- plt + scale_x_continuous("adaptive choice: mean log rt (ms)",
     limits = c(x_breaks[1], x_breaks[3]+0.05), breaks = x_breaks, labels = x_labels, expand = c(0, 0))
 plt <- plt + scale_y_continuous("foraging (feature): mean log rt (ms)",
     limits = c(y_breaks[1], y_breaks[3]), breaks = y_breaks, labels = y_labels, expand = c(0, 0))
-plt <- plt + geom_text(label=paste("r =", r_feat), x= 11.1, y= 15)
+# plt <- plt + geom_text(label=paste("r =", r_feat), x= 11.1, y= 15)
 plt <- plt + theme(
   panel.grid.major = element_blank(), 
   panel.grid.minor = element_blank())
@@ -116,7 +116,7 @@ plt <- plt + geom_smooth(method = lm, colour = "black", fullrange = TRUE, linety
 plt <- plt + theme_bw()
 plt <- plt + scale_x_continuous("adaptive choice: mean log rt (ms)",
     limits = c(x_breaks[1], x_breaks[3]+0.05), breaks = x_breaks, labels = x_labels, expand = c(0, 0))
-plt <- plt + scale_y_continuous("foraging (conjunction): mean log rt (ms)",
[…]

### 2018-08-13 Scripts/correlation_collection.R
new correlation figure example

@@ -1,0 +1,47 @@
+library(tidyverse)
+library(forcats)
+
+figXn <- 3.5
+figYn <- 2.5
+
+dat <- read_csv("summaryData.csv")
+
+
+cor_dat <- tibble(
+	comparison = c(
+		"test-retest - ls-rt absent", 
+		"test-retest - ls-rt a versus b hard", 
+		"test-retest - ls-rt a versus b easy",
+		"test-retest - acvs prop optimal",
+		"test-retest - acvs switch rate"),
+	estimate = c(0,0,0,0.83, 0.77),
+	lower = c(0.65, 0.66, 0.56, 0.72, 0.63),
+	upper = c(0.86, 0.87, 0.82, 0.90, 0.87))
+
+add_r_95 <- function(x1, x2, df) {
+	ci95 <- cor.test(x1[[1]], x2[[1]])
+
+	df <- bind_rows(df, 
+		tibble(
+			comparison = paste(names(x1), names(x2), sep = "-"),
+			estimate = ci95$estimate,
+			lower = ci95$conf.int[1],
+			upper = ci95$conf.int[2]))
+
+	return(df)
+}
+
+cor_dat <- add_r_95(dat[3], dat[8], cor_dat)
+
+
+cor_dat$comparison <- as_factor(cor_dat$comparison)
+
+plt <- ggplot(cor_dat, aes(x = comparison, ymin = lower, ymax = upper))
+plt <- plt + geom_errorbar()
+plt <- plt + geom_hline(yintercept = 0)
+plt <- plt + scale_y_continuous(limits = c(-0.5, 1), expand = c(0,0))
+plt <- plt + theme_bw() 
+plt <- plt + theme(
+	axis.title.x = element_blank(),
+	axis.text.x = element_text(angle = 60, hjust = 1))
+ggsave("scratch/cor_comparison.pdf", width = 4, height = 4)

### 2018-08-13 Scripts/correlation_collection.R
edits in cinema bar!

@@ -9,39 +9,51 @@ dat <- read_csv("summaryData.csv")
 
 cor_dat <- tibble(
 	comparison = c(
-		"test-retest - ls-rt absent", 
-		"test-retest - ls-rt a versus b hard", 
-		"test-retest - ls-rt a versus b easy",
-		"test-retest - acvs prop optimal",
-		"test-retest - acvs switch rate"),
+		"ls-rt absent", 
+		"ls-rt a versus b hard", 
+		"ls-rt a versus b easy",
+		"acvs prop optimal",
+		"acvs switch rate"),
 	estimate = c(0,0,0,0.83, 0.77),
 	lower = c(0.65, 0.66, 0.56, 0.72, 0.63),
-	upper = c(0.86, 0.87, 0.82, 0.90, 0.87))
+	upper = c(0.86, 0.87, 0.82, 0.90, 0.87),
+	type = rep('test-retest', 5))
 
-add_r_95 <- function(x1, x2, df) {
+add_r_95 <- function(x1, x2, df, t) {
 	ci95 <- cor.test(x1[[1]], x2[[1]])
 
-	df <- bind_rows(df, 
-		tibble(
+	new_r <- tibble(
 			comparison = paste(names(x1), names(x2), sep = "-"),
 			estimate = ci95$estimate,
 			lower = ci95$conf.int[1],
-			upper = ci95$conf.int[2]))
+			upper = ci95$conf.int[2],
+			type = t)
+
+	df <- bind_rows(df, new_r)
 
 	return(df)
 }
 
-cor_dat <- add_r_95(dat[3], dat[8], cor_dat)
+cor_dat <- add_r_95(dat[2], dat[5], cor_dat, 'rt-strat')
+cor_dat <- add_r_95(dat[7], -dat[8], cor_dat, 'rt-strat')
 
+cor_dat <- add_r_95(dat[3], dat[8], cor_dat, 'cross paradigm')
+cor_dat <- add_r_95(dat[3], dat[9], cor_dat, 'cross paradigm')
+cor_dat <- add_r_95(dat[3], dat[13], cor_dat, 'cross paradigm')
+cor_dat <- add_r_95(dat[3], dat[14], cor_dat, 'cross paradigm')
+cor_dat <- add_r_95(dat[8], dat[13], cor_dat, 'cross paradigm')
+cor_dat <- add_r_95(dat[8], dat[14], cor_dat, 'cross paradigm')
 
 cor_dat$comparison <- as_factor(cor_dat$comparison)
 
[…]

### 2018-08-13 writeup/manuscript.tex
edits in cinema bar!
add mention to mindfullness study

@@
 This strategy has previously been observers in animal foraging literature \cite{dawkins1971}.
-However, a sub-set of observers, termed `super-searchers' showed no switch cost.
+However, a sub-set of observers, termed `super-foragers' showed no switch cost.
+This study has been run on ipad touch displays\cite{kristjansson2014} (observers are asked to tap on as many targets as they can as quickly as possible) and a 3D computer game (in which participants navigate a squirrel through a virtual environment picking up targets with different feature combinations)[IN PREP], with super-foragers present in both versions.
+While test-retest reliability has not been measured explicitly for the foraging paradigm, the task was used as a measure to assess the effect of a six day long mindfulness retreat on cognitive performance\cite{hartkamp2017}.
+The data from this study will be re-analysed below to give us an estimate for the reliability of the mouse-click foraging task used in the present study.
 
@@
 
+\begin{figure*}
+\centering
+\includegraphics[width=\textwidth]{../Scripts/scratch/cor_comparison.pdf}
+\caption{Lots of correlations!}
+\label{fig:all_the_cor}
+\end{figure*}
+
 While there is no indication of a relationship between strategies across the different paradigms, perhaps there is still a correlation between the reaction times due to some participants having higher levels of motivation than others, or stable speed-accuracy trade-offs between the different tasks.

### 2018-08-13 Scripts/correlation_collection.R

@@ -1,5 +1,6 @@
 library(tidyverse)
 library(forcats)
+library(ggthemes)
 
 figXn <- 3.5
 figYn <- 2.5
@@ -9,15 +10,16 @@ dat <- read_csv("summaryData.csv")
 
 cor_dat <- tibble(
 	comparison = c(
-		"ls-rt absent", 
-		"ls-rt a versus b hard", 
-		"ls-rt a versus b easy",
+		"sh-rt absent", 
+		"sh-rt a versus b hard", 
+		"sh-rt a versus b easy",
+		"sh - strategy",
 		"acvs prop optimal",
 		"acvs switch rate"),
-	estimate = c(0,0,0,0.83, 0.77),
-	lower = c(0.65, 0.66, 0.56, 0.72, 0.63),
-	upper = c(0.86, 0.87, 0.82, 0.90, 0.87),
-	type = rep('test-retest', 5))
+	estimate = c(0,0,0, 0.73, 0.83, 0.77),
+	lower = c(0.65, 0.66, 0.56, 0.585, 0.72, 0.63),
+	upper = c(0.86, 0.87, 0.82, 0.832, 0.90, 0.87),
+	type = rep('test-retest', 6))
 
 add_r_95 <- function(x1, x2, df, t) {
 	ci95 <- cor.test(x1[[1]], x2[[1]])
@@ -44,16 +46,21 @@ cor_dat <- add_r_95(dat[3], dat[14], cor_dat, 'cross paradigm')
 cor_dat <- add_r_95(dat[8], dat[13], cor_dat, 'cross paradigm')
 cor_dat <- add_r_95(dat[8], dat[14], cor_dat, 'cross paradigm')
 
-cor_dat$comparison <- as_factor(cor_dat$comparison)
+cor_dat$comparison <- fct_rev(as_factor(cor_dat$comparison))
 
 plt <- ggplot(cor_dat, aes(x = comparison, ymin = lower, ymax = upper, colour = type))
-plt <- plt + geom_errorbar()
-plt <- plt + geom_hline(yintercept = 0)
+plt <- plt + geom_hline(yintercept = 0, linetype = 2)
+plt <- plt + geom_linerange(size = 1)
+plt <- ggplot(cor_dat, aes(x = comparison, ymin = lower, ymax = upper, colour = type))
+plt <- plt + geom_hline(yintercept = 0, linetype = 2)
+plt <- plt + geom_linerange(size = 1.5)
[…]

### 2018-08-13 Scripts/lineseg/3_saccadeStrategy.R

@@ -147,8 +147,8 @@ agg_dat = (filter(fix_dat, side!="central", n<=5, n>1, targSide=="absent")
   %>%  separate(b, into = c("b_strat", "b_lower", "b_upper"), sep = "_", convert = TRUE)) -> t_rt_dat
 
 
-
 cor.test(t_rt_dat$a_strat, t_rt_dat$b_strat)
+
 
 
 plt <- ggplot(t_rt_dat, aes(x = a_strat, y = b_strat, xmin = a_lower, xmax = a_upper, ymin = b_lower, ymax = b_upper))

### 2018-08-14 writeup/manuscript.tex
small edits

--- 2018-08-10 writeup/manuscript.tex
@@
 
-\linenumbers
+% \linenumbers
 %%%% Article title to be placed here
@@
 %%%% Keyword entries to be placed here %%%%
-\keywords{visual search, optimal behaviour,
-eye movements}
+\keywords{visual search, optimal behaviour, eye movements}
 
@@
 Eye movement strategies have also been shown to be an important source or individual differences in visual search tasks.
-Nowakowska, Clarke \& Hunt\cite{nowakowska2017} designed a simple search paradigm (referred to here as the Split-Half Search Array paradigm) to discriminate between optimal\cite{najemnik-geisler2008} and stochastic \cite{clarke2016} search strategies involving arrays of line segments (see Figure \ref{fig:exampleStimuli}.
-The line segments were arranged such that those on one side of the display all had a very similar orientation, while those on the other side had higher variance.
-This was done so that if the target appeared on the homogeneous side, it would be highly salient.
-Trials in which the target appeared on the heterogeneous side of the display would be much harder.
+Nowakowska, Clarke \& Hunt\cite{nowakowska2017} designed a simple search paradigm to discriminate between optimal\cite{najemnik-geisler2008} and stochastic \cite{clarke2016} search strategies.
+The task involved searching through arrays of line segments arranged such that those on one side of the display all had a very similar orientation, while those on the other side had higher variance (see Figure \ref{fig:exampleStimuli} for an example).
+This meant that if the target appeared on the homogeneous side, it would be highly salient.
+Trials in which the target appeared on the heterogeneous side of the display however would be much harder.
 With these stimuli, the optimal eye movement strategy is to only search the heterogeneous half of the stimulus, as targets on the homogeneous side can be detected with peripheral vision.
+We will refer to this paradigm here as the Split-Half Line Segment task (SHLS).
 While some participants initially searched the displays near optimally, others carried out strategies counter to this, failing to even match the performance of the stochastic searcher.
@@
 This strategy has previously been observers in animal foraging literature \cite{dawkins1971}.
-However, a sub-set of observers, termed `super-searchers' showed no switch cost.
+However, a sub-set of observers, termed `super-foragers' showed no switch cost.
+This study has been run on touch displays\cite{kristjansson2014} (observers are asked to tap on as many targets as they can as quickly as possible) and a 3D computer game (in which participants navigate a squirrel through a virtual environment picking up targets with different feature combinations)[IN PREP], with super-foragers present in both versions.
+While test-retest reliability has not been measured explicitly for the foraging paradigm, the task was used as a measure to assess the effect of a six day long mindfulness retreat on cognitive performance\cite{hartkamp2017}.
+From a re-analysis of these data, we can estimate that test-retest reliability is <INSERT DETAILS>
 
-Previous research has investigated the relationship between these behaviours to psychometric measures, but to date, these differences have not shown strong correlations with other attributes.
+Previous research has investigated the relationship between these behaviours to \hyphenation{psychometric} measures, but to date, these differences have not shown strong correlations with other attributes.
 In the ACVS paradigm, Irons \& Leber found no evidence of a correlation between the proportion of optimal choices made by observers and measures of visual working memory or trait compulsivity\cite{irons-leber2016}.
@@
 The aim of the present study is to investigate the extent to which individual differences are stable across different visual search paradigms.
-Are observers who use the optimal strategy in the split-half search arrays also more optimal in the ACVS task?
+Are observers who use the optimal strategy in the SHLS paradigm also more optimal in the ACVS task?
 Does it make sense to talk about `super-searchers' who show above average performance in a range of search tasks?
 Are the super-foragers consistently better or worse than more typical searchers in the other two paradigms?
-As a secondary question, we will measure the test-retest reliability of the differences found in the split-half array paradigm.
+As a secondary question, we will measure the test-retest reliability of the differences found in the SHLS paradigm.
 
@@
 
-The results presented in Figure \ref{fig:between_para_rt} convincingly demonstrate that there are no strong correlations between the strategies by observers in split-half, adaptive choice and foraging visual search paradigms\footnote{More comparisons are presented in the \textit{supplementary materials.}}.
+The results presented in Figure \ref{fig:all_the_cor} convincingly demonstrate that there are no strong correlations between the strategies by observers in split-half, adaptive choice and foraging visual search paradigms\footnote{More comparisons are presented in the \textit{supplementary materials.}}.
+
+% \begin{figure}
+% \centering
+% \subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/scratch/ls_v_ac_opt.pdf}}
+% \subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/scratch/ls_v_ac_sr.pdf}}
+% \subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/scratch/ls_v_fg_runlength.pdf}}
+% \caption{Correlation between the optimal behaviour in the split-half and (a) adaptive choice paradigms; (b) average run length in the conjunction foraging paradigm; and (b) optimal behaviour in the adaptive choice paradigm and mean run length on the conjunction experiment.}
+% \label{fig:between_para_rt}
+% \end{figure}
 
@@
 \centering
-\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/scratch/ls_v_ac_opt.pdf}}
-\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/scratch/ls_v_ac_sr.pdf}}
-\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/scratch/ls_v_fg_runlength.pdf}}
-\caption{Correlation between the optimal behaviour in the split-half and (a) adaptive choice paradigms; (b) average run length in the conjunction foraging paradigm; and (b) optimal behaviour in the adaptive choice paradigm and mean run length on the conjunction experiment.}
-\label{fig:between_para_rt}
+\includegraphics[width=6.5cm]{../Scripts/scratch/cor_comparison.pdf}
+\caption{Lots of correlations!}
+\label{fig:all_the_cor}
 \end{figure}
@@
 While there is no indication of a relationship between strategies across the different paradigms, perhaps there is still a correlation between the reaction times due to some participants having higher levels of motivation than others, or stable speed-accuracy trade-offs between the different tasks.
-Differences relating to their information-processing speed and their ability to ignore distractors would also play in to such a correlation.However, as with search strategy, we again find all the correlations to be weak, typically $0.27 < r <0.30$ but positive (Figure \ref{fig:between_para_rt}).
+Differences relating to their information-processing speed and their ability to ignore distractors would also play in to such a correlation.However, as with search strategy, we again find all the correlations to be weak, typically $0.27 < r <0.30$ but positive (Figure \ref{fig:all_the_cor}).
 None of these correlations are statistically significant ($p>0.05$).

### 2018-08-17 writeup/manuscript.tex
changing abbrevs.

@@
 The three tasks will be completed over two sessions, approximately one week apart.
-The split-half array search will be run in both sessions allowing us to measure test-retest reliability.
+The SHLS task will be run in both sessions allowing us to measure test-retest reliability.
 The order in which participants completed the tasks was counter-balanced.
@@
 
-\subsubsection{Split-half Array Search}
+\subsubsection{Split-half Line Segments}
 
@@
 The same screen was used as in the Split-half Array Search, however, due to changes of screen resolution, the size of the squares changed.
-Participants, were sat $\approx$47cm from the screen.
+Participants, were sat $\approx 47$cm from the screen.
 Of the 54 squares, 13 were red, 13 were blue, 14 were green and 14 were "variable".
-Variable distractors change colours from trial-to-trial according to a 24 trial cyclical pattern: the distractors would be red for 5 trials (called a "red plateau"), then across a period of 7 trials, they would change colour from almost red to magenta (at the fourth trial in the transition) to almost blue.
-The variable distractor would then be blue for 5 trials (blue plateau), and then transition back from almost blue through magenta to almost red.
+Variable distractors change colours from trial-to-trial according to a 24 trial cyclical pattern: the distractors would be red for five trials (called a "red plateau"), then across a period of seven trials, they would change colour from almost red to magenta (at the fourth trial in the transition) to almost blue.
+The variable distractor would then be blue for five trials (blue plateau), and then transition back from almost blue through magenta to almost red.
 
@@
 
-\subsubsection{Conjunction Foraging}
+\subsubsection{Mouse Click Foraging Task}
 
-The foraging task was based on \cite{kristjansson2014} and \cite{johannesson2016}.
-Participants completed the feature foraging and conjunction foraging tasks on separate days, with the order counterbalanced (was it counterbalanced?).
+The foraging task (MCFT) was based on \cite{kristjansson2014} and \cite{johannesson2016} except that we used a mouse clicks to register responses rather than a touchpad.
 
 In the feature foraging task, search displays contained 80 small circles, 20 red, 20 green, 20 blue  and 20 yellow.
-Stimuli were arranged in a 10 x 8 grid, but the position of each item within the grid space was jittered to create a more random spatial arrangement.
+Stimuli were arranged in a $10 \times 8$ grid, but the position of each item within the grid space was jittered to create a more random spatial arrangement.
 The location of item colours to grid locations was completely randomized.
@@
 If the participant clicked erroneously on a non-target, the trial was immediately ended and a replacement trial was begun.
-
 In the conjunction foraging task, search displays were composed of both circles and squares.
@@
 The procedure was otherwise identical to the feature foraging task.
-
-%% For the assignment of distractors and targets, we generated a two lists of random numbers (1-2 for easy search, and 1-4 for hard search).
-Pretty sure we did that because counterbalancing became very tricky once you accounted for that as well.
 
@@
 
-\subsubsection{Split-half Array Search}
-Our results are in line with the original split-half array study\cite{nowakowska2017}.
+\subsubsection{Split-half Line Segments}
+
+Our results are consistent with the original SHLS study\cite{nowakowska2017}.
 Only trials with a correct target absent/present response were included in the analysis.
-Some participants performed exceptionally poorly and were removed from further analysis (full details given in the \textit{supplementary materials}).
+Some participants performed exceptionally poorly and were removed from further analysis\footnote{Full details given in the \textit{supplementary materials}}.
 All reaction times were $\log_2$ transformed.
-In order to characterise an individual's behaviour in this task, we will compute the proportion of the first $n$ fixations that were on the heterogeneous (difficult) side of the stimuli, over all correct target absent trials.
-Previous work\cite{nowakowska2017} demonstrated a strong correlation between this metric (for $n=5$) and reaction times ($r=.53$).
+In order to characterise each participant's behaviour in this task, we will compute the proportion of the first $n$ fixations that were on the heterogeneous (difficult) side of the stimuli, over all correct target absent trials.
+Previous work\cite{nowakowska2017} demonstrated a strong correlation between this metric (for $n=5$) and reaction times ($r=.93$).
 
@@
 \caption{Each point represents a participant and the error-bars indicate 95\% confidence intervals.
-Correlation between the two sessions of the \textit{split-half} paradigm for (a)  accuracy (TP-heterogeneous trials only); (b) reaction times and (c) search strategy (TA trials only).
+Correlation between the two sessions of the SHLS paradigm for (a)  accuracy (TP-heterogeneous trials only); (b) reaction times and (c) search strategy (TA trials only).
 (d) Initial search strategy correlates with reaction times in both sessions.
@@
 
-\subsubsection{Adaptive Choice}
+\subsubsection{Adaptive Choice Visual Search}
 
@@
 
-\subsubsection{Conjunction Foraging}
+\subsubsection{Mouse Click Foraging Task}
 
@@
 
-The results presented in Figure \ref{fig:all_the_cor} convincingly demonstrate that there are no strong correlations between the strategies by observers in split-half, adaptive choice and foraging visual search paradigms\footnote{More comparisons are presented in the \textit{supplementary materials.}}.
+The results presented in Figure \ref{fig:all_the_cor} convincingly demonstrate that there are no strong correlations between any of the strategies chosen by observers in SHLS, ACVS and MCFT tasks \footnote{More comparisons are presented in the \textit{supplementary materials.}}.
+While there is no indication of a relationship between strategies across the different paradigms, perhaps there is still a correlation between the reaction times due to some participants having higher levels of motivation than others, or stable speed-accuracy trade-offs between the different tasks.
+Differences relating to their information-processing speed and their ability to ignore distractors would also play in to such a correlation.
+However, as with search strategy, we again find all the correlations to be weak, typically $0.27 < r <0.30$ but positive (Figure \ref{fig:all_the_cor}).
+None of these correlations are statistically significant ($p>0.05$).
+Even if we optimistically take all the data together as suggesting a robust correlation in reaction times from paradigm to paradigm, the upper bound of $r=0.30$ means that this correlation only accounts for at best $10\%$\footnote{i.e., $R^2 = 0.3^2 = 0.09$} an individual's performance.
 
@@
 
-While there is no indication of a relationship between strategies across the different paradigms, perhaps there is still a correlation between the reaction times due to some participants having higher levels of motivation than others, or stable speed-accuracy trade-offs between the different tasks.
-Differences relating to their information-processing speed and their ability to ignore distractors would also play in to such a correlation.However, as with search strategy, we again find all the correlations to be weak, typically $0.27 < r <0.30$ but positive (Figure \ref{fig:all_the_cor}).
-None of these correlations are statistically significant ($p>0.05$).
-Even if we optimistically take all the data together as suggesting a robust correlation in reaction times from paradigm to paradigm, the upper bound of $r=0.30$ means that this correlation only accounts for at best $10\%$\footnote{i.e., $R^2 = 0.3^2 = 0.09$} an individual's performance.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Mention \cite{vogel2008}.
-From \cite{proulx2011} - \textit{Vogel and colleagues have found that an individual’s ability to remember a greater number of items using working memory is related to a filtering capacity in visual search that suppresses attentional capture by distracting visual information [10,11,12].
+From \cite{proulx2011} - \textit{Vogel and colleagues have found that an individual's ability to remember a greater number of items using working memory is related to a filtering capacity in visual search that suppresses attentional capture by distracting visual information [10,11,12].
 Behavioural work in visual search has extended this research to

### 2018-08-17 Scripts/correlation_collection.R

@@ -48,6 +48,14 @@ cor_dat <- add_r_95(dat[8], dat[14], cor_dat, 'cross paradigm')
 
 cor_dat$comparison <- fct_rev(as_factor(cor_dat$comparison))
 
+cor_dat$comparison <- fct_recode(cor_dat$comparison, 
+	`ACVS (opt) - MCFT (rl)`  = "ac_propOpt-fg_conj_run_length",
+	`ACVS (opt) - MCFT (rn)`  = "ac_propOpt-fg_conj_run_num",
+	`SHLS (opt) - MCFT (rl)` = "ls_prop_hetero-fg_conj_run_length",
+	`SHLS (opt) - MCFT (rn)` = "ls_prop_hetero-fg_conj_run_num",
+	`SHLS (opt) - ACVS (sw)` = "ls_prop_hetero-ac_switchRate",
+	`SHLS (opt) - ACVS (opt)` = "ls_prop_hetero-ac_propOpt")
+
 plt <- ggplot(cor_dat, aes(x = comparison, ymin = lower, ymax = upper, colour = type))
 plt <- plt + geom_hline(yintercept = 0, linetype = 2)
 plt <- plt + geom_linerange(size = 1)
@@ -63,4 +71,5 @@ plt <- plt + theme(
 	legend.position = "top",
 	axis.title.y = element_blank())
 
-ggsave("scratch/cor_comparison.pdf", width = 7, height = 7)
+ggsave("scratch/cor_comparison.pdf", width = 5, height = 7)
+ggsave("scratch/cor_comparison.png", width = 5, height = 7)

### 2018-08-17 Scripts/correlation_collection.R
bug s due to changed column names. need fixed

@@ -15,11 +15,13 @@ cor_dat <- tibble(
 		"sh-rt a versus b easy",
 		"sh - strategy",
 		"acvs prop optimal",
-		"acvs switch rate"),
-	estimate = c(0,0,0, 0.73, 0.83, 0.77),
-	lower = c(0.65, 0.66, 0.56, 0.585, 0.72, 0.63),
-	upper = c(0.86, 0.87, 0.82, 0.832, 0.90, 0.87),
-	type = rep('test-retest', 6))
+		"acvs switch rate",
+		"MCFT (rt)",
+		"MCFT (rn)"),
+	estimate = c(0,0,0, 0.73, 0.83, 0.77, 0, 0),
+	lower = c(0.65, 0.66, 0.56, 0.585, 0.72, 0.63, -1, -1),
+	upper = c(0.86, 0.87, 0.82, 0.832, 0.90, 0.87, 1, 1),
+	type = rep('test-retest', 8))
 
 add_r_95 <- function(x1, x2, df, t) {
 	ci95 <- cor.test(x1[[1]], x2[[1]])
@@ -36,8 +38,10 @@ add_r_95 <- function(x1, x2, df, t) {
 	return(df)
 }
 
-cor_dat <- add_r_95(dat[2], dat[5], cor_dat, 'rt-strat')
-cor_dat <- add_r_95(dat[7], -dat[8], cor_dat, 'rt-strat')
+cor_dat <- add_r_95(dat[3], dat[5], cor_dat, 'rt-strat')
+cor_dat <- add_r_95(dat[8], dat[7], cor_dat, 'rt-strat')
+cor_dat <- add_r_95(dat[13], dat[12], cor_dat, 'rt-strat')
+cor_dat <- add_r_95(dat[14], dat[12], cor_dat, 'rt-strat')
 
 cor_dat <- add_r_95(dat[3], dat[8], cor_dat, 'cross paradigm')
 cor_dat <- add_r_95(dat[3], dat[9], cor_dat, 'cross paradigm')
@@ -46,15 +50,39 @@ cor_dat <- add_r_95(dat[3], dat[14], cor_dat, 'cross paradigm')
 cor_dat <- add_r_95(dat[8], dat[13], cor_dat, 'cross paradigm')
 cor_dat <- add_r_95(dat[8], dat[14], cor_dat, 'cross paradigm')
 
+cor_dat <- add_r_95(dat[5], dat[7], cor_dat,  'cross paradigm')
[…]

### 2018-08-17 Scripts/lineseg/3_saccadeStrategy.R

@@ -172,8 +172,8 @@ ggsave("scratch/strat_corr.png", width = figYn, height = figYn)
 
 # --------------------------------------------------------------------------------
 # output data for cross experiment correlations!
-# base statistic for correlation on only first 3 fixations
-# use session B only
+# 
+# over both sessions
 # --------------------------------------------------------------------------------
 
-write_csv(filter(dat, session == "b"), "scratch/lineseg_output.csv")
+write_csv(filter(dat, session == "b"),  "scratch/lineseg_output.csv")

### 2018-08-20 writeup/manuscript.tex
bug s due to changed column names. need fixed
Added new figures from Jess

@@
 While test-retest reliability has not been measured explicitly for the foraging paradigm, the task was used as a measure to assess the effect of a six day long mindfulness retreat on cognitive performance\cite{hartkamp2017}.
-From a re-analysis of these data, we can estimate that test-retest reliability is <INSERT DETAILS>
+From a re-analysis of these data, we can estimate that the test-retest reliability is $r \approx 0.7$ for the feature condition and $r \approx 0.88$ for the conjunction search.
 
@@
 The location of item colours to grid locations was completely randomized.
-
 For half of the participants, targets were red and green circles, and for the other half of participants, targets were blue and yellow circles.
@@
 Two measures of individual strategy use were used: 1) Optimal choices, defined as percent of plateau trials in which the individual chose the optimal target (i.e., the target with the fewest distractors.
-When the variable distractor was red, the optimal choice was blue, and vice versa), and 2) Switch rate, the percent of trials in which the individual switched target colour (i.e., the colour chosen on trial N was different to the colour chosen on trial N-1).
+When the variable distractor was red, the optimal choice was blue, and vice versa), and 2) Switch rate, the percent of trials in which the individual switched target colour (i.e., the colour chosen on trial $N$ was different to the colour chosen on trial $N-1$).
 
-The results for the ACVS were consistent with previous findings \cite{irons-leber2016,irons-leber2018} (see Figure \ref{fig:acvs_summary}).
-shows that there were wide individual differences in both percent option (range $33.62\%$ - $97.50\%$, $M = 56.99$, $SD = 14.75$) and switch rate (range = $0\% - 56.68\%$, $M = 28.46$, $SD = 13.54$).
+The results for the ACVS were consistent with previous findings \cite{irons-leber2016,irons-leber2018}.
+We can clearly see from figure \ref{fig:acvs_summary} that there are individual differences in both the proportion of optimal targets reported (range $33.62\%$ - $97.50\%$, $M = 56.99$, $SD = 14.75$) and switch rate (range = $0\% - 56.68\%$, $M = 28.46$, $SD = 13.54$).
 
@@
 \centering
-\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/adaptchoice/AC_OptCh_x_SwRate.png}}
-\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/adaptchoice/AC_groupplot.pdf}}
-\caption{Needs checked and updated. replace png with pdf!}
+\subfigure{\includegraphics[width=6.5cm]{../Scripts/adaptchoice/ac_percentOpt_hist.pdf}}
+\subfigure{\includegraphics[width=6.5cm]{../Scripts/adaptchoice/ac_switchRate_hist.pdf}}
+\caption{Histograms showing the range of individual differences found in the ACVS task.}
 \label{fig:acvs_summary}
@@
 
-\begin{figure*}
+\begin{figure}
 \centering
-\includegraphics[width=\textwidth]{../Scripts/foraging/FG_IndivDiffsFig.png}
+\subfigure{\includegraphics[width=6.5cm]{../Scripts/foraging/fg_featureRunLength_hist.pdf}}
+\subfigure{\includegraphics[width=6.5cm]{../Scripts/foraging/fg_conjRunLength_hist.pdf}}
 \caption{What do we want this figure to actually be?}
 \label{fig:foraging_summary}
-\end{figure*}
+\end{figure}
 
@@
 Given this, we now investigate the extent to which an individual's performance in one of the tasks tells us about how well they will do in the other two.
+
+The feature search condition from the MCFT will be discarded from this analysis, as the individual differences of interest relate to how people search in the conjunction condition.
+Measures for the SHLS task will be taken from
 

### 2018-08-20 Scripts/adaptchoice/AC_FG_Histograms.R

@@ -1,0 +1,114 @@
+library(ggplot2)
+#library(ggplot)
+dat<- read.csv("summaryData.csv", header = TRUE,sep = ",")
+
+dat$ac_propOpt <- dat$ac_propOpt*100 # Convert to %
+dat$ac_switchRate <- dat$ac_switchRate*100 # Convert to %
+
+
+##### ALASDAIR'S TEMPLATE
+#plt <- ggplot(dat, aes(x = ls_mean_log_rt, y = ac_meanlog2rt))
+#plt <- plt + geom_point() 
+#plt <- plt + geom_smooth(method = lm, colour = "black", fullrange = TRUE, linetype = 0)
+#plt <- plt + theme_bw()
+#plt <- plt + scale_x_continuous("split-half: mean log rt (s)",
+#                                limits = c(0, 14.5 ), breaks = x_breaks, labels = x_labels)
+#plt <- plt + scale_y_continuous("adaptive choice: mean log rt (s)",
+#                                breaks = y_breaks, labels = y_labels)
+#plt <- plt + coord_cartesian(xlim=c(9.9, 13.1), ylim=c(11,12.3))
+#plt <- plt + theme(
+#  panel.grid.major = element_blank(), 
+#  panel.grid.minor = element_blank())
+# plt <- plt + ggtitle('Split-half and Attentional Control')
+#ggsave("ls_v_ac_mean_log2rt.pdf", width = figYn, height = figYn)
+#ggsave("ls_v_ac_mean_log2rt.png", width = figYn, height = figYn)
+#plt
+
+figXn <- 3.5
+figYn <- 2
+
+
+
+###### Percent Opt histogram
+
+#png(file="AC_PercentOpt_Hist.png",width=1600,height=1600,res = 300)
+plt<-ggplot(dat,aes(x=ac_propOpt)) + 
+  geom_histogram(col = 'black',fill = "grey", alpha = 1,breaks = seq(30,100,2))
+plt <- plt + scale_x_continuous(limits = c(30, 100), breaks = seq(30,100,10))
+plt <- plt + scale_y_continuous(limits = c(0, 8), breaks = seq(0,8,1))
+plt <- plt + theme_classic()
+plt <- plt + labs(x = "Optimal Choices (%)", y = "Frequency")
+plt <- plt + theme(axis.text.x = element_text(size=8),axis.text.y = element_text(size=8),
+                   axis.title.x = element_text(size=10),axis.title.y = element_text(size=10))
+                   #legend.position = c(.80, .95))
[…]

### 2018-08-20 Scripts/collectDataFromExps.R

@@ -11,8 +11,8 @@ names(adapt) = c("observer", "ac_acc", "ac_rt", "ac_propOpt", "ac_switchRate", "
 forage <- select_(forage, "SubNo", "Feature_log2RT", "Conj_log2RT", "Conj_RunNum", "Conj_RunLength")
 names(forage) = c("observer", "fg_feat_log2", "fg_conj_log2", "fg_conj_run_num", "fg_conj_run_length")
 
-lineseg <- select(lineseg, observer, prop_homo, prop_hetero, median_rt, meanlogrt)
-names(lineseg) <- c("observer", "ls_prop_homo", "ls_prop_hetero", "ls_median_rt", "ls_mean_log_rt")
+lineseg <- select(lineseg, observer, prop_homo, prop_hetero, meanlogrt)
+names(lineseg) <- c("observer", "ls_prop_homo", "ls_prop_hetero", "ls_mean_log_rt")
 
 dat = full_join(lineseg, adapt, by = "observer")
 dat = full_join(dat, forage)

### 2018-08-21 writeup/manuscript.tex
Fixig correlation graph

--- 2018-08-17 writeup/manuscript.tex
@@
 While test-retest reliability has not been measured explicitly for the foraging paradigm, the task was used as a measure to assess the effect of a six day long mindfulness retreat on cognitive performance\cite{hartkamp2017}.
-From a re-analysis of these data, we can estimate that test-retest reliability is <INSERT DETAILS>
+From a re-analysis of these data, we can estimate that test-retest reliability for the mean lengths of runs is $r\approx 0.88$.
 
@@
 
+The feature search condition from the MCFT will be discarded from this analysis, as the individual differences of interest relate to how people search in the conjunction condition.
+Measures for thr SHLS task will be taken from
+
 The results presented in Figure \ref{fig:all_the_cor} convincingly demonstrate that there are no strong correlations between any of the strategies chosen by observers in SHLS, ACVS and MCFT tasks \footnote{More comparisons are presented in the \textit{supplementary materials.}}.

### 2018-08-21 Scripts/correlation_collection.R

@@ -16,11 +16,11 @@ cor_dat <- tibble(
 		"sh - strategy",
 		"acvs prop optimal",
 		"acvs switch rate",
-		"MCFT (rt)",
-		"MCFT (rn)"),
-	estimate = c(0,0,0, 0.73, 0.83, 0.77, 0, 0),
-	lower = c(0.65, 0.66, 0.56, 0.585, 0.72, 0.63, -1, -1),
-	upper = c(0.86, 0.87, 0.82, 0.832, 0.90, 0.87, 1, 1),
+		"MCFT feature (rn)",
+		"MCFT conjunction (rn)"),
+	estimate = c(0,0,0, 0.73, 0.83, 0.77,  0.7, 0.88),
+	lower = c(0.65, 0.66, 0.56, 0.585, 0.72, 0.63, 0.55, .81),
+	upper = c(0.86, 0.87, 0.82, 0.832, 0.90, 0.87, .8, .92),
 	type = rep('test-retest', 8))
 
 add_r_95 <- function(x1, x2, df, t) {
@@ -38,24 +38,18 @@ add_r_95 <- function(x1, x2, df, t) {
 	return(df)
 }
 
-cor_dat <- add_r_95(dat[3], dat[5], cor_dat, 'rt-strat')
-cor_dat <- add_r_95(dat[8], dat[7], cor_dat, 'rt-strat')
-cor_dat <- add_r_95(dat[13], dat[12], cor_dat, 'rt-strat')
-cor_dat <- add_r_95(dat[14], dat[12], cor_dat, 'rt-strat')
+cor_dat <- add_r_95(dat["ls_prop_hetero"], dat["ls_mean_log_rt"], cor_dat, 'rt-strat')
+cor_dat <- add_r_95(dat["ac_propOpt"], dat["ac_meanlog2rt"], cor_dat, 'rt-strat')
+cor_dat <- add_r_95(dat["fg_conj_run_num"], dat["fg_conj_log2"], cor_dat, 'rt-strat')
 
-cor_dat <- add_r_95(dat[3], dat[8], cor_dat, 'cross paradigm')
-cor_dat <- add_r_95(dat[3], dat[9], cor_dat, 'cross paradigm')
-cor_dat <- add_r_95(dat[3], dat[13], cor_dat, 'cross paradigm')
-cor_dat <- add_r_95(dat[3], dat[14], cor_dat, 'cross paradigm')
[…]

### 2018-08-30 writeup/manuscript.tex
updated figures to remove title.

--- 2018-08-20 writeup/manuscript.tex
@@
 \centering
-\subfigure{\includegraphics[width=6.5cm]{../Scripts/adaptchoice/ac_percentOpt_hist.pdf}}
-\subfigure{\includegraphics[width=6.5cm]{../Scripts/adaptchoice/ac_switchRate_hist.pdf}}
+\subfigure[][]{\includegraphics[width=6.5cm]{../Scripts/adaptchoice/ac_percentOpt_hist.pdf}}
+\subfigure[][]{\includegraphics[width=6.5cm]{../Scripts/adaptchoice/ac_switchRate_hist.pdf}}
 \caption{Histograms showing the range of individual differences found in the ACVS task.}
@@
 \centering
-\subfigure{\includegraphics[width=6.5cm]{../Scripts/foraging/fg_featureRunLength_hist.pdf}}
-\subfigure{\includegraphics[width=6.5cm]{../Scripts/foraging/fg_conjRunLength_hist.pdf}}
-\caption{What do we want this figure to actually be?}
+\subfigure[][]{\includegraphics[width=6.5cm]{../Scripts/foraging/fg_featureRunLength_hist.pdf}}
+\subfigure[][]{\includegraphics[width=6.5cm]{../Scripts/foraging/fg_conjRunLength_hist.pdf}}
+\caption{Histogram of mean run lengths for (a) feature and (b) conjunction foraging tasks.}
 \label{fig:foraging_summary}

### 2018-08-30 Scripts/foraging/AC_FG_Histograms.r

@@ -1,0 +1,114 @@
+library(ggplot2)
+#library(ggplot)
+dat<- read.csv("summaryData.csv", header = TRUE,sep = ",")
+
+dat$ac_propOpt <- dat$ac_propOpt*100 # Convert to %
+dat$ac_switchRate <- dat$ac_switchRate*100 # Convert to %
+
+
+##### ALASDAIR'S TEMPLATE
+#plt <- ggplot(dat, aes(x = ls_mean_log_rt, y = ac_meanlog2rt))
+#plt <- plt + geom_point() 
+#plt <- plt + geom_smooth(method = lm, colour = "black", fullrange = TRUE, linetype = 0)
+#plt <- plt + theme_bw()
+#plt <- plt + scale_x_continuous("split-half: mean log rt (s)",
+#                                limits = c(0, 14.5 ), breaks = x_breaks, labels = x_labels)
+#plt <- plt + scale_y_continuous("adaptive choice: mean log rt (s)",
+#                                breaks = y_breaks, labels = y_labels)
+#plt <- plt + coord_cartesian(xlim=c(9.9, 13.1), ylim=c(11,12.3))
+#plt <- plt + theme(
+#  panel.grid.major = element_blank(), 
+#  panel.grid.minor = element_blank())
+# plt <- plt + ggtitle('Split-half and Attentional Control')
+#ggsave("ls_v_ac_mean_log2rt.pdf", width = figYn, height = figYn)
+#ggsave("ls_v_ac_mean_log2rt.png", width = figYn, height = figYn)
+#plt
+
+figXn <- 3.5
+figYn <- 2
+
+
+
+###### Percent Opt histogram
+
+#png(file="AC_PercentOpt_Hist.png",width=1600,height=1600,res = 300)
+plt<-ggplot(dat,aes(x=ac_propOpt)) + 
+  geom_histogram(col = 'black',fill = "grey", alpha = 1,breaks = seq(30,100,2))
+plt <- plt + scale_x_continuous(limits = c(30, 100), breaks = seq(30,100,10))
+plt <- plt + scale_y_continuous(limits = c(0, 8), breaks = seq(0,8,1))
+plt <- plt + theme_classic()
+plt <- plt + labs(x = "Optimal Choices (%)", y = "Frequency")
+plt <- plt + theme(axis.text.x = element_text(size=8),axis.text.y = element_text(size=8),
+                   axis.title.x = element_text(size=10),axis.title.y = element_text(size=10))
+                   #legend.position = c(.80, .95))
[…]

### 2018-10-30 NowakowskaClarkeHunt2017/learningDuringTrial.R
Looks like there's a still a person missing - mistake with resolution?

@@ -1,0 +1,72 @@
+library(tidyverse)
+library(binom)
+library(ggthemes)
+# library(lme4)
+# library(scales)
+
+fixdat = readRDS(file="data/processedFixData.Rda")
+fixdat = (filter(fixdat, subj!=4, subj!=15)) 
+#=======
+
+fixdat = readRDS(file="data/processedFixData.Rda")
+
+levels(fixdat$subj) = 1:14
+#>>>>>>> Stashed changes
+cbPalette <- c("#56B4E9", "#E69F00")
+
+rtdat = readRDS(file="data/processedRTandAccData.Rda")
+medianRT = aggregate(RT~subj, rtdat, "median")
+
+# classify every fixation as homo (left), central, or hetro (right)
+centralWidth = 64 #change to 1 visual degree
+fixdat$side = 'central'
+fixdat$side[which(fixdat$fixX <(512-centralWidth/2))] = "homo"
+fixdat$side[which(fixdat$fixX >(512+centralWidth/2))] = "hetro"
+fixdat$side = as.factor(fixdat$side)
+
+aggData = (filter(fixdat, side!="central", fixNum<26, fixNum>1, targSide=="absent") 
+  %>% group_by(subj, fixNum) 
+    %>% summarise(
+     propHetro=mean(side=="hetro"), 
+     nTrials=length(trial),
+     lower = binom.confint(propHetro*nTrials,nTrials, method='wilson')$lower,
+     upper = binom.confint(propHetro*nTrials,nTrials, method='wilson')$upper))
+
+plt = ggplot(aggData, aes(x=fixNum, y=propHetro, ymin=lower, ymax=upper))
+plt = plt + geom_errorbar(colour = "grey") + geom_point() + geom_path()
+plt = plt + theme_tufte() + facet_wrap(~subj, nrow=2)
+plt = plt + scale_x_continuous(name="fixation number")
+plt = plt + scale_y_continuous(name="proportion of fixations to heterogeneous side")
+ggsave("over_first_25_fixations.png", width = 10, height = 6)
+
+
+
+one_person = filter(aggData, subj == 6)
+one_person$fixNum <- one_person$fixNum - 1
+plt <- ggplot(one_person, aes(x = fixNum, y = propHetro))
+plt <- plt + geom_errorbar(aes( ymin = lower, ymax = upper), colour = "grey") + geom_point() 
+
[…]

### 2018-10-30 Scripts/lineseg/1_init_processing.R

@@ -109,7 +109,7 @@ process_acs <- function(asc, ss) {
 	return(list(fixDat,trlDat))
 }
 
-participants <- 1:68
+participants <- 1:74
 participants <- participants[!(participants %in% c(18, 32, 48, 57))] 
 
 
@@ -244,6 +244,10 @@ incTrials <- with(trlDat, paste(observer, session, trial))
 fixDat <- filter(fixDat, paste(observer, session, trial) %in% incTrials)
 rm(incTrials)
 
+# remove people who had a 1028 x 768 resolution 
+idx <- filter(resDat, xRes == 1024)$observer
+trlDat <- filter(trlDat, !(observer %in% idx))
+fixDat <- filter(fixDat, !(observer %in% idx))
 
 # save
 saveRDS(trlDat, "scratch/processedRTandAccData.Rda")

### 2018-11-02 Scripts/lineseg/1_init_processing.R
forgot to save this file/

@@ -109,7 +109,7 @@ process_acs <- function(asc, ss) {
 	return(list(fixDat,trlDat))
 }
 
-participants <- 1:74
+participants <- 1:75
 participants <- participants[!(participants %in% c(18, 32, 48, 57))] 
 
 
@@ -248,6 +248,9 @@ rm(incTrials)
 idx <- filter(resDat, xRes == 1024)$observer
 trlDat <- filter(trlDat, !(observer %in% idx))
 fixDat <- filter(fixDat, !(observer %in% idx))
+
+trlDat$observer <- fct_drop(trlDat$observer)
+fixDat$observer <- fct_drop(fixDat$observer)
 
 # save
 saveRDS(trlDat, "scratch/processedRTandAccData.Rda")

### 2018-11-08 Scripts/lineseg/1_init_processing.R
more details on resolutions

@@ -248,6 +248,7 @@ rm(incTrials)
 idx <- filter(resDat, xRes == 1024)$observer
 trlDat <- filter(trlDat, !(observer %in% idx))
 fixDat <- filter(fixDat, !(observer %in% idx))
+resDat <- filter(resDat, !(observer %in% idx))
 
 trlDat$observer <- fct_drop(trlDat$observer)
 fixDat$observer <- fct_drop(fixDat$observer)

### 2018-11-20 Scripts/collectDataFromExps.R
checking the final data :)

@@ -2,21 +2,32 @@ library(tidyverse)
 
 
 lineseg <- read_csv("lineseg/scratch/lineseg_output.csv")
-adapt   <- read_delim("adaptchoice/Data_AdaptChoice_allsubs_Summary.txt", delim = "\t")
-forage  <- read_delim("foraging/Data_MultiTargForag_allsubs.txt", delim = "\t;")
 
-adapt <- select_(adapt, "SubNo", "Acc", "RT", "ProportionOptimalChoices", "SwitchRate", "Log2RT")
-names(adapt) = c("observer", "ac_acc", "ac_rt", "ac_propOpt", "ac_switchRate", "ac_meanlog2rt")
 
-forage <- select_(forage, "SubNo", "Feature_log2RT", "Conj_log2RT", "Conj_RunNum", "Conj_RunLength")
-names(forage) = c("observer", "fg_feat_log2", "fg_conj_log2", "fg_conj_run_num", "fg_conj_run_length")
+# adapt   <- read_delim("adaptchoice/Data_AdaptChoice_allsubs_Summary.txt", delim = "\t")
+# forage  <- read_delim("foraging/Data_MultiTargForag_allsubs.txt", delim = "\t;")
+
+# adapt <- select_(adapt, "SubNo", "Acc", "RT", "ProportionOptimalChoices", "SwitchRate", "Log2RT")
+# names(adapt) = c("observer", "ac_acc", "ac_rt", "ac_propOpt", "ac_switchRate", "ac_meanlog2rt")
+
+# forage <- select_(forage, "SubNo", "Feature_log2RT", "Conj_log2RT", "Conj_RunNum", "Conj_RunLength")
+# names(forage) = c("observer", "fg_feat_log2", "fg_conj_log2", "fg_conj_run_num", "fg_conj_run_length")
 
 lineseg <- select(lineseg, observer, prop_homo, prop_hetero, meanlogrt)
 names(lineseg) <- c("observer", "ls_prop_homo", "ls_prop_hetero", "ls_mean_log_rt")
 
-dat = full_join(lineseg, adapt, by = "observer")
-dat = full_join(dat, forage)
- 
+# read in summary stats from Jess
+dat <- read_csv("summaryData_75.csv")
+
+dat$ls_prop_homo[which(dat$observer %in% 67:75)]
+
+# remove people who had the wrong resolution!
+# also remove person 32 who only did one session
[…]

### 2018-11-20 Scripts/compareExp.R

@@ -4,7 +4,17 @@ library(tidyverse)
 figXn <- 3.5
 figYn <- 2.5
 
-dat <- read_csv("summaryData.csv")
+dat <- read_csv("summaryData_75.csv")
+
+
+dat <- full_join(dat, lineseg)
+# remove people who had the wrong resolution!
+idx <- c(1, 2, 3, 4, 11, 31, 69)
+
+dat <- filter(dat, !(observer %in% idx))
+
+# numbers taken from inital parsing script for split half paradigm
+
 
 ############################################################
 # first look at rt

### 2018-11-20 Scripts/correlation_collection.R

@@ -40,12 +40,12 @@ add_r_95 <- function(x1, x2, df, t) {
 
 cor_dat <- add_r_95(dat["ls_prop_hetero"], dat["ls_mean_log_rt"], cor_dat, 'rt-strat')
 cor_dat <- add_r_95(dat["ac_propOpt"], dat["ac_meanlog2rt"], cor_dat, 'rt-strat')
-cor_dat <- add_r_95(dat["fg_conj_run_num"], dat["fg_conj_log2"], cor_dat, 'rt-strat')
+cor_dat <- add_r_95(dat["fg_conj_run_length"], dat["fg_conj_log2"], cor_dat, 'rt-strat')
 
 
 cor_dat <- add_r_95(dat["ls_prop_hetero"], dat["ac_propOpt"], cor_dat, 'cross paradigm')
-cor_dat <- add_r_95(dat["ls_prop_hetero"], dat["fg_conj_run_num"], cor_dat, 'cross paradigm')
-cor_dat <- add_r_95(dat["ac_propOpt"], dat["fg_conj_run_num"], cor_dat, 'cross paradigm')
+cor_dat <- add_r_95(dat["ls_prop_hetero"], dat["fg_conj_run_length"], cor_dat, 'cross paradigm')
+cor_dat <- add_r_95(dat["ac_propOpt"], dat["fg_conj_run_length"], cor_dat, 'cross paradigm')
 
 cor_dat <- add_r_95(dat["ls_mean_log_rt"], dat["ac_meanlog2rt"], cor_dat,  'cross paradigm')
 cor_dat <- add_r_95(dat["ls_mean_log_rt"], dat["fg_conj_log2"], cor_dat, 'cross paradigm')
@@ -55,12 +55,12 @@ cor_dat$comparison <- fct_rev(as_factor(cor_dat$comparison))
 
 cor_dat$comparison <- fct_recode(cor_dat$comparison, 
 	`ACVS (opt) - MCFT (rl)`  = "ac_propOpt-fg_conj_run_length",
-	`ACVS (opt) - MCFT (rn)`  = "ac_propOpt-fg_conj_run_num",
+	`ACVS (opt) - MCFT (rl)`  = "ac_propOpt-fg_conj_run_length",
 	`SHLS (opt) - MCFT (rl)`  = "ls_prop_hetero-fg_conj_run_length",
[…]

### 2018-11-29 Manuscript/manuscript.tex
paper edits
streamlining methods and results

\RequirePackage{fix-cm}
\documentclass[]{rsos}%%%%where rsos is the template name

%% *** Do not adjust lengths that control margins, column widths, etc. ***
\usepackage{subfigure}
\usepackage{lineno}
\usepackage{hyperref}
\begin{document}

% \linenumbers
%%%% Article title to be placed here
\title{Stable individual differences in strategies within, but not between, visual search tasks}

\author{%%%% Author details
Alasdair D. F. Clarke$^1$, Jessica L Irons$^2$, Warren James$^3$, Andrew B Leber$^2$ and Amelia R Hunt$^3$}

%%%%%%%%% Insert author address here
\address{$^{1}$Department of Psychology, University of Essex, Colchester, UK\\
$^{2}$Department of Psychology, The Ohio State University, Columbus, USA\\
$^{3}$School of Psychology, University of Aberdeen, Aberdeen, UK}

%%%% Subject entries to be placed here %%%%
\subject{Behaviour, evolution}

%%%% Keyword entries to be placed here %%%%
\keywords{visual search, optimal behaviour, eye movements}

%%%% Insert corresponding author and its email address}
\corres{Alasdair Clarke\\
\email{a.clarke@essex.ac.uk}}

\begin{abstract}
A striking range of individual differences has recently been reported in three different visual search tasks. These differences in performance can be attributed to strategy, that is, the efficiency with which participants control their search to complete the task quickly and accurately. Here we ask if an individual's strategy and performance in one search task is correlated with how they perform in the other two. We tested 64 observers in the three tasks mentioned above over two sessions. Even though the test-retest reliability of the tasks is high, an observer’s performance and strategy in one task did not reliably predict their behaviour in the other two. These results suggest search strategies are stable over time, but context-specific. To understand visual search we therefore need to account not only for differences between individuals, but also how individuals interact with the search task and context. These context-specific but stable individual differences in strategy can account for a substantial proportion of variability in search performance.
\end{abstract}

%%%%%%%%%% Insert the texts which can accomdate on firstpage in the tag "fmtext" %%%%%

\begin{fmtext}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

As is common in cognitive psychology, most visual search literature has focused on how the average participant performs in the task, despite it being well known that there is a great deal of variability between one subject and the next. From Treisman's work on \end{fmtext}
\maketitle
\twocolumn Feature Integration Theory\cite{treisman1980} to the latest incarnation of the Guided Search Model\cite{wolfe2015}, we now have a good understanding of what makes some search targets effortless to find, while others require careful inspection. However, these theories and models have neglected the question of why some observers find visual search so much harder than others. These differences can emerge from several different sources of variation: tiredness\cite{mackworth1948}, information-processing ability, speed-accuracy trade-off, motivation, visual impairments\cite{nowakowska2016}, and search strategies\cite{boot2006}. Although their existence has previously been noted\cite{mackworth1948}, a rigorous examination of individual differences in visual search is a challenge that has not been taken up by many researchers, and questions about their importance and stability remain relatively under explored.

In the current study, we focus on one source of individual differences in visual search: strategy. By search strategies, we refer to a collection of behaviours that all observers can freely choose from when they search a display. Examples include choosing to adopt a systematic left-to-right and top-to-bottom strategy\cite{gilchrist2006}, or the type of guided search behaviour in which locations that are more likely to contain the target are prioritised\cite{wolfe2015}.

A striking example of the effect of strategy is given by Boot and colleagues\cite{boot2006}. They asked participants to monitor a cluttered display for an object changing colour or suddenly appearing. Large individual differences were found with respect to the number of saccades participants made while monitoring the stimulus, and this was negatively correlated with detection performance. Proulx\cite{proulx2011} demonstrated that participants differed in how they prioritised visual features (color or orientation) when searching through a set of objects for one with a particular color-orientation combination. These differences in search strategy explained some of the variation in the extent to which participants were distracted by an irrelevant object of a unique size. However, participants were largely unaware of the search strategy they employed, and the majority were unable, or unwilling, to comply with instructions to employ a particular strategy.

Eye movement strategies have also been shown to be an important source of individual differences in visual search efficiency. Nowakowska, Clarke \& Hunt\cite{nowakowska2017} designed a simple search paradigm to discriminate between optimal\cite{najemnik-geisler2008} and stochastic \cite{clarke2016} search strategies. The task involved searching through arrays of line segments arranged such that those on one side of the display all had a very similar orientation ("homogeneous"), while those on the other side had higher variance ("heterogeneous", see Figure \ref{fig:exampleStimuli} for an example). This meant that targets appearing on the homogeneous side would be highly salient, and targets on the heterogeneous side  would be much harder to find. With these stimuli, the optimal eye movement strategy is to only search the heterogeneous half , as targets on the homogeneous side can be detected with peripheral vision. We will refer to this paradigm here as the Split-Half Line Segment task (SHLS). While some participants initially searched the displays near optimally, others carried out strategies counter to this, failing to even match the performance of the stochastic searcher. Furthermore, the degree to which they made saccades in line with the optimal search strategy was strongly correlated with their reaction times. A related version of this paradigm has been used in research investigating eye movement strategies in response to (simulated) hemianopia\cite{nowakowska2016,nowakowska2018}, with similar conclusions: the full spectrum of individual differences in strategy was observed, from near-optimal to the opposite of optimal. It is therefore not possible to conclude whether optimal or stochastic models better describe search without first explaining individual variablility.

A similar range of strategies, from random to near-optimal, has been found by Irons \& Leber with the Adaptive Choice Visual Search (ACVS) paradigm\cite{irons-leber2016}, designed to explore how feature-based attention is used. This paradigm involves stimuli made up of small coloured boxes (red, blue, green and a fourth colour that varies from red, through purple, to blue and back again) with numerals written inside them (See Figure \ref{fig:exampleStimuli}). The target is a defined as a red or blue box with a numeral between 1 and 4, and on each trial one target of each colour is present. The participant's task is to find one of either target as quickly as possible and report the numeral. On trials in which the fourth colour is red (or close to red), participants should search through the blue boxes and report the blue target, as there will be fewer distracters. As the fourth colour changes to through purple to blue, participants should update their strategy and search for the red target. The results showed that participants varied substantially along two key dimensions: how frequently they used the more effective target color to search (varying from chance performance to near optimal), and how often they changed between colours. Further work has shown that these differences are stable over time (between one and ten days) with test-retest correlations of around $r \approx 0.8$\cite{irons-leber2018}.

\begin{figure*}
\centering
\subfigure[][]{\includegraphics[height=3cm]{figures/split-half.png}}
\subfigure[][]{\includegraphics[height=3cm]{figures/adaptive.png}}
\subfigure[][]{\includegraphics[height=3cm]{figures/foraging.png}}
\caption{Example stimulus from the (a) \textit{split-half}, (b) \textit{adaptive choice} and (c) \textit{foraging} paradigms.}
\label{fig:exampleStimuli}
\end{figure*}

Another example of differences in search strategy comes from the foraging literature \cite{kristjansson2014,johannesson2016}. In this context, foraging is a visual search task in which there are multiple targets on each trial. Participants were asked to search through a set of items from four categories, with two categories classed as targets. In the conjunction condition (searching for red-horizontal and green-vertical line segments among red-vertical and green-horizontal distracters), most observers searched in runs, finding all the targets of one target category, and then switching and finding the targets in the other category. This strategy has previously been observers in animal foraging \cite{dawkins1971}, and suggests holding one complex target template in mind at a time is a better strategy than switching templates. However, a sub-set of observers, termed `super-foragers', were able to change between search target categories with no cost to performance. This study has been run on touch displays\cite{kristjansson2014} (observers are asked to tap on as many targets as they can as quickly as possible) and a 3D computer game (in which participants navigate a squirrel through a virtual environment picking up targets with different feature combinations)[IN PREP], with super-foragers present in both versions. While test-retest reliability has not been measured explicitly for the foraging paradigm, the task was used as a measure to assess the effect of a six day long mindfulness retreat on cognitive performance\cite{hartkamp2017}. From a re-analysis of these data, we can estimate that the test-retest reliability for the mean run length is $r \approx 0.7$ for the feature condition and $r \approx 0.88$ for the conjunction search.

Previous research has investigated the relationship between these behaviours to \hyphenation{psychometric} measures, but to date, these differences have not shown strong correlations with other attributes. In the ACVS paradigm, Irons \& Leber found no evidence of a correlation between the proportion of optimal choices made by observers and measures of visual working memory or trait compulsivity\cite{irons-leber2016}. Similarly, the differences foraging behaviour are not accounted for by working memory or inhibitory control\cite{johannesson2017}.

A common theme emerging from these studies is the observation that individual strategies vary in their degree of effectiveness or optimality. However, ``visual search'' encompasses a wide range of specific tasks, each tapping into a different aspect of behaviour (e.g. feature-based attention, information sampling). The aim of the present study is to investigate the extent to which individual differences are stable across different visual search paradigms. Are observers who use the optimal strategy in the SHLS paradigm also more optimal in the ACVS task? Does it make sense to talk about `super-searchers' who show above average performance in a range of search tasks (analogous to the 'super-recognizers' of the face-recognition literature \cite{russell2009}? Are the super-foragers consistently better or worse than more typical searchers in the other two paradigms? As a secondary question, we will measure the test-retest reliability of the differences found in the SHLS paradigm.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Methods}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The methods and planned analysis for this study were registered on the Open Science Framework\footnote{\url{https://osf.io/scv4u/}} before data collection started.

\subsection{Participants}
64 students from the University of Aberdeen took part in this study\footnote{data from an additional 11 participants was discarded due to being recorded with an inappropriate screen resolution.}. Participants were compensated for their time with either  course credit or \pounds 15. All participants gave informed consent. The study was approved by the University of Aberdeen Psychology Ethics Committee.

Sample size was determined in part by a power analysis, and in part due to constraints with counter-balancing. $n = 64$ participants means we should be able to detect correlations with $r > 0.34$ with $\alpha = 0.05$, $\beta = 0.80$ between the different visual search paradigms. The sample size is therefore of sufficient size to detect relatively small correlations.

\subsection{Materials and Procedures}

The study consists of three paradigms from the visual search literature in which large individual differences have been  found\cite{nowakowska2017, irons-leber2016, kristjansson2014}. Example stimuli can be seen in Figure \ref{fig:exampleStimuli}. A brief overview of each paradigm is given below, with full details in \textit{supplementary materials}. The three tasks will be completed over two sessions, approximately one week apart. The SHLS was run in both sessions allowing us to measure test-retest reliability. The order in which participants completed the tasks was counter-balanced. There are 16 different possible orders of tasks/conditions; four participants completed each order for a total of 64.

The display was presented on a 17-inch CRT monitor with a resolutions of $1400 \times 1050$ ($n = 40$) or $1600 \times 1200$ ($n = 24$). Stimulus generation, presentation and data collection were controlled by MATLAB and the psychophysics and eyelink toolboxes \cite{brainard1997,cornelissen2002} run on a Powermac. Participants sat $\approx 47$cm from the screen.

\subsubsection{Split-half Line Segments}

Stimuli consisted of arrays of black oriented line segments against a grey background. The target was oriented $45^{\circ}$ clockwise, while the distractor items had a random orientation with a mean of $45^{\circ}$ anti-clockwise. The variance was low ($18^{\circ}$) on one half of the display to create a homogeneous texture, and high ($95^{\circ}$) on the other side to create a heterogeneous texture. This means that when the target is present on the homogeneous half, it can be easily be detected with peripheral vision, but when it is in the heterogeneous half, it is much harder to detect. There were 160 trials in total and homo- and heterogeneous sides of the display were randomly varied from trial to trial. The position of the dominant eye was recorded using a desktop-mounted EyeLink 1000 eye tracker (SR Research, Canada).

This paradigm was carried out twice, once in each testing session, to give us an estimate of how consistent participants are in their search strategy over time.

\subsubsection{Adaptive Choice Visual Search}

Each search display was composed of red, blue, green and variable-coloured small squares arranged in three concentric rings around fixation. Variable distractors changed colours from trial-to-trial according to a 24 trial cyclical pattern: the distractors would be red for five trials, then across a period of seven trials, they would gradually change colour from red to blue. The variable distractor would then be blue for five trials, and then gradually transition back to red.

A white digit appeared inside each square. Participants were informed that two targets - a red square and a blue square each with a digit between 2 and 5 - were embedded in every search display. The two target digits were always different, to enable us to distinguish the chosen target. The remaining red, blue and variable squares all contained digits between 6-9. Green squares could contain any digit between 2-9. The location of the targets and distractor within the search display were randomized on each trial. Participants were only required to find one target on each trial, and they were free to search for either one.

\subsubsection{Mouse Click Foraging Task}

In the feature foraging task, search displays contained small red, green, yellow and blue circles. For half of the participants, targets were red and green circles, and for the other half of participants, targets were blue and yellow circles. Participants were asked to collect all of the targets within a trial by using the mouse to click on each target. Clicking on a target caused it to disappear from the display. If the participant clicked erroneously on a non-target, the trial immediately ended and a replacement trial begun. In the conjunction foraging task, search displays were composed of both circles and squares. For half of the participants, the shapes were red and green, and for the remaining participants the shapes were blue and yellow. Targets were defined by conjunctions of colour and shape (e.g., red squares and green circles, with red circles and green squares as distractors). The assignment of targets and distractors was assigned at random for each participant. The procedure was otherwise identical to the feature foraging task.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Replication of each task}

A brief summary of participants' behaviour is given below. More time is spent on SHLS as the test-retest validity of it has not previously been assessed. Further analysis and details can be found in the \textit{supplementary materials}.

\subsubsection{Split-half Line Segments}

Our results are consistent with the original SHLS study\cite{nowakowska2017}: we find a large range of individual differences in search reaction time and accuracy (see Figure \ref{fig:splithalf_summary}). Furthermore, these differences are stable from between the two testing sessions, with Pearson's $r \in [0.71, 0.89]$ ($95\%$ confidence interval) for accuracy in finding hard targets. We get similar scores for the correlation in reaction times between sessions \textit{a} and \textit{b} for hard targets, ($r \in [0.54-0.81]$), easy targets ($r \in [0.52-0.80]$) and target absent trials ($r \in [0.66-0.86]$).

\begin{figure}
\centering
\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/lineseg/scratch/acc_correlation.pdf}}
\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/lineseg/scratch/rt_correlation.pdf}}
\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/lineseg/scratch/strat_corr.pdf}}
\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/lineseg/scratch/strat_compare_meanlog_rt.pdf}}
\caption{Each point represents a participant and the error-bars indicate 95\% confidence intervals. Correlation between the two sessions of the SHLS paradigm for (a)  accuracy (TP-heterogeneous trials only); (b) reaction times and (c) search strategy (TA trials only). (d) Initial search strategy correlates with reaction times in both sessions. }
\label{fig:splithalf_summary}
\end{figure}

We can also look at the initial search strategies adopted by our participants \ref{fig:splithalf_summary}(c, d). Again, we see large and stable individual differences across the two sessions (test-retest $r \in [0.63, 0.86]$ for the proportion of the first five saccades to the heterogeneous half of the display for target absent trials). More importantly, as with \cite{nowakowska2017}, we see that the search strategies give a good correlation with reaction times in both session a, $r \in [0.52, 0.82]$ and session b, $r \in [0.50, 0.80]$.

\subsubsection{Adaptive Choice Visual Search}

We measured an individual's strategy as the percent of plateau trials in which the individual chose the optimal target (i.e., the target with the fewest distractors: When the variable distractor was red, the optimal choice was blue, and vice versa).
The results for the ACVS were consistent with previous findings \cite{irons-leber2016,irons-leber2018}. We can clearly see from figure \ref{fig:acvs_summary} that there are individual differences in both the proportion of optimal targets reported (range $33.62\%$ - $100.00\%$, $\bar{x} = 59.15$, $s = 16.54$) and switch rate (range = $0\% - 56.68\%$, $\bar{x} = 28.50$, $s = 14.13$).

\begin{figure}
\centering
\includegraphics[width=6.5cm]{../Scripts/adaptchoice/ac_percentOpt_hist.pdf}
\caption{Histograms showing the range of individual differences found in the ACVS task.}
\label{fig:acvs_summary}
\end{figure}

\subsubsection{Mouse Click Foraging Task}

The main measure of interest was average run length per trial in the conjunction condition, with a run defined as a succession of one or more of the same target type, which was followed and preceded by the other target or no target. The average run length was the mean number of target selections in a run. The multiple-target foraging results were in line with previous findings \cite{kristjansson2014,johannesson2016}, with shorter run lengths for feature foraging ($\bar{x} = 3.16$, $s = 3.14$) than conjunction foraging ($\bar{x} = 11.73$, $s = 7.09$). This suggests more frequent foraging for multiple targets concurrently when those targets were defined by features than by conjunctions. Figure \ref{fig:foraging_summary} depicts the individual differences in terms of run length: twenty ``super-searchers'' were revealed, identified by short run lengths for both feature and conjunction targets.

\begin{figure}
\centering
\includegraphics[width=6.5cm]{../Scripts/foraging/fg_conjRunLength_hist.pdf}
\caption{Histogram of mean run lengths for the conjunction foraging task.}
\label{fig:foraging_summary}
\end{figure}

\subsection{Correlations Between Tasks}

We have successfully replicated the previous findings around individual differences in visual search strategy in each of the three tasks. Furthermore, the SHLS task has been shown to have good test-retest reliability, similar to that of the ACVS  and MCFT tasks. Given this, we now investigate the extent to which an individual's performance in one of the tasks tells us about how well they will do in the other two.

The results show that the correlations between the strategy metrics in the three tasks (Figure \ref{fig:all_the_cor}) are weak. Perhaps even more surprisingly, there is also little evidence for meaningful correlations between reaction times in the different tasks. Even if we optimistically take all the data together as suggesting a robust correlation in reaction times from task to task, the upper bound of $r=0.30$ means that this correlation only accounts for at best $10\%$\footnote{i.e., $R^2 = 0.3^2 = 0.09$} an individual's performance.

\begin{figure}
\centering
\includegraphics[width=6.5cm]{../Scripts/scratch/cor_comparison.pdf}
\caption{The between- and within-task correlations for the three different search tasks. The bars indicate the $95\%$ confidence intervals for Pearson's correlation coefficient. Blue bars represent test-retest scores for each task for reaction times (\textit{rt}), optimality (\textit{opt}) or run length (\textit{rl}). Yellow bars indicate how well the strategy measures predict reaction times, while the red bars show that performance in one task is not a good indication of performance in another, either for reaction times of strategy.}
\label{fig:all_the_cor}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We successfully replicated the wide range of individual differences in strategy and performance that had previously been observed in each of these three visual search paradigms, with a larger sample size than the original experiments. Surprisingly, however, the between-paradigm correlations give at most $R^2 = 0.1$, and this is a generous interpretation that would fail to pass the usual criteria for null hypothesis significance testing. Knowing how one person will behave in one of these paradigms apparently tells us very little about how they will perform in the others. This can be contrasted with the relatively high test-retest correlations of all three of the tasks individually, which range from [x to x].

There are many reasons why two measurements might be uncorrelated, such as range restriction or measurement noise. The high test-retest correlations on each of the individual visual search tasks rules out many of these alternatives, leaving a true absence of shared variance between these tasks as a likely explanation. One might have expected reaction time to be at least modestly correlated from one search task to the next, even in the absence of correlations in strategy, as a general factor like an individual's motivation or conscientiousness might lead to better or worse overall performance across all the tasks. However, even reaction times were not highly correlated between tasks. What we did observe were correlations between our measures of strategy and reaction time within each task, suggesting our strategy metrics are predictive of search performance, and reinforcing the interpretation that an individual who is strategic in one task is not necessarily strategic in the others.

Although the tasks in this experiment all have visual search in common, they also have unique aspects that appear to have resonated with particular individuals' strengths, and not others. Our definition of a successful strategy in the SHLS task was fixating the locations that provide new information. In the ACVS task, a successful strategy meant appropriately altering search goals to match changes in the environment. In the MCFT task, success involved minimizing cognitive load by minimizing target switching. Each of these tasks clearly taps into unique aspects of visual search strategies, and performance on one of these aspects has no bearing on any of the others.

Individual differences pose a challenge for efforts to devise a comprehensive model of visual search. Our understanding of the underlying mechanisms of visual search is based predominantly on experiments that systematically vary details of the search task and measure their effects on performance. This approach has led to many important insights, for example, about the kinds of visual features that can be used to guide attention (e.g. \cite{treisman1980, wolfe2007}; how attentional control settings filter out distractors (e.g. \cite{folk1992,yantis1999}); and  biases in attention, such as a bias towards unexplored locations (e.g. \cite{klein2000}). These insights are based on search performance averaged over some number of individual participants. For all three of the experiments included in the current study, however, the average performance would be highly misleading, as it would describe very few of the individuals who completed the tasks. In the original SHLS study \cite{nowakowska2017}, for example, the original aim of the experiment was to assess whether search behaviour could be better described by an optimal \cite{najemnik-geisler2008}, versus a stochastic \cite{clarke2016}, model. Considering only the average search performance, the stochastic model was a good explanation. Underlying that average performance, however, was a very large spectrum of search behaviour, replicated here, some of which would be clearly categorized as optimal, and some as stochastic, and some as neither. The original question needed to be refined into new question: for whom is search optimal and for whom is it stochastic? The current findings add even further challenges for researchers interested in understanding visual search, by suggesting we need to not only account for individual differences, but also the interaction of a given individual with a particular search context.

Add something about learning, experience, reinforcement - Hayhoe/Land references?

Mention \cite{vogel2008}.
From \cite{proulx2011} - \textit{Vogel and colleagues have found that an individual's ability to remember a greater number of items using working memory is related to a filtering capacity in visual search that suppresses attentional capture by distracting visual information [10,11,12]. Behavioural work in visual search has extended this research to
demonstrate that working memory correlates only with top-down
visual search performance where task relevance is crucial, but not
with  bottom-up  visual  search  tasks  where  salience  in  the
environment guides attention \cite{sobel2007}}

Mention \cite{stoet2011}.

\bibliographystyle{plain}
\bibliography{literature}

\end{document}

### 2018-11-29 Manuscript/sup_mat.tex
paper edits
streamlining methods and results

--- 2018-08-10 Writeup/sup_mat.tex
@@
 \subsection{Split-half}
+
+Stimuli consisted of arrays of black oriented line segments against a grey background.
+Each line segment had a length of $\approx$$1.6^{\circ}$ of visual angle irrespective of screen resolution.
+The target was oriented $45^{\circ}$ clockwise, while the distractor items had a random orientation with a mean of $45^{\circ}$ anti-clockwise.
+The variance was low ($18^{\circ}$) on one half of the display to create a homogeneous texture, and high ($95^{\circ}$) on the other side to create a heterogeneous texture.
+This means that when the target is present on the homogeneous half, it can be easily be detected with peripheral vision, but when it is in the heterogeneous half, it is much harder to detect.
+This was verified in a pilot experiment reported in \cite{nowakowska2017}.
+There were 160 trials in total and homo- and heterogeneous sides of the display were randomly varied from trial to trial.
+The position of the dominant eye was recorded using a desktop-mounted EyeLink 1000 eye tracker (SR Research, Canada).
+
+This paradigm was carried out twice, once in each testing session, to give us an estimate of how consistent participants are in their search strategy over time.
 

### 2018-11-29 NowakowskaClarkeHunt2017/sample_size.R

@@ -1,0 +1,63 @@
+library(tidyverse)
+library(binom)
+library(ggthemes)
+# library(lme4)
+# library(scales)
+
+fixdat = readRDS(file="data/processedFixData.Rda")
+fixdat = (filter(fixdat, subj!=4, subj!=15)) 
+#=======
+
+fixdat = as.tibble(readRDS(file="data/processedFixData.Rda"))
+
+levels(fixdat$subj) = 1:14
+#>>>>>>> Stashed changes
+cbPalette <- c("#56B4E9", "#E69F00")
+
+rtdat = as.tibble(readRDS(file="data/processedRTandAccData.Rda"))
+medianRT = aggregate(RT~subj, rtdat, "median")
+
+# classify every fixation as homo (left), central, or hetro (right)
+centralWidth = 64 #change to 1 visual degree
+fixdat$side = 'central'
+fixdat$side[which(fixdat$fixX <(512-centralWidth/2))] = "homo"
+fixdat$side[which(fixdat$fixX >(512+centralWidth/2))] = "hetro"
+fixdat$side = as.factor(fixdat$side)
+
+all_scores = tibble()
+
+for (n in 10:80) {
+
+	# sample a subset of trials
+	ss_dat <- tibble()
+	for (pp in levels(rtdat$subj)) {
+		ta_dat <- filter(rtdat, targSide == "absent", subj == pp)
+		ss_trl <- sample_n(ta_dat, n, replace = FALSE)
+		ss_dat <- bind_rows(ss_dat, filter(fixdat, subj == pp, trial %in% ss_trl$trial))
+
+	}
+
+	aggData = (filter(ss_dat, side!="central", fixNum<6, fixNum>1, targSide=="absent") 
+	  %>% group_by(subj, fixNum) 
+	    %>% summarise(
+	     propHetro=mean(side=="hetro"), 
+	     nTrials=length(trial)))
+
+	scores <- aggregate(data = aggData, propHetro ~ subj, mean)
+	scores$n <- n
+	all_scores <- bind_rows(all_scores, scores)
+
+}
+
+# all_scores_ref <- filter(all_scores, n == 80)
+# all_scores$error <- abs(all_scores$propHetro - rep(all_scores_ref$propHetro, 71))
+# all_scores <- filter(all_scores, n < 76)
+# mean_error <- aggregate(data = all_scores, error ~ n, mean)
+
+plt <- ggplot(all_scores, aes(x = n, y = propHetro, group = subj))
[…]

### 2018-11-29 Scripts/correlation_collection.R

@@ -14,14 +14,12 @@ cor_dat <- tibble(
 		"sh-rt a versus b hard", 
 		"sh-rt a versus b easy",
 		"sh - strategy",
-		"acvs prop optimal",
-		"acvs switch rate",
-		"MCFT feature (rn)",
+		"acvs prop optimal",	
 		"MCFT conjunction (rn)"),
-	estimate = c(0,0,0, 0.73, 0.83, 0.77,  0.7, 0.88),
-	lower = c(0.65, 0.66, 0.56, 0.585, 0.72, 0.63, 0.55, .81),
-	upper = c(0.86, 0.87, 0.82, 0.832, 0.90, 0.87, .8, .92),
-	type = rep('test-retest', 8))
+	estimate = c(0,0,0, 0.73, 0.83,  0.88),
+	lower = c(0.65, 0.66, 0.56, 0.585, 0.72,  .81),
+	upper = c(0.86, 0.87, 0.82, 0.832, 0.90, .92),
+	type = rep('test-retest', 6))
 
 add_r_95 <- function(x1, x2, df, t) {
 	ci95 <- cor.test(x1[[1]], x2[[1]])

### 2018-11-29 Manuscript/manuscript.tex
more small edits

@@
 Perhaps even more surprisingly, there is also little evidence for meaningful correlations between reaction times in the different tasks.
-Even if we optimistically take all the data together as suggesting a robust correlation in reaction times from task to task, the upper bound of $r=0.30$ means that this correlation only accounts for at best $10\%$\footnote{i.e., $R^2 = 0.3^2 = 0.09$} an individual's performance.
+Even if we optimistically take all data together as suggesting a robust correlation in reaction times from one task to another, the mean correlation over the three tasks is only $r = 0.2$, implying that this correlation accounts for  $R^2 = 0.04 = 4\%$ an individual's performance.
 
@@
 We successfully replicated the wide range of individual differences in strategy and performance that had previously been observed in each of these three visual search paradigms, with a larger sample size than the original experiments.
-Surprisingly, however, the between-paradigm correlations give at most $R^2 = 0.1$, and this is a generous interpretation that would fail to pass the usual criteria for null hypothesis significance testing.
+Surprisingly, however, the between-paradigm correlations give $R^2 = 0.04$, and this is a generous interpretation that would fail to pass the usual criteria for null hypothesis significance testing.
 Knowing how one person will behave in one of these paradigms apparently tells us very little about how they will perform in the others.
-This can be contrasted with the relatively high test-retest correlations of all three of the tasks individually, which range from [x to x].
+This can be contrasted with the relatively high test-retest correlations of all three of the tasks individually, which range from a lower bound of 0.58 to an upper bound of 0.92 .
 
 There are many reasons why two measurements might be uncorrelated, such as range restriction or measurement noise.
-The high test-retest correlations on each of the individual visual search tasks rules out many of these alternatives, leaving a true absence of shared variance between these tasks as a likely explanation.
-One might have expected reaction time to be at least modestly correlated from one search task to the next, even in the absence of correlations in strategy, as a general factor like an individual's motivation or conscientiousness might lead to better or worse overall performance across all the tasks.
+The test-retest correlations on each of the individual visual search tasks rules out many of these alternatives, leaving a true absence of shared variance between these tasks as a likely explanation.
+One might have expected reaction time to be at least modestly correlated from one search task to the next, even in the absence of correlations in strategy, as a general factor like an individual's speed-accuracy trade-off, motivation or conscientiousness might lead to better or worse overall performance across all the tasks.
 However, even reaction times were not highly correlated between tasks.
@@
 
+\section*{Acknowledgements}
+
+We would like to thanks Anna Nowakowska, {\'A}rn Kristj{\'a}nsson and Ian Thornton for sharing data and their helpful comments and suggestions.
+We would like to thank Charles Rigitano and Jacqueline Von Seth who helped with data collection.
+We acknowledge the funding support of the James S.
+McDonnell Foundation (Scholar Award to ARH).
+
 \bibliographystyle{plain}

### 2018-11-29 Scripts/correlation_collection.R

@@ -9,17 +9,15 @@ dat <- read_csv("summaryData.csv")
 
 
 cor_dat <- tibble(
-	comparison = c(
-		"sh-rt absent", 
-		"sh-rt a versus b hard", 
-		"sh-rt a versus b easy",
+	comparison = c(		
+		"sh-rt a versus b hard", 		
 		"sh - strategy",
 		"acvs prop optimal",	
-		"MCFT conjunction (rn)"),
-	estimate = c(0,0,0, 0.73, 0.83,  0.88),
-	lower = c(0.65, 0.66, 0.56, 0.585, 0.72,  .81),
-	upper = c(0.86, 0.87, 0.82, 0.832, 0.90, .92),
-	type = rep('test-retest', 6))
+		"MCFT (rn)"),
+	estimate = c(0, 0.73, 0.83,  0.88),
+	lower = c( 0.66, 0.585, 0.72,  .81),
+	upper = c( 0.87, 0.832, 0.90, .92),
+	type = rep('test-retest', 4))
 
 add_r_95 <- function(x1, x2, df, t) {
 	ci95 <- cor.test(x1[[1]], x2[[1]])
@@ -62,9 +60,7 @@ cor_dat$comparison <- fct_recode(cor_dat$comparison,
 	`SHLS (opt) - SHLS (rt)`  = "ls_prop_hetero-ls_mean_log_rt",
 	`ACVS (sw)`   = "acvs switch rate",
 	`ACVS (opt)`  = "acvs prop optimal",
-	`SHLS absent (rt)`  = "sh-rt absent",
-	`SHLS easy (rt)`  = "sh-rt a versus b easy",
-	`SHLS hard(rt)`  = "sh-rt a versus b hard",
+	`SHLS (rt)`  = "sh-rt a versus b hard",
 	`SHLS (opt)` = "sh - strategy",
 	`MCFT (rl) - MCFT (rt)`  = "fg_conj_run_length-fg_conj_log2",
 	`MCFT (rl) - MCFT (rt)`  = "fg_conj_run_length-fg_conj_log2",
@@ -91,5 +87,5 @@ plt <- plt + theme(
 	legend.position = "top",
 	axis.title.y = element_blank())
 plt
-ggsave("scratch/cor_comparison.pdf", width = 5, height = 7)
-ggsave("scratch/cor_comparison.png", width = 5, height = 7)
+ggsave("scratch/cor_comparison.pdf", width = 4, height = 5)
+ggsave("scratch/cor_comparison.png", width = 4, height = 5)

### 2018-11-30 Manuscript/manuscript.tex
Draft 0.1 Finished!

@@
 This paradigm involves stimuli made up of small coloured boxes (red, blue, green and a fourth colour that varies from red, through purple, to blue and back again) with numerals written inside them (See Figure \ref{fig:exampleStimuli}).
-The target is a defined as a red or blue box with a numeral between 1 and 4, and on each trial one target of each colour is present.
+The target is a defined as a red or blue box containing one of four numerals (e.g., 2-5), and on each trial one target of each colour is present.
 The participant's task is to find one of either target as quickly as possible and report the numeral.
@@
 The results showed that participants varied substantially along two key dimensions: how frequently they used the more effective target color to search (varying from chance performance to near optimal), and how often they changed between colours.
-Further work has shown that these differences are stable over time (between one and ten days) with test-retest correlations of around $r \approx 0.8$\cite{irons-leber2018}.
+Further work\cite{irons-leber2018} has shown that these differences are stable over time (between one and ten days) with test-retest correlations of around $r = 0.83$ ($95\%$ confidence interval $= [0.72, 0.90]$).
 
@@
 \subfigure[][]{\includegraphics[height=3cm]{figures/foraging.png}}
-\caption{Example stimulus from the (a) \textit{split-half}, (b) \textit{adaptive choice} and (c) \textit{foraging} paradigms.}
+\caption{Example stimulus from the (a) \textit{split-half line segment} (SHLS), (b) \textit{adaptive choice visual search} (ACVS) and (c) \textit{mouse click foraging task} (MCFT) paradigms.}
 \label{fig:exampleStimuli}
@@
 In the conjunction condition (searching for red-horizontal and green-vertical line segments among red-vertical and green-horizontal distracters), most observers searched in runs, finding all the targets of one target category, and then switching and finding the targets in the other category.
-This strategy has previously been observers in animal foraging \cite{dawkins1971}, and suggests holding one complex target template in mind at a time is a better strategy than switching templates.
+This strategy has previously been observed in animal foraging \cite{dawkins1971}, and suggests holding one complex target template in mind at a time is a better strategy than switching templates.
 However, a sub-set of observers, termed `super-foragers', were able to change between search target categories with no cost to performance.
@@
 
-Previous research has investigated the relationship between these behaviours to \hyphenation{psychometric} measures, but to date, these differences have not shown strong correlations with other attributes.
-In the ACVS paradigm, Irons \& Leber found no evidence of a correlation between the proportion of optimal choices made by observers and measures of visual working memory or trait compulsivity\cite{irons-leber2016}.
+Previous research has investigated the relationship between these behaviours to psychometric measures, but to date, these differences have not shown strong correlations with other attributes.
+In the ACVS paradigm, Irons \& Leber found no evidence of a correlation between the proportion of optimal choices made by observers and measures of visual working memory; trait impulsivity\cite{irons-leber2016}; novelty seeking; need for cognition; and intolerance of uncertainty\cite{irons-leber2018}.
 Similarly, the differences foraging behaviour are not accounted for by working memory or inhibitory control\cite{johannesson2017}.
@@
 Are the super-foragers consistently better or worse than more typical searchers in the other two paradigms?
-As a secondary question, we will measure the test-retest reliability of the differences found in the SHLS paradigm.
+As a secondary question, we will measure the test-retest reliability of the differences found in the SHLS paradigm, and compare it with existing estimates of reliability for ACVS and MCFT.
 
@@
 $n = 64$ participants means we should be able to detect correlations with $r > 0.34$ with $\alpha = 0.05$, $\beta = 0.80$ between the different visual search paradigms.
-The sample size is therefore of sufficient size to detect relatively small correlations.
+The sample is therefore of sufficient size to detect relatively small correlations.
 
@@
 A brief overview of each paradigm is given below, with full details in \textit{supplementary materials}.
-The three tasks will be completed over two sessions, approximately one week apart.
+The three tasks were completed over two sessions, approximately one week apart.
 The SHLS was run in both sessions allowing us to measure test-retest reliability.
@@
 
-The display was presented on a 17-inch CRT monitor with a resolutions of $1400 \times 1050$ ($n = 40$) or $1600 \times 1200$ ($n = 24$).
+The display was presented on a 17-inch CRT monitor with a resolution of $1400 \times 1050$ ($n = 40$) or $1600 \times 1200$ ($n = 24$).
 Stimulus generation, presentation and data collection were controlled by MATLAB and the psychophysics and eyelink toolboxes \cite{brainard1997,cornelissen2002} run on a Powermac.
@@
 Our results are consistent with the original SHLS study\cite{nowakowska2017}: we find a large range of individual differences in search reaction time and accuracy (see Figure \ref{fig:splithalf_summary}).
-Furthermore, these differences are stable from between the two testing sessions, with Pearson's $r \in [0.71, 0.89]$ ($95\%$ confidence interval) for accuracy in finding hard targets.
+Furthermore, these differences are stable across the two sessions, with Pearson's $r \in [0.71, 0.89]$ ($95\%$ confidence interval) for accuracy in finding hard targets.
 We get similar scores for the correlation in reaction times between sessions \textit{a} and \textit{b} for hard targets, ($r \in [0.54-0.81]$), easy targets ($r \in [0.52-0.80]$) and target absent trials ($r \in [0.66-0.86]$).
@@
 \subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/lineseg/scratch/strat_compare_meanlog_rt.pdf}}
-\caption{Each point represents a participant and the error-bars indicate 95\% confidence intervals.
-Correlation between the two sessions of the SHLS paradigm for (a)  accuracy (TP-heterogeneous trials only); (b) reaction times and (c) search strategy (TA trials only).
+\caption{Correlation between the two sessions of the SHLS paradigm for (a)  accuracy (TP-heterogeneous trials only); (b) reaction times and (c) search strategy (TA trials only).
 (d) Initial search strategy correlates with reaction times in both sessions.
-}
+Each point represents a participant and the error-bars indicate 95\% confidence intervals.}
 \label{fig:splithalf_summary}
@@
 The results for the ACVS were consistent with previous findings \cite{irons-leber2016,irons-leber2018}.
-We can clearly see from figure \ref{fig:acvs_summary} that there are individual differences in both the proportion of optimal targets reported (range $33.62\%$ - $100.00\%$, $\bar{x} = 59.15$, $s = 16.54$) and switch rate (range = $0\% - 56.68\%$, $\bar{x} = 28.50$, $s = 14.13$).
+We can clearly see from figure \ref{fig:acvs_mcft_summary}(a) that there are individual differences in the proportion of optimal targets reported (range $33.62\%$ - $100.00\%$, $\bar{x} = 59.15$, $s = 16.54$) and the mean ($\log_2$) reaction times (range $1.90$ - $4.80$ seconds).
+As with the SHLS task, the degree to which participants follow the optimal strategy is correlated with reaction times ($r \in [-0.65, -0.25]$).
 
@@
 \centering
-\includegraphics[width=6.5cm]{../Scripts/adaptchoice/ac_percentOpt_hist.pdf}
-\caption{Histograms showing the range of individual differences found in the ACVS task.}
-\label{fig:acvs_summary}
+\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/scratch/acvs_opt_rt}}
+\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/scratch/mcft_rl_rt}}
+\caption{Correlation between strategy and reaction times for (a) ACVS and (b) MCFT. Each point represents a participant.}
+\label{fig:acvs_mcft_summary}
 \end{figure}
@@
 This suggests more frequent foraging for multiple targets concurrently when those targets were defined by features than by conjunctions.
-Figure \ref{fig:foraging_summary} depicts the individual differences in terms of run length: twenty ``super-searchers'' were revealed, identified by short run lengths for both feature and conjunction targets.
-
-\begin{figure}
-\centering
-\includegraphics[width=6.5cm]{../Scripts/foraging/fg_conjRunLength_hist.pdf}
-\caption{Histogram of mean run lengths for the conjunction foraging task.}
-\label{fig:foraging_summary}
-\end{figure}
+Figure \ref{fig:acvs_mcft_summary}(b) depicts the individual differences in terms of run length and the correlation with reaction time ($r \in [-0.55, -0.10]$).
 
@@
 There are many reasons why two measurements might be uncorrelated, such as range restriction or measurement noise.
-The test-retest correlations on each of the individual visual search tasks rules out many of these alternatives, leaving a true absence of shared variance between these tasks as a likely explanation.
+The test-retest correlations on each of the individual visual search tasks rule out many of these alternatives, leaving a true absence of shared variance between these tasks as a likely explanation.
 One might have expected reaction time to be at least modestly correlated from one search task to the next, even in the absence of correlations in strategy, as a general factor like an individual's speed-accuracy trade-off, motivation or conscientiousness might lead to better or worse overall performance across all the tasks.
@@
 
-Add something about learning, experience, reinforcement - Hayhoe/Land references?
-
-Mention \cite{vogel2008}.
-From \cite{proulx2011} - \textit{Vogel and colleagues have found that an individual's ability to remember a greater number of items using working memory is related to a filtering capacity in visual search that suppresses attentional capture by distracting visual information [10,11,12].
-Behavioural work in visual search has extended this research to
-demonstrate that working memory correlates only with top-down
-visual search performance where task relevance is crucial, but not
-with  bottom-up  visual  search  tasks  where  salience  in  the
-environment guides attention \cite{sobel2007}}
-
-Mention \cite{stoet2011}.
+We view these findings, not as a disappointing null result, but as thought-provoking and exciting.
+Vogel and Awh\cite{vogel2008} argued that studying individual differences in cognitive psychology (in their case, working memory) provides valuable insight to containing potential theories of the underlying cognitive mechanisms.
+Our results suggest that context and structure of the task also needs to be taking into account and we hope that studying how an individual's behaviour varies across different search tasks will lead to the development of a more comprehensive theory of search.
 
@@
 We acknowledge the funding support of the James S.
-McDonnell Foundation (Scholar Award to ARH).
+McDonnell Foundation (Scholar Award to ARH) and NSF BCS-1632296 to ABL.
 

### 2018-11-30 Scripts/make_scatter_for_acvs_mcft.R

@@ -1,0 +1,282 @@
+library(tidyverse)
+
+
+figXn <- 3.5
+figYn <- 2.5
+
+dat <- read_csv("summaryData_75.csv")
+
+
+# remove people who had the wrong resolution!
+idx <- c(1, 2, 3, 4, 11, 31, 69)
+
+dat <- filter(dat, !(observer %in% idx))
+
+# numbers taken from inital parsing script for split half paradigm
+
+
+############################################################
+# ACVS opt v rt
+############################################################
+
+r <- (with(dat, cor.test(ac_propOpt, ac_meanlog2rt)))
+
+y_labels = seq(2,5, 0.5)
+y_breaks = log(1000* y_labels, 2)
+
+
+
+plt <- ggplot(dat, aes(x = ac_propOpt, y = ac_meanlog2rt))
+plt <- plt + geom_point() 
+plt <- plt + geom_smooth(method = lm, colour = "black", fullrange = TRUE, linetype = 1)
+plt <- plt + theme_bw()
+plt <- plt + scale_x_continuous("ACVS proportion optimal",
+	  limits = c(0, 1 ), breaks = c(0, 1), expand = c(0, 0))
+plt <- plt + scale_y_continuous("ACVS reaction time (s)",
+	  breaks = y_breaks, labels = y_labels, expand = c(0, 0))
+plt <- plt + coord_cartesian(xlim=c(0, 1), ylim=c(10.8, 12.3))
+plt <- plt + theme(
+  panel.grid.major = element_blank(), 
+  panel.grid.minor = element_blank())
+# plt <- plt + ggtitle('Split-half and Attentional Control')
+ggsave("scratch/acvs_opt_rt.pdf", width = figYn, height = figYn)
+plt
+
+############################################################
+# MCFT opt v rt
+############################################################
+
+
+r <- (with(dat, cor.test(fg_conj_run_length, fg_conj_log2)))
+
+y_labels = seq(22.5, 60,  7.5)
+y_breaks = log(1000* y_labels, 2)
+
+
+plt <- ggplot(dat, aes(x = fg_conj_run_length, y = fg_conj_log2))
+plt <- plt + geom_point() 
+plt <- plt + geom_smooth(method = lm, colour = "black", fullrange = TRUE, linetype = 1)
+plt <- plt + theme_bw()
[…]

### 2018-11-30 Manuscript/manuscript.tex
changed to default template

@@
 \RequirePackage{fix-cm}
-\documentclass[]{rsos}%%%%where rsos is the template name
+\documentclass[twocolumn]{article}
 
@@
 \usepackage{hyperref}
-\begin{document}
+\usepackage{graphicx}
+\usepackage{authblk}
 
@@
 
-\author{%%%% Author details
-Alasdair D. F. Clarke$^1$, Jessica L Irons$^2$, Warren James$^3$, Andrew B Leber$^2$ and Amelia R Hunt$^3$}
+\author[1, *]{A. D. F. Clarke}
+\author[2]{J. L. Irons} 
+\author[3]{W. James}
+\author[2]{A. B. Leber}
+\author[3]{A. R. Hunt}
 
-%%%%%%%%% Insert author address here
-\address{$^{1}$Department of Psychology, University of Essex, Colchester, UK\\
-$^{2}$Department of Psychology, The Ohio State University, Columbus, USA\\
-$^{3}$School of Psychology, University of Aberdeen, Aberdeen, UK}
+\affil[1]{Department of Psychology, University of Essex, Colchester, UK}
+\affil[2]{Department of Psychology, The Ohio State University, Columbus, USA}
+\affil[3]{School of Psychology, University of Aberdeen, Aberdeen, UK}
+\affil[*]{Corresponding author: a.clarke@essex.ac.uk}
+\renewcommand\Affilfont{\itshape\small}
 
-%%%% Subject entries to be placed here %%%%
-\subject{Behaviour, evolution}
+% %%%% Subject entries to be placed here %%%%
+% \subject{Behaviour, evolution}
 
-%%%% Keyword entries to be placed here %%%%
-\keywords{visual search, optimal behaviour, eye movements}
+% %%%% Keyword entries to be placed here %%%%
+% \keywords{visual search, optimal behaviour, eye movements}
 
-%%%% Insert corresponding author and its email address}
-\corres{Alasdair Clarke\\
-\email{a.clarke@essex.ac.uk}}
+% %%%% Insert corresponding author and its email address}
+% \corres{Alasdair Clarke\\
+% \email{a.clarke@essex.ac.uk}}
+
+\begin{document}
+\maketitle
 
@@
 
-%%%%%%%%%% Insert the texts which can accomdate on firstpage in the tag "fmtext" %%%%%
-
-\begin{fmtext}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 As is common in cognitive psychology, most visual search literature has focused on how the average participant performs in the task, despite it being well known that there is a great deal of variability between one subject and the next.
-From Treisman's work on \end{fmtext}
-\maketitle
-\twocolumn Feature Integration Theory\cite{treisman1980} to the latest incarnation of the Guided Search Model\cite{wolfe2015}, we now have a good understanding of what makes some search targets effortless to find, while others require careful inspection.
+From Treisman's work on Feature Integration Theory\cite{treisman1980} to the latest incarnation of the Guided Search Model\cite{wolfe2015}, we now have a good understanding of what makes some search targets effortless to find, while others require careful inspection.
 However, these theories and models have neglected the question of why some observers find visual search so much harder than others.
@@
 Large individual differences were found with respect to the number of saccades participants made while monitoring the stimulus, and this was negatively correlated with detection performance.
-Proulx\cite{proulx2011} demonstrated that participants differed in how they prioritised visual features (color or orientation) when searching through a set of objects for one with a particular color-orientation combination.
+Proulx\cite{proulx2011} demonstrated that participants differed in how they prioritised visual features (colour or orientation) when searching through a set of objects for one with a particular colour-orientation combination.
 These differences in search strategy explained some of the variation in the extent to which participants were distracted by an irrelevant object of a unique size.
@@
 A related version of this paradigm has been used in research investigating eye movement strategies in response to (simulated) hemianopia\cite{nowakowska2016,nowakowska2018}, with similar conclusions: the full spectrum of individual differences in strategy was observed, from near-optimal to the opposite of optimal.
-It is therefore not possible to conclude whether optimal or stochastic models better describe search without first explaining individual variablility.
+It is therefore not possible to conclude whether optimal or stochastic models better describe search without first explaining individual variability.
 
@@
 As the fourth colour changes to through purple to blue, participants should update their strategy and search for the red target.
-The results showed that participants varied substantially along two key dimensions: how frequently they used the more effective target color to search (varying from chance performance to near optimal), and how often they changed between colours.
+The results showed that participants varied substantially along two key dimensions: how frequently they used the more effective target colour to search (varying from chance performance to near optimal), and how often they changed between colours.
 Further work\cite{irons-leber2018} has shown that these differences are stable over time (between one and ten days) with test-retest correlations of around $r = 0.83$ ($95\%$ confidence interval $= [0.72, 0.90]$).
@@
 Are observers who use the optimal strategy in the SHLS paradigm also more optimal in the ACVS task?
-Does it make sense to talk about `super-searchers' who show above average performance in a range of search tasks (analogous to the 'super-recognizers' of the face-recognition literature \cite{russell2009}?
+Does it make sense to talk about `super-searchers' who show above average performance in a range of search tasks (analogous to the 'super-recognizers' of the face-recognition literature \cite{russell2009})?
 Are the super-foragers consistently better or worse than more typical searchers in the other two paradigms?

### 2018-11-30 Scripts/make_scatter_for_acvs_mcft.R
y axis edit
As the previous one didn’t save

@@ -49,7 +49,7 @@ plt
 
 r <- (with(dat, cor.test(fg_conj_run_length, fg_conj_log2)))
 
-y_labels = seq(22.5, 60,  7.5)
+y_labels = seq(24, 60, 6)
 y_breaks = log(1000* y_labels, 2)
 
 

### 2018-11-30 Manuscript/sup_mat/sup_mat.Rmd
Added Rmarkdown file for sup_mat

---
title: "Supplementary Materials"
output:
  html_document:
    toc: yes
    toc_depth: 2
  pdf_document:
    toc: yes
    toc_depth: '2'
---

```{r setup, include=FALSE}
# setting options
knitr::opts_chunk$set(echo = TRUE)

# Packages
library(tidyverse)
library(ggthemes)

# what data do we need?
# get line seg acc and rt 
ls_acc_RT <- readRDS(file = "../../Scripts/lineseg/scratch/processedRTandAccData.Rda")

```

# 1 Participants
```{r Participants, echo = FALSE}
# sort out participants 
ls_acc_RT$observer <- as.factor(as.numeric(ls_acc_RT$observer))

# number of participants used
num_participants <- length(unique(ls_acc_RT$observer))

avg_acc_all <- ls_acc_RT %>%
  group_by(observer,targSide) %>%
  summarise(Acc = mean(accuracy))

```

Data was collected from 64 Participants as originally planned. Four of these participants did not complete all parts of the experiment (either declining to participate in the second session, or could not be calibrated with the eye tracker), so four new participants were recruited to bring the total back up to `r num_participants`.

## 1.1 Split-Half
Accuracy data is shown in Figure 1. From this we can see that there are a number of outliers:  4, 21, 33, 56, and 58. These participants, in at least one session, either missed the majority of easy targets, or responded with false positives on the majority of target absent trials. After removing these participants, the lowest accuracy in either session was 84.6% for the easy targets, and 76.9% for target absent trials. This leaves us with 59 participants for the split-half paradigm.

```{r Figure 1, echo = FALSE}

# make the plot
plt <- ls_acc_RT %>%
  group_by(observer, targSide, session) %>%
  summarise(Accuracy = mean(accuracy)) %>%
  ggplot(aes(targSide, Accuracy, fill = session)) + 
  geom_bar(stat = "identity", position = position_dodge()) + 
  scale_y_continuous(breaks = c(0,1)) + 
  theme_bw() +
  theme(axis.text.x  = element_text(angle=90, vjust=0.5), legend.position = "top", strip.text.x = element_text(margin = margin(0.01,0,0.01,0, "mm"))) + 
  scale_fill_ptol() +
  facet_wrap(~observer)
plt$labels$x <- "Target Condition"
plt

### 2018-11-30 Manuscript/manuscript.tex
Fixing some typos

@@
 We tested 64 observers in the three tasks mentioned above over two sessions.
-Even though the test-retest reliability of the tasks is high, an observer’s performance and strategy in one task did not reliably predict their behaviour in the other two.
+Even though the test-retest reliability of the tasks is high, an observer's performance and strategy in one task did not reliably predict their behaviour in the other two.
 These results suggest search strategies are stable over time, but context-specific.
@@
 They asked participants to monitor a cluttered display for an object changing colour or suddenly appearing.
-Large individual differences were found with respect to the number of saccades participants made while monitoring the stimulus, and this was negatively correlated with detection performance.
+Large individual differences were found with respect to the number of saccades participants made while monitoring the stimulus, and the number of saccades was negatively correlated with detection performance.
 Proulx\cite{proulx2011} demonstrated that participants differed in how they prioritised visual features (colour or orientation) when searching through a set of objects for one with a particular colour-orientation combination.
@@
 Nowakowska, Clarke \& Hunt\cite{nowakowska2017} designed a simple search paradigm to discriminate between optimal\cite{najemnik-geisler2008} and stochastic \cite{clarke2016} search strategies.
-The task involved searching through arrays of line segments arranged such that those on one side of the display all had a very similar orientation ("homogeneous"), while those on the other side had higher variance ("heterogeneous", see Figure \ref{fig:exampleStimuli} for an example).
+The task involved searching through arrays of line segments arranged such that those on one side of the display all had a very similar orientation (homogeneous), while those on the other side had higher variance (heterogeneous).
+See Figure \ref{fig:exampleStimuli} for an example.
 This meant that targets appearing on the homogeneous side would be highly salient, and targets on the heterogeneous side  would be much harder to find.
@@
 In the ACVS paradigm, Irons \& Leber found no evidence of a correlation between the proportion of optimal choices made by observers and measures of visual working memory; trait impulsivity\cite{irons-leber2016}; novelty seeking; need for cognition; and intolerance of uncertainty\cite{irons-leber2018}.
-Similarly, the differences foraging behaviour are not accounted for by working memory or inhibitory control\cite{johannesson2017}.
+Similarly, the differences in foraging behaviour are not accounted for by working memory or inhibitory control\cite{johannesson2017}.
 
@@
 \subsection{Participants}
-64 students from the University of Aberdeen took part in this study\footnote{data from an additional 11 participants was discarded due to being recorded with an inappropriate screen resolution.}.
+64 students with normal or corrected-to-normal vision from the University of Aberdeen took part in this study\footnote{data from an additional 11 participants was discarded due to being recorded with an inappropriate screen resolution.
+Another participant was exluded due to colour blindness.}.
 Participants were compensated for their time with either  course credit or \pounds 15.
@@
 Blue bars represent test-retest scores for each task for reaction times (\textit{rt}), optimality (\textit{opt}) or run length (\textit{rl}).
-Yellow bars indicate how well the strategy measures predict reaction times, while the red bars show that performance in one task is not a good indication of performance in another, either for reaction times of strategy.}
+Yellow bars indicate how well the strategy measures predict reaction times, while the red bars show that performance in one task is not a good indication of performance in another, either for reaction times or strategy.}
 \label{fig:all_the_cor}

### 2018-12-10 Manuscript/sup_mat/sup_mat.Rmd
Updated Sup_mat
Added a table and new numbers for the trials etc with the most up to date data

@@
 output:
-  html_document:
+  bookdown::html_document2:
     toc: yes
     toc_depth: 2
-  pdf_document:
-    toc: yes
-    toc_depth: '2'
+    fig_caption: yes
 ---
@@
 library(ggthemes)
+library(gridExtra)
+library(knitr)
 
@@
 
-# 1 Participants
+# Participants
 ```{r Participants, echo = FALSE}
 # sort out participants 
-ls_acc_RT$observer <- as.factor(as.numeric(ls_acc_RT$observer))
+ls_acc_RT$observer <- as.numeric(as.factor(as.numeric(ls_acc_RT$observer)))
 
@@
 
+```
+
+```{r processing ls data, echo = FALSE, include = FALSE}
+# load in unprocessed data 
+load("../../Scripts/lineseg/scratch/unfiltered_fixDat")
+load("../../Scripts/lineseg/scratch/unfiltered_trlDat")
+trlDat_unf <- trlDat
+# tidy 
+rm(trlDat)
+
+# sort out participant levels 
+fixDat$observer <- as.numeric(as.factor(as.numeric(fixDat$observer)))
+
+fixDat_unf <- fixDat
+# tidy 
+rm(fixDat)
+
+#### getting accuracy and mistaken keys ####
+invalid_kp <- trlDat_unf %>%
+  group_by(responseKey) %>%
+  summarise(n = n()) %>%
+  filter(responseKey == "Key_x")
+invalid_kp <- invalid_kp$n
+
+# filter out bad participants 
 avg_acc_all <- ls_acc_RT %>%
-  group_by(observer,targSide) %>%
+  filter(observer != 15,
+         observer != 25,
+         observer != 47,
+         observer != 48) %>%
+  group_by(observer, targSide) %>%
   summarise(Acc = mean(accuracy))
 
+# min acc easy 
+min_easy <- round(min(avg_acc_all$Acc[avg_acc_all$targSide == "easy"]), digits = 3)*100
+
+# min acc absent 
+min_absent <- round(min(avg_acc_all$Acc[avg_acc_all$targSide == "absent"]), digits = 3)*100
+
+#### sorting out fixation data #### 
+num_fixations <- nrow(fixDat_unf)
+
+# get removed fixations data 
+load("../../Scripts/lineseg/scratch/processedFixationData")
+# get difference value 
+num_removed <- num_fixations - nrow(fixDat)
+
 ```
-
 Data was collected from 64 Participants as originally planned.
@@
 
-## 1.1 Split-Half
-Accuracy data is shown in Figure 1.
-From this we can see that there are a number of outliers:  4, 21, 33, 56, and 58.
+## Split-Half
+Accuracy data is shown in Figure \ref{fig:fig1}.
+From this we can see that there are a number of outliers: 15, 25, 47, and 48 (NB: these may have changed with new labelling).
 These participants, in at least one session, either missed the majority of easy targets, or responded with false positives on the majority of target absent trials.
-After removing these participants, the lowest accuracy in either session was 84.6% for the easy targets, and 76.9% for target absent trials.
-This leaves us with 59 participants for the split-half paradigm.
+After removing these participants, the lowest accuracy in either session was `r paste(min_easy,"%", sep = "")` for the easy targets, and `r paste(min_absent, "%", sep = "")` for target absent trials.
+This leaves us with `r length(unique(avg_acc_all$observer))` participants for the split-half paradigm.
 
-```{r Figure 1, echo = FALSE}
-
+```{r fig1, fig.cap = "\\label{fig1} Accuracy data for each participant for the split-half paradigm. ", echo = FALSE, fig.align = "center"}
 # make the plot
@@
 plt
+```
+
+```{r fig2, fig.cap = "\\label{fig2} Distribution of reaction times in split-half paradigm.", echo = FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
+plt <- ls_acc_RT %>%
+  ggplot(aes(rt)) + 
+  geom_histogram() + 
+  theme_bw() +  
+  facet_wrap(~targSide)
+plt$labels$x <- "Response Time (msecs)"
+plt2 <- ls_acc_RT %>%
+  mutate(log2_RT = log2(rt)) %>%
+  ggplot(aes(log2_RT)) + 
+  geom_histogram() + 
+  theme_bw() +
+  facet_wrap(~ targSide)
+plt2$labels$x <- "log2 Response Time"
+
+# put together 
+grid.arrange(plt,plt2)
+```
+
+# Data Processing
+
+## Split-Half 
+`r invalid_kp` trials with invalid key responses were removed.
+After removing data from the four outlier participants (see above), all remaining incorrect trials `r #find out what this number is meant to be` (n = 2529) were removed, leaving a total of `r nrow(trlDat_unf) - invalid_kp` trials over 60 participants.
+
+### Reaction Times 
+As expected, reaction times were highly skewed (Figure 2), so were log2 transformed (in ms units) before the participant means were calculated for each session and target condition (Figure )
+
+### Eye Movements
+`r num_fixations` fixations were recorded.
+Of these, `r num_removed` fell outside of the stimuli area and were removed.
+Fixations landing within a vertical strip consisting of 10% of the stimuli's width were classed as central.
+All remaining fixations were then classed as landing on the homogeneous or heterogeneous half of the stimulus.
+Initial fixations were not included in the analysis.
+Numbers of fixations are given in Table 2.
+
+```{r make table, echo = FALSE, results='asis'}
+# get fixation location
+fixDat <- fixDat %>%
+  mutate(fix_loc = "central")
+fixDat$fix_loc[fixDat$x < -0.1 & fixDat$easySide == "left"] <- "homogenous"
+fixDat$fix_loc[fixDat$x > 0.1 & fixDat$easySide == "right"] <- "homogenous"
+fixDat$fix_loc[fixDat$x < -0.1 & fixDat$easySide == "right"] <- "heterogenous"
+fixDat$fix_loc[fixDat$x > 0.1 & fixDat$easySide == "left"] <- "heterogenous"
+
+# get num fixations in these locations 
+table_dat_all <- fixDat %>%
+  group_by(targSide, fix_loc) %>%
+  filter(n < 6) %>%
+  summarise(number = n()) %>%
+  mutate(range = "1 < n")
+
+table_dat_2_to_5 <- fixDat %>%
+  group_by(targSide, fix_loc) %>%
+  filter(n >= 2,
+         n <= 5) %>%
+  summarise(number = n()) %>%
+  mutate(range = "2 <= n <= 5")
+
+table_dat <- rbind(table_dat_all, table_dat_2_to_5) %>%
+  spread(range, number)
+
+# make table 
+kable(table_dat, caption = "table thing")
+```
+
+## Adaptive Choice
+
+## Foraging

### 2018-12-10 Scripts/lineseg/1_init_processing.R

@@ -229,9 +229,23 @@ fixDat$x[which(fixDat$easySide=="right")] <- -fixDat$x[which(fixDat$easySide=="r
 # plt <- plt + facet_wrap(~observer)
 # plt
 
+
+# remove people who had a 1028 x 768 resolution 
+idx <- filter(resDat, xRes == 1024)$observer
+trlDat <- filter(trlDat, !(observer %in% idx))
+fixDat <- filter(fixDat, !(observer %in% idx))
+resDat <- filter(resDat, !(observer %in% idx))
+
+# save fixdat before filtering out fixations out of range
+save(fixDat, file = "scratch/unfiltered_fixDat")
+
 # only take fixations that fall within screen
 fixDat$x <- with(fixDat, ifelse(x > -1 & x <1, x, NaN))
 fixDat$y <- with(fixDat, ifelse(y > -1 & y <1, y, NaN))
+
+
+# save before filtering 
+save(trlDat, file = "scratch/unfiltered_trlDat")
 
 
 # remove trials which are invalid for one reason or another
@@ -244,15 +258,10 @@ incTrials <- with(trlDat, paste(observer, session, trial))
 fixDat <- filter(fixDat, paste(observer, session, trial) %in% incTrials)
 rm(incTrials)
 
-# remove people who had a 1028 x 768 resolution 
-idx <- filter(resDat, xRes == 1024)$observer
-trlDat <- filter(trlDat, !(observer %in% idx))
-fixDat <- filter(fixDat, !(observer %in% idx))
-resDat <- filter(resDat, !(observer %in% idx))
 
 trlDat$observer <- fct_drop(trlDat$observer)
 fixDat$observer <- fct_drop(fixDat$observer)
 
 # save
-saveRDS(trlDat, "scratch/processedRTandAccData.Rda")
-saveRDS(fixDat, "scratch/processedFixationData.Rda")
+save(trlDat, file = "scratch/processedRTandAccData")
+save(fixDat, file = "scratch/processedFixationData")

### 2018-12-11 Manuscript/sup_mat/sup_mat.Rmd
changes to sup_mat
Added some more information and sorted plots

@@
 
+# Methods 
+## Split-Half
+In this task, a chin rest with forehead bar was used in order to ensure a viewing distance of 47cm.
+Participants' fixations were tracked using a deskmounted Eylink 1000 (version 4.594) to record eye position at 1000 Hz.
+Prior to every block, a 9-point calibration was carried out.
+This task lasted approximately 30 minutes.
+
+The line segments subtended approximately 1.6&deg; of visual angle.
+
+Any other details needed?
+
+## Adaptive Choice
+For this task, participants were sat approximately 47cm from the screen though no chin rest was used to ensure a constant viewing distance.
+Participants were give 10 practice trials (check this) before starting the actual experiment.
+(Check how many blocks as well).
+Participants were told they were to search for a target number (2-5 inclusive).
+There would be two of these target numbers on every trial; one in a blue square and one in a red square.
+They were told they only needed to report one of these numbers.
+The squares subtended between ~1.1&deg; and ~1.3&deg; depending on the screen resolution the participant was tested at (either 1600x1200 or 1400x1050, respectively).
+Participants were instructed to be as fast and accuracte as possible.
+They were also told there would be a tone if they were to report a number that was not present within any of the boxes matching the two target colours.
+
+## Foraging 
+Same as the in the Adaptive Choice task, participants were not sat in a chin rest and so viewing distance was approximately.
+There were (get number of objects on display, I think it was 40?), half of which were the targets for that trial.
+The squares and circles subtended between ~0.6&deg; and ~0.7&deg; depending on the screen resolution the participant was tested at (either 1600x1200 or 1400x1050, respectively).
+
+Before starting the experiment, participants had 10 (check this number) practice trials to familiarise themeselves with the task.
+After completing the task with either the feature or conjunction search, participants would then repeat the task in the remaining condition.
+This took approximately 20 minutes.
+
 # Participants
+
 ```{r Participants, echo = FALSE}
@@
 
+#### get number of incorrect trials ####
+incorrect_trials <- ls_acc_RT %>%
+  filter(observer != 15,
+         observer != 25,
+         observer != 47,
+         observer != 48,
+         responseKey != "Key_x") %>%
+  group_by(accuracy) %>%
+  summarise(n = n())
+
 # min acc easy 
@@
 
-```{r fig1, fig.cap = "\\label{fig1} Accuracy data for each participant for the split-half paradigm. ", echo = FALSE, fig.align = "center"}
+```{r acc_plt, fig.cap = "Accuracy data for each participant for the split-half paradigm. ", echo = FALSE, fig.align = "center"}
 # make the plot
@@
 
-```{r fig2, fig.cap = "\\label{fig2} Distribution of reaction times in split-half paradigm.", echo = FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
+```{r rt_plt, fig.cap = "Distribution of reaction times in split-half paradigm.", echo = FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
 plt <- ls_acc_RT %>%
@@
 `r invalid_kp` trials with invalid key responses were removed.
-After removing data from the four outlier participants (see above), all remaining incorrect trials `r #find out what this number is meant to be` (n = 2529) were removed, leaving a total of `r nrow(trlDat_unf) - invalid_kp` trials over 60 participants.
+After removing data from the four outlier participants (see above), all remaining incorrect trials (n = `r incorrect_trials$n[incorrect_trials$accuracy == 0]`) were removed, leaving a total of `r incorrect_trials$n[incorrect_trials$accuracy == 1]` trials over 60 participants.
 

### 2018-12-11 Manuscript/sup_mat/sup_mat.Rmd
more updates to sup_mat

@@
 ## Split-Half
-Accuracy data is shown in Figure \ref{fig:fig1}.
+Accuracy data is shown in Figure \ref{fig:acc_plt}.
 From this we can see that there are a number of outliers: 15, 25, 47, and 48 (NB: these may have changed with new labelling).
@@
 
-```{r acc_plt, fig.cap = "Accuracy data for each participant for the split-half paradigm. ", echo = FALSE, fig.align = "center"}
+```{r acc_plt, fig.cap = "\\label{fig:acc_plt} Accuracy data for each participant for the split-half paradigm. ", echo = FALSE, fig.align = "center"}
 # make the plot
@@
 
-```{r rt_plt, fig.cap = "Distribution of reaction times in split-half paradigm.", echo = FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
+```{r rt_plt, fig.cap = "\\label{fig:rt_plt} Distribution of reaction times in split-half paradigm.", echo = FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
 plt <- ls_acc_RT %>%

### 2018-12-12 Manuscript/sup_mat/sup_mat.Rmd
More sup_mat work
Added some new plots.
Started work on adding information about the ACS task and its analysis

@@
 For this task, participants were sat approximately 47cm from the screen though no chin rest was used to ensure a constant viewing distance.
-Participants were give 10 practice trials (check this) before starting the actual experiment.
-(Check how many blocks as well).
+Participants were give 10 practice trials before starting the actual experiment which consisted of 288 trials.
 Participants were told they were to search for a target number (2-5 inclusive).
@@
 Same as the in the Adaptive Choice task, participants were not sat in a chin rest and so viewing distance was approximately.
-There were (get number of objects on display, I think it was 40?), half of which were the targets for that trial.
+There were 84 objects on screen, half of which were the targets for that trial.
 The squares and circles subtended between ~0.6&deg; and ~0.7&deg; depending on the screen resolution the participant was tested at (either 1600x1200 or 1400x1050, respectively).
 
-Before starting the experiment, participants had 10 (check this number) practice trials to familiarise themeselves with the task.
+Before starting the experiment, participants had 5 practice trials to familiarise themeselves with the task, after which they would begin the real task which cosisted of 20 trials.
 After completing the task with either the feature or conjunction search, participants would then repeat the task in the remaining condition.
@@
 num_removed <- num_fixations - nrow(fixDat)
+
+```
+
+```{r processing ACS data, echo = FALSE}
+# load data 
+load("scratch/dat_ACS")
+
+# filter out participants that were removed 
+dat_ACS <- dat_ACS %>%
+  filter(SubNo >= 5)
+
+# probably want to work out things like accuracy etc?
+# as in, exclude participants that are around chance level
+
+```
+
+```{r processing Foraging data, echo = FALSE}
+# load data 
+load("scratch/dat_for")
+
+# filter out participants that were removed 
+dat_for <- dat_for %>%
+  filter(sub_no >= 5)
 
@@
 ## Adaptive Choice
+```{r ACS plotting, echo = FALSE, message = FALSE, fig.align = "center"}
+# what sort of things do we care about....
+
+# RT by optimal choice
+plt <- dat_ACS %>%
+  na.omit() %>%
+  mutate(Optimal_Choice = as.factor(Optimal_Choice)) %>%
+  filter(Block_num > 0) %>%
+  mutate(se = sd(RT)/sqrt(n())) %>%
+  filter(RT > RT - 3*se,
+         RT < RT + 3*se,
+         RT > 300) %>%
+  ggplot(aes(RT/1000, fill = Optimal_Choice)) + 
+  geom_histogram() +
+  theme_bw() + 
+  theme(strip.text.x =  element_blank()) + 
+  coord_cartesian(expand = FALSE) + 
+  scale_fill_ptol() +
+  facet_wrap(~ Optimal_Choice) 
+plt$labels$x <- "Response Time (secs)"
+plt$labels$fill <- "Optimal Choice"
+plt
+
+# what about RT by number of optimal choices
+# only: - correct trials
+#       - RT > 300ms
+plt2 <- dat_ACS %>%
+  na.omit() %>%
+  filter(Block_num > 0) %>%
+  mutate(se = sd(RT)/sqrt(n())) %>%
+  filter(RT > RT - 3*se,
+         RT < RT + 3*se,
+         RT > 300) %>%
+  group_by(SubNo) %>%
+  summarise(mean_RT = mean(RT),
+            sum_optchoices = sum(Optimal_Choice)) %>%
+  ggplot(aes(sum_optchoices, mean_RT, label = SubNo)) + 
+  geom_point() + 
+  geom_text() + 
+  theme_bw()
+plt2
+
+# Get accuracy for each participant 
+# probably want to exclude participant 39 going by their accuracy 
+plt3 <- dat_ACS %>%
+  filter(Block_num > 0) %>%
+  mutate(se = sd(RT)/sqrt(n())) %>%
+  filter(RT > RT - 3*se,
+         RT < RT + 3*se,
+         RT > 300) %>%
+  group_by(SubNo) %>%
+  summarise(mean_acc = mean(Acc)) %>%
+  mutate(mean_acc_ov = mean(mean_acc)) %>%
+  ggplot(aes(SubNo, mean_acc)) + 
+  geom_point() + 
+  theme_bw()
+plt3
+
+```
 

### 2018-12-12 Manuscript/sup_mat/run_before_sup_mat.R

@@ -1,0 +1,120 @@
+#### To run before sup_mat ####
+# this will read in all the data and produce a file of the data to be used in 
+# the sup_mat for plotting etc...
+
+#### packages ####
+library(tidyverse)
+
+#### ACS ####
+#### ACS: read in data ####
+# set participants to look for
+participants <- 1:75
+participants <- participants[!(participants %in% c(18, 32, 48, 57, 11, 31, 69))] 
+
+# setup empty frame 
+dat_ACS <- data.frame(SubNo = numeric(),
+                      Trial = numeric(),
+                      Block_trial = numeric(),
+                      Block_num = numeric(),
+                      Plateau_cond = numeric(),
+                      Transition_cond = numeric(),
+                      Run_number = numeric(),
+                      Targ1_position = numeric(),
+                      Targ2_position = numeric(),
+                      FixationCheck = numeric(),
+                      Red_targ_digit = numeric(),
+                      Blue_targ_digit = numeric(),
+                      Response = numeric(),
+                      Targ_Choice = numeric(),
+                      Acc = numeric(),
+                      RT = numeric(),
+                      Optimal_Choice = numeric(),
+                      StarEndOptimal = numeric(),
+                      Repeat_Switch = numeric(),
+                      session = numeric())
+
+# loop to get data 
+for(pp in participants){
+  # get file name
+  temp <- dir(paste("../../Data/", pp, "/adaptchoice/", sep = ""))
+  
+  # setup temp frame
+  d <- read.csv(paste("../../Data/", pp, "/adaptchoice/",
+                      temp[1],
+                      sep = ""),
+                skip = 3, header = T, sep = "\t")
+  
+  # get session info
+  session <- strsplit(temp[1], '[_]')[[1]]
+  session <- substring(session[4],5,5)
+  
+  # add in session info
+  d$session <- session
+  
+  # add to dataset 
+  dat_ACS <- rbind(dat_ACS, d)
+}
+
+# tidy 
+rm(d, pp, session, temp)
+
+# sort participant labels 
+dat_ACS$SubNo[dat_ACS$SubNo == "56b"] <- "56"
+dat_ACS$SubNo <- as.numeric(dat_ACS$SubNo)
+
+#### Foraging ####
+#### Foraging: read in data ####
+# setup empty frame 
+dat_for <- data.frame(Trial = numeric(),
+                      Click_Num = numeric(),
+                      Target_Click_Order = numeric(),
[…]

### 2018-12-23 Manuscript/sup_mat/sup_mat.Rmd
Sup mat added details

@@
 avg_acc_all <- ls_acc_RT %>%
-  filter(observer != 15,
-         observer != 25,
-         observer != 47,
-         observer != 48) %>%
+  filter(!observer %in% c(15, 25, 47, 48)) %>%
   group_by(observer, targSide) %>%
@@
 incorrect_trials <- ls_acc_RT %>%
-  filter(observer != 15,
-         observer != 25,
-         observer != 47,
-         observer != 48,
+  filter(!observer %in% c(15, 25, 47, 48),
          responseKey != "Key_x") %>%
@@
 # as in, exclude participants that are around chance level
+
+# add in log2 RT 
+# there is a trial with RT 0 so make sure RT is greater than that too
+dat_ACS <- dat_ACS %>%
+  mutate(log2_RT = log2(RT)) %>%
+  filter(RT > 0)
 
@@
   filter(Block_num > 0) %>%
-  mutate(se = sd(RT)/sqrt(n())) %>%
-  filter(RT > RT - 3*se,
-         RT < RT + 3*se,
+  mutate(sdev = sd(RT)) %>%
+  filter(RT > RT - 3*sdev,
+         RT < RT + 3*sdev,
          RT > 300) %>%
-  ggplot(aes(RT/1000, fill = Optimal_Choice)) + 
+  ggplot(aes(RT, fill = Optimal_Choice)) + 
   geom_histogram() +
@@
   facet_wrap(~ Optimal_Choice) 
-plt$labels$x <- "Response Time (secs)"
+plt$labels$x <- "Response Time (msecs)"
 plt$labels$fill <- "Optimal Choice"
-plt
+
+plt1_5 <- dat_ACS %>%
+  na.omit() %>%
+  mutate(Optimal_Choice = as.factor(Optimal_Choice)) %>%
+  filter(Block_num > 0) %>%
+  mutate(sdev = sd(RT)) %>%
+  filter(RT > RT - 3*sdev,
+         RT < RT + 3*sdev,
+         RT > 300) %>%
+  ggplot(aes(log2_RT, fill = Optimal_Choice)) + 
+  geom_histogram() +
+  theme_bw() + 
+  theme(strip.text.x =  element_blank()) + 
+  coord_cartesian(expand = FALSE) + 
+  scale_fill_ptol() +
+  facet_wrap(~ Optimal_Choice) 
+plt1_5$labels$x <- "log2 transformed Response Time"
+plt1_5$labels$fill <- "Optimal Choice"
+
+# plot together 
+grid.arrange(plt,plt1_5)
 
@@
   filter(Block_num > 0) %>%
-  mutate(se = sd(RT)/sqrt(n())) %>%
-  filter(RT > RT - 3*se,
-         RT < RT + 3*se,
+  mutate(sdev = sd(RT)) %>%
+  filter(RT > RT - 3*sdev,
+         RT < RT + 3*sdev,
          RT > 300) %>%
@@
   theme_bw()
-plt2
+plt2$labels$X <- "No. of Optimal Choices"
+plt2$labels$y <- "Mean RT (msecs)"
+
+# same as above but using the log2_RT as criteria to exclude
+plt2_5 <- dat_ACS %>%
+  na.omit() %>%
+  filter(Block_num > 0) %>%
+  mutate(sdev = sd(log2_RT)) %>%
+  filter(log2_RT > log2(300),
+         log2_RT < log2_RT + 3 * sdev,
+         log2_RT > log2_RT - 3 * sdev) %>%
+  group_by(SubNo) %>%
+  summarise(mean_RT = mean(log2_RT),
+            sum_optchoices = sum(Optimal_Choice)) %>%
+  ggplot(aes(sum_optchoices, mean_RT, label = SubNo)) + 
+  geom_point() + 
+  geom_text() + 
+  theme_bw()
+plt2_5$labels$x <- "No. Optimal Choices"
+plt2_5$labels$y <- "Mean log2 RT"
+
+grid.arrange(plt2, plt2_5)
 
@@
 
+# RT and Acc, does this help at all?
+plt4 <- dat_ACS %>%
+  filter(Block_num > 0) %>%
+  mutate(sdev = sd(RT)) %>%
+  filter(RT > RT - 3*sdev,
+         RT < RT + 3*sdev,
+         RT > 300) %>%
+  group_by(SubNo) %>%
+  summarise(mean_RT = mean(RT), 
+            Accuracy = mean(Acc)) %>%
+  ggplot(aes(mean_RT, Accuracy, label = SubNo)) +
+  geom_point() + 
+  geom_text() + 
+  theme_bw()
+plt4
+
 ```
@@
 ## Foraging
+
+```{r plotting foraging, echo = FALSE, warnings = FALSE, message = FALSE, fig.align = "center"}
+# again, what sort of plots are we interester in?
+
+# mean RT by repetition rate? in each condition?
+plt <- dat_for %>%
+  na.omit() %>%
+  mutate(sub_no = as.numeric(as.factor(sub_no))) %>%
+  # filter(!sub_no %in% c(27,40:43)) %>% # missing data for these participants
+  group_by(sub_no, search_type, Trial) %>%
+  mutate(RT_max = max(RT)) %>%
+  group_by(sub_no, search_type) %>%
+  summarise(mean_RT = mean(RT_max),
+            mean_SW = mean(repetition)) %>%
+  ggplot(aes(mean_SW, mean_RT, colour = search_type)) + 
+  geom_point() +
+  # geom_line(aes(group = sub_no), alpha = 0.3, colour = "black") + # do we want it on one plot?
+  theme_bw() + 
+  scale_x_continuous(breaks = c(0.5)) +
+  scale_y_continuous(breaks = c(10, 30, 50)) + 
+  theme(legend.position = "bottom", strip.text.x = element_text(margin = margin(0.01,0,0.01,0, "mm"))) +
+  scale_colour_ptol() +
+  facet_wrap(~sub_no)
+plt$labels$y <- "Response Time (secs)"
+plt$labels$x <- "Average Repetition Rate"
+plt$labels$colour <- "Search Condition"
+plt
+
+```

### 2018-12-23 Manuscript/sup_mat/run_before_sup_mat.R

@@ -114,7 +114,40 @@ for(pp in participants){
 # tidy
 rm(d, search_info, idx, participants, pp, participant, search_type, Targets, temp)
 
+# need to calculate run length and switch rate 
+# setup columns to fill 
+dat_for$run_length <- 0
+dat_for$repetition <- 0 
+
+# start counter?
+run_length <- 0
+
+# anyone that knows a quicker way, please feel free to edit
+# start loop
+for(row in 1:nrow(dat_for)){
+  # store information 
+  if(dat_for[row, 2] == 1){
+    # if first click, store as na?
+    dat_for[row, 15] <- NA
+    run_length <- 0
+    dat_for[row, 14] <- NA
+  } else {
+    if(dat_for[row, 9] == dat_for[row-1, 9]){
+      run_length <- run_length + 1
+      dat_for[row, 14] <- run_length
+      dat_for[row, 15] <- 1
+    } else{
+      run_length <- 0
+      dat_for[row, 14] <- run_length
+      dat_for[row, 15] <- 0
+    }
+  }
+}
+
+# tidy 
+rm(row, run_length)
 
 # save these files 
 save(dat_ACS, file = "scratch/dat_ACS")
 save(dat_for, file = "scratch/dat_for")
+

### 2018-12-24 Manuscript/manuscript.tex
Fixed a couple of typos

@@
 However, a sub-set of observers, termed `super-foragers', were able to change between search target categories with no cost to performance.
-This study has been run on touch displays\cite{kristjansson2014} (observers are asked to tap on as many targets as they can as quickly as possible) and a 3D computer game (in which participants navigate a squirrel through a virtual environment picking up targets with different feature combinations)[IN PREP], with super-foragers present in both versions.
+This study has been run on touch displays\cite{kristjansson2014} (observers are asked to tap on as many targets as they can as quickly as possible) and a 3D computer game (in which participants navigate a squirrel through a virtual environment picking up targets with different feature combinations)\cite{prpic2018}, with super-foragers present in both versions.
 While test-retest reliability has not been measured explicitly for the foraging paradigm, the task was used as a measure to assess the effect of a six day long mindfulness retreat on cognitive performance\cite{hartkamp2017}.
@@
 64 students with normal or corrected-to-normal vision from the University of Aberdeen took part in this study\footnote{data from an additional 11 participants was discarded due to being recorded with an inappropriate screen resolution.
-Another participant was exluded due to colour blindness.}.
+Another participant was excluded due to colour blindness.}.
 Participants were compensated for their time with either  course credit or \pounds 15.
@@
 Vogel and Awh\cite{vogel2008} argued that studying individual differences in cognitive psychology (in their case, working memory) provides valuable insight to containing potential theories of the underlying cognitive mechanisms.
-Our results suggest that context and structure of the task also needs to be taking into account and we hope that studying how an individual's behaviour varies across different search tasks will lead to the development of a more comprehensive theory of search.
+Our results suggest that context and structure of the task also needs to be taken into account and we hope that studying how an individual's behaviour varies across different search tasks will lead to the development of a more comprehensive theory of search.
 

### 2019-01-07 Manuscript/sup_mat/sup_mat.Rmd
Updated sup_mat
Added to the methods descriptions so they're a bit more fleshed out.
Sorted labelling of figures... still need to get table labels working...
Made output PDF instead of HTML (and removed it)

@@
 output:
-  bookdown::html_document2:
+  pdf_document:
     toc: yes
@@
     fig_caption: yes
+fig_height: 4
+fig_width: 6
 ---
@@
 # Methods 
+The experiment took part over two sessions both lasting approximately 1 hour.
+All participants reported normal or corrected to normal vision and were from the University of Aberdeen.
+Participants were either compensated with course credit or £15 for their time.
+All participants gave informed consent.
+
+All tasks were completed on a 17-inch CRT monitor with a resolution of 1400$x$1050 (*n* = 40) or 1600$x$1200 (*n* = 24).
+All tasks were programmed in MATLAB using the psychophysics and eyelink toolboxes.
+
 ## Split-Half
@@
 Prior to every block, a 9-point calibration was carried out.
-This task lasted approximately 30 minutes.
+This task lasted approximately 30 minutes and was carried out in both sessions
 
+Participants were instructed to state the presence, or absence, of a small target line segment that was tilted 45&deg; to the right.
+The distractor line segments were arranged in such a way to create a "hard" and "easy" search side.
+All distractors were orthogonal to the target with either a low variance (18&deg;) which created a relatively homogenous texture ("easy" side), or a high amount of variance (95&deg;) creating a more heterogenous texture ("hard" side).
 The line segments subtended approximately 1.6&deg; of visual angle.
+For 50% of the trials, there was a target present.
+Particiapnts were told to establish whether the target was present or absent on each trial as quickly and as accuractely as possible.
 
-Any other details needed?
+In total, particiapnts completed 160 trials in each session with the hetero- and homogenous side randomly varying from trial to trial.
 
@@
 For this task, participants were sat approximately 47cm from the screen though no chin rest was used to ensure a constant viewing distance.
-Participants were give 10 practice trials before starting the actual experiment which consisted of 288 trials.
-Participants were told they were to search for a target number (2-5 inclusive).
-There would be two of these target numbers on every trial; one in a blue square and one in a red square.
-They were told they only needed to report one of these numbers.
-The squares subtended between ~1.1&deg; and ~1.3&deg; depending on the screen resolution the participant was tested at (either 1600x1200 or 1400x1050, respectively).
-Participants were instructed to be as fast and accuracte as possible.
-They were also told there would be a tone if they were to report a number that was not present within any of the boxes matching the two target colours.
+The search display consisted of small red, blue, and green squares arranged in three rings around a fixation point.
+the squares subtended between ~1.1&deg; and ~1.3&deg; depending on the screen resolution the participant was tested at (either 1600$x$1200 or 1400$x$1050, respectively).
+The participants' task was to find the blue or red square that contained the a number between 2 and 5 inclusive.
+On every trial there, both target colour squares contained a number between 2 and 5, but participants were told they only needed to report one of them.
+To ensure we could tell which colour they had decided, the blue and red target squares would always have a different number.
+The distractor blue and red squares would always contain a number between 6 and 9.
+The green squares contained numbers between 2 and 9.
+Again, they were instructed to complete the task as quickly and as accurately as possible.
+
+Before starting the task, participants weregiven 10 practice trials and were free to ask any questions before starting the main expriment.
+If a participant was to report a number that was not in one of the two target boxes, a tone would sound to alert them to their mistake.
+
+At the beginning of the experiment, there would be more red than blue squares (**need to check this is accuracte**) for five trials.
+Then, across the next seven trials, these would gradually change from red to blue, stay blue for five, and change etc.
+After completing the task, participants were then asked to fill out a short 3 item question asking them about their strategy and whether they noticed the gradual shift from one colour being the majority to the other.
 
 ## Foraging 
-Same as the in the Adaptive Choice task, participants were not sat in a chin rest and so viewing distance was approximately.
-There were 84 objects on screen, half of which were the targets for that trial.
-The squares and circles subtended between ~0.6&deg; and ~0.7&deg; depending on the screen resolution the participant was tested at (either 1600x1200 or 1400x1050, respectively).
+Same as the in the Adaptive Choice task, participants were not sat in a chin rest and so viewing distance was approximately 47cm.
+In this task, participants were presented with 84 small objects on the screen which subtended between ~0.6&deg; and ~0.7&deg; depending on the screen resolution the participant was tested at (either 1600$x$1200 or 1400$x$1050, respectively).
+Half of these were target items that participants were to click on until they had collected all of them.
+There were two types of search with this task.
+Either a feature search in which participants were presented with circles of 4 different colours (red, blue, yellow, and green) in which they were to click on all circles of two of the colours (e.g.
+click on the red and green, not the blue and yellow).
+The other being a conjunction search in which there were squares and circles coloured with two of the four possible colours, for example, they could be tasked with clicking on the blue squares and yellow circles, but try to avoid the blue circles and yellow squares.
+Participants completed both of these and the order was counterbalanced with the colours of the targets being randomised.
 
@@
 Accuracy data is shown in Figure \ref{fig:acc_plt}.
-From this we can see that there are a number of outliers: 15, 25, 47, and 48 (NB: these may have changed with new labelling).
+From this we can see that there are a number of outliers: 15, 25, 47, and 48.
 These participants, in at least one session, either missed the majority of easy targets, or responded with false positives on the majority of target absent trials.
@@
 ### Reaction Times 
-As expected, reaction times were highly skewed (Figure 2), so were log2 transformed (in ms units) before the participant means were calculated for each session and target condition (Figure )
+As expected, reaction times were highly skewed (Figure \ref{fig:rt_plt}), so were log2 transformed (in ms units) before the participant means were calculated for each session and target condition (Figure \ref{fig:rt_plt})
 
@@
 Initial fixations were not included in the analysis.
-Numbers of fixations are given in Table 2.
+Numbers of fixations are given in Table \ref{tab:table}.
 
-```{r make table, echo = FALSE, results='asis'}
+```{r make table, fig.cap = "\\label{tab:table} No. of fixations to each side in each condition.", echo = FALSE, results='asis'}
 # get fixation location
@@
 # make table 
-kable(table_dat, caption = "table thing")
+kable(table_dat)
 ```
@@
 # RT by optimal choice
-plt <- dat_ACS %>%
+plt1 <- dat_ACS %>%
   na.omit() %>%
@@
   facet_wrap(~ Optimal_Choice) 
-plt$labels$x <- "Response Time (msecs)"
-plt$labels$fill <- "Optimal Choice"
+plt1$labels$x <- "Response Time (msecs)"
+plt1$labels$fill <- "Optimal Choice"
 
@@
 # plot together 
-grid.arrange(plt,plt1_5)
+# grid.arrange(plt,plt1_5)
 
@@
   theme_bw()
-plt2$labels$X <- "No. of Optimal Choices"
+plt2$labels$x <- "No. of Optimal Choices"
 plt2$labels$y <- "Mean RT (msecs)"
@@
 
-grid.arrange(plt2, plt2_5)
+# grid.arrange(plt2, plt2_5)
 
@@
   theme_bw()
-plt3
+plt3$labels$x <- "Participant"
+plt3$labels$y <- "Mean Accuracy"
+# plt3
 
@@
   theme_bw()
-plt4
+# plt4
 
+```
+
+```{r ACS_rt, fig.cap = "\\label{fig:ACS_rt_plt} Distribution of reaction times in Adaptive Choice paradigm.", echo = FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
+grid.arrange(plt1, plt1_5)
+```
+
+```{r ACS_rt_optchoice, fig.cap = "\\label{fig:ACS_rt_opt_plt} Response Time (ms) by number of optimal choices", echo = FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
+plt2
+```
+
+```{r ACS_acc, fig.cap = "\\label{fig:ACS_acc} Mean Accuracy for each Participant", echo = FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
+plt3
 ```
@@
 
-```{r plotting foraging, echo = FALSE, warnings = FALSE, message = FALSE, fig.align = "center"}
+```{r plotting foraging, fig.cap = "\\label{fig:For_switch_rt} Switch Rate and Response Times (seconds) for each participant accross conditions", echo = FALSE, warnings = FALSE, message = FALSE, fig.align = "center"}
 # again, what sort of plots are we interester in?

### 2019-01-15 sup_mat/sup_mat.Rmd
Tidied
Should be a bit clearer where the supplementary material is now

--- 2019-01-07 Manuscript/sup_mat/sup_mat.Rmd
@@
 # RT by optimal choice
-plt1 <- dat_ACS %>%
+plt_ACS_rt_opt <- dat_ACS %>%
   na.omit() %>%
@@
   facet_wrap(~ Optimal_Choice) 
-plt1$labels$x <- "Response Time (msecs)"
-plt1$labels$fill <- "Optimal Choice"
+plt_ACS_rt_opt$labels$x <- "Response Time (msecs)"
+plt_ACS_rt_opt$labels$fill <- "Optimal Choice"
 
-plt1_5 <- dat_ACS %>%
+plt_ACS_logrt_opt <- dat_ACS %>%
   na.omit() %>%
@@
   facet_wrap(~ Optimal_Choice) 
-plt1_5$labels$x <- "log2 transformed Response Time"
-plt1_5$labels$fill <- "Optimal Choice"
+plt_ACS_logrt_opt$labels$x <- "log2 transformed Response Time"
+plt_ACS_logrt_opt$labels$fill <- "Optimal Choice"
 
@@
 #       - RT > 300ms
-plt2 <- dat_ACS %>%
+plt_ACS_meanrt_opt <- dat_ACS %>%
   na.omit() %>%
@@
   theme_bw()
-plt2$labels$x <- "No. of Optimal Choices"
-plt2$labels$y <- "Mean RT (msecs)"
+plt_ACS_meanrt_opt$labels$x <- "No. of Optimal Choices"
+plt_ACS_meanrt_opt$labels$y <- "Mean RT (msecs)"
 
@@
 # probably want to exclude participant 39 going by their accuracy 
-plt3 <- dat_ACS %>%
+plt_ACS_mean_acc <- dat_ACS %>%
   filter(Block_num > 0) %>%
@@
   theme_bw()
-plt3$labels$x <- "Participant"
-plt3$labels$y <- "Mean Accuracy"
+plt_ACS_mean_acc$labels$x <- "Participant"
+plt_ACS_mean_acc$labels$y <- "Mean Accuracy"
 # plt3
@@
 ```{r ACS_rt, fig.cap = "\\label{fig:ACS_rt_plt} Distribution of reaction times in Adaptive Choice paradigm.", echo = FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
-grid.arrange(plt1, plt1_5)
+grid.arrange(plt_ACS_rt_opt, plt_ACS_logrt_opt)
 ```
@@
 ```{r ACS_rt_optchoice, fig.cap = "\\label{fig:ACS_rt_opt_plt} Response Time (ms) by number of optimal choices", echo = FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
-plt2
+plt_ACS_meanrt_opt
 ```
@@
 ```{r ACS_acc, fig.cap = "\\label{fig:ACS_acc} Mean Accuracy for each Participant", echo = FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
-plt3
+plt_ACS_mean_acc
 ```
@@
 # mean RT by repetition rate? in each condition?
-plt <- dat_for %>%
+plt_for_sr_rt <- dat_for %>%
   na.omit() %>%
@@
   facet_wrap(~sub_no)
-plt$labels$y <- "Response Time (secs)"
-plt$labels$x <- "Average Repetition Rate"
-plt$labels$colour <- "Search Condition"
-plt
+plt_for_sr_rt$labels$y <- "Response Time (secs)"
+plt_for_sr_rt$labels$x <- "Average Repetition Rate"
+plt_for_sr_rt$labels$colour <- "Search Condition"
+plt_for_sr_rt
 

### 2019-01-17 sup_mat/sup_mat.Rmd
some text edits

@@
 # Methods 
-The experiment took part over two sessions both lasting approximately 1 hour.
+The experiment took part over two sessions, each lasting approximately 1 hour.
 All participants reported normal or corrected to normal vision and were from the University of Aberdeen.
@@
 All tasks were completed on a 17-inch CRT monitor with a resolution of 1400$x$1050 (*n* = 40) or 1600$x$1200 (*n* = 24).
-All tasks were programmed in MATLAB using the psychophysics and eyelink toolboxes.
+All tasks were programmed in MATLAB (which version?) using psychtoolbox and eyelinktoolbox.
 
 ## Split-Half
-In this task, a chin rest with forehead bar was used in order to ensure a viewing distance of 47cm.
-Participants' fixations were tracked using a deskmounted Eylink 1000 (version 4.594) to record eye position at 1000 Hz.
+This task lasted approximately 30 minutes and was carried out in both sessions.
+A chin rest with forehead bar ensured a viewing distance of 47cm.
+Participants' fixations were tracked using a deskmounted Eylink 1000 to record eye position at 1000 Hz.
 Prior to every block, a 9-point calibration was carried out.
-This task lasted approximately 30 minutes and was carried out in both sessions
-
 Participants were instructed to state the presence, or absence, of a small target line segment that was tilted 45&deg; to the right.
-The distractor line segments were arranged in such a way to create a "hard" and "easy" search side.
-All distractors were orthogonal to the target with either a low variance (18&deg;) which created a relatively homogenous texture ("easy" side), or a high amount of variance (95&deg;) creating a more heterogenous texture ("hard" side).
-The line segments subtended approximately 1.6&deg; of visual angle.
+The distractor line segments (how many, i.e.
+how many rows/columns?) were arranged in such a way to create a "hard" and "easy" search side.
+The mean orientation of the distractors was orthogonal to the target orientation, with either a low variance (18&deg;) which created a relatively homogenous texture ("easy" side), or a high amount of variance (95&deg;) creating a more heterogeneous texture ("hard" side).
+Each line segment subtended approximately 1.6&deg; of visual angle.
 For 50% of the trials, there was a target present.
-Particiapnts were told to establish whether the target was present or absent on each trial as quickly and as accuractely as possible.
+Participants were told to report (how?) whether the target was present or absent on each trial as quickly and as accuractely as possible.
 
@@
 ## Adaptive Choice
-For this task, participants were sat approximately 47cm from the screen though no chin rest was used to ensure a constant viewing distance.
-The search display consisted of small red, blue, and green squares arranged in three rings around a fixation point.
+For this task, participants viewed the display from approximately 47cm away, but no chin rest was used to ensure a constant viewing distance.
+The search display consisted of small red, blue, and green squares arranged in three rings around a fixation point (how many of each colour?).
 the squares subtended between ~1.1&deg; and ~1.3&deg; depending on the screen resolution the participant was tested at (either 1600$x$1200 or 1400$x$1050, respectively).
-The participants' task was to find the blue or red square that contained the a number between 2 and 5 inclusive.
-On every trial there, both target colour squares contained a number between 2 and 5, but participants were told they only needed to report one of them.
-To ensure we could tell which colour they had decided, the blue and red target squares would always have a different number.
-The distractor blue and red squares would always contain a number between 6 and 9.
+The participants' task was to find either a blue or a red square that contained a number between 2 and 5 inclusive.
+On every trial, just one blue and one red square contained a number between 2 and 5.
+Participants were instructed to find and report one of them.
+To ensure we could tell which colour they had decided, the blue and red target squares would always have a different number inside.
+The distractor blue and red squares would always contain numbers between 6 and 9.
 The green squares contained numbers between 2 and 9.
-Again, they were instructed to complete the task as quickly and as accurately as possible.
+Participants were instructed to complete the task as quickly and as accurately as possible.
 
-Before starting the task, participants weregiven 10 practice trials and were free to ask any questions before starting the main expriment.
-If a participant was to report a number that was not in one of the two target boxes, a tone would sound to alert them to their mistake.
+Before starting the task, participants were given 10 practice trials and were free to ask any questions before starting the main expriment.
+If a participant reported a number that was not in one of the two target boxes, a tone would sound to alert them to their mistake.
+(How many trials in the experiment?)
 
 At the beginning of the experiment, there would be more red than blue squares (**need to check this is accuracte**) for five trials.
-Then, across the next seven trials, these would gradually change from red to blue, stay blue for five, and change etc.
-After completing the task, participants were then asked to fill out a short 3 item question asking them about their strategy and whether they noticed the gradual shift from one colour being the majority to the other.
+Then, across the next seven trials, the red squares would gradually change from red to blue, stay blue for five trials, and then change from blue to red across seven trials, stay red for five trials, and so on.
+The number of green squares was constant.
+After completing the task, participants were then asked to fill out a short three-item questionnaire asking them about their strategy and whether they noticed the gradual shift from one colour being the majority to the other.
 
 ## Foraging 
-Same as the in the Adaptive Choice task, participants were not sat in a chin rest and so viewing distance was approximately 47cm.
-In this task, participants were presented with 84 small objects on the screen which subtended between ~0.6&deg; and ~0.7&deg; depending on the screen resolution the participant was tested at (either 1600$x$1200 or 1400$x$1050, respectively).
-Half of these were target items that participants were to click on until they had collected all of them.
+Viewing distance was approximately 47cm (no chin rest was used).
+At the beginning of each trial, participants were presented with 84 small shapes on the screen which subtended between ~0.6&deg; and ~0.7&deg; depending on the screen resolution the participant was tested at (either 1600$x$1200 or 1400$x$1050, respectively).
+Half of these were target items that participants were to click on, using the mouse cursor, until they had "collected" all of them (they disappeared when clicked).
 There were two types of search with this task.
-Either a feature search in which participants were presented with circles of 4 different colours (red, blue, yellow, and green) in which they were to click on all circles of two of the colours (e.g.
+In feature search, participants were presented with circles of 4 different colours (red, blue, yellow, and green) and were instructed to click on all circles of two of the colours (e.g.
 click on the red and green, not the blue and yellow).
-The other being a conjunction search in which there were squares and circles coloured with two of the four possible colours, for example, they could be tasked with clicking on the blue squares and yellow circles, but try to avoid the blue circles and yellow squares.
-Participants completed both of these and the order was counterbalanced with the colours of the targets being randomised.
+In conjunction search, there were squares and circles coloured with two of the four possible colours, for example, they could be instructed to collect the blue squares and yellow circles, but to avoid the blue circles and yellow squares.
+In both conditions, if participants clicked on a non-target shape the trial immediately ended and re-started with 84 shapes in a new set of locations.
+Participants completed both of these conditions and the order was counterbalanced with the colours of the targets being randomised across participants.
 
-Before starting the experiment, participants had 5 practice trials to familiarise themeselves with the task, after which they would begin the real task which cosisted of 20 trials.
+Before starting the experiment, participants had 5 practice trials to familiarise themeselves with the task, after which they would begin 20 experimental trials.
 After completing the task with either the feature or conjunction search, participants would then repeat the task in the remaining condition.
@@
 `r num_fixations` fixations were recorded.
-Of these, `r num_removed` fell outside of the stimuli area and were removed.
+Of these, `r num_removed` fell outside of the stimulus area and were removed.
 Fixations landing within a vertical strip consisting of 10% of the stimuli's width were classed as central.

### 2019-01-22 sup_mat/sup_mat.Rmd
Added exclusion criteria
Added in accuracy exclusion criteria for ACS task

--- 2019-01-15 sup_mat/sup_mat.Rmd
@@
 # get line seg acc and rt 
-ls_acc_RT <- readRDS(file = "../../Scripts/lineseg/scratch/processedRTandAccData.Rda")
+ls_acc_RT <- readRDS(file = "../Scripts/lineseg/scratch/processedRTandAccData.Rda")
 
@@
 # load in unprocessed data 
-load("../../Scripts/lineseg/scratch/unfiltered_fixDat")
-load("../../Scripts/lineseg/scratch/unfiltered_trlDat")
+load("../Scripts/lineseg/scratch/unfiltered_fixDat")
+load("../Scripts/lineseg/scratch/unfiltered_trlDat")
 trlDat_unf <- trlDat
@@
 # get removed fixations data 
-load("../../Scripts/lineseg/scratch/processedFixationData")
+load("../Scripts/lineseg/scratch/processedFixationData")
 # get difference value 
@@
          RT > 300) %>%
+  ungroup() %>%
+  mutate(mean_acc_ov = mean(Acc)) %>%
   group_by(SubNo) %>%
-  summarise(mean_acc = mean(Acc)) %>%
-  mutate(mean_acc_ov = mean(mean_acc)) %>%
+  summarise(mean_acc = mean(Acc),
+            mean_acc_ov = mean(mean_acc_ov)) %>%
+  mutate(sd_acc = sd(mean_acc)) %>%
+  filter(mean_acc > mean_acc_ov - 3*sd_acc) %>%
   ggplot(aes(SubNo, mean_acc)) + 

### 2019-01-28 sup_mat/sup_mat.Rmd
fixed some of the plots
Made plots clearer with more developed captions

@@
 
-```{r ACS_rt, fig.cap = "\\label{fig:ACS_rt_plt} Distribution of reaction times in Adaptive Choice paradigm.", echo = FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
+```{r ACS_rt, fig.cap = "\\label{fig:ACS_rt_plt} Distribution of reaction times in Adaptive Choice paradigm.
+Optimal choice corresponds to reporting the number that was in the box with the minority colour group.", echo = FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
 grid.arrange(plt_ACS_rt_opt, plt_ACS_logrt_opt)
@@
 
-```{r ACS_rt_optchoice, fig.cap = "\\label{fig:ACS_rt_opt_plt} Response Time (ms) by number of optimal choices", echo = FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
+```{r ACS_rt_optchoice, fig.cap = "\\label{fig:ACS_rt_opt_plt} Response Time (ms) by number of optimal choices in the Adaptive Choice Task", echo = FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
 plt_ACS_meanrt_opt
@@
 
-```{r ACS_acc, fig.cap = "\\label{fig:ACS_acc} Mean Accuracy for each Participant", echo = FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
+```{r ACS_acc, fig.cap = "\\label{fig:ACS_acc} Mean Accuracy for each Participant in the Adaptive Choice Task", echo = FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
 plt_ACS_mean_acc
@@
 
-```{r plotting foraging, fig.cap = "\\label{fig:For_switch_rt} Switch Rate and Response Times (seconds) for each participant accross conditions", echo = FALSE, warnings = FALSE, message = FALSE, fig.align = "center"}
+```{r plotting foraging, fig.cap = "\\label{fig:For_switch_rt} Average repetition rate (i.e.
+when the curret clicked on target is the same as the previously clicked target) and Response Times (seconds) for each participant accross conditions in the Foraging task", echo = FALSE, warnings = FALSE, message = FALSE, fig.align = "center"}
 # again, what sort of plots are we interester in?
@@
   na.omit() %>%
-  mutate(sub_no = as.numeric(as.factor(sub_no))) %>%
+  mutate(sub_no = as.numeric(as.factor(sub_no)))
+
+plt_for_sr_rt$Search_cond <- "Feature"
+plt_for_sr_rt$Search_cond[plt_for_sr_rt$search_type == 2] <- "Conjunctive"
+
+plt_for_sr_rt <- plt_for_sr_rt %>%
   # filter(!sub_no %in% c(27,40:43)) %>% # missing data for these participants
-  group_by(sub_no, search_type, Trial) %>%
+  group_by(sub_no, Search_cond, Trial) %>%
   mutate(RT_max = max(RT)) %>%
-  group_by(sub_no, search_type) %>%
+  group_by(sub_no, Search_cond) %>%
   summarise(mean_RT = mean(RT_max),
             mean_SW = mean(repetition)) %>%
-  ggplot(aes(mean_SW, mean_RT, colour = search_type)) + 
+  ggplot(aes(mean_SW, mean_RT, colour = Search_cond)) + 
   geom_point() +
@@
   scale_y_continuous(breaks = c(10, 30, 50)) + 
-  theme(legend.position = "bottom", strip.text.x = element_text(margin = margin(0.01,0,0.01,0, "mm"))) +
+  theme(legend.position = "bottom",
+        strip.text.x = element_text(margin = margin(0.01,0,0.01,0, "mm"))) +
   scale_colour_ptol() +

### 2019-01-28 sup_mat/sup_mat.Rmd
More changes to sup_mat
Answered some of the questions in the sup_mat

@@
 
+```{r processing ACS data, echo = FALSE}
+# load data 
+load("scratch/dat_ACS")
+
+# filter out participants that were removed 
+dat_ACS <- dat_ACS %>%
+  filter(SubNo >= 5)
+
+# probably want to work out things like accuracy etc?
+# as in, exclude participants that are around chance level
+
+# add in log2 RT 
+# there is a trial with RT 0 so make sure RT is greater than that too
+dat_ACS <- dat_ACS %>%
+  mutate(log2_RT = log2(RT)) %>%
+  filter(RT > 0)
+
+```
+
+```{r processing Foraging data, echo = FALSE}
+# load data 
+load("scratch/dat_for")
+
+# filter out participants that were removed 
+dat_for <- dat_for %>%
+  filter(sub_no >= 5)
+
+```
 # Methods 
@@
 
-All tasks were completed on a 17-inch CRT monitor with a resolution of 1400$x$1050 (*n* = 40) or 1600$x$1200 (*n* = 24).
-All tasks were programmed in MATLAB (which version?) using psychtoolbox and eyelinktoolbox.
+All tasks were completed on a 17-inch CRT monitor with a resolution of 1400x1050 (*n* = 40) or 1600x1200 (*n* = 24).
+All tasks were programmed in MATLAB R2009b (version 7.9.0.529) using psychtoolbox and eyelinktoolbox.
 
@@
 Participants were instructed to state the presence, or absence, of a small target line segment that was tilted 45&deg; to the right.
-The distractor line segments (how many, i.e.
-how many rows/columns?) were arranged in such a way to create a "hard" and "easy" search side.
+The distractor line segments were arranged in such a way to create a "hard" and "easy" search side.
+`r 16*22` line segemets were arranged in 16 rows and 22 columns, with the easy and hard search sides being split vertically.
 The mean orientation of the distractors was orthogonal to the target orientation, with either a low variance (18&deg;) which created a relatively homogenous texture ("easy" side), or a high amount of variance (95&deg;) creating a more heterogeneous texture ("hard" side).
@@
 For 50% of the trials, there was a target present.
-Participants were told to report (how?) whether the target was present or absent on each trial as quickly and as accuractely as possible.
+Participants were told to report whether the target was present or absent on each trial as quickly and as accuractely as possible by pressing either the left or right arrow key respectively.
 
@@
 For this task, participants viewed the display from approximately 47cm away, but no chin rest was used to ensure a constant viewing distance.
-The search display consisted of small red, blue, and green squares arranged in three rings around a fixation point (how many of each colour?).
-the squares subtended between ~1.1&deg; and ~1.3&deg; depending on the screen resolution the participant was tested at (either 1600$x$1200 or 1400$x$1050, respectively).
+The search display consisted of 54 small red, blue, and green squares arranged in three rings around a fixation point (how many of each colour?).
+the squares subtended between ~1.1&deg; and ~1.3&deg; depending on the screen resolution the participant was tested at (either 1600x1200 or 1400x1050, respectively).
 The participants' task was to find either a blue or a red square that contained a number between 2 and 5 inclusive.
@@
 If a participant reported a number that was not in one of the two target boxes, a tone would sound to alert them to their mistake.
-(How many trials in the experiment?)
+After the practice trials, they would then complete `r max(dat_ACS$Trial)` trials split into 4 equal length blocks (`r max(dat_ACS$Block_trial)` trials per block).
 
-At the beginning of the experiment, there would be more red than blue squares (**need to check this is accuracte**) for five trials.
+At the beginning of the experiment, there would be more red than blue squares for five trials.
 Then, across the next seven trials, the red squares would gradually change from red to blue, stay blue for five trials, and then change from blue to red across seven trials, stay red for five trials, and so on.
@@
 
-```{r processing ACS data, echo = FALSE}
-# load data 
-load("scratch/dat_ACS")
-
-# filter out participants that were removed 
-dat_ACS <- dat_ACS %>%
-  filter(SubNo >= 5)
-
-# probably want to work out things like accuracy etc?
-# as in, exclude participants that are around chance level
-
-# add in log2 RT 
-# there is a trial with RT 0 so make sure RT is greater than that too
-dat_ACS <- dat_ACS %>%
-  mutate(log2_RT = log2(RT)) %>%
-  filter(RT > 0)
-
-```
-
-```{r processing Foraging data, echo = FALSE}
-# load data 
-load("scratch/dat_for")
-
-# filter out participants that were removed 
-dat_for <- dat_for %>%
-  filter(sub_no >= 5)
-
-```
 Data was collected from 64 Participants as originally planned.
@@
 
+excluded <- dat_ACS %>%
+  filter(Block_num > 0) %>%
+  ungroup() %>%
+  mutate(mean_acc_ov = mean(Acc)) %>%
+  group_by(SubNo) %>%
+  summarise(mean_acc = mean(Acc),
+            mean_acc_ov = mean(mean_acc_ov)) %>%
+  mutate(sd_acc = sd(mean_acc)) %>%
+  filter(mean_acc < mean_acc_ov - 3*sd_acc)
+excluded <- unique(excluded$SubNo)
+
+# average accuracy
+avg_1 <- mean(dat_ACS$Acc)
+
 ```
+A participant was excluded if their accuracy in the task was more than 3 standard deviations below the average for all participants.
+Participants `r paste(excluded[1], "&", excluded[2])` were excluded for having an accuracy that was 3 standard deviations below the global average of `r round(avg_1, digits = 2)`.
 

### 2019-01-30 sup_mat/sup_mat.Rmd
added some details to AC

@@
 For this task, participants viewed the display from approximately 47cm away, but no chin rest was used to ensure a constant viewing distance.
-The search display consisted of 54 small red, blue, and green squares arranged in three rings around a fixation point (how many of each colour?).
-the squares subtended between ~1.1&deg; and ~1.3&deg; depending on the screen resolution the participant was tested at (either 1600x1200 or 1400x1050, respectively).
+The search display consisted of two target squares (one red and one blue), and 52 distractor squares: 12 red, 12 blue, 14 green, and 14 squares of variable colour, arranged in three rings around a fixation point.
+The squares subtended between ~1.1&deg; and ~1.3&deg; depending on the screen resolution the participant was tested at (either 1600x1200 or 1400x1050, respectively).
 The participants' task was to find either a blue or a red square that contained a number between 2 and 5 inclusive.
@@
 
-## Split-Half
+## Participant exclusions in the Split-Half task
 Accuracy data is shown in Figure \ref{fig:acc_plt}.
-From this we can see that there are a number of outliers: 15, 25, 47, and 48.
+From this we can see that there are a number of participants who did not perform the task to a reasonable standard: 15, 25, 47, and 48.
 These participants, in at least one session, either missed the majority of easy targets, or responded with false positives on the majority of target absent trials.
@@
 # Data Processing
+
+The
 

### 2019-01-30 sup_mat/sup_mat.Rmd
Made changes to sup_mat
Removed uneeded plots and reorganised

@@
     toc: yes
-    toc_depth: 2
+    toc_depth: 4
     fig_caption: yes
@@
 
-# Participants
-
+# Data Processing
+## Participant Exclusions
 ```{r Participants, echo = FALSE}
@@
 ```
+
+Data was collected from 64 Participants as originally planned.
+Four of these participants did not complete all parts of the experiment (either declining to participate in the second session, or could not be calibrated with the eye tracker), so four new participants were recruited to bring the total back up to `r num_participants`.
 
@@
 
-Data was collected from 64 Participants as originally planned.
-Four of these participants did not complete all parts of the experiment (either declining to participate in the second session, or could not be calibrated with the eye tracker), so four new participants were recruited to bring the total back up to `r num_participants`.
-
-## Participant exclusions in the Split-Half task
-Accuracy data is shown in Figure \ref{fig:acc_plt}.
+### Split-Half task
+Accuracy data is shown in Figure \ref{fig:ls_acc_plt}.
 From this we can see that there are a number of participants who did not perform the task to a reasonable standard: 15, 25, 47, and 48.
@@
 
-```{r acc_plt, fig.cap = "\\label{fig:acc_plt} Accuracy data for each participant for the split-half paradigm. ", echo = FALSE, fig.align = "center"}
+```{r ls_acc_plt, fig.cap = "\\label{fig:ls_acc_plt} Accuracy data for each participant for the split-half paradigm. ", echo = FALSE, fig.align = "center"}
 # make the plot
@@
 
-```{r rt_plt, fig.cap = "\\label{fig:rt_plt} Distribution of reaction times in split-half paradigm.", echo = FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
-plt <- ls_acc_RT %>%
-  ggplot(aes(rt)) + 
-  geom_histogram() + 
-  theme_bw() +  
-  facet_wrap(~targSide)
-plt$labels$x <- "Response Time (msecs)"
-plt2 <- ls_acc_RT %>%
-  mutate(log2_RT = log2(rt)) %>%
-  ggplot(aes(log2_RT)) + 
-  geom_histogram() + 
-  theme_bw() +
-  facet_wrap(~ targSide)
-plt2$labels$x <- "log2 Response Time"
-
-# put together 
-grid.arrange(plt,plt2)
-```
-
-# Data Processing
-
-The
-
-## Split-Half 
-`r invalid_kp` trials with invalid key responses were removed.
-After removing data from the four outlier participants (see above), all remaining incorrect trials (n = `r incorrect_trials$n[incorrect_trials$accuracy == 0]`) were removed, leaving a total of `r incorrect_trials$n[incorrect_trials$accuracy == 1]` trials over 60 participants.
-
-### Reaction Times 
-As expected, reaction times were highly skewed (Figure \ref{fig:rt_plt}), so were log2 transformed (in ms units) before the participant means were calculated for each session and target condition (Figure \ref{fig:rt_plt})
-
-### Eye Movements
-`r num_fixations` fixations were recorded.
-Of these, `r num_removed` fell outside of the stimulus area and were removed.
-Fixations landing within a vertical strip consisting of 10% of the stimuli's width were classed as central.
-All remaining fixations were then classed as landing on the homogeneous or heterogeneous half of the stimulus.
-Initial fixations were not included in the analysis.
-Numbers of fixations are given in Table \ref{tab:table}.
-
-```{r make table, fig.cap = "\\label{tab:table} No. of fixations to each side in each condition.", echo = FALSE, results='asis'}
-# get fixation location
-fixDat <- fixDat %>%
-  mutate(fix_loc = "central")
-fixDat$fix_loc[fixDat$x < -0.1 & fixDat$easySide == "left"] <- "homogenous"
-fixDat$fix_loc[fixDat$x > 0.1 & fixDat$easySide == "right"] <- "homogenous"
-fixDat$fix_loc[fixDat$x < -0.1 & fixDat$easySide == "right"] <- "heterogenous"
-fixDat$fix_loc[fixDat$x > 0.1 & fixDat$easySide == "left"] <- "heterogenous"
-
-# get num fixations in these locations 
-table_dat_all <- fixDat %>%
-  group_by(targSide, fix_loc) %>%
-  filter(n < 6) %>%
-  summarise(number = n()) %>%
-  mutate(range = "1 < n")
-
-table_dat_2_to_5 <- fixDat %>%
-  group_by(targSide, fix_loc) %>%
-  filter(n >= 2,
-         n <= 5) %>%
-  summarise(number = n()) %>%
-  mutate(range = "2 <= n <= 5")
-
-table_dat <- rbind(table_dat_all, table_dat_2_to_5) %>%
-  spread(range, number)
-
-# make table 
-kable(table_dat)
-```
-
-## Adaptive Choice
+### Adaptive Choice
 ```{r ACS plotting, echo = FALSE, message = FALSE, fig.align = "center"}
@@
 A participant was excluded if their accuracy in the task was more than 3 standard deviations below the average for all participants.
-Participants `r paste(excluded[1], "&", excluded[2])` were excluded for having an accuracy that was 3 standard deviations below the global average of `r round(avg_1, digits = 2)`.
+As can be seen in Figure \ref{fig:ACS_acc}, participants `r paste(excluded[1], "&", excluded[2])` were excluded for having an accuracy that was 3 standard deviations below the global average of `r round(avg_1, digits = 2)`.
 
@@
 Optimal choice corresponds to reporting the number that was in the box with the minority colour group.", echo = FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
-grid.arrange(plt_ACS_rt_opt, plt_ACS_logrt_opt)
+# grid.arrange(plt_ACS_rt_opt, plt_ACS_logrt_opt)
 ```
@@
 ```{r ACS_rt_optchoice, fig.cap = "\\label{fig:ACS_rt_opt_plt} Response Time (ms) by number of optimal choices in the Adaptive Choice Task", echo = FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
-plt_ACS_meanrt_opt
+# plt_ACS_meanrt_opt
 ```
@@
 ```
-
-## Foraging
+### Foraging
+No participants were exlucded from the analysis of these data. However, participants 27, 40, 41, 42, and 43 were missing their data from the Feature search condition (Figure \ref{fig:For_switch_rt})
 
@@
 ```
+
+## Data Processing
+### Response Times 
+Response Times in the Adaptive Choice and Split-Half tasks were normalised by applying a log2 transformation to the data as can be seen in Figure \ref{fig:ACS_SH_rt}.
+Also, response times that were 3 standard deviations from the mean were discarded.
+
+```{r ACS_SH_rt, fig.cap = "\\label{fig:ACS_SH_rt} Log2 transformed Response time distributions for the Split-Half (top) and Adaptive Choice (bottom) tasks.
+The plot for the Adaptive Choice task is split between RTs for optimal choices (i.e.
+picking the colour in the minority as indicated by a 1) and the suboptimal choice", echo = F, warnings = F, message = F, fig.align = "centre"}
+# make rt plots 
+# do SH first 
+plt_sh_rt <- ls_acc_RT %>%
+  mutate(log2rt = log2(rt)) %>%
+  ggplot(aes(log2rt)) + 
+  geom_histogram() + 
+  theme_bw() + 
+  facet_wrap(~targSide)
+plt_sh_rt$labels$x <- "Log2 Response Time (msecs)"
+
+plt_acs_logrt <- dat_ACS %>%
+  na.omit() %>%
+  mutate(Optimal_Choice = as.factor(Optimal_Choice),
+         sdev = sd(log2_RT),
+         mean_rt = mean(log2_RT)) %>%
+  filter(log2_RT > mean_rt - 3*sdev,
+         log2_RT < mean_rt + 3*sdev,
+         log2_RT > log2(300)) %>%  
+  ggplot(aes(log2_RT,
+             colour = Optimal_Choice,
+             fill = Optimal_Choice)) + 
+  geom_histogram() +
+  theme_bw() + 
+  theme(legend.position = "bottom",
+        strip.text.x = element_blank()) + 
+  scale_colour_ptol() + 
+  scale_fill_ptol() + 
+  facet_wrap(~Optimal_Choice)
+plt_acs_logrt$labels$x <- "Log2 Response Time (msecs)"
+
+grid.arrange(plt_sh_rt, plt_acs_logrt, ncol = 1)
+
+```
+### Split-Half
+
+#### Invalid responses
+`r invalid_kp` trials with invalid key responses were removed.
+After removing data from the four outlier participants (see above), all remaining incorrect trials (n = `r incorrect_trials$n[incorrect_trials$accuracy == 0]`) were removed, leaving a total of `r incorrect_trials$n[incorrect_trials$accuracy == 1]` trials over 60 participants.
+
+```{r, echo = F, include = F}
+#Reaction Times 
+#As expected, reaction times were highly skewed (Figure \ref{fig:ls_rt_plt}), so were log2 transformed (in ms units) before the participant means were calculated for each session and target condition (Figure \ref{fig:ls_rt_plt})
+```
+#### Eye Movements
+`r num_fixations` fixations were recorded.
+Of these, `r num_removed` fell outside of the stimulus area and were removed.
+Fixations landing within a vertical strip consisting of 10% of the stimuli's width were classed as central.
+All remaining fixations were then classed as landing on the homogeneous or heterogeneous half of the stimulus.
+Initial fixations were not included in the analysis.
+Numbers of fixations are given in Table \ref{tab:table}.
+
+```{r make table, fig.cap = "\\label{tab:table} No. of fixations to each side in each condition.", echo = FALSE, results='asis'}
+# get fixation location
+fixDat <- fixDat %>%
+  mutate(fix_loc = "central")
+fixDat$fix_loc[fixDat$x < -0.1 & fixDat$easySide == "left"] <- "homogenous"
+fixDat$fix_loc[fixDat$x > 0.1 & fixDat$easySide == "right"] <- "homogenous"
+fixDat$fix_loc[fixDat$x < -0.1 & fixDat$easySide == "right"] <- "heterogenous"
+fixDat$fix_loc[fixDat$x > 0.1 & fixDat$easySide == "left"] <- "heterogenous"
+
+# get num fixations in these locations 
+table_dat_all <- fixDat %>%
+  group_by(targSide, fix_loc) %>%
+  filter(n < 6) %>%
+  summarise(number = n()) %>%
+  mutate(range = "1 < n")
+
+table_dat_2_to_5 <- fixDat %>%
+  group_by(targSide, fix_loc) %>%
+  filter(n >= 2,
+         n <= 5) %>%
+  summarise(number = n()) %>%
+  mutate(range = "2 <= n <= 5")
+
+table_dat <- rbind(table_dat_all, table_dat_2_to_5) %>%
+  spread(range, number)
+
+# make table 
+kable(table_dat, caption = "\\label{tab:table} No. of fixations to each side in each condition.")
+```

### 2019-01-30 sup_mat/sup_mat.Rmd
a few changes to text and Fig 4

@@
 
-In total, particiapnts completed 160 trials in each session with the hetero- and homogenous side randomly varying from trial to trial.
+In total, particiapnts completed 160 trials in each session, with the hetero- and homogenous side randomly varying from trial to trial.
 
@@
 Participants were instructed to find and report one of them.
-To ensure we could tell which colour they had decided, the blue and red target squares would always have a different number inside.
+To ensure we could tell which colour they found, the blue and red target squares would always have a different number inside.
 The distractor blue and red squares would always contain numbers between 6 and 9.
@@
 
-Before starting the task, participants were given 10 practice trials and were free to ask any questions before starting the main expriment.
+Before starting the task, participants were given 10 practice trials and were free to ask any questions before starting the main experiment.
 If a participant reported a number that was not in one of the two target boxes, a tone would sound to alert them to their mistake.
@@
 In both conditions, if participants clicked on a non-target shape the trial immediately ended and re-started with 84 shapes in a new set of locations.
-Participants completed both of these conditions and the order was counterbalanced with the colours of the targets being randomised across participants.
+Participants completed both of these conditions.
+Condition order was counterbalanced, and the colours of the targets was randomised across participants.
 
-Before starting the experiment, participants had 5 practice trials to familiarise themeselves with the task, after which they would begin 20 experimental trials.
-After completing the task with either the feature or conjunction search, participants would then repeat the task in the remaining condition.
+Before starting the experiment, participants completed five practice trials to familiarise themeselves with the task, after which they completed 20 experimental trials in each condition.
 This took approximately 20 minutes.
@@
 
-Data was collected from 64 Participants as originally planned.
+Data were collected from 64 participants as originally planned.
 Four of these participants did not complete all parts of the experiment (either declining to participate in the second session, or could not be calibrated with the eye tracker), so four new participants were recruited to bring the total back up to `r num_participants`.
@@
   mutate(sd_acc = sd(mean_acc)) %>%
-  filter(mean_acc > mean_acc_ov - 3*sd_acc) %>%
+  # filter(mean_acc > mean_acc_ov - 3*sd_acc) %>%
   ggplot(aes(SubNo, mean_acc)) + 
@@
 ```
-A participant was excluded if their accuracy in the task was more than 3 standard deviations below the average for all participants.
+We excluded any participant with accuracy more than 3 standard deviations below the average for all participants.
 As can be seen in Figure \ref{fig:ACS_acc}, participants `r paste(excluded[1], "&", excluded[2])` were excluded for having an accuracy that was 3 standard deviations below the global average of `r round(avg_1, digits = 2)`.
@@
 ### Foraging
-No participants were exlucded from the analysis of these data. However, participants 27, 40, 41, 42, and 43 were missing their data from the Feature search condition (Figure \ref{fig:For_switch_rt})
+No participants were excluded for poor performance on the foraging task.
+However, participant 27 and participants 40 to 43 were missing their data from the feature search condition (Figure \ref{fig:For_switch_rt}).
+We had not planned to use the results from the feature search condition in the correlation calculations, so these participants were not excluded.
 
@@
 ### Response Times 
-Response Times in the Adaptive Choice and Split-Half tasks were normalised by applying a log2 transformation to the data as can be seen in Figure \ref{fig:ACS_SH_rt}.
-Also, response times that were 3 standard deviations from the mean were discarded.
+Response Times in the Adaptive Choice and Split-Half tasks were skewed, as can be seen in Figure \ref{fig:ACS_SH_rt}.
+We therefore normalised the data by applying a log2 transformation.
+Response times that were 3 standard deviations from the mean were discarded.
 

### 2019-01-30 sup_mat/sup_mat.Rmd
made changes to plots
RT plots show raw RT instead of log2(RT)

@@
     fig_caption: yes
-fig_height: 4
+fig_height: 2
 fig_width: 6
@@
 
-```{r ls_acc_plt, fig.cap = "\\label{fig:ls_acc_plt} Accuracy data for each participant for the split-half paradigm. ", echo = FALSE, fig.align = "center"}
+```{r ls_acc_plt, fig.cap = "\\label{fig:ls_acc_plt} Accuracy data for each participant for the split-half paradigm. ", echo = FALSE, fig.align = "center", fig.asp = 0.6}
 # make the plot
@@
 
-```{r ACS_acc, fig.cap = "\\label{fig:ACS_acc} Mean Accuracy for each Participant in the Adaptive Choice Task", echo = FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
+```{r ACS_acc, fig.cap = "\\label{fig:ACS_acc} Mean Accuracy for each Participant in the Adaptive Choice Task", echo = FALSE, warning = FALSE, message = FALSE, fig.align = "center", fig.asp = 0.6}
 plt_ACS_mean_acc
@@
 ```{r plotting foraging, fig.cap = "\\label{fig:For_switch_rt} Average repetition rate (i.e.
-when the curret clicked on target is the same as the previously clicked target) and Response Times (seconds) for each participant accross conditions in the Foraging task", echo = FALSE, warnings = FALSE, message = FALSE, fig.align = "center"}
+when the curret clicked on target is the same as the previously clicked target) and Response Times (seconds) for each participant accross conditions in the Foraging task", echo = FALSE, warnings = FALSE, message = FALSE, fig.align = "center", fig.asp = 0.6}
 # again, what sort of plots are we interester in?
@@
   theme(legend.position = "bottom",
-        strip.text.x = element_text(margin = margin(0.01,0,0.01,0, "mm"))) +
+        strip.text.x = element_text(margin = margin(0.008,0,0.008,0, "mm"))) +
   scale_colour_ptol() +
@@
 
-```{r ACS_SH_rt, fig.cap = "\\label{fig:ACS_SH_rt} Log2 transformed Response time distributions for the Split-Half (top) and Adaptive Choice (bottom) tasks.
+```{r ACS_SH_rt, fig.cap = "\\label{fig:ACS_SH_rt} Response time distributions for the Split-Half (top) and Adaptive Choice (bottom) tasks.
 The plot for the Adaptive Choice task is split between RTs for optimal choices (i.e.
-picking the colour in the minority as indicated by a 1) and the suboptimal choice", echo = F, warnings = F, message = F, fig.align = "centre"}
+picking the colour in the minority as indicated by a 1) and the suboptimal choice", echo = F, warnings = F, message = F, fig.align = "centre", fig.asp = 0.6}
 # make rt plots 
@@
 plt_sh_rt <- ls_acc_RT %>%
-  mutate(log2rt = log2(rt)) %>%
-  ggplot(aes(log2rt)) + 
+  ggplot(aes(rt)) + 
   geom_histogram() + 
@@
   facet_wrap(~targSide)
-plt_sh_rt$labels$x <- "Log2 Response Time (msecs)"
+plt_sh_rt$labels$x <- "Response Time (msecs)"
 
@@
   mutate(Optimal_Choice = as.factor(Optimal_Choice),
-         sdev = sd(log2_RT),
-         mean_rt = mean(log2_RT)) %>%
-  filter(log2_RT > mean_rt - 3*sdev,
-         log2_RT < mean_rt + 3*sdev,
-         log2_RT > log2(300)) %>%  
-  ggplot(aes(log2_RT,
+         sdev = sd(RT),
+         mean_rt = mean(RT)) %>%
+  filter(RT > mean_rt - 3*sdev,
+         RT < mean_rt + 3*sdev,
+         RT > 300) %>%  
+  ggplot(aes(RT,
              colour = Optimal_Choice,
@@
   facet_wrap(~Optimal_Choice)
-plt_acs_logrt$labels$x <- "Log2 Response Time (msecs)"
+plt_acs_logrt$labels$x <- "Response Time (msecs)"
 

### 2019-02-14 Manuscript/manuscript.tex
Super minor edits

@@
 The results showed that participants varied substantially along two key dimensions: how frequently they used the more effective target colour to search (varying from chance performance to near optimal), and how often they changed between colours.
-Further work\cite{irons-leber2018} has shown that these differences are stable over time (between one and ten days) with test-retest correlations of around $r = 0.83$ ($95\%$ confidence interval $= [0.72, 0.90]$).
+Further work\cite{irons-leber2018} has shown that these differences are stable over time (between one and ten days) with test-retest correlations of around $r = 0.83$ ($95\%$ confidence interval $= [0.72, 0.90]$) for optimal choices.
 
@@
 Clicking on a target caused it to disappear from the display.
-If the participant clicked erroneously on a non-target, the trial immediately ended and a replacement trial begun.
+If the participant clicked erroneously on a non-target, the trial immediately ended and a replacement trial began.
 In the conjunction foraging task, search displays were composed of both circles and squares.

### 2019-02-14 Scripts/lineseg/9_planning_a_follow_up_ignore.R

@@ -1,0 +1,19 @@
+library(tidyverse)
+
+ 
+fix_dat <- readRDS(file="scratch/processedFixationData.Rda")
+trl_dat <- readRDS(file="scratch/processedRTandAccData.Rda")
+
+
+# remove people with poor target easy/absent accuracy
+fix_dat <- filter(fix_dat, !(observer %in% c(4, 21, 33, 56, 58)))
+trl_dat <- filter(trl_dat, !(observer %in% c(4, 21, 33, 56, 58)))
+
+# remove fixations falling outside of simulus
+fix_dat <- filter(fix_dat, is.finite(x), is.finite(y))
+
+# classify every fixation as homo (left), central, or hetro (right)
+centralWidth <- 0.1 # used to be 64 pixels! #change to 1 visual degree
+fix_dat$side <- 'central'
+fix_dat$side[which(fix_dat$x <(0-centralWidth/2))] <- "homo"
+fix_dat$side[which(fix_dat$x >(0+centralWidth/2))] <- "hetero"

### 2019-02-14 Manuscript/manuscript.tex
Reformatted to APA and shortened a little
Into + Discussion must be <= 2000
Abstract <= 150

@@
 \RequirePackage{fix-cm}
-\documentclass[twocolumn]{article}
+\documentclass[a4paper, jou, natbib]{apa6}
 
@@
 \usepackage{subfigure}
-\usepackage{lineno}
-\usepackage{hyperref}
+% \usepackage{lineno}
+% \usepackage{hyperref}
 \usepackage{graphicx}
-\usepackage{authblk}
 
@@
 \title{Stable individual differences in strategies within, but not between, visual search tasks}
+\shorttitle{Differences in search}
+\fiveauthors{A. D. F. Clarke}{J. L. Irons}{W. James}{A. B. Leber}{A. R. Hunt}
 
-\author[1, *]{A. D. F. Clarke}
-\author[2]{J. L. Irons} 
-\author[3]{W. James}
-\author[2]{A. B. Leber}
-\author[3]{A. R. Hunt}
-
-\affil[1]{Department of Psychology, University of Essex, Colchester, UK}
-\affil[2]{Department of Psychology, The Ohio State University, Columbus, USA}
-\affil[3]{School of Psychology, University of Aberdeen, Aberdeen, UK}
-\affil[*]{Corresponding author: a.clarke@essex.ac.uk}
-\renewcommand\Affilfont{\itshape\small}
+\fiveaffiliations{Department of Psychology, University of Essex, Colchester, UK}{Department of Psychology, The Ohio State University, Columbus, USA}{School of Psychology, University of Aberdeen, Aberdeen, UK}{Department of Psychology, The Ohio State University, Columbus, USA}{School of Psychology, University of Aberdeen, Aberdeen, UK}
+% {Corresponding author: a.clarke@essex.ac.uk}
+% \renewcommand\Affilfont{\itshape\small}
 
@@
 
-\begin{document}
-\maketitle
-
-\begin{abstract}
+\abstract{
 A striking range of individual differences has recently been reported in three different visual search tasks.
@@
 Here we ask if an individual's strategy and performance in one search task is correlated with how they perform in the other two.
-We tested 64 observers in the three tasks mentioned above over two sessions.
-Even though the test-retest reliability of the tasks is high, an observer's performance and strategy in one task did not reliably predict their behaviour in the other two.
+We tested 64 observers and found that even though the test-retest reliability of the tasks was high, an observer's performance and strategy in one task was not predictive of their behaviour in the other two.
 These results suggest search strategies are stable over time, but context-specific.
-To understand visual search we therefore need to account not only for differences between individuals, but also how individuals interact with the search task and context.
-These context-specific but stable individual differences in strategy can account for a substantial proportion of variability in search performance.
-\end{abstract}
+To understand visual search we therefore need to account not only for differences between individuals, but also how individuals interact with the search task and context.}
+
+\begin{document}
+\maketitle
 
@@
 As is common in cognitive psychology, most visual search literature has focused on how the average participant performs in the task, despite it being well known that there is a great deal of variability between one subject and the next.
-From Treisman's work on Feature Integration Theory\cite{treisman1980} to the latest incarnation of the Guided Search Model\cite{wolfe2015}, we now have a good understanding of what makes some search targets effortless to find, while others require careful inspection.
+From Treisman's work on Feature Integration Theory \citep{treisman1980} to the latest incarnation of the Guided Search Model \citep{wolfe2015}, we have a good understanding of what makes some search targets effortless to find, while others require careful inspection.
 However, these theories and models have neglected the question of why some observers find visual search so much harder than others.
-These differences can emerge from several different sources of variation: tiredness\cite{mackworth1948}, information-processing ability, speed-accuracy trade-off, motivation, visual impairments\cite{nowakowska2016}, and search strategies\cite{boot2006}.
-Although their existence has previously been noted\cite{mackworth1948}, a rigorous examination of individual differences in visual search is a challenge that has not been taken up by many researchers, and questions about their importance and stability remain relatively under explored.
+These differences can emerge from several different sources of variation: tiredness \citep{mackworth1948}, information-processing ability, speed-accuracy trade-off, motivation, visual impairments \citep{nowakowska2016}, and search strategies \citep{boot2006}.
+Although their existence has previously been noted \citep{mackworth1948}, a rigorous examination of individual differences in visual search is a challenge that has not been taken up by many researchers, and questions about their importance and stability remain relatively under explored.
 
 In the current study, we focus on one source of individual differences in visual search: strategy.
-By search strategies, we refer to a collection of behaviours that all observers can freely choose from when they search a display.
-Examples include choosing to adopt a systematic left-to-right and top-to-bottom strategy\cite{gilchrist2006}, or the type of guided search behaviour in which locations that are more likely to contain the target are prioritised\cite{wolfe2015}.
+Here we refer to a collection of behaviours that all observers can freely choose from when they search a display.
+Examples include choosing to adopt a systematic left-to-right and top-to-bottom strategy \citep{gilchrist2006}, or the type of guided search behaviour in which locations that are more likely to contain the target are prioritised \citep{wolfe2015}.
 
-A striking example of the effect of strategy is given by Boot and colleagues\cite{boot2006}.
+A striking example of the effect of strategy is given by \cite{boot2006}.
 They asked participants to monitor a cluttered display for an object changing colour or suddenly appearing.
-Large individual differences were found with respect to the number of saccades participants made while monitoring the stimulus, and the number of saccades was negatively correlated with detection performance.
-Proulx\cite{proulx2011} demonstrated that participants differed in how they prioritised visual features (colour or orientation) when searching through a set of objects for one with a particular colour-orientation combination.
+Large individual differences were found with respect to the number of saccades participants made while monitoring the stimulus, which was negatively correlated with detection performance.
+Proulx \citeyearpar{proulx2011} demonstrated that participants differed in how they prioritised visual features (colour or orientation) when searching through a set of objects for one with a particular colour-orientation combination.
 These differences in search strategy explained some of the variation in the extent to which participants were distracted by an irrelevant object of a unique size.
@@
 Eye movement strategies have also been shown to be an important source of individual differences in visual search efficiency.
-Nowakowska, Clarke \& Hunt\cite{nowakowska2017} designed a simple search paradigm to discriminate between optimal\cite{najemnik-geisler2008} and stochastic \cite{clarke2016} search strategies.
-The task involved searching through arrays of line segments arranged such that those on one side of the display all had a very similar orientation (homogeneous), while those on the other side had higher variance (heterogeneous).
-See Figure \ref{fig:exampleStimuli} for an example.
-This meant that targets appearing on the homogeneous side would be highly salient, and targets on the heterogeneous side  would be much harder to find.
-With these stimuli, the optimal eye movement strategy is to only search the heterogeneous half , as targets on the homogeneous side can be detected with peripheral vision.
+\cite{nowakowska2017} designed a simple search paradigm to discriminate between optimal \citep{najemnik-geisler2008} and stochastic  \citep{clarke2016} search strategies.
+The task involved searching through arrays of line segments (Figure \ref{fig:exampleStimuli}) arranged such that those on one side of the display all had a very similar orientation (homogeneous), while those on the other side had higher variance (heterogeneous).
+This meant that targets appearing on the homogeneous side would be highly salient, while targets on the heterogeneous side  would be harder to find.
+With these stimuli, the optimal eye movement strategy is to search the heterogeneous half, as targets on the homogeneous side can be detected with peripheral vision.
 We will refer to this paradigm here as the Split-Half Line Segment task (SHLS).
@@
 Furthermore, the degree to which they made saccades in line with the optimal search strategy was strongly correlated with their reaction times.
-A related version of this paradigm has been used in research investigating eye movement strategies in response to (simulated) hemianopia\cite{nowakowska2016,nowakowska2018}, with similar conclusions: the full spectrum of individual differences in strategy was observed, from near-optimal to the opposite of optimal.
+A related version of this paradigm has been used in research investigating eye movement strategies in response to (simulated) hemianopia \citep{nowakowska2016,nowakowska2018}, with similar conclusions: the full spectrum of individual differences in strategy was observed, from near-optimal to the opposite of optimal.
 It is therefore not possible to conclude whether optimal or stochastic models better describe search without first explaining individual variability.
 
-A similar range of strategies, from random to near-optimal, has been found by Irons \& Leber with the Adaptive Choice Visual Search (ACVS) paradigm\cite{irons-leber2016}, designed to explore how feature-based attention is used.
-This paradigm involves stimuli made up of small coloured boxes (red, blue, green and a fourth colour that varies from red, through purple, to blue and back again) with numerals written inside them (See Figure \ref{fig:exampleStimuli}).
+A similar range of strategies, from random to near-optimal, has been found by \cite{irons-leber2016} with the Adaptive Choice Visual Search (ACVS) paradigm.
+This paradigm involves stimuli made up of small coloured boxes (red, blue, green and a fourth colour that varies from red, through purple, to blue and back again) with numerals written inside them (Figure \ref{fig:exampleStimuli}).
 The target is a defined as a red or blue box containing one of four numerals (e.g., 2-5), and on each trial one target of each colour is present.
@@
 The results showed that participants varied substantially along two key dimensions: how frequently they used the more effective target colour to search (varying from chance performance to near optimal), and how often they changed between colours.
-Further work\cite{irons-leber2018} has shown that these differences are stable over time (between one and ten days) with test-retest correlations of around $r = 0.83$ ($95\%$ confidence interval $= [0.72, 0.90]$) for optimal choices.
+Further work \citep{irons-leber2018} has shown that these differences are stable over time (between one and ten days) with test-retest correlations of around $r = 0.83$ ($95\%$ CI $= [0.72, 0.90]$) for optimal choices.
 
@@
 
-Another example of differences in search strategy comes from the foraging literature \cite{kristjansson2014,johannesson2016}.
+Another example of differences in search strategy comes from the foraging literature  \citep{kristjansson2014,johannesson2016}.
 In this context, foraging is a visual search task in which there are multiple targets on each trial.
@@
 In the conjunction condition (searching for red-horizontal and green-vertical line segments among red-vertical and green-horizontal distracters), most observers searched in runs, finding all the targets of one target category, and then switching and finding the targets in the other category.
-This strategy has previously been observed in animal foraging \cite{dawkins1971}, and suggests holding one complex target template in mind at a time is a better strategy than switching templates.
+This strategy has previously been observed in animal foraging  \citep{dawkins1971}, and suggests holding one complex target template in mind at a time is a better strategy than switching templates.
 However, a sub-set of observers, termed `super-foragers', were able to change between search target categories with no cost to performance.
-This study has been run on touch displays\cite{kristjansson2014} (observers are asked to tap on as many targets as they can as quickly as possible) and a 3D computer game (in which participants navigate a squirrel through a virtual environment picking up targets with different feature combinations)\cite{prpic2018}, with super-foragers present in both versions.
-While test-retest reliability has not been measured explicitly for the foraging paradigm, the task was used as a measure to assess the effect of a six day long mindfulness retreat on cognitive performance\cite{hartkamp2017}.
+This study has been run on touch displays \citep{kristjansson2014} (observers are asked to tap on as many targets as they can as quickly as possible) and a 3D computer game (in which participants navigate a squirrel through a virtual environment picking up targets with different feature combinations) \citep{prpic2018}, with super-foragers present in both versions.
+While test-retest reliability has not been measured explicitly for the foraging paradigm, the task was used as a measure to assess the effect of a six day long mindfulness retreat on cognitive performance \citep{hartkamp2017}.
 From a re-analysis of these data, we can estimate that the test-retest reliability for the mean run length is $r \approx 0.7$ for the feature condition and $r \approx 0.88$ for the conjunction search.
@@
 Previous research has investigated the relationship between these behaviours to psychometric measures, but to date, these differences have not shown strong correlations with other attributes.
-In the ACVS paradigm, Irons \& Leber found no evidence of a correlation between the proportion of optimal choices made by observers and measures of visual working memory; trait impulsivity\cite{irons-leber2016}; novelty seeking; need for cognition; and intolerance of uncertainty\cite{irons-leber2018}.
-Similarly, the differences in foraging behaviour are not accounted for by working memory or inhibitory control\cite{johannesson2017}.
+In the ACVS paradigm, Irons \& Leber found no evidence of a correlation between the proportion of optimal choices made by observers and measures of visual working memory; trait impulsivity \citep{irons-leber2016}; novelty seeking; need for cognition; and intolerance of uncertainty \citep{irons-leber2018}.
+Similarly, the differences in foraging behaviour are not accounted for by working memory or inhibitory control \citep{johannesson2017}.
 
@@
 Are observers who use the optimal strategy in the SHLS paradigm also more optimal in the ACVS task?
-Does it make sense to talk about `super-searchers' who show above average performance in a range of search tasks (analogous to the 'super-recognizers' of the face-recognition literature \cite{russell2009})?
-Are the super-foragers consistently better or worse than more typical searchers in the other two paradigms?
+Does it make sense to talk about `super-searchers' who show above average performance in a range of search tasks (analogous to the 'super-recognizers' of the face-recognition literature  \citep{russell2009})?
 As a secondary question, we will measure the test-retest reliability of the differences found in the SHLS paradigm, and compare it with existing estimates of reliability for ACVS and MCFT.
@@
 
-The study consists of three paradigms from the visual search literature in which large individual differences have been  found\cite{nowakowska2017, irons-leber2016, kristjansson2014}.
+The study consists of three paradigms from the visual search literature in which large individual differences have been  found \citep{nowakowska2017, irons-leber2016, kristjansson2014}.
 Example stimuli can be seen in Figure \ref{fig:exampleStimuli}.
@@
 The display was presented on a 17-inch CRT monitor with a resolution of $1400 \times 1050$ ($n = 40$) or $1600 \times 1200$ ($n = 24$).
-Stimulus generation, presentation and data collection were controlled by MATLAB and the psychophysics and eyelink toolboxes \cite{brainard1997,cornelissen2002} run on a Powermac.
+Stimulus generation, presentation and data collection were controlled by MATLAB and the psychophysics and eyelink toolboxes  \citep{brainard1997,cornelissen2002} run on a Powermac.
 Participants sat $\approx 47$cm from the screen.
@@
 
-Our results are consistent with the original SHLS study\cite{nowakowska2017}: we find a large range of individual differences in search reaction time and accuracy (see Figure \ref{fig:splithalf_summary}).
-Furthermore, these differences are stable across the two sessions, with Pearson's $r \in [0.71, 0.89]$ ($95\%$ confidence interval) for accuracy in finding hard targets.
+Our results are consistent with the original SHLS study \citep{nowakowska2017}: we find a large range of individual differences in search reaction time and accuracy (see Figure \ref{fig:splithalf_summary}).
+Furthermore, these differences are stable across the two sessions, with Pearson's $r \in [0.71, 0.89]$ ($95\%$ CI.) for accuracy in finding hard targets.
 We get similar scores for the correlation in reaction times between sessions \textit{a} and \textit{b} for hard targets, ($r \in [0.54-0.81]$), easy targets ($r \in [0.52-0.80]$) and target absent trials ($r \in [0.66-0.86]$).
@@
 Again, we see large and stable individual differences across the two sessions (test-retest $r \in [0.63, 0.86]$ for the proportion of the first five saccades to the heterogeneous half of the display for target absent trials).
-More importantly, as with \cite{nowakowska2017}, we see that the search strategies give a good correlation with reaction times in both session a, $r \in [0.52, 0.82]$ and session b, $r \in [0.50, 0.80]$.
+More importantly, as with  \citep{nowakowska2017}, we see that the search strategies give a good correlation with reaction times in both session a, $r \in [0.52, 0.82]$ and session b, $r \in [0.50, 0.80]$.
 
@@
 We measured an individual's strategy as the percent of plateau trials in which the individual chose the optimal target (i.e., the target with the fewest distractors: When the variable distractor was red, the optimal choice was blue, and vice versa).
-The results for the ACVS were consistent with previous findings \cite{irons-leber2016,irons-leber2018}.
+The results for the ACVS were consistent with previous findings  \citep{irons-leber2016,irons-leber2018}.
 We can clearly see from figure \ref{fig:acvs_mcft_summary}(a) that there are individual differences in the proportion of optimal targets reported (range $33.62\%$ - $100.00\%$, $\bar{x} = 59.15$, $s = 16.54$) and the mean ($\log_2$) reaction times (range $1.90$ - $4.80$ seconds).
@@
 The average run length was the mean number of target selections in a run.
-The multiple-target foraging results were in line with previous findings \cite{kristjansson2014,johannesson2016}, with shorter run lengths for feature foraging ($\bar{x} = 3.16$, $s = 3.14$) than conjunction foraging ($\bar{x} = 11.73$, $s = 7.09$).
+The multiple-target foraging results were in line with previous findings  \citep{kristjansson2014,johannesson2016}, with shorter run lengths for feature foraging ($\bar{x} = 3.16$, $s = 3.14$) than conjunction foraging ($\bar{x} = 11.73$, $s = 7.09$).
 This suggests more frequent foraging for multiple targets concurrently when those targets were defined by features than by conjunctions.
@@
 We successfully replicated the wide range of individual differences in strategy and performance that had previously been observed in each of these three visual search paradigms, with a larger sample size than the original experiments.
-Surprisingly, however, the between-paradigm correlations give $R^2 = 0.04$, and this is a generous interpretation that would fail to pass the usual criteria for null hypothesis significance testing.
-Knowing how one person will behave in one of these paradigms apparently tells us very little about how they will perform in the others.
-This can be contrasted with the relatively high test-retest correlations of all three of the tasks individually, which range from a lower bound of 0.58 to an upper bound of 0.92 .
+Surprisingly, however, the between-paradigm correlations give $R^2 \approx 0.04$, and this is a generous interpretation that would fail to pass the usual criteria for null hypothesis significance testing.
+Knowing how one person will behave in one of these paradigms tells us very little about how they will perform in the others.
+This can be contrasted with the relatively high test-retest correlations of all three of the tasks individually, which range from  0.58 to 0.92.
 
@@
 In the MCFT task, success involved minimizing cognitive load by minimizing target switching.
-Each of these tasks clearly taps into unique aspects of visual search strategies, and performance on one of these aspects has no bearing on any of the others.
+Each of these tasks clearly taps into unique aspects of visual search strategies, and performance on one  has little bearing on the others.
 
@@
 Our understanding of the underlying mechanisms of visual search is based predominantly on experiments that systematically vary details of the search task and measure their effects on performance.
-This approach has led to many important insights, for example, about the kinds of visual features that can be used to guide attention (e.g.
-\cite{treisman1980, wolfe2007}; how attentional control settings filter out distractors (e.g.
-\cite{folk1992,yantis1999}); and  biases in attention, such as a bias towards unexplored locations (e.g.
-\cite{klein2000}).
+This approach has led to important insights, for example, about the kinds of visual features that can be used to guide attention (e.g.
+\citep{treisman1980, wolfe2007}; how attentional control settings filter out distractors (e.g.
+\citep{folk1992,yantis1999}); and  biases in attention, such as a bias towards unexplored locations (e.g.
+\citep{klein2000}).
 These insights are based on search performance averaged over some number of individual participants.
 For all three of the experiments included in the current study, however, the average performance would be highly misleading, as it would describe very few of the individuals who completed the tasks.
-In the original SHLS study \cite{nowakowska2017}, for example, the original aim of the experiment was to assess whether search behaviour could be better described by an optimal \cite{najemnik-geisler2008}, versus a stochastic \cite{clarke2016}, model.
+In the original SHLS study  \citep{nowakowska2017}, for example, the original aim of the experiment was to assess whether search behaviour could be better described by an optimal  \citep{najemnik-geisler2008}, versus a stochastic  \citep{clarke2016}, model.
 Considering only the average search performance, the stochastic model was a good explanation.
@@
 We view these findings, not as a disappointing null result, but as thought-provoking and exciting.
-Vogel and Awh\cite{vogel2008} argued that studying individual differences in cognitive psychology (in their case, working memory) provides valuable insight to containing potential theories of the underlying cognitive mechanisms.
+Vogel and Awh \citep{vogel2008} argued that studying individual differences in cognitive psychology (in their case, working memory) provides valuable insight to containing potential theories of the underlying cognitive mechanisms.
 Our results suggest that context and structure of the task also needs to be taken into account and we hope that studying how an individual's behaviour varies across different search tasks will lead to the development of a more comprehensive theory of search.
@@
 
-\bibliographystyle{plain}
 \bibliography{literature}

### 2019-02-14 Manuscript/manuscript.tex
shortened to try and meet length restrictions

@@
 As is common in cognitive psychology, most visual search literature has focused on how the average participant performs in the task, despite it being well known that there is a great deal of variability between one subject and the next.
-From Treisman's work on Feature Integration Theory \citep{treisman1980} to the latest incarnation of the Guided Search Model \citep{wolfe2015}, we have a good understanding of what makes some search targets effortless to find, while others require careful inspection.
+From Treisman's work on Feature Integration Theory \citep{treisman1980} to the latest incarnation of the Guided Search Model \citep{wolfe2015}, we have a good understanding of what makes particular objects easier or harder to find.
 However, these theories and models have neglected the question of why some observers find visual search so much harder than others.
 These differences can emerge from several different sources of variation: tiredness \citep{mackworth1948}, information-processing ability, speed-accuracy trade-off, motivation, visual impairments \citep{nowakowska2016}, and search strategies \citep{boot2006}.
-Although their existence has previously been noted \citep{mackworth1948}, a rigorous examination of individual differences in visual search is a challenge that has not been taken up by many researchers, and questions about their importance and stability remain relatively under explored.
+Although their existence has previously been noted \citep{mackworth1948}, a rigorous examination of individual differences in visual search is a challenge that has not been taken up by many researchers, and questions about their impact and stability remain relatively under-explored.
 
-In the current study, we focus on one source of individual differences in visual search: strategy.
-Here we refer to a collection of behaviours that all observers can freely choose from when they search a display.
-Examples include choosing to adopt a systematic left-to-right and top-to-bottom strategy \citep{gilchrist2006}, or the type of guided search behaviour in which locations that are more likely to contain the target are prioritised \citep{wolfe2015}.
-
+Here we focus on one source of individual differences in visual search: strategy.
+By strategy we mean a collection of search behaviours from which all observers can freely choose.
+Examples include adopting a systematic left-to-right and top-to-bottom strategy \citep{gilchrist2006}, or prioritizing locations that, based on knowledge or context, are more likely to contain the target \citep{wolfe2015}.
 A striking example of the effect of strategy is given by \cite{boot2006}.
@@
 Large individual differences were found with respect to the number of saccades participants made while monitoring the stimulus, which was negatively correlated with detection performance.
-Proulx \citeyearpar{proulx2011} demonstrated that participants differed in how they prioritised visual features (colour or orientation) when searching through a set of objects for one with a particular colour-orientation combination.
+In another example, Proulx \citeyearpar{proulx2011} demonstrated that participants differed in how they prioritised visual features (colour or orientation) when searching through a set of objects for one with a particular colour-orientation combination.
 These differences in search strategy explained some of the variation in the extent to which participants were distracted by an irrelevant object of a unique size.
-However, participants were largely unaware of the search strategy they employed, and the majority were unable, or unwilling, to comply with instructions to employ a particular strategy.
+However, participants were largely unaware of the search strategy they employed.
 
@@
 \cite{nowakowska2017} designed a simple search paradigm to discriminate between optimal \citep{najemnik-geisler2008} and stochastic  \citep{clarke2016} search strategies.
-The task involved searching through arrays of line segments (Figure \ref{fig:exampleStimuli}) arranged such that those on one side of the display all had a very similar orientation (homogeneous), while those on the other side had higher variance (heterogeneous).
-This meant that targets appearing on the homogeneous side would be highly salient, while targets on the heterogeneous side  would be harder to find.
-With these stimuli, the optimal eye movement strategy is to search the heterogeneous half, as targets on the homogeneous side can be detected with peripheral vision.
+Participants searched through arrays of line segments (Figure \ref{fig:exampleStimuli}) arranged such that those on one side of the display all had a very similar orientation (homogeneous), while those on the other side had higher variance (heterogeneous).
+This meant that targets appearing on the homogeneous side were highly salient, while targets on the heterogeneous side were harder to find.
+The optimal eye movement strategy here is to search only the heterogeneous half, as targets on the homogeneous side can be detected with peripheral vision.
 We will refer to this paradigm here as the Split-Half Line Segment task (SHLS).
-While some participants initially searched the displays near optimally, others carried out strategies counter to this, failing to even match the performance of the stochastic searcher.
-Furthermore, the degree to which they made saccades in line with the optimal search strategy was strongly correlated with their reaction times.
+Some participants searched the displays near optimally, but others carried out strategies counter to this, failing to even match the performance of the stochastic searcher.
+The degree to which participants made saccades in line with the optimal search strategy was strongly correlated with the speed of their search.
 A related version of this paradigm has been used in research investigating eye movement strategies in response to (simulated) hemianopia \citep{nowakowska2016,nowakowska2018}, with similar conclusions: the full spectrum of individual differences in strategy was observed, from near-optimal to the opposite of optimal.
@@
 Another example of differences in search strategy comes from the foraging literature  \citep{kristjansson2014,johannesson2016}.
-In this context, foraging is a visual search task in which there are multiple targets on each trial.
+In this context, foraging tasks involve searching for multiple targets on each trial.
 Participants were asked to search through a set of items from four categories, with two categories classed as targets.
@@
 This strategy has previously been observed in animal foraging  \citep{dawkins1971}, and suggests holding one complex target template in mind at a time is a better strategy than switching templates.
-However, a sub-set of observers, termed `super-foragers', were able to change between search target categories with no cost to performance.
+However, a sub-set of participants, termed `super-foragers', were able to change between search target categories with no cost to performance.
 This study has been run on touch displays \citep{kristjansson2014} (observers are asked to tap on as many targets as they can as quickly as possible) and a 3D computer game (in which participants navigate a squirrel through a virtual environment picking up targets with different feature combinations) \citep{prpic2018}, with super-foragers present in both versions.
@@
 Are observers who use the optimal strategy in the SHLS paradigm also more optimal in the ACVS task?
-Does it make sense to talk about `super-searchers' who show above average performance in a range of search tasks (analogous to the 'super-recognizers' of the face-recognition literature  \citep{russell2009})?
+Does it make sense to talk about `super-searchers' who show above-average performance in a range of search tasks (analogous to the 'super-recognizers' of the face-recognition literature  \citep{russell2009})?
 As a secondary question, we will measure the test-retest reliability of the differences found in the SHLS paradigm, and compare it with existing estimates of reliability for ACVS and MCFT.
@@
 
-Sample size was determined in part by a power analysis, and in part due to constraints with counter-balancing.
-$n = 64$ participants means we should be able to detect correlations with $r > 0.34$ with $\alpha = 0.05$, $\beta = 0.80$ between the different visual search paradigms.
+Sample size was determined in part by a power analysis, and in part by counter-balancing.
+With $n = 64$ participants, correlations with $r > 0.34$ with $\alpha = 0.05$, $\beta = 0.80$ between the different visual search paradigms can be detected.
 The sample is therefore of sufficient size to detect relatively small correlations.
@@
 The three tasks were completed over two sessions, approximately one week apart.
-The SHLS was run in both sessions allowing us to measure test-retest reliability.
+The SHLS was run in both sessions.
 The order in which participants completed the tasks was counter-balanced.
@@
 The variance was low ($18^{\circ}$) on one half of the display to create a homogeneous texture, and high ($95^{\circ}$) on the other side to create a heterogeneous texture.
-This means that when the target is present on the homogeneous half, it can be easily be detected with peripheral vision, but when it is in the heterogeneous half, it is much harder to detect.
+When the target is present on the homogeneous half, it can be easily be detected with peripheral vision, but when it is in the heterogeneous half, it is much harder to detect (this was verified in \cite{nowakowska2017}).
 There were 160 trials in total and homo- and heterogeneous sides of the display were randomly varied from trial to trial.
-The position of the dominant eye was recorded using a desktop-mounted EyeLink 1000 eye tracker (SR Research, Canada).
+The dominant eye position was recorded using a desktop-mounted EyeLink 1000 eye tracker (SR Research, Canada).
 
@@
 
-In the feature foraging task, search displays contained small red, green, yellow and blue circles.
+In the feature foraging condition, search displays contained small red, green, yellow and blue circles.
 For half of the participants, targets were red and green circles, and for the other half of participants, targets were blue and yellow circles.
@@
 If the participant clicked erroneously on a non-target, the trial immediately ended and a replacement trial began.
-In the conjunction foraging task, search displays were composed of both circles and squares.
+The conjunction foraging task was the same, except search displays were composed of both circles and squares.
 For half of the participants, the shapes were red and green, and for the remaining participants the shapes were blue and yellow.
@@
 Our results are consistent with the original SHLS study \citep{nowakowska2017}: we find a large range of individual differences in search reaction time and accuracy (see Figure \ref{fig:splithalf_summary}).
-Furthermore, these differences are stable across the two sessions, with Pearson's $r \in [0.71, 0.89]$ ($95\%$ CI.) for accuracy in finding hard targets.
+These differences are stable across the two sessions, with Pearson's $r \in [0.71, 0.89]$ ($95\%$ CI.) for accuracy in finding hard targets.
 We get similar scores for the correlation in reaction times between sessions \textit{a} and \textit{b} for hard targets, ($r \in [0.54-0.81]$), easy targets ($r \in [0.52-0.80]$) and target absent trials ($r \in [0.66-0.86]$).
@@
 Furthermore, the SHLS task has been shown to have good test-retest reliability, similar to that of the ACVS  and MCFT tasks.
-Given this, we now investigate the extent to which an individual's performance in one of the tasks tells us about how well they will do in the other two.
+Given this, we can report the extent to which an individual's performance in one of the tasks predicts performance in the other two.
 
@@
 One might have expected reaction time to be at least modestly correlated from one search task to the next, even in the absence of correlations in strategy, as a general factor like an individual's speed-accuracy trade-off, motivation or conscientiousness might lead to better or worse overall performance across all the tasks.
-However, even reaction times were not highly correlated between tasks.
-What we did observe were correlations between our measures of strategy and reaction time within each task, suggesting our strategy metrics are predictive of search performance, and reinforcing the interpretation that an individual who is strategic in one task is not necessarily strategic in the others.
+However, what we did observe were high correlations between our measures of strategy and reaction time within each task, suggesting our strategy metrics determine a large proportion of search performance, and reinforcing the interpretation that an individual who is strategic in one task is not necessarily strategic in the others.
 
@@
 Individual differences pose a challenge for efforts to devise a comprehensive model of visual search.
-Our understanding of the underlying mechanisms of visual search is based predominantly on experiments that systematically vary details of the search task and measure their effects on performance.
-This approach has led to important insights, for example, about the kinds of visual features that can be used to guide attention (e.g.
-\citep{treisman1980, wolfe2007}; how attentional control settings filter out distractors (e.g.
+Our understanding of the mechanisms of visual search is based predominantly on experiments that systematically vary details of the search task and measure their effects on averaged performance.
+This approach has led to important insights, for example, about the kinds of visual features that can guide attention (e.g.
+\citep{treisman1980, wolfe2007}; how attentional control settings filter  distractors (e.g.
 \citep{folk1992,yantis1999}); and biases in attention, such as a bias towards unexplored locations (e.g.
 \citep{klein2000}).
-These insights are based on search performance averaged over some number of individual participants.
-For all three of the experiments included in the current study, however, the average performance would be highly misleading, as it would describe very few of the individuals who completed the tasks.
+For all three of the experiments included in the current study, however, the average performance would be highly misleading, as it would describe very few of the individuals' performance.
 In the original SHLS study  \citep{nowakowska2017}, for example, the original aim of the experiment was to assess whether search behaviour could be better described by an optimal  \citep{najemnik-geisler2008}, versus a stochastic  \citep{clarke2016}, model.
 Considering only the average search performance, the stochastic model was a good explanation.
-Underlying that average performance, however, was a very large spectrum of search behaviour, replicated here, some of which would be clearly categorized as optimal, and some as stochastic, and some as neither.
+Underlying that average performance, however, was a large spectrum of search behaviour, replicated here, some of which would be clearly categorized as optimal, and some as stochastic, and some as neither.
 The original question needed to be refined into new question: for whom is search optimal and for whom is it stochastic?
-The current findings add even further challenges for researchers interested in understanding visual search, by suggesting we need to not only account for individual differences, but also the interaction of a given individual with a particular search context.
+The current findings add even further challenges for researchers interested in understanding visual search, by suggesting we need to account not only for individual differences, but also for the interaction of a given individual with a particular search context.
 
-We view these findings, not as a disappointing null result, but as thought-provoking and exciting.
+We view these findings not as a discouraging result, but as thought-provoking and exciting.
 Vogel and Awh \citep{vogel2008} argued that studying individual differences in cognitive psychology (in their case, working memory) provides valuable insight to containing potential theories of the underlying cognitive mechanisms.
-Our results suggest that context and structure of the task also needs to be taken into account and we hope that studying how an individual's behaviour varies across different search tasks will lead to the development of a more comprehensive theory of search.
+Our results suggest that context and structure of the task also needs to be taken into account.
+Understanding how an individual's behaviour varies across different search tasks can lead to the development of a more comprehensive theory of search.
 

### 2019-02-20 Scripts/lineseg/3_saccadeStrategy.R
gender differences

@@ -11,6 +11,16 @@ figYn <- 2.5
 fix_dat <- readRDS(file="scratch/processedFixationData.Rda")
 trl_dat <- readRDS(file="scratch/processedRTandAccData.Rda")
 
+
+# load demographic data
+datFolder <- '../../Data/'
+demDat <- read_delim(paste(datFolder, "demographics.txt", sep = ""), delim = "\t")
+names(demDat)[1] <- c("observer")
+demDat$observer <- as.factor(demDat$observer)
+fix_dat <- full_join(fix_dat, demDat)
+fix_dat$gender <- as_factor(fix_dat$gender)
+
+
 # only take correct trials
 fix_dat <- filter(left_join(fix_dat, trl_dat), accuracy == 1)
 trl_dat <- filter(trl_dat, accuracy == 1)
@@ -105,6 +115,9 @@ r_df = tibble(
 a_labels = c(1, 2, 4, 8, 16)
 a_breaks = log(1000*a_labels, 2)
 
+
+dat <- full_join(dat, demDat)
+
 plt <- ggplot(dat, aes(x = prop_homo, xmin = lowerS, xmax = upperS, y = meanlogrt, ymin = lowerRT, ymax = upperRT, colour = session))
 plt <- plt + geom_errorbar(size=0.25, colour = "grey")
 plt <- plt + geom_errorbarh(size=0.25, colour = "grey")
@@ -123,8 +136,21 @@ plt <- plt + theme(
   panel.grid.major = element_blank(), 
   panel.grid.minor = element_blank())
 plt
-ggsave("./scratch/strat_compare_meanlog_rt.pdf", width = figYn, height = figYn)
-ggsave("./scratch/strat_compare_meanlog_rt.png", width = figYn, height = figYn)
+ggsave("/scratch/strat_compare_meanlog_rt.pdf", width = figYn, height = figYn)
+ggsave("/scratch/strat_compare_meanlog_rt.png", width = figYn, height = figYn)
+
+
+# --------------------------------------------------------------------------------
+# check for gender difference
+# --------------------------------------------------------------------------------
+plt <- ggplot(dat, aes( x = prop_hetero, fill = gender))
+plt <- plt + geom_density(alpha = 0.5)
+plt <- plt + facet_wrap(~ session)
+plt <- plt + scale_fill_viridis_d()
+plt
+ggsave("scratch/gender_strat.pdf")
+
+
 
 # --------------------------------------------------------------------------------
 # how consistent is stratety between session a and b?

### 2019-02-22 Manuscript/manuscript.tex
Chopping more words!

@@
 \RequirePackage{fix-cm}
-\documentclass[a4paper, jou, natbib]{apa6}
+\documentclass[a4paper, man, natbib, floatsintext]{apa6}
 
@@
 \fiveaffiliations{Department of Psychology, University of Essex, Colchester, UK}{Department of Psychology, The Ohio State University, Columbus, USA}{School of Psychology, University of Aberdeen, Aberdeen, UK}{Department of Psychology, The Ohio State University, Columbus, USA}{School of Psychology, University of Aberdeen, Aberdeen, UK}
-% {Corresponding author: a.clarke@essex.ac.uk}
-% \renewcommand\Affilfont{\itshape\small}
-
-% %%%% Subject entries to be placed here %%%%
-% \subject{Behaviour, evolution}
-
-% %%%% Keyword entries to be placed here %%%%
-% \keywords{visual search, optimal behaviour, eye movements}
-
-% %%%% Insert corresponding author and its email address}
-% \corres{Alasdair Clarke\\
-% \email{a.clarke@essex.ac.uk}}
 
@@
 Large individual differences were found with respect to the number of saccades participants made while monitoring the stimulus, which was negatively correlated with detection performance.
-In another example, Proulx \citeyearpar{proulx2011} demonstrated that participants differed in how they prioritised visual features (colour or orientation) when searching through a set of objects for one with a particular colour-orientation combination.
-These differences in search strategy explained some of the variation in the extent to which participants were distracted by an irrelevant object of a unique size.
-However, participants were largely unaware of the search strategy they employed.
 
@@
 This meant that targets appearing on the homogeneous side were highly salient, while targets on the heterogeneous side were harder to find.
-The optimal eye movement strategy here is to search only the heterogeneous half, as targets on the homogeneous side can be detected with peripheral vision.
-We will refer to this paradigm here as the Split-Half Line Segment task (SHLS).
+The optimal strategy here is to search the heterogeneous half, as targets on the homogeneous side can be detected with peripheral vision.
+We will refer to this paradigm as the Split-Half Line Segment task (SHLS).
 Some participants searched the displays near optimally, but others carried out strategies counter to this, failing to even match the performance of the stochastic searcher.
 The degree to which participants made saccades in line with the optimal search strategy was strongly correlated with the speed of their search.
-A related version of this paradigm has been used in research investigating eye movement strategies in response to (simulated) hemianopia \citep{nowakowska2016,nowakowska2018}, with similar conclusions: the full spectrum of individual differences in strategy was observed, from near-optimal to the opposite of optimal.
+A related version of this paradigm has been used in research investigating eye movement strategies in response to (simulated) hemianopia \citep{nowakowska2016,nowakowska2018}, with similar conclusions: the full spectrum of individual differences in strategy was observed.
 It is therefore not possible to conclude whether optimal or stochastic models better describe search without first explaining individual variability.
@@
 However, a sub-set of participants, termed `super-foragers', were able to change between search target categories with no cost to performance.
-This study has been run on touch displays \citep{kristjansson2014} (observers are asked to tap on as many targets as they can as quickly as possible) and a 3D computer game (in which participants navigate a squirrel through a virtual environment picking up targets with different feature combinations) \citep{prpic2018}, with super-foragers present in both versions.
-While test-retest reliability has not been measured explicitly for the foraging paradigm, the task was used as a measure to assess the effect of a six day long mindfulness retreat on cognitive performance \citep{hartkamp2017}.
+While test-retest reliability has not been measured explicitly for the foraging paradigm, the task was used as a measure to assess the effect of a six day mindfulness retreat on cognitive performance \citep{hartkamp2017}.
 From a re-analysis of these data, we can estimate that the test-retest reliability for the mean run length is $r \approx 0.7$ for the feature condition and $r \approx 0.88$ for the conjunction search.
@@
 Previous research has investigated the relationship between these behaviours to psychometric measures, but to date, these differences have not shown strong correlations with other attributes.
-In the ACVS paradigm, Irons \& Leber found no evidence of a correlation between the proportion of optimal choices made by observers and measures of visual working memory; trait impulsivity \citep{irons-leber2016}; novelty seeking; need for cognition; and intolerance of uncertainty \citep{irons-leber2018}.
+\cite{irons-leber2016,irons-leber2018} found no evidence of a correlation between the proportion of optimal choices made by observers in the ACVS paradigm and measures of visual working memory; trait impulsivity; novelty seeking; need for cognition; and intolerance of uncertainty.
 Similarly, the differences in foraging behaviour are not accounted for by working memory or inhibitory control \citep{johannesson2017}.
@@
 A common theme emerging from these studies is the observation that individual strategies vary in their degree of effectiveness or optimality.
-However, ``visual search'' encompasses a wide range of specific tasks, each tapping into a different aspect of behaviour (e.g.
+However, ``visual search'' encompasses a wide range of tasks, each tapping into a different aspect of behaviour (e.g.
 feature-based attention, information sampling).
 The aim of the present study is to investigate the extent to which individual differences are stable across different visual search paradigms.
-Are observers who use the optimal strategy in the SHLS paradigm also more optimal in the ACVS task?
 Does it make sense to talk about `super-searchers' who show above-average performance in a range of search tasks (analogous to the 'super-recognizers' of the face-recognition literature  \citep{russell2009})?
@@
 We view these findings not as a discouraging result, but as thought-provoking and exciting.
-Vogel and Awh \citep{vogel2008} argued that studying individual differences in cognitive psychology (in their case, working memory) provides valuable insight to containing potential theories of the underlying cognitive mechanisms.
+Vogel and Awh \citep{vogel2008} argued that studying individual differences in cognitive psychology (in their case, working memory) provides valuable insight to constraining potential theories of the underlying cognitive mechanisms.
 Our results suggest that context and structure of the task also needs to be taken into account.

### 2019-02-22 Scripts/lineseg/1_init_processing.R

@@ -119,6 +119,11 @@ fixDat <- tibble(observer=numeric(), session=character(), trial=numeric(), n=num
 trlDat <- tibble(observer=numeric(), session=character(), trial=numeric(), targPres=character(), targSide=character(), row=character(), column=character(), easySide=character(), responseKey=character())
 resDat <- tibble(observer=numeric(), session=character(), xRes=numeric(), yRes=numeric())	
 
+
+# load demographic data
+demDat <- read_delim(paste(datFolder, "demographics.txt", sep = ""), delim = "\t")
+
+
 for (pp in participants) {
 	print(pp)
 	for (ss in c('a', 'b')) 	{
@@ -147,6 +152,7 @@ temp <- resDat %>%
   group_by(xRes,session) %>%
   summarise(num_participants = n())
 
+names(demDat) <- c("observer")
 
 ##### Tidy up trlDat
 
@@ -264,4 +270,5 @@ fixDat$observer <- fct_drop(fixDat$observer)
 
 # save
 save(trlDat, file = "scratch/processedRTandAccData")
+
 save(fixDat, file = "scratch/processedFixationData")

### 2019-02-22 Manuscript/manuscript.tex
Chopped more words  from discussion. Should now be fine!

@@
 
-\begin{figure*}
+\begin{figure}
 \centering
@@
 \label{fig:exampleStimuli}
-\end{figure*}
+\end{figure}
 
@@
 Knowing how one person will behave in one of these paradigms tells us very little about how they will perform in the others.
-This can be contrasted with the relatively high test-retest correlations of all three of the tasks individually, which range from  0.58 to 0.92.
+This can be contrasted with the relatively high test-retest correlations of all three of the tasks individually.
 
@@
 The test-retest correlations on each of the individual visual search tasks rule out many of these alternatives, leaving a true absence of shared variance between these tasks as a likely explanation.
-One might have expected reaction time to be at least modestly correlated from one search task to the next, even in the absence of correlations in strategy, as a general factor like an individual's speed-accuracy trade-off, motivation or conscientiousness might lead to better or worse overall performance across all the tasks.
-However, what we did observe were high correlations between our measures of strategy and reaction time within each task, suggesting our strategy metrics determine a large proportion of search performance, and reinforcing the interpretation that an individual who is strategic in one task is not necessarily strategic in the others.
+One might have expected reaction time to be at least modestly correlated from one search task to the next, as a general factor like an individual's speed-accuracy trade-off, or motivation might lead to better or worse overall performance.
+However, we did observe correlations between measures of strategy and reaction time within each task, suggesting our strategy metrics determine a large proportion of search performance.
 
@@
 In the MCFT task, success involved minimizing cognitive load by minimizing target switching.
-Each of these tasks clearly taps into unique aspects of visual search strategies, and performance on one has little bearing on the others.
+Each of these tasks taps into unique aspects of visual search strategies, and performance on one has little bearing on the others.
 
 Individual differences pose a challenge for efforts to devise a comprehensive model of visual search.
-Our understanding of the mechanisms of visual search is based predominantly on experiments that systematically vary details of the search task and measure their effects on averaged performance.
+Our understanding of the mechanisms of visual search is based predominantly on experiments that systematically vary details of the search task and measure effects on averaged performance.
 This approach has led to important insights, for example, about the kinds of visual features that can guide attention (e.g.
@@
 For all three of the experiments included in the current study, however, the average performance would be highly misleading, as it would describe very few of the individuals' performance.
-In the original SHLS study  \citep{nowakowska2017}, for example, the original aim of the experiment was to assess whether search behaviour could be better described by an optimal  \citep{najemnik-geisler2008}, versus a stochastic  \citep{clarke2016}, model.
-Considering only the average search performance, the stochastic model was a good explanation.
-Underlying that average performance, however, was a large spectrum of search behaviour, replicated here, some of which would be clearly categorized as optimal, and some as stochastic, and some as neither.
-The original question needed to be refined into new question: for whom is search optimal and for whom is it stochastic?
-The current findings add even further challenges for researchers interested in understanding visual search, by suggesting we need to account not only for individual differences, but also for the interaction of a given individual with a particular search context.
+In the original SHLS study, for example, the original aim of the experiment was to assess whether search behaviour could be better described by an optimal  \citep{najemnik-geisler2008}, versus a stochastic  \citep{clarke2016}, model.
+Considering only the average performance, the stochastic model was a good explanation.
+Underlying that average performance, however, was a spectrum of search behaviour, replicated here, some of which would be clearly categorized as optimal, and some as stochastic, and some as neither.
+The original question needed to be refined: for whom is search optimal and for whom is it stochastic?
+The current findings add even further challenges for researchers, by suggesting we need to account not only for individual differences, but also for the interaction of a given individual with a particular search context.
 
@@
 Our results suggest that context and structure of the task also needs to be taken into account.
-Understanding how an individual's behaviour varies across different search tasks can lead to the development of a more comprehensive theory of search.
+Understanding how an individual's behaviour varies across different search tasks can lead to the development of a comprehensive theory of search.
 

### 2019-05-28 Manuscript/manuscript.tex
added citation of Hedge et al 2018
changing to Sage template

@@
-\RequirePackage{fix-cm}
-\documentclass[a4paper, man, natbib, floatsintext]{apa6}
+\documentclass[Afour, sageh, times]{sagej}
+% \RequirePackage{fix-cm}
+% \documentclass[a4paper, man, natbib, floatsintext]{apa6}
 
@@
 \usepackage{graphicx}
+\usepackage{natbib}
 
@@
 \title{Stable individual differences in strategies within, but not between, visual search tasks}
-\shorttitle{Differences in search}
-\fiveauthors{A. D. F. Clarke}{J. L. Irons}{W. James}{A. B. Leber}{A. R. Hunt}
+\runninghead{Clarke et al.}
+\author{A. D. F. Clarke\affilnum{1} and J. L. Irons\affilnum{2} and W. James\affilnum{3} and A. B. Leber\affilnum{2} and A. R. Hunt\affilnum{3}}
 
-\fiveaffiliations{Department of Psychology, University of Essex, Colchester, UK}{Department of Psychology, The Ohio State University, Columbus, USA}{School of Psychology, University of Aberdeen, Aberdeen, UK}{Department of Psychology, The Ohio State University, Columbus, USA}{School of Psychology, University of Aberdeen, Aberdeen, UK}
+\affiliation{\affilnum{1}Department of Psychology, University of Essex, Colchester, UK \\ 
+\affilnum{2}Department of Psychology, The Ohio State University, Columbus, USA \\ 
+\affilnum{3}School of Psychology, University of Aberdeen, Aberdeen, UK}
 
-\abstract{
+\corrauth{Alasdair D. F. Clarke, Department of Psychology, University of Essex, Colchester, UK.}
+
+\email{a.clarke@essex.ac.uk}
+
+\begin{abstract}
 A striking range of individual differences has recently been reported in three different visual search tasks.
@@
 These results suggest search strategies are stable over time, but context-specific.
-To understand visual search we therefore need to account not only for differences between individuals, but also how individuals interact with the search task and context.}
+To understand visual search we therefore need to account not only for differences between individuals, but also how individuals interact with the search task and context.
+\end{abstract}
 
@@
 
-\begin{figure}
+\begin{figure*}
 \centering
-\subfigure[][]{\includegraphics[height=3cm]{figures/split-half.png}}
-\subfigure[][]{\includegraphics[height=3cm]{figures/adaptive.png}}
-\subfigure[][]{\includegraphics[height=3cm]{figures/foraging.png}}
+\subfigure[][]{\includegraphics[height=5cm]{figures/split-half.png}}
+\subfigure[][]{\includegraphics[height=5cm]{figures/adaptive.png}}
+\subfigure[][]{\includegraphics[height=5cm]{figures/foraging.png}}
 \caption{Example stimulus from the (a) \textit{split-half line segment} (SHLS), (b) \textit{adaptive choice visual search} (ACVS) and (c) \textit{mouse click foraging task} (MCFT) paradigms.}
 \label{fig:exampleStimuli}
-\end{figure}
+\end{figure*}
 
@@
 
-The methods and planned analysis for this study were registered on the Open Science Framework\footnote{\url{https://osf.io/scv4u/}} before data collection started.
+The methods and planned analysis for this study were registered on the Open Science Framework\endnote{https://osf.io/scv4u/} before data collection started.
 
@@
 
-\begin{figure}
+\begin{figure*}
 \centering
-\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/lineseg/scratch/acc_correlation.pdf}}
-\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/lineseg/scratch/rt_correlation.pdf}}
-\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/lineseg/scratch/strat_corr.pdf}}
-\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/lineseg/scratch/strat_compare_meanlog_rt.pdf}}
+\subfigure[][]{\includegraphics[width=6cm]{../Scripts/lineseg/scratch/acc_correlation.pdf}}
+\subfigure[][]{\includegraphics[width=6cm]{../Scripts/lineseg/scratch/rt_correlation.pdf}}
+\subfigure[][]{\includegraphics[width=6cm]{../Scripts/lineseg/scratch/strat_corr.pdf}}
+\subfigure[][]{\includegraphics[width=6cm]{../Scripts/lineseg/scratch/strat_compare_meanlog_rt.pdf}}
 \caption{Correlation between the two sessions of the SHLS paradigm for (a)  accuracy (TP-heterogeneous trials only); (b) reaction times and (c) search strategy (TA trials only).
@@
 \label{fig:splithalf_summary}
-\end{figure}
+\end{figure*}
 
@@
 
-\begin{figure}
+\begin{figure*}
 \centering
-\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/scratch/acvs_opt_rt}}
-\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/scratch/mcft_rl_rt}}
+\subfigure[][]{\includegraphics[width=6cm]{../Scripts/scratch/acvs_opt_rt}}
+\subfigure[][]{\includegraphics[width=6cm]{../Scripts/scratch/mcft_rl_rt}}
 \caption{Correlation between strategy and reaction times for (a) ACVS and (b) MCFT. Each point represents a participant.}
 \label{fig:acvs_mcft_summary}
-\end{figure}
+\end{figure*}
 
@@
 
-\begin{figure}
+\begin{figure*}
 \centering
-\includegraphics[width=6.5cm]{../Scripts/scratch/cor_comparison.pdf}
+\includegraphics[width=10cm]{../Scripts/scratch/cor_comparison.pdf}
 \caption{The between- and within-task correlations for the three different search tasks.
@@
 \label{fig:all_the_cor}
-\end{figure}
+\end{figure*}
 
@@
 This can be contrasted with the relatively high test-retest correlations of all three of the tasks individually.
+Indeed, we find that the visual search tasks under consideration here compare favourably to other cognitive psychology paradigms, such as Erkison Flanker and Posner Cueing tasks in terms of test-retest reliability \citep{hedge2018}.
 
@@
 
+\bibliographystyle{sageh}
 \bibliography{literature}

### 2019-05-28 Manuscript/manuscript.tex
minor typo

@@
-\documentclass[Afour, sageh, times]{sagej}
+\documentclass[Afour, sageapa, times]{sagej}
 % \RequirePackage{fix-cm}
@@
 \usepackage{graphicx}
-\usepackage{natbib}
+% \usepackage{natbib}
 
@@
 As is common in cognitive psychology, most visual search literature has focused on how the average participant performs in the task, despite it being well known that there is a great deal of variability between one subject and the next.
-From Treisman's work on Feature Integration Theory \citep{treisman1980} to the latest incarnation of the Guided Search Model \citep{wolfe2015}, we have a good understanding of what makes particular objects easier or harder to find.
+From Treisman's work on Feature Integration Theory \cite{treisman1980} to the latest incarnation of the Guided Search Model \cite{wolfe2015}, we have a good understanding of what makes particular objects easier or harder to find.
 However, these theories and models have neglected the question of why some observers find visual search so much harder than others.
-These differences can emerge from several different sources of variation: tiredness \citep{mackworth1948}, information-processing ability, speed-accuracy trade-off, motivation, visual impairments \citep{nowakowska2016}, and search strategies \citep{boot2006}.
-Although their existence has previously been noted \citep{mackworth1948}, a rigorous examination of individual differences in visual search is a challenge that has not been taken up by many researchers, and questions about their impact and stability remain relatively under-explored.
+These differences can emerge from several different sources of variation: tiredness \cite{mackworth1948}, information-processing ability, speed-accuracy trade-off, motivation, visual impairments \cite{nowakowska2016}, and search strategies \cite{boot2006}.
+Although their existence has previously been noted \cite{mackworth1948}, a rigorous examination of individual differences in visual search is a challenge that has not been taken up by many researchers, and questions about their impact and stability remain relatively under-explored.
 
@@
 By strategy we mean a collection of search behaviours from which all observers can freely choose.
-Examples include adopting a systematic left-to-right and top-to-bottom strategy \citep{gilchrist2006}, or prioritizing locations that, based on knowledge or context, are more likely to contain the target \citep{wolfe2015}.
+Examples include adopting a systematic left-to-right and top-to-bottom strategy \cite{gilchrist2006}, or prioritizing locations that, based on knowledge or context, are more likely to contain the target \cite{wolfe2015}.
 A striking example of the effect of strategy is given by \cite{boot2006}.
@@
 Eye movement strategies have also been shown to be an important source of individual differences in visual search efficiency.
-\cite{nowakowska2017} designed a simple search paradigm to discriminate between optimal \citep{najemnik-geisler2008} and stochastic  \citep{clarke2016} search strategies.
+\cite{nowakowska2017} designed a simple search paradigm to discriminate between optimal \cite{najemnik-geisler2008} and stochastic  \cite{clarke2016} search strategies.
 Participants searched through arrays of line segments (Figure \ref{fig:exampleStimuli}) arranged such that those on one side of the display all had a very similar orientation (homogeneous), while those on the other side had higher variance (heterogeneous).
@@
 The degree to which participants made saccades in line with the optimal search strategy was strongly correlated with the speed of their search.
-A related version of this paradigm has been used in research investigating eye movement strategies in response to (simulated) hemianopia \citep{nowakowska2016,nowakowska2018}, with similar conclusions: the full spectrum of individual differences in strategy was observed.
+A related version of this paradigm has been used in research investigating eye movement strategies in response to (simulated) hemianopia \cite{nowakowska2016,nowakowska2018}, with similar conclusions: the full spectrum of individual differences in strategy was observed.
 It is therefore not possible to conclude whether optimal or stochastic models better describe search without first explaining individual variability.
@@
 The results showed that participants varied substantially along two key dimensions: how frequently they used the more effective target colour to search (varying from chance performance to near optimal), and how often they changed between colours.
-Further work \citep{irons-leber2018} has shown that these differences are stable over time (between one and ten days) with test-retest correlations of around $r = 0.83$ ($95\%$ CI $= [0.72, 0.90]$) for optimal choices.
+Further work \cite{irons-leber2018} has shown that these differences are stable over time (between one and ten days) with test-retest correlations of around $r = 0.83$ ($95\%$ CI $= [0.72, 0.90]$) for optimal choices.
 
@@
 
-Another example of differences in search strategy comes from the foraging literature  \citep{kristjansson2014,johannesson2016}.
+Another example of differences in search strategy comes from the foraging literature  \cite{kristjansson2014,johannesson2016}.
 In this context, foraging tasks involve searching for multiple targets on each trial.
@@
 In the conjunction condition (searching for red-horizontal and green-vertical line segments among red-vertical and green-horizontal distracters), most observers searched in runs, finding all the targets of one target category, and then switching and finding the targets in the other category.
-This strategy has previously been observed in animal foraging  \citep{dawkins1971}, and suggests holding one complex target template in mind at a time is a better strategy than switching templates.
+This strategy has previously been observed in animal foraging  \cite{dawkins1971}, and suggests holding one complex target template in mind at a time is a better strategy than switching templates.
 However, a sub-set of participants, termed `super-foragers', were able to change between search target categories with no cost to performance.
-While test-retest reliability has not been measured explicitly for the foraging paradigm, the task was used as a measure to assess the effect of a six day mindfulness retreat on cognitive performance \citep{hartkamp2017}.
+While test-retest reliability has not been measured explicitly for the foraging paradigm, the task was used as a measure to assess the effect of a six day mindfulness retreat on cognitive performance \cite{hartkamp2017}.
 From a re-analysis of these data, we can estimate that the test-retest reliability for the mean run length is $r \approx 0.7$ for the feature condition and $r \approx 0.88$ for the conjunction search.
@@
 \cite{irons-leber2016,irons-leber2018} found no evidence of a correlation between the proportion of optimal choices made by observers in the ACVS paradigm and measures of visual working memory; trait impulsivity; novelty seeking; need for cognition; and intolerance of uncertainty.
-Similarly, the differences in foraging behaviour are not accounted for by working memory or inhibitory control \citep{johannesson2017}.
+Similarly, the differences in foraging behaviour are not accounted for by working memory or inhibitory control \cite{johannesson2017}.
 
@@
 The aim of the present study is to investigate the extent to which individual differences are stable across different visual search paradigms.
-Does it make sense to talk about `super-searchers' who show above-average performance in a range of search tasks (analogous to the 'super-recognizers' of the face-recognition literature  \citep{russell2009})?
+Does it make sense to talk about `super-searchers' who show above-average performance in a range of search tasks (analogous to the 'super-recognizers' of the face-recognition literature  \cite{russell2009})?
 As a secondary question, we will measure the test-retest reliability of the differences found in the SHLS paradigm, and compare it with existing estimates of reliability for ACVS and MCFT.
@@
 
-The study consists of three paradigms from the visual search literature in which large individual differences have been  found \citep{nowakowska2017, irons-leber2016, kristjansson2014}.
+The study consists of three paradigms from the visual search literature in which large individual differences have been  found \cite{nowakowska2017, irons-leber2016, kristjansson2014}.
 Example stimuli can be seen in Figure \ref{fig:exampleStimuli}.
@@
 The display was presented on a 17-inch CRT monitor with a resolution of $1400 \times 1050$ ($n = 40$) or $1600 \times 1200$ ($n = 24$).
-Stimulus generation, presentation and data collection were controlled by MATLAB and the psychophysics and eyelink toolboxes  \citep{brainard1997,cornelissen2002} run on a Powermac.
+Stimulus generation, presentation and data collection were controlled by MATLAB and the psychophysics and eyelink toolboxes  \cite{brainard1997,cornelissen2002} run on a Powermac.
 Participants sat $\approx 47$cm from the screen.
@@
 
-Our results are consistent with the original SHLS study \citep{nowakowska2017}: we find a large range of individual differences in search reaction time and accuracy (see Figure \ref{fig:splithalf_summary}).
+Our results are consistent with the original SHLS study \cite{nowakowska2017}: we find a large range of individual differences in search reaction time and accuracy (see Figure \ref{fig:splithalf_summary}).
 These differences are stable across the two sessions, with Pearson's $r \in [0.71, 0.89]$ ($95\%$ CI.) for accuracy in finding hard targets.
@@
 Again, we see large and stable individual differences across the two sessions (test-retest $r \in [0.63, 0.86]$ for the proportion of the first five saccades to the heterogeneous half of the display for target absent trials).
-More importantly, as with  \citep{nowakowska2017}, we see that the search strategies give a good correlation with reaction times in both session a, $r \in [0.52, 0.82]$ and session b, $r \in [0.50, 0.80]$.
+More importantly, as with  \cite{nowakowska2017}, we see that the search strategies give a good correlation with reaction times in both session a, $r \in [0.52, 0.82]$ and session b, $r \in [0.50, 0.80]$.
 
@@
 We measured an individual's strategy as the percent of plateau trials in which the individual chose the optimal target (i.e., the target with the fewest distractors: When the variable distractor was red, the optimal choice was blue, and vice versa).
-The results for the ACVS were consistent with previous findings  \citep{irons-leber2016,irons-leber2018}.
+The results for the ACVS were consistent with previous findings  \cite{irons-leber2016,irons-leber2018}.
 We can clearly see from figure \ref{fig:acvs_mcft_summary}(a) that there are individual differences in the proportion of optimal targets reported (range $33.62\%$ - $100.00\%$, $\bar{x} = 59.15$, $s = 16.54$) and the mean ($\log_2$) reaction times (range $1.90$ - $4.80$ seconds).
@@
 The average run length was the mean number of target selections in a run.
-The multiple-target foraging results were in line with previous findings  \citep{kristjansson2014,johannesson2016}, with shorter run lengths for feature foraging ($\bar{x} = 3.16$, $s = 3.14$) than conjunction foraging ($\bar{x} = 11.73$, $s = 7.09$).
+The multiple-target foraging results were in line with previous findings  \cite{kristjansson2014,johannesson2016}, with shorter run lengths for feature foraging ($\bar{x} = 3.16$, $s = 3.14$) than conjunction foraging ($\bar{x} = 11.73$, $s = 7.09$).
 This suggests more frequent foraging for multiple targets concurrently when those targets were defined by features than by conjunctions.
@@
 This can be contrasted with the relatively high test-retest correlations of all three of the tasks individually.
-Indeed, we find that the visual search tasks under consideration here compare favourably to other cognitive psychology paradigms, such as Erkison Flanker and Posner Cueing tasks in terms of test-retest reliability \citep{hedge2018}.
+Indeed, we find that the visual search tasks under consideration here compare favourably to other cognitive psychology paradigms, such as the Erkison Flanker and Posner Cueing tasks in terms of test-retest reliability \cite{hedge2018}.
 
@@
 This approach has led to important insights, for example, about the kinds of visual features that can guide attention (e.g.
-\citep{treisman1980, wolfe2007}; how attentional control settings filter  distractors (e.g.
-\citep{folk1992,yantis1999}); and biases in attention, such as a bias towards unexplored locations (e.g.
-\citep{klein2000}).
+\cite{treisman1980}; how attentional control settings filter  distractors (e.g.
+\cite{folk1992,yantis1999}); and biases in attention, such as a bias towards unexplored locations (e.g.
+\cite{klein2000}).
 For all three of the experiments included in the current study, however, the average performance would be highly misleading, as it would describe very few of the individuals' performance.
-In the original SHLS study, for example, the original aim of the experiment was to assess whether search behaviour could be better described by an optimal  \citep{najemnik-geisler2008}, versus a stochastic  \citep{clarke2016}, model.
+In the original SHLS study, for example, the original aim of the experiment was to assess whether search behaviour could be better described by an optimal  \cite{najemnik-geisler2008}, versus a stochastic  \cite{clarke2016}, model.
 Considering only the average performance, the stochastic model was a good explanation.
@@
 We view these findings not as a discouraging result, but as thought-provoking and exciting.
-Vogel and Awh \citep{vogel2008} argued that studying individual differences in cognitive psychology (in their case, working memory) provides valuable insight to constraining potential theories of the underlying cognitive mechanisms.
+Vogel and Awh \cite{vogel2008} argued that studying individual differences in cognitive psychology (in their case, working memory) provides valuable insight to constraining potential theories of the underlying cognitive mechanisms.
 Our results suggest that context and structure of the task also needs to be taken into account.
@@
 
-\bibliographystyle{sageh}
+\bibliographystyle{mslapa}
 \bibliography{literature}

### 2019-05-28 Manuscript/manuscript.tex
tidied up a few bits

@@
 The variance was low ($18^{\circ}$) on one half of the display to create a homogeneous texture, and high ($95^{\circ}$) on the other side to create a heterogeneous texture.
-When the target is present on the homogeneous half, it can be easily be detected with peripheral vision, but when it is in the heterogeneous half, it is much harder to detect (this was verified in \cite{nowakowska2017}).
+When the target is present on the homogeneous half, it can be easily be detected with peripheral vision, but when it is in the heterogeneous half, it is much harder to detect.
+This was verified in \cite{nowakowska2017}: for brief presentations viewed from the center, detection performance was close to chance for targets presented on the heterogeneous texture, and close to ceiling for targets presented on the homogeneous texture).
 There were 160 trials in total and homo- and heterogeneous sides of the display were randomly varied from trial to trial.
@@
 
-Each search display was composed of red, blue, green and variable-coloured small squares arranged in three concentric rings around fixation.
-Variable distractors changed colours from trial-to-trial according to a 24 trial cyclical pattern: the distractors would be red for five trials, then across a period of seven trials, they would gradually change colour from red to blue.
-The variable distractor would then be blue for five trials, and then gradually transition back to red.
+Each search display was composed of 54 red, blue, green and variable-coloured small squares arranged in three concentric rings around fixation (see \ref{fig:exampleStimuli}).
+Variable distractors changed colours from trial-to-trial according to a 24 trial cyclical pattern: these distractors would be red for five trials, then across a period of seven trials, they would gradually change colour from red to blue.
+The variable distractors would then be blue for five trials, and then gradually transition back to red.
+%A missing detail reviewers might want to know here is how many distractors are variable vs fixed colors
 
@@
 Participants were informed that two targets - a red square and a blue square each with a digit between 2 and 5 - were embedded in every search display.
-The two target digits were always different, to enable us to distinguish the chosen target.
+The two target digits were always different, to enable us to distinguish the color of the target that had been found on each trial.
 The remaining red, blue and variable squares all contained digits between 6-9.
@@
 We successfully replicated the wide range of individual differences in strategy and performance that had previously been observed in each of these three visual search paradigms, with a larger sample size than the original experiments.
-Surprisingly, however, the between-paradigm correlations give $R^2 \approx 0.04$, and this is a generous interpretation that would fail to pass the usual criteria for null hypothesis significance testing.
+Surprisingly, however, the between-paradigm correlations give $R^2 \approx 0.04$; even a generous interpretation of the correlation between tasks would fail to pass the usual criteria for null hypothesis significance testing.
 Knowing how one person will behave in one of these paradigms tells us very little about how they will perform in the others.
-This can be contrasted with the relatively high test-retest correlations of all three of the tasks individually.
-Indeed, we find that the visual search tasks under consideration here compare favourably to other cognitive psychology paradigms, such as the Erkison Flanker and Posner Cueing tasks in terms of test-retest reliability \cite{hedge2018}.
+This lack of any consistent relationship between the search tasks occured despite the relatively high test-retest correlations of all three of the tasks individually.
+Indeed, the test-retest reliability of each of the three measures of visual search strategy we used in this study compare favourably to other cognitive psychology paradigms, such as the Erkison Flanker and Posner Cueing tasks, making them well suited for detecting relationships with other variables \cite{hedge2018}.
+We also observe strong correlations between measures of strategy and reaction time \textit{within} each task.
+These correlations demonstrate that our strategy metrics determine a large proportion of search performance, and that our measurements are sufficiently reliable to produce clear correlations where they exist.
 
-There are many reasons why two measurements might be uncorrelated, such as range restriction or measurement noise.
-The test-retest correlations on each of the individual visual search tasks rule out many of these alternatives, leaving a true absence of shared variance between these tasks as a likely explanation.
-One might have expected reaction time to be at least modestly correlated from one search task to the next, as a general factor like an individual's speed-accuracy trade-off, or motivation might lead to better or worse overall performance.
-However, we did observe correlations between measures of strategy and reaction time within each task, suggesting our strategy metrics determine a large proportion of search performance.
-
+There are many reasons why two measurements might be uncorrelated, such as range restriction or measurement noise, but the test-retest correlations and within-task correlations on each of the individual visual search task metrics rule out many of these alternatives, leaving a true absence of shared variance between these tasks as a likely explanation for the lack of correlation.
+One might have expected reaction time to be at least modestly correlated from one search task to the next, as a general factor like an individual's speed-accuracy trade-off, or motivation might lead to better or worse overall performance, but there was no relationship.
 Although the tasks in this experiment all have visual search in common, they also have unique aspects that appear to have resonated with particular individuals' strengths, and not others.

### 2019-05-30 Manuscript/manuscript.tex
getting ready to submit again!

@@
 \usepackage{graphicx}
-% \usepackage{natbib}
 
@@
 Examples include adopting a systematic left-to-right and top-to-bottom strategy \cite{gilchrist2006}, or prioritizing locations that, based on knowledge or context, are more likely to contain the target \cite{wolfe2015}.
-A striking example of the effect of strategy is given by \cite{boot2006}.
+A striking example of the effect of strategy is given by Boot, Kramer, Becic, Wiegmann and Kubose \citeyear{boot2006}.
 They asked participants to monitor a cluttered display for an object changing colour or suddenly appearing.
@@
 
-A similar range of strategies, from random to near-optimal, has been found by \cite{irons-leber2016} with the Adaptive Choice Visual Search (ACVS) paradigm.
+A similar range of strategies, from random to near-optimal, has been found by Irons and Leber \citeyear{irons-leber2016} with the Adaptive Choice Visual Search (ACVS) paradigm.
 This paradigm involves stimuli made up of small coloured boxes (red, blue, green and a fourth colour that varies from red, through purple, to blue and back again) with numerals written inside them (Figure \ref{fig:exampleStimuli}).
@@
 
-The methods and planned analysis for this study were registered on the Open Science Framework\endnote{https://osf.io/scv4u/} before data collection started.
+The methods and planned analysis for this study were registered on the Open Science Framework\footnote{https://osf.io/scv4u/} before data collection started.
 
@@
 
-Each search display was composed of 54 red, blue, green and variable-coloured small squares arranged in three concentric rings around fixation (see \ref{fig:exampleStimuli}).
+Each search display was composed of 54 red, blue , green and variable-coloured small squares (14 of each colour) arranged in three concentric rings around fixation (see \ref{fig:exampleStimuli}).
 Variable distractors changed colours from trial-to-trial according to a 24 trial cyclical pattern: these distractors would be red for five trials, then across a period of seven trials, they would gradually change colour from red to blue.
 The variable distractors would then be blue for five trials, and then gradually transition back to red.
-%A missing detail reviewers might want to know here is how many distractors are variable vs fixed colors
 
@@
 We view these findings not as a discouraging result, but as thought-provoking and exciting.
-Vogel and Awh \cite{vogel2008} argued that studying individual differences in cognitive psychology (in their case, working memory) provides valuable insight to constraining potential theories of the underlying cognitive mechanisms.
+Vogel and Awh \citeyear{vogel2008} argued that studying individual differences in cognitive psychology (in their case, working memory) provides valuable insight to constraining potential theories of the underlying cognitive mechanisms.
 Our results suggest that context and structure of the task also needs to be taken into account.

### 2019-10-21 Manuscript/manuscript.tex
Tackling easy Reviewer comments

@@
 \usepackage{graphicx}
+\usepackage{xcolor}
 
@@
 On trials in which the fourth colour is red (or close to red), participants should search through the blue boxes and report the blue target, as there will be fewer distracters.
-As the fourth colour changes to through purple to blue, participants should update their strategy and search for the red target.
+As the fourth colour changes through purple to blue, participants should update their strategy and search for the red target.
 The results showed that participants varied substantially along two key dimensions: how frequently they used the more effective target colour to search (varying from chance performance to near optimal), and how often they changed between colours.
@@
 This strategy has previously been observed in animal foraging  \cite{dawkins1971}, and suggests holding one complex target template in mind at a time is a better strategy than switching templates.
-However, a sub-set of participants, termed `super-foragers', were able to change between search target categories with no cost to performance.
+However, a sub-set of participants, termed `super-foragers', were able to change between search target categories with \textcolor{blue}{very little} cost to performance.
 While test-retest reliability has not been measured explicitly for the foraging paradigm, the task was used as a measure to assess the effect of a six day mindfulness retreat on cognitive performance \cite{hartkamp2017}.
@@
 
-Previous research has investigated the relationship between these behaviours to psychometric measures, but to date, these differences have not shown strong correlations with other attributes.
+\textcolor{red} {Insert discussion of \cite{woods2013} here?}
+
+Previous research has investigated the relationship between these behaviours \textcolor{blue}{and} psychometric measures, but to date, these differences have not shown strong correlations with other attributes.
 \cite{irons-leber2016,irons-leber2018} found no evidence of a correlation between the proportion of optimal choices made by observers in the ACVS paradigm and measures of visual working memory; trait impulsivity; novelty seeking; need for cognition; and intolerance of uncertainty.
 Similarly, the differences in foraging behaviour are not accounted for by working memory or inhibitory control \cite{johannesson2017}.
+\textcolor{blue}{However, there is evidence of a link between Attention Deficit/Hyperactivity Disorder and various search behaviours \cite{vandendriessche2019}.}
 
@@
 When the target is present on the homogeneous half, it can be easily be detected with peripheral vision, but when it is in the heterogeneous half, it is much harder to detect.
-This was verified in \cite{nowakowska2017}: for brief presentations viewed from the center, detection performance was close to chance for targets presented on the heterogeneous texture, and close to ceiling for targets presented on the homogeneous texture).
+This was verified in \cite{nowakowska2017}: for brief presentations viewed from the center, detection performance was close to chance for targets presented on the heterogeneous texture, and close to ceiling for targets presented on the homogeneous texture.
 There were 160 trials in total and homo- and heterogeneous sides of the display were randomly varied from trial to trial.
@@
 
-We would like to thanks Anna Nowakowska, {\'A}rn Kristj{\'a}nsson and Ian Thornton for sharing data and their helpful comments and suggestions.
+We would like to thanks Anna Nowakowska, {\'A}rni Kristj{\'a}nsson and Ian Thornton for sharing data and their helpful comments and suggestions.
 We would like to thank Charles Rigitano and Jacqueline Von Seth who helped with data collection.

### 2019-10-22 Manuscript/manuscript.tex
more minor corrections

@@
 These differences can emerge from several different sources of variation: tiredness \cite{mackworth1948}, information-processing ability, speed-accuracy trade-off, motivation, visual impairments \cite{nowakowska2016}, and search strategies \cite{boot2006}.
-Although their existence has previously been noted \cite{mackworth1948}, a rigorous examination of individual differences in visual search is a challenge that has not been taken up by many researchers, and questions about their impact and stability remain relatively under-explored.
+Although their existence has previously been noted \cite{mackworth1948, clarke2019}, a rigorous examination of individual differences in visual search is a challenge that has not been taken up by many researchers, and questions about their impact and stability remain relatively under-explored.
 
@@
 
-\textcolor{red} {Insert discussion of \cite{woods2013} here?}
-
-Previous research has investigated the relationship between these behaviours \textcolor{blue}{and} psychometric measures, but to date, these differences have not shown strong correlations with other attributes.
+Previous research has investigated the relationship between these behaviours \textcolor{blue}{and} psychometrics, but to date, these differences have not shown strong correlations with other attributes.
 \cite{irons-leber2016,irons-leber2018} found no evidence of a correlation between the proportion of optimal choices made by observers in the ACVS paradigm and measures of visual working memory; trait impulsivity; novelty seeking; need for cognition; and intolerance of uncertainty.
 Similarly, the differences in foraging behaviour are not accounted for by working memory or inhibitory control \cite{johannesson2017}.
-\textcolor{blue}{However, there is evidence of a link between Attention Deficit/Hyperactivity Disorder and various search behaviours \cite{vandendriessche2019}.}
+\textcolor{blue}{However, there is evidence of a link between Attention Deficit/Hyperactivity Disorder and various search behaviours \cite{vandendriessche2019}.
+Furthermore, the degree to which children exhibit organised scanpaths appears to develop in tandem with executive function \cite{woods2013}.}
 
@@
 Again, we see large and stable individual differences across the two sessions (test-retest $r \in [0.63, 0.86]$ for the proportion of the first five saccades to the heterogeneous half of the display for target absent trials).
-More importantly, as with  \cite{nowakowska2017}, we see that the search strategies give a good correlation with reaction times in both session a, $r \in [0.52, 0.82]$ and session b, $r \in [0.50, 0.80]$.
+More importantly, as with  Nowakowska et al.
+\citeyear{nowakowska2017}, we see that the search strategies give a good correlation with reaction times in both session a, $r \in [0.52, 0.82]$ and session b, $r \in [0.50, 0.80]$.
 
@@
 \subfigure[][]{\includegraphics[width=6cm]{../Scripts/scratch/mcft_rl_rt}}
-\caption{Correlation between strategy and reaction times for (a) ACVS and (b) MCFT. Each point represents a participant.}
+\caption{Correlation between strategy and reaction times for (a) ACVS and (b) MCFT \textcolor{blue}{(conjunction condition only)}. Each point represents a participant.}
 \label{fig:acvs_mcft_summary}
@@
 This suggests more frequent foraging for multiple targets concurrently when those targets were defined by features than by conjunctions.
-Figure \ref{fig:acvs_mcft_summary}(b) depicts the individual differences in terms of run length and the correlation with reaction time ($r \in [-0.55, -0.10]$).
+Figure \ref{fig:acvs_mcft_summary}(b) depicts the individual differences in \textcolor{blue}{the conjunction condition} in terms of run length and the correlation with reaction time ($r \in [-0.55, -0.10]$).
 
@@
 The results show that the correlations between the strategy metrics in the three tasks (Figure \ref{fig:all_the_cor}) are weak.
-Perhaps even more surprisingly, there is also little evidence for meaningful correlations between reaction times in the different tasks.
+\textcolor{blue}{(Analysis of accuracy correlations is included in the supplementary materials.)} Perhaps even more surprisingly, there is also little evidence for meaningful correlations between reaction times in the different tasks.
 Even if we optimistically take all data together as suggesting a robust correlation in reaction times from one task to another, the mean correlation over the three tasks is only $r = 0.2$, implying that this correlation accounts for  $R^2 = 0.04 = 4\%$ an individual's performance.
@@
 This approach has led to important insights, for example, about the kinds of visual features that can guide attention (e.g.
-\cite{treisman1980}; how attentional control settings filter  distractors (e.g.
-\cite{folk1992,yantis1999}); and biases in attention, such as a bias towards unexplored locations (e.g.
-\cite{klein2000}).
+\cite{treisman1980}; how attentional control settings filter distractors \cite(e.g.){folk1992,yantis1999}; and biases in attention, such as a bias towards unexplored locations \cite(e.g.){klein2000}.
 For all three of the experiments included in the current study, however, the average performance would be highly misleading, as it would describe very few of the individuals' performance.
@@
 The original question needed to be refined: for whom is search optimal and for whom is it stochastic?
+Our approach in this experiment puts into practice several of the recommendations of Clarke et al.
+\citeyear{clarke2019}, who suggest that a focus on accounting for variance, in addition to interpreting average patterns, will lead to important new insights.
+Another recommendation from that paper is to examine the generalizability of conclusions across paradigms, which we have also done here.
+Taking this further, it would be interesting to examine the extent to which the results of each of these search paradigms would scale to similar, but more familiar and realistic, contexts.
 The current findings add even further challenges for researchers, by suggesting we need to account not only for individual differences, but also for the interaction of a given individual with a particular search context.

### 2019-10-22 sup_mat/sup_mat.Rmd
Altered sup mat
Added a small section on Accuracy in the ACS and SHVS tasks in terms of how correlated accuracy was between these tasks

@@
 
-## Split-Half
+## Split-Half Visual Search 
 This task lasted approximately 30 minutes and was carried out in both sessions.
@@
 
-### Split-Half task
+### Split-Half Visual Search task
 Accuracy data is shown in Figure \ref{fig:ls_acc_plt}.
@@
 ```{r ls_acc_plt, fig.cap = "\\label{fig:ls_acc_plt} Accuracy data for each participant for the split-half paradigm. ", echo = FALSE, fig.align = "center", fig.asp = 0.6}
+#  fig.width = 6, fig.height = 6
 # make the plot
@@
   theme_bw() +
-  theme(axis.text.x  = element_text(angle=90, vjust=0.5), legend.position = "top", strip.text.x = element_text(margin = margin(0.01,0,0.01,0, "mm"))) + 
+  theme(axis.text.x  = element_text(angle=90, vjust=0.5),
+        legend.position = "top",
+        # strip.text.x = element_text(margin = margin(0.01,0,0.01,0, "mm"))) +
+        strip.text.x = element_blank()) + 
   scale_fill_ptol() +
@@
   theme(legend.position = "bottom",
-        strip.text.x = element_text(margin = margin(0.008,0,0.008,0, "mm"))) +
+        # strip.text.x = element_text(margin = margin(0.008,0,0.008,0, "mm"))) +
+        strip.text.x = element_blank()) + 
   scale_colour_ptol() +
@@
 ```
+
+## Accuracy 
+The results of these experiments show there is no meaningful correlation with how accurate participants were in the ACS and SHVS tasks.
+Even when breaking the data from the SVHS task into the 3 different trial types, there were still no meaningful correlations.
+
+```{r, echo = F}
+# clear above 
+rm(list = ls())
+
+# load in data 
+ls_acc_RT <- readRDS(file = "../Scripts/lineseg/scratch/processedRTandAccData.Rda")
+load("scratch/dat_ACS")
+
+# filter out participants that were removed 
+dat_ACS <- dat_ACS %>%
+  filter(SubNo >= 5)
+
+# average accuracy for each task
+acc_ACS <- dat_ACS %>% 
+  group_by(SubNo) %>% 
+  summarise(Accuracy = mean(Acc)) %>% 
+  ungroup() %>% 
+  mutate(Task = "ACS",
+         participant = SubNo) %>% 
+  select(-SubNo)
+acc_LS <- ls_acc_RT %>% 
+  group_by(observer, targSide) %>% 
+  summarise(Accuracy = mean(accuracy)) %>% 
+  ungroup() %>% 
+  mutate(Task = paste("SHVS_", targSide, sep = ""),
+         participant = observer) %>% 
+  select(-observer, -targSide)
+
+# plot accuracy across tasks 
+dat_all <- rbind(acc_ACS, acc_LS) %>% 
+  spread(key = Task,
+         value = Accuracy) %>% 
+  gather(SHVS_absent:SHVS_hard,
+         key = "s_type", 
+         value = "acc")
+plt_task <- dat_all %>% 
+  ggplot(aes(ACS, acc, colour = s_type)) + 
+  geom_point() + 
+  facet_wrap(~s_type)
+# plt_task
+
+# get some numbers 
+get_cors <- function(df_in, task){
+  # filter data 
+  ss <- df_in %>% 
+    filter(s_type == task)
+
+  # get cor 
+  ci95 <- cor.test(ss$ACS, ss$acc)
+
+  output <- tibble(comparison = paste("ACS", task, sep = " "),
+                   est = ci95$estimate,
+                   lower = ci95$conf.int[1],
+                   upper = ci95$conf.int[2])
+  return(output)
+}
+
+# get correlation data 
+dat_cor <- tibble()
+for(i in unique(dat_all$s_type)){
+  dat_cor <- rbind(dat_cor, get_cors(dat_all, i))
+}
+
+# plot 
+dat_cor %>% 
+  ggplot(aes(comparison, ymin = lower, ymax = upper)) +
+  geom_hline(yintercept = 0, linetype = "dashed") +
+  geom_linerange(size = 1) +
+  scale_y_continuous(limits = c(-1,1)) +
+  coord_flip() +
+  theme_bw()
+
+# session for LS
+acc_LS <- ls_acc_RT %>%
+  group_by(observer, session) %>%
+  summarise(Accuracy = mean(accuracy)) %>%
+  ungroup() %>%
+  mutate(Task = "LS",
+         participant = as.factor(observer)) %>%
+         # session = as.numeric(ifelse(session == "a", 1, 2))) %>%
+  select(-observer) %>%
+  spread(key = session, value = Accuracy)
+
+# cor plots
+plt_session_acc <- acc_LS %>%
+  ggplot(aes(a, b)) +
+  geom_point()
+```

### 2019-10-22 Manuscript/manuscript.tex

@@
 The display was presented on a 17-inch CRT monitor with a resolution of $1400 \times 1050$ ($n = 40$) or $1600 \times 1200$ ($n = 24$).
-Stimulus generation, presentation and data collection were controlled by MATLAB and the psychophysics and eyelink toolboxes  \cite{brainard1997,cornelissen2002} run on a Powermac.
+Stimulus generation, presentation and data collection were controlled by MATLAB and the psychophysics and eyelink toolboxes  \cite{brainard1997,cornelissen2002,kleiners2007} run on a Powermac.
 Participants sat $\approx 47$cm from the screen.

### 2019-10-24 Manuscript/manuscript.tex
nearly finished revisions.

--- 2019-10-22 Manuscript/manuscript.tex
@@
 Each of these tasks taps into unique aspects of visual search strategies, and performance on one has little bearing on the others.
+\textcolor{blue}{For example, recent work on the ACVS task suggests that that enumerating the color subsets plays an important role in achieving the optimal strategy \cite{hansen2019taking}.
+Clearly this step isn't required in the SHLS search, as the stimulus consists of grey lines.
+Instead, participants have to judge the variability in orientation across the scene.
+}
 
@@
 The original question needed to be refined: for whom is search optimal and for whom is it stochastic?
-Our approach in this experiment puts into practice several of the recommendations of Clarke et al.
+\textcolor{blue}{Our approach in this experiment puts into practice several of the recommendations of Clarke et al.
 \citeyear{clarke2019}, who suggest that a focus on accounting for variance, in addition to interpreting average patterns, will lead to important new insights.
@@
 Taking this further, it would be interesting to examine the extent to which the results of each of these search paradigms would scale to similar, but more familiar and realistic, contexts.
-The current findings add even further challenges for researchers, by suggesting we need to account not only for individual differences, but also for the interaction of a given individual with a particular search context.
+Leber \& Irons \citeyear{leber-irons2019} have summarised a range of methods and measures that can be used to study attention strategy, (e.g.
+saccadic choice, speed-accuracy tradeoff, meta-cognitive report, etc).} The current findings add even further challenges for researchers, by suggesting we need to account not only for individual differences, but also for the interaction of a given individual with a particular search context.
 

### 2019-10-24 Manuscript/manuscript.tex
nearly finished revisions

@@
 Blue bars represent test-retest scores for each task for reaction times (\textit{rt}), optimality (\textit{opt}) or run length (\textit{rl}).
-Yellow bars indicate how well the strategy measures predict reaction times, while the red bars show that performance in one task is not a good indication of performance in another, either for reaction times or strategy.}
+Yellow bars indicate how well the strategy measures predict reaction times, while the red bars show that performance in one task is not a good indication of performance in another, either for reaction times or strategy.
+\textcolor{blue}{The \textit{opt} measures reflect the extent to which participants adhered to an optimal strategy.}}
 \label{fig:all_the_cor}

### 2019-10-25 Manuscript/manuscript.tex
fixed a citation (I think)

@@
 Previous research has investigated the relationship between these behaviours \textcolor{blue}{and} psychometrics, but to date, these differences have not shown strong correlations with other attributes.
-\cite{irons-leber2016,irons-leber2018} found no evidence of a correlation between the proportion of optimal choices made by observers in the ACVS paradigm and measures of visual working memory; trait impulsivity; novelty seeking; need for cognition; and intolerance of uncertainty.
+Irons and Leber \citeyear{irons-leber2016,irons-leber2018} found no evidence of a correlation between the proportion of optimal choices made by observers in the ACVS paradigm and measures of visual working memory; trait impulsivity; novelty seeking; need for cognition; and intolerance of uncertainty.
 Similarly, the differences in foraging behaviour are not accounted for by working memory or inhibitory control \cite{johannesson2017}.

### 2019-10-25 Manuscript/manuscript.tex
moved accuracy edit to end of paragraph

@@
 The results show that the correlations between the strategy metrics in the three tasks (Figure \ref{fig:all_the_cor}) are weak.
-\textcolor{blue}{(Analysis of accuracy correlations is included in the supplementary materials.)} Perhaps even more surprisingly, there is also little evidence for meaningful correlations between reaction times in the different tasks.
+Perhaps even more surprisingly, there is also little evidence for meaningful correlations between reaction times in the different tasks.
 Even if we optimistically take all data together as suggesting a robust correlation in reaction times from one task to another, the mean correlation over the three tasks is only $r = 0.2$, implying that this correlation accounts for  $R^2 = 0.04 = 4\%$ an individual's performance.
+\textcolor{blue}{(Analysis of accuracy correlations is also weak, and is included in the supplementary materials.)}
 

### 2019-10-25 sup_mat/sup_mat.Rmd
Made some edits to figure
Fixed Legend label
Changed SHVS to SHLS to be consistent with the paper

@@
         strip.text.x = element_blank()) + 
-  scale_colour_ptol() + 
-  scale_fill_ptol() + 
+  scale_colour_ptol(name = "Optimal Choice") + 
+  scale_fill_ptol(name = "Optimal Choice") + 
   facet_wrap(~Optimal_Choice)
@@
 ## Accuracy 
-The results of these experiments show there is no meaningful correlation with how accurate participants were in the ACS and SHVS tasks.
-Even when breaking the data from the SVHS task into the 3 different trial types, there were still no meaningful correlations.
+The results of these experiments show there is no meaningful correlation with how accurate participants were in the ACS and SHLS tasks.
+Even when breaking the data from the SHLS task into the 3 different trial types, there were still no meaningful correlations.
 
@@
   ungroup() %>% 
-  mutate(Task = paste("SHVS_", targSide, sep = ""),
+  mutate(Task = paste("SHLS_", targSide, sep = ""),
          participant = observer) %>% 
@@
          value = Accuracy) %>% 
-  gather(SHVS_absent:SHVS_hard,
+  gather(SHLS_absent:SHLS_hard,
          key = "s_type", 

### 2019-10-29 Manuscript/manuscript.tex
fixed citation

@@
 Eye movement strategies have also been shown to be an important source of individual differences in visual search efficiency.
-\cite{nowakowska2017} designed a simple search paradigm to discriminate between optimal \cite{najemnik-geisler2008} and stochastic  \cite{clarke2016} search strategies.
+Nowakowska, Clarke & Hunt \citeyear{nowakowska2017} designed a simple search paradigm to discriminate between optimal \cite{najemnik-geisler2008} and stochastic  \cite{clarke2016} search strategies.
 Participants searched through arrays of line segments (Figure \ref{fig:exampleStimuli}) arranged such that those on one side of the display all had a very similar orientation (homogeneous), while those on the other side had higher variance (heterogeneous).

### 2019-10-29 Manuscript/manuscript.tex
fixed another citation

@@
 When the target is present on the homogeneous half, it can be easily be detected with peripheral vision, but when it is in the heterogeneous half, it is much harder to detect.
-This was verified in \cite{nowakowska2017}: for brief presentations viewed from the center, detection performance was close to chance for targets presented on the heterogeneous texture, and close to ceiling for targets presented on the homogeneous texture.
+This was verified in Nowakowska et al.
+\citeyear{nowakowska2017}: for brief presentations viewed from the center, detection performance was close to chance for targets presented on the heterogeneous texture, and close to ceiling for targets presented on the homogeneous texture.
 There were 160 trials in total and homo- and heterogeneous sides of the display were randomly varied from trial to trial.

### 2019-10-30 Manuscript/manuscript.tex
Revised version!

@@
 Eye movement strategies have also been shown to be an important source of individual differences in visual search efficiency.
-Nowakowska, Clarke & Hunt \citeyear{nowakowska2017} designed a simple search paradigm to discriminate between optimal \cite{najemnik-geisler2008} and stochastic  \cite{clarke2016} search strategies.
+Nowakowska, Clarke \& Hunt \citeyear{nowakowska2017} designed a simple search paradigm to discriminate between optimal \cite{najemnik-geisler2008} and stochastic  \cite{clarke2016} search strategies.
 Participants searched through arrays of line segments (Figure \ref{fig:exampleStimuli}) arranged such that those on one side of the display all had a very similar orientation (homogeneous), while those on the other side had higher variance (heterogeneous).
